### 2020-07-20 pre-analysis-plan/freire-skarbek-lynching.Rmd
first commit

---
title:  |
        | Pre-Analysis Plan:
        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil
author:
  - Danilo Freire[^freire]
  - David Skarbek[^skarbek]
date: \today
abstract: "Why do citizens resort to extrajudicial violence? While vigilantism has significantly decreased in advanced democracies, lynchings continue to be common practice in many developing nations. In this pre-analysis plan, we propose three survey experiments to investigate (i) who are the potential lynching victims, (ii) how citizens justify mob violence, and (iii) whether information provision can reduce support for vigilantism. First, we will run a conjoint experiment to assess which victim characteristics are associated with higher likelihood of lynching. Then we will show respondents a short news article about a real lynching episode and ask them whether they perceive the motivations of the lynch mob as legitimate. Lastly, we test whether providing information about legal punishment for lynching perpetrators, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence. We will run the experiments in Brazil, a country which has seen a sharp rise in vigilante attacks and currently experiences one lynching attempt per day. Our survey will be conducted online and include 1,000 participants."
abstractspacing: double
keywords: Brazil, crime, extralegal violence, lynching, vigilantism
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
if (!require("kableExtra")) {
    install.packages("kableExtra")
}
```

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, [`danilofreire@gmail.com`](mailto:danilofreire@gmail.com), <https://danilofreire.github.io>.

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, USA, [`david_skarbek@brown.edu`](mailto:david_skarbek@brown.edu), <http://davidskarbek.com>.

\newpage

# Motivation
\label{sec:motivation}

\doublespacing

Why do citizens resort to extralegal punishment?[^definitions] Although mob
violence has decreased in advanced democracies, vigilantism remains widespread
in the developing world. In particular, Latin America has been severely affected
by a recent increase in lynchings. Motivated by growing numbers of drug-related
crime and by police ineffectiveness, citizen violence has surged in the region
[@mallen2014vigilantes]. Brazil provides a telling example. From 2011 to 2015,
the country registered about 2,500 lynching episodes, and in 2015 alone 173
people were killed by angry mobs, an average of one execution every two days
[@barbara2015vigilantes; @zechmeister2014political]. According to José Martins,
who has studied lynchings in Brazil for more than 30 years, those figures are
not only the highest in the country's history, but also the highest in the world
[@pearson2018latam]. Victims are generally accused of petty theft, and many are
beaten to death for stealing mobile phones, cooking utensils, or pairs of
sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men, but
they also include female teenagers, elderly women, and even members of local
police forces [@oliveira2016mob].

[^definitions]: Here we consider extralegal violence, vigilantism, lynching,
and related terms as synonyms. We follow @moncada2017varieties [6] and define
vigilantism as "the collective use or threat of extralegal violence in
response to an alleged criminal act". While we focus here on vigilantism that
directly involves physical violence, we make no distinction between lethal and
non-lethal lynching episodes.

Recent research suggests that support for vigilantism in Latin America is
associated with exposure to violence [@garcia2019anger], untrustworthy law
enforcement [@zizumbo2017community], perceived insecurity [@ceobanu2011crime;
@godoy2004justice], and social inequality [@arias2010violent]. However, approval
for extrajudicial violence raises important questions about the relationship
between states and societies in the region. First, while vigilantism provides
social order to vulnerable populations, it also undermines the legitimacy of
state institutions [@schuberth2013challenging]. Lynching episodes reinforce the
idea that civilians should not wait for legal proceedings and that social
control is better exerted by the people themselves [@black1983crime]. Second,
victim characteristics greatly impact the likelihood and severity of lynchings.
In Brazil, a person is rarely lynched when they commit a crime against males,
and females that commit the same crimes as males also receive less
punishment.[^fapesp] Moreover, there is no significant social difference between
victims and perpetrators, nor black Brazilians are particularly targeted by
lynch mobs [@oliveira2016mob]. These dynamics pose a puzzle to existing
explanations for mob violence support and stand in sharp contrast with the
American experience [@smaangs2016doing; @tolnay1995festival; @wood2011lynching].

[^fapesp]: See
<https://revistapesquisa.fapesp.br/en/mob-injustice>. Access: June, 2020.

In this study, we endeavour to answer the following questions: 1) which victim
characteristics increase individual support for extralegal punishment?; 2) how
do individuals justify their approval for vigilantism?; and 3) can information
provision reduce support for mob violence? We design a set of three experiments
to tackle these issues. Our first experiment consists of a conjoint analysis
where we present respondents with different profiles of lynching victims and ask
them which individual they believe deserved the punishment. In our second
experiment, we test how ineffective policing, slow criminal justice systems,
and demand for hasher punishment for criminals affect individual propensity to
support mob violence. Finally, we assess whether citizens who support
extrajudicial killings change their opinions when informed about the legal
consequences of lynchings, constitutional human rights, or the risk of
_vendettas_ associated with mob violence.

# Experiment 01
\label{sub:exp01}

We start our analysis with a choice-based conjoint experimental design. Each
respondent will be shown ten pairs of lynching victims. Each profile will
consist of five attributes: 1) crime perpetrator; 2) race of the crime
perpetrator; 3) offense; 4) victim of the motivating crime; 5) lynching
perpetrators. The levels in each attribute are available in table
\ref{tab:categories} below. They will be randomised in the experiment. Each
respondent will read a short description of the survey experiment and we will
ask them to choose the profile in which lynching seems less justified. We phrase
the experiment in negative terms (who should _not_ be lynched) to protect
subjects from making the uncomfortable choice of actively selecting a lynching
victim.

\begin{table}[htpb]
\small
\begin{center}
\caption{\textbf{Attributes and Levels}}
\label{tab:categories}
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
\Xhline{2\arrayrulewidth}
\footnotesize
Crime perpetrator & Adult male; adult female; male teenager; female teenager; elderly man; elderly woman \\
\\
Race & Black; white; native Brazilian; Asian \\
\\
Offense & Picks the pocket; steals the car; molests; rapes; murders \\
\\
Crime victim & Adult male; adult female; male child; female child; male teenager; female teenager; elderly man; elderly woman\\
\\
Lynching perpetrators & Bystanders; acquaintances; the family of the victim;
police\\
\Xhline{2\arrayrulewidth}
\end{tabular}
\end{center}
\end{table}

\newpage

Respondents are also required to rate each profile on a scale from 1
to 7, where 1 indicates they definitely believe lynching was not justified
and 7 indicates they definitely believe lynching was justified. We take this
measure as a robustness check for our main experimental estimate.

Before each profile pair, respondents will read the following
message:

* Lynching is often used as social punishment in Brazil. We are interested in
  knowing more about how Brazilians see these episodes. In the next ten
  questions, please read the description of two possible lynching victims in
  Brazil and indicate in which case you believe the punishment is _less_
  justified.[^portuguese]

[^portuguese]: The text will be displayed in Portuguese. The translation is as
follows: Linchamento é por vezes usado como punição social no Brasil. Estamos
interessados em saber mais sobre como os brasileiros vêem estes episódios. Nas
próximas cinco questões, por favor, leia a descrição de duas possíveis vítimas
de linchamento no Brasil e indique em quais delas você acredita que a punição
é _menos_ justificada.

## Sample
\label{sub:sample}

We invite respondents from all regions of Brazil to participate in our
experiment. Qualtrics will recruit 1,000 adult Brazilian citizens to take part
in our survey experiment.

We will also include 15 questions on demographics that we believe may influence
the results. The questions are: 1) the respondent's age, 2) gender, 3) state of
birth, 4) state they currently live in, 5) ethnicity, 6) level of education, 7)
religion (if any), 8) monthly family income in minimum wages, 9) political
orientation (left to right), 10) support for death penalty, 11) whether they had
been victimised in the last year, 12) whether they believe crime has worsened,
13) whether they believe militias improve law and order, 14) trust in the
police, 15) trust in the judicial system.

## Estimation
\label{sub:estimation}

We will estimate our models with the `cregg` package [@leeper2018cregg] for the
R statistical language [@rstats2019]. We will report marginal means instead of
average marginal conditional effects (AMCE) of attitudes towards lynchings.
@leeper2018subgroup show that AMCEs can be misleading in subgroup analysis as
model results are sensitive to the choice of reference categories in
interactions. In contrast, marginal means provide a clear description of
quantities of interest, in our case preferences towards lynching, while allowing
for easy comparisons between groups of respondents. Their interpretation is also
straightforward: a 50% marginal means estimate represents that respondents are
indifferent when a given attribute appears vis-à-vis other attributes. When the
coefficient is lower than 50%, respondents dislike profiles with that attribute.
Conversely, when the point estimate is higher than 50%, respondents prefer
profiles containing a given attribute. We will cluster standard errors by
respondent.

## Hypotheses
\label{sec:hypotheses}

We expect that, on average, respondents will select profiles with the following
characteristics:

1) Crime perpetrator: male teenager
2) Race: blacks
3) Offense: murder
4) Victim: female child
5) Lynching perpetrators: the family of the victim

We also expect that punishment will be lower for females of any age, whites
and Asians, pick pocketers, and if the victim of the motivating crime is male.
Additionally, we expect that respondents see lynchings as less legitimate if
they are carried out by bystanders and the police forces. We have no prior
beliefs about the size of each coefficient.

## Heterogeneous Effects
\label{sub:het01}

We will also run subgroup comparisons in our sample. We hypothesise that
attitudes towards lynching vary according to age, gender, race, level of
education, political ideology, and previous victimisation. In particular, we
hypothesise that:

* Younger respondents believe that lynchings by the police are less justified.

* Female respondents believe that lynchings against females are less justified.

* Respondents of a particular race are less likely to choose individuals of
  the same race as lynching victims.

* More educated individuals show less support for lynchings against petty
  criminals.

* Political ideology has no effect on support for lynchings when the victim is
  female.

* Right-wingers show stronger support for lynchings against males than
  left-wingers.

* Respondents who were victimised in the last year are more likely to support
  lynchings by bystanders and the police.

# Experiment 02

In our second experiment, we will measure how respondents justify their
support for extralegal violence. We test the effect of three explanations for
lynching in Brazil: 1) police ineffectiveness; 2) slow criminal justice; 3)
demand for harsher punishment for criminals. Below, we discuss these hypotheses
in further detail.

Research shows that police ineffectiveness frequently appears as a strong
predictor for vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
result of the weakness of police institutions is that citizens decide to take
criminal matters "in their own hands", thus persecuting and punishing the
criminals by themselves. A recent statistic indicates that the police
solves only 10% of the homicides in Brazil, what lends evidence to the link
between weak law enforcement and lynchings [@pearson2018latam].

Another aspect that is often suggested in the literature is that vigilantism
rises where citizens have little faith in courts. Most commonly, this is due to
delays in the criminal justice administration, which makes criminals stay at
large for many years. In Brazil, the penal code allows the accused to appeal
each decision several times, so it can take decades before a criminal case is
closed [@sousa2005utilizaccao]. In this respect, citizens do not believe that,
even if the criminal is put to trial, he/she will be punished in a timely
matter. Note that although the police is part of the criminal justice system, we
separate the two institutions in our experiment. This is because respondents may
not associate the two, mainly when it comes to legal procedures against
lawbreakers.

Lastly, we evaluate whether respondents believe that the legal punishment
assigned to criminals is not proportional to the severity of the crimes. In
particular, we hope to gauge the demand for iron-fisted criminal justice in
Brazil. Although this treatment arm is related to the previous ones, it
questions not the efficiency of the institutions, but their legitimacy. We
believe that the demand for harsher laws is on the rise in Brazil, and this may
be a major reason why citizens justify their support for mob violence.
In fact, Brazilians are often vocal about their preference for repressive legal
punishment. After having his son murdered by a local thug, a bar owner told the
Wall Street Journal that "_even if he had been put behind bars for 100 years it
wouldn't have been enough to pay for all his crimes_" [@pearson2018latam]. We
hypothesise that this feeling is widespread in the population.

The experiment consists of three treatment conditions and one control group.
Respondents will read a short excerpt of a news article describing a real
lynching case, which will be slightly edited so that respondents have no prior
knowledge of the crime.[^jornal] The vignette for the control group includes no
information about the reasons behind the lynching. We will ask respondents
to show their level of support for mob violence using a 0-100 slider, where 0
means no support and 100 means full support. Respondents in each of the three
treatment arms will read the same piece, but with one additional sentence
explaining the motivation of the lynch mob. The vignettes are as follows:

[^jornal]: The original article is available at the following address:
<http://folhadeibitinga.com.br/materia/5543/suspeito-de-estuprar-menina-e-linchado-e-morto-em-jau>.
Access: June 2020.

* *Control group*: A young man between 20 and 25 years old was lynched and
  killed on the 1\textsuperscript{st} of June. He was accused of raping an
  11-year-old girl in São Paulo. He was clubbed to death by about 20 residents
  who heard the girl screaming after she was taken to an empty lot and forced
  to have sex with him at gunpoint.[^control-exp02]

[^control-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
forcada a ter relações sexuais com ele sob ameaça de morte.

* *Treatment 01 - Police ineffectiveness*: A young man between 20 and 25
  years old was lynched and killed on the 1\textsuperscript{st} of June. He was
  accused of raping an 11-year-old girl in São Paulo. He was clubbed to death
  by about 20 residents who heard the girl screaming after she was taken to an
  empty lot and forced to have sex with him at gunpoint. **One of the
  residents who took part in the lynching said they did so because "the police
  never patrols the area"**.[^treat01-exp02]

[^treat01-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
forçada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
envolvidos no linchamento disse que eles fizeram isso porque "a polícia nunca
patrulha o local".**

* *Treatment 02 - Criminal justice ineffectiveness*: A young man between 20
  and 25 years old was lynched and killed on the 1\textsuperscript{st} of June.
  He was accused of raping an 11-year-old girl in São Paulo. He was clubbed to
  death by about 20 residents who heard the girl screaming after she was taken
  to an empty lot and forced to have sex with him at gunpoint. **One of the
  residents who took part in the lynching said they did so because "the
  judicial system is too slow"**.[^treat02-exp02]

[^treat02-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
forçada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
envolvidos no linchamento disse que eles fizeram isso porque "a justiça é muito
lenta"**.

* *Treatment 03 - Demand for harsher legal punishment*: A young man between 20
  and 25 years old was lynched and killed on the 1\textsuperscript{st} of June.
  He was accused of raping an 11-year-old girl in São Paulo. He was clubbed to
  death by about 20 residents who heard the girl screaming after she was taken
  to an empty lot and forced to have sex with him at gunpoint. **One of the
  residents who took part in the lynching said they did so because "the
  judicial punishment is not harsh enough"**.[^treat03-exp02]

[^treat03-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
forcada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
envolvidos no linchamento disse que eles fizeram isso porque "a punição da
justiça não é dura o suficiente"**.

Before each vignette, respondents will read the following text:

* You will be shown a news article. Please read it carefully. After you read
  the article, we will ask one question about it.[^vig01-exp02]

[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por favor,
leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta sobre
ele.

After the vignette, respondents will be presented with this question:

* Would you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp02]

[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
discordar.

## Sample

We will randomise the treatment and control conditions to the entire respondent
pool. The randomisation procedure here is independent of that of the previous
experiment.

## Estimation

We will carry out our hypothesis tests with OLS. We will compare the average
score given by the control group with the average score attributed by
respondents in each treatment condition. We will use robust standard errors for
all the models.

## Hypotheses

On average, we expect that:

\vspace{.5cm}

\noindent _H1_: Respondents assigned to the _police ineffectiveness_ treatment
group will show stronger support for lynchings when compared to the control
group. We believe that the effect will be smaller than for the other two
treatment conditions.

\vspace{.3cm}

\noindent _H2_: Respondents assigned to the _criminal justice ineffectiveness_
treatment group will show stronger support for lynchings when compared to the
control group. We hypothesise that the effect for this group will be higher
than that of the first treatment condition but lower than that of the third
treatment group.

\vspace{.3cm}

\noindent _H3_: Respondents assigned to the _demand for harsher punishment_
treatment group will show the strongest support for lynchings.

## Heterogeneous Effects

We hypothesise that these respondents are more likely to agree that lynchings
are justified:

1) Older citizens
2) White
3) Low levels of education
4) Right-wingers
5) Had been previously victimised

# Experiment 03

Our last experiment aims to measure the effect of information provision on
attitudes about lynching. More specifically, we will test whether reminding
respondents about the legal and social consequences of mob violence reduces
the subjects' level of support for such practice.

The experiment has three treatment conditions plus a control group. In all of
them we will present respondents with a short statement affirming that some
Brazilians support vigilantism under certain conditions. The control group will
be asked to rate their agreement with the statement with a 0-100 slider where
100 indicates full agreement with the statement and 0 indicates no agreement.
Respondents will be asked to use 0 to 49 if they disagree, 50 if they neither
agree nor disagree, and 50-100 if they agree with the sentence.

Each of the three treatment groups will receive a different message about the
legal or social consequences of lynching in Brazil. In the first treatment
arm, we will inform subjects about how the Brazilian constitution and penal code
punishes civilian violence. The second treatment group will be notified about
the human rights guarantees enshrined in Brazil's legal framework. The last
group will read a vignette that mentions how lynchings can spark _vendettas_ and
initiate a cycle of violence in the community. Subjects in the control group
will receive no information about the consequences of lynchings. The text shown
to the control and treatment groups can be read below.

* *Control group*: In Brazil, some people believe that lynching may be
  justified under certain conditions. To what degree do you agree or disagree
  that lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^control-exp03]

[^control-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. O quanto você concorda ou
discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo
para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para
concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem
discorde.

* *Treatment 01 - Legal punishment for lynching perpetrators*: In Brazil,
  some people believe that lynching may be justified under certain conditions.
  **However, the Brazilian constitution and penal code strictly forbid
  lynching and those involved can be accused of torture or murder**. To what
  degree do you agree or disagree that lynching can be justified? Please use
  the slider below to indicate your preference. For disagreement, use 0 to 49;
  for agreement, use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^treat01-exp03]

[^treat01-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição e o código penal do Brasil proíbem estritamente os linchamentos e
os envolvidos podem ser acusados de tortura ou assassinato.** O quanto você
concorda ou discorda que linchamentos podem ser justificados? Por favor, use a
barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0
a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
nem discorde.

* *Treatment 02 - Human rights*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, the Brazilian
  constitution states that all individuals have the right of not being
  tortured, including criminals**. To what degree do you agree or disagree that
  lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^treat02-exp03]

[^treat02-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição do Brasil afirma que todos os indivíduos têm o direito de não
serem torturados, inclusive criminosos**. O quanto você concorda ou discorda que
linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar
sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use
de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.

* *Treatment 03 - Vendettas*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, lynchings can trigger
  a new cycle of violence as the family or friends of the victim may retaliate
  the community**. To what degree do you agree or disagree that lynching can be
  justified? Please use the slider below to indicate your preference. For
  disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you
  neither agree nor disagree.[^treat03-exp03]

[^treat03-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, linchamentos
podem iniciar um ciclo de violência pois a família ou amigos da vítima podem
retaliar a comunidade**. O quanto você concorda ou discorda que linchamentos
podem ser justificados? Por favor, use a barra abaixo para indicar sua
preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de
51 a 100. Por favor, use 50 caso você não concorde nem discorde.

## Sample

We will randomise the treatment and control conditions to all subjects included
in our sample. The treatment assignment here is independent of that of the
previous two experiments.

## Estimation

We are interested in the difference between the average score assigned by each
of the treatment groups minus the average score assigned by the control group.
We will estimate average treatment effects using OLS with dummy indicators for
the treatment groups.

## Hypotheses

In this experiment, we test the following hypotheses:

\vspace{.5cm}

\noindent _H1_: Providing information about the criminal consequences of
lynchings reduces individual support for vigilantism.

\vspace{.3cm}

\noindent _H2_: Reminding respondents that torture violates human rights does
not decrease their support for vigilantism.

\vspace{.3cm}

\noindent _H3_: Information about _vendettas_ decrease individual support for
vigilantism.

\vspace{.5cm}

These three hypotheses will allow us to test how respondents react to different
consequences of extralegal legal and, hopefully, also help policy-makers design
more effective campaigns against vigilantism in Brazil.

## Heterogeneous Effects

As with the previous two experiments, we will measure whether our treatments
have heterogeneous effects. The same demographic characteristics we describe
above -- age, gender, race, education level, political ideology, and previous
victimisation -- will also be used here.

\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

### 2020-08-08 pre-analysis-plan/freire-skarbek-lynching.Rmd
update pap, address comments egap and livia

@@
         | Pre-Analysis Plan:
-        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil
+        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil[^thanks]
 author:
@@
 date: \today
-abstract: "Why do citizens resort to extrajudicial violence?
-While vigilantism has significantly decreased in advanced democracies, lynchings continue to be common practice in many developing nations.
-In this pre-analysis plan, we propose three survey experiments to investigate (i) who are the potential lynching victims, (ii) how citizens justify mob violence, and (iii) whether information provision can reduce support for vigilantism.
-First, we will run a conjoint experiment to assess which victim characteristics are associated with higher likelihood of lynching.
-Then we will show respondents a short news article about a real lynching episode and ask them whether they perceive the motivations of the lynch mob as legitimate.
-Lastly, we test whether providing information about legal punishment for lynching perpetrators, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence.
+abstract: "Why do citizens support extrajudicial violence?
+While endorsement for vigilantism has significantly decreased in advanced democracies, lynchings remain tolerated throughout the developing world.
+In this pre-analysis plan, we propose three survey experiments to investigate (i) which criminal profiles citizens prefer for extralegal punishment, (ii) how individuals justify mob violence, and (iii) whether information provision reduces support for vigilantism.
+First, we run a conjoint experiment to identify criminal characteristics that are associated with higher likelihood of lynching.
+In our second experiment, we show respondents a short article about a real lynching episode and ask them whether they see the mob's motivations as legitimate.
+Lastly, we test whether providing information about the legal consequences of lynching, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence.
 We will run the experiments in Brazil, a country which has seen a sharp rise in vigilante attacks and currently experiences one lynching attempt per day.
-Our survey will be conducted online and include 1,000 participants."
+Our survey will be conducted online and include 2,000 participants."
 abstractspacing: double
@@
 
+[^thanks]: We thank Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
+
 [^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, [`danilofreire@gmail.com`](mailto:danilofreire@gmail.com), <https://danilofreire.github.io>.
@@
 
-Why do citizens resort to extralegal punishment?[^definitions] Although mob
+Why do citizens endorse extralegal punishment?[^definitions] Although mob
 violence has decreased in advanced democracies, vigilantism remains widespread
@@
 people were killed by angry mobs, an average of one execution every two days
-[@barbara2015vigilantes; @zechmeister2014political]. According to José Martins,
-who has studied lynchings in Brazil for more than 30 years, those figures are
-not only the highest in the country's history, but also the highest in the world
+[@zechmeister2014political]. According to José Martins, who has studied
+lynchings in Brazil for more than 30 years, those figures are not only the
+highest in the country's history, but also the highest in the world
 [@pearson2018latam]. Victims are generally accused of petty theft, and many are
 beaten to death for stealing mobile phones, cooking utensils, or pairs of
-sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men, but
-they also include female teenagers, elderly women, and even members of local
-police forces [@oliveira2016mob].
+sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men,
+but they also include female teenagers, elderly women, and even members of
+local police forces [@moura2017linchamentos; @oliveira2016mob].
 
@@
 for extrajudicial violence raises important questions about the relationship
-between states and societies in the region. First, while vigilantism provides
-social order to vulnerable populations, it also undermines the legitimacy of
-state institutions [@schuberth2013challenging]. Lynching episodes reinforce the
-idea that civilians should not wait for legal proceedings and that social
-control is better exerted by the people themselves [@black1983crime]. Second,
-victim characteristics greatly impact the likelihood and severity of lynchings.
-In Brazil, a person is rarely lynched when they commit a crime against males,
-and females that commit the same crimes as males also receive less
-punishment.[^fapesp] Moreover, there is no significant social difference between
-victims and perpetrators, nor black Brazilians are particularly targeted by
-lynch mobs [@oliveira2016mob]. These dynamics pose a puzzle to existing
-explanations for mob violence support and stand in sharp contrast with the
-American experience [@smaangs2016doing; @tolnay1995festival; @wood2011lynching].
+between states and societies in the region [@nivette2016institutional]. First,
+while vigilantism provides social order to vulnerable populations, it also
+undermines the legitimacy of state institutions [@schuberth2013challenging].
+Lynching episodes reinforce the idea that civilians should not wait for legal
+proceedings and that social control is better exerted by the people themselves
+[@black1983crime]. Second, victim characteristics greatly impact the likelihood
+and severity of lynchings. In Brazil, a person is rarely lynched when they
+commit a crime against males, and females that commit the same crimes as males
+also receive less punishment.[^fapesp] Moreover, there is no significant social
+difference between victims and perpetrators, nor black Brazilians are
+particularly targeted by lynch mobs [@oliveira2016mob]. These dynamics pose a
+puzzle to existing explanations for mob violence support and stand in sharp
+contrast with the American experience [@smaangs2016doing; @wood2011lynching].
 
@@
 to tackle these issues. Our first experiment consists of a conjoint analysis
-where we present respondents with different profiles of lynching victims and ask
-them which individual they believe deserved the punishment. In our second
-experiment, we test how ineffective policing, slow criminal justice systems,
-and demand for hasher punishment for criminals affect individual propensity to
-support mob violence. Finally, we assess whether citizens who support
-extrajudicial killings change their opinions when informed about the legal
-consequences of lynchings, constitutional human rights, or the risk of
-_vendettas_ associated with mob violence.
+in which we show respondents different profiles of lynching victims and ask them
+who they believe deserve the punishment. In our second experiment, we test how
+ineffective policing, slow criminal justice systems, and demand for hasher legal
+punishment affect individual propensity to support mob violence. Finally, we
+assess whether citizens become less supportive of vigilantism when they are
+informed about the legal consequences of lynchings, constitutional human rights,
+or the risk of _vendettas_ associated with mob violence. While in this
+pre-analysis plan we present the three experiments as described above,
+their order will be randomised in our survey to mitigate potential order bias.
 
@@
 
-We start our analysis with a choice-based conjoint experimental design. Each
-respondent will be shown ten pairs of lynching victims. Each profile will
-consist of five attributes: 1) crime perpetrator; 2) race of the crime
-perpetrator; 3) offense; 4) victim of the motivating crime; 5) lynching
-perpetrators. The levels in each attribute are available in table
-\ref{tab:categories} below. They will be randomised in the experiment. Each
-respondent will read a short description of the survey experiment and we will
-ask them to choose the profile in which lynching seems less justified. We phrase
-the experiment in negative terms (who should _not_ be lynched) to protect
-subjects from making the uncomfortable choice of actively selecting a lynching
-victim.
+We start our analysis with a choice-based conjoint experimental design. We will
+present five pairs of criminal profiles to respondents. Each profile consists
+of seven attributes: 1) gender of the crime perpetrator; 2) age of the crime
+perpetrator; 3) race of the crime perpetrator; 4) offense; 5) gender of the victim
+of the motivating crime; 6) age of the victim of the motivating crime; 7)
+lynching perpetrators. The attributes and levels are displayed in table
+\ref{tab:categories} below.
+
+\vspace{.3cm}
 
@@
 \Xhline{2\arrayrulewidth}
-\footnotesize
-Crime perpetrator & Adult male; adult female; male teenager; female teenager; elderly man; elderly woman \\
-\\
-Race & Black; white; native Brazilian; Asian \\
-\\
-Offense & Picks the pocket; steals the car; molests; rapes; murders \\
-\\
-Crime victim & Adult male; adult female; male child; female child; male teenager; female teenager; elderly man; elderly woman\\
-\\
-Lynching perpetrators & Bystanders; acquaintances; the family of the victim;
-police\\
+\small
+Gender of crime perpetrator & Male; female \\ [4pt]
+Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
+Race of crime perpetrator & Black; white; native Brazilian; Asian \\ [4pt]
+Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
+Gender of crime victim & Male; female\\ [4pt]
+Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
+Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
 \Xhline{2\arrayrulewidth}
@@
 
-Respondents are also required to rate each profile on a scale from 1
-to 7, where 1 indicates they definitely believe lynching was not justified
-and 7 indicates they definitely believe lynching was justified. We take this
-measure as a robustness check for our main experimental estimate.
+Respondents have to indicate which profile they prefer for extrajudicial
+punishment. They are are also required to rate each profile on a scale from 1 to
+7, where 1 indicates they definitely believe lynching was not justified and 7
+indicates they definitely believe lynching was justified. We take this measure
+as a robustness check for our main experimental estimate.
 
-Before each profile pair, respondents will read the following
-message:
+Respondents will read the following prompt before they start the experiment:
 
-* Lynching is often used as social punishment in Brazil. We are interested in
-  knowing more about how Brazilians see these episodes. In the next ten
-  questions, please read the description of two possible lynching victims in
-  Brazil and indicate in which case you believe the punishment is _less_
-  justified.[^portuguese]
+* Lynchings are often used as social punishment in Brazil. Lynchings are
+  cases in which three or more people physically attack or execute a suspected
+  criminal in public. We are interested in knowing more about how Brazilians see
+  these episodes. In the next five questions, please read the description of two
+  possible lynching victims in Brazil and indicate in which case you believe the
+  punishment is more justified. Even if you are not entirely sure, please select
+  one of the cases.[^portuguese]
 
-[^portuguese]: The text will be displayed in Portuguese. The translation is as
-follows: Linchamento é por vezes usado como punição social no Brasil. Estamos
-interessados em saber mais sobre como os brasileiros vêem estes episódios. Nas
-próximas cinco questões, por favor, leia a descrição de duas possíveis vítimas
-de linchamento no Brasil e indique em quais delas você acredita que a punição
-é _menos_ justificada.
+[^portuguese]: We will conduct the survey experiments in Portuguese. The
+translation for the first experiment is as follows: Linchamentos são às vezes
+usados como punição social no Brasil. Linchamentos são casos nos quais três ou
+mais pessoas agridem fisicamente ou executam em público um suspeito de um
+crime. Estamos interessados em saber mais sobre como os brasileiros vêem estes
+episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
+possíveis vítimas de linchamento no Brasil e indique em quais delas você
+acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
+por favor, escolha um dos casos.
 
@@
 We invite respondents from all regions of Brazil to participate in our
-experiment. Qualtrics will recruit 1,000 adult Brazilian citizens to take part
+experiment. Qualtrics will recruit 2,000 adult Brazilian citizens to take part
 in our survey experiment.
@@
 We will estimate our models with the `cregg` package [@leeper2018cregg] for the
-R statistical language [@rstats2019]. We will report marginal means instead of
-average marginal conditional effects (AMCE) of attitudes towards lynchings.
-@leeper2018subgroup show that AMCEs can be misleading in subgroup analysis as
-model results are sensitive to the choice of reference categories in
+R statistical language [@rstats2019]. We will report marginal means and 
+average marginal component effects (AMCEs) in our main analysis.
+However, @leeper2018subgroup show that AMCEs can be misleading in subgroup
+comparisons as model results are sensitive to the choice of reference categories in
 interactions. In contrast, marginal means provide a clear description of
 quantities of interest, in our case preferences towards lynching, while allowing
-for easy comparisons between groups of respondents. Their interpretation is also
-straightforward: a 50% marginal means estimate represents that respondents are
-indifferent when a given attribute appears vis-à-vis other attributes. When the
-coefficient is lower than 50%, respondents dislike profiles with that attribute.
-Conversely, when the point estimate is higher than 50%, respondents prefer
-profiles containing a given attribute. We will cluster standard errors by
+for easy comparisons between groups of respondents. So while we will include
+both AMCEs and marginal means estimators in our article, we will conduct our
+subgroup analysis using only the latter. We will cluster standard errors by
 respondent.
@@
 
-We expect that, on average, respondents will select profiles with the following
-characteristics:
+We expect that, on average, respondents are more likely to select profiles with
+the following attributes levels:
 
-1) Crime perpetrator: male teenager
-2) Race: blacks
-3) Offense: murder
-4) Victim: female child
-5) Lynching perpetrators: the family of the victim
+1) Gender of crime perpetrator: male 
+2) Age of crime perpetrator: teenager
+3) Race of crime perpetrator: blacks
+4) Offense: murder
+5) Gender of victim: female 
+6) Age of victim: child
+7) Lynching perpetrators: the family of the victim
 
-We also expect that punishment will be lower for females of any age, whites
-and Asians, pick pocketers, and if the victim of the motivating crime is male.
-Additionally, we expect that respondents see lynchings as less legitimate if
-they are carried out by bystanders and the police forces. We have no prior
-beliefs about the size of each coefficient.
+We also expect that support for extralegal punishment will be lower for females
+of any age, whites and Asians, pick pocketers, and if the victim of the
+motivating crime is male. Additionally, we expect that respondents see lynchings
+as less legitimate if they are carried out by bystanders, gangs, or the police
+forces. We have no prior beliefs about the size of each coefficient.
 
@@
 
-We will also run subgroup comparisons in our sample. We hypothesise that
-attitudes towards lynching vary according to age, gender, race, level of
+We also intend to run subgroup analysis in our sample. We believe that
+preferences towards lynching may vary according to age, gender, race, level of
 education, political ideology, and previous victimisation. In particular, we
@@
 * Respondents who were victimised in the last year are more likely to support
-  lynchings by bystanders and the police.
+  lynchings by neighbours and the police.
 
@@
 
-In our second experiment, we will measure how respondents justify their
-support for extralegal violence. We test the effect of three explanations for
-lynching in Brazil: 1) police ineffectiveness; 2) slow criminal justice; 3)
-demand for harsher punishment for criminals. Below, we discuss these hypotheses
-in further detail.
+In our second experiment, we analyse how respondents justify their preferences
+for extralegal violence. We assess the impact of three factors that have been
+cited as major drivers of vigilante justice in Brazil: 1) police
+ineffectiveness; 2) slow criminal justice; 3) demand for harsher punishment for
+criminals. Below, we discuss them in further detail.
 
@@
 
-Another aspect that is often suggested in the literature is that vigilantism
-rises where citizens have little faith in courts. Most commonly, this is due to
-delays in the criminal justice administration, which makes criminals stay at
-large for many years. In Brazil, the penal code allows the accused to appeal
-each decision several times, so it can take decades before a criminal case is
-closed [@sousa2005utilizaccao]. In this respect, citizens do not believe that,
-even if the criminal is put to trial, he/she will be punished in a timely
-matter. Note that although the police is part of the criminal justice system, we
-separate the two institutions in our experiment. This is because respondents may
-not associate the two, mainly when it comes to legal procedures against
-lawbreakers.
+Another determinant of support for vigilante justice that is suggested in the
+literature is the lack of trust in the justice system [@godoy2004justice]. This
+is often due to long criminal proceedings, which cause significant anxiety for
+the victims. In Brazil, the penal code allows the accused to appeal each
+decision several times, so it can take decades before a criminal case is closed
+[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
+the criminal is put to trial, he/she will be punished in a timely matter. Note
+that although the police is part of the criminal justice system, we separate the
+two institutions in our experiment.
 
-Lastly, we evaluate whether respondents believe that the legal punishment
-assigned to criminals is not proportional to the severity of the crimes. In
+Lastly, we evaluate whether respondents think that the legal punishment
+assigned to criminals is not proportional to the severity of their crimes. In
 particular, we hope to gauge the demand for iron-fisted criminal justice in
 Brazil. Although this treatment arm is related to the previous ones, it
-questions not the efficiency of the institutions, but their legitimacy. We
-believe that the demand for harsher laws is on the rise in Brazil, and this may
-be a major reason why citizens justify their support for mob violence.
-In fact, Brazilians are often vocal about their preference for repressive legal
-punishment. After having his son murdered by a local thug, a bar owner told the
-Wall Street Journal that "_even if he had been put behind bars for 100 years it
-wouldn't have been enough to pay for all his crimes_" [@pearson2018latam]. We
-hypothesise that this feeling is widespread in the population.
+addresses not the efficiency of the institutions, but their legitimacy
+[@nivette2016institutional]. We believe that the demand for harsher laws is on
+the rise in Brazil, and this may be a major reason why citizens justify their
+support for mob violence. In fact, Brazilians are often vocal about their
+preference for repressive legal punishment. In a recent article in
+_The Wall Street Journal_, a bar owner justified the lynching of the local thug
+who killed his son by saying that "_even if he had been put behind bars for 100
+years it wouldn't have been enough to pay for all his crimes_"
+[@pearson2018latam]. We hypothesise that many Brazilians also share this view.
 
 The experiment consists of three treatment conditions and one control group.
-Respondents will read a short excerpt of a news article describing a real
-lynching case, which will be slightly edited so that respondents have no prior
-knowledge of the crime.[^jornal] The vignette for the control group includes no
-information about the reasons behind the lynching. We will ask respondents
-to show their level of support for mob violence using a 0-100 slider, where 0
-means no support and 100 means full support. Respondents in each of the three
-treatment arms will read the same piece, but with one additional sentence
-explaining the motivation of the lynch mob. The vignettes are as follows:
+Respondents will read an excerpt of a news article describing a real
+lynching case. We have slightly edited the original text so that respondents
+have no prior knowledge of the crime.[^jornal] The vignette for the control
+group includes no information about the reasons behind the lynching. We will ask
+respondents to show their level of support for mob violence using a 0-100
+slider, where 0 means no support and 100 means full support. Respondents in each
+of the three treatment arms will read the same piece, but with one additional
+sentence explaining the motivations behind the lynching. The vignettes are as
+follows:
 
 [^jornal]: The original article is available at the following address:
-<http://folhadeibitinga.com.br/materia/5543/suspeito-de-estuprar-menina-e-linchado-e-morto-em-jau>.
-Access: June 2020.
+<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
+Access: August 2020.
 
-* *Control group*: A young man between 20 and 25 years old was lynched and
-  killed on the 1\textsuperscript{st} of June. He was accused of raping an
-  11-year-old girl in São Paulo. He was clubbed to death by about 20 residents
-  who heard the girl screaming after she was taken to an empty lot and forced
-  to have sex with him at gunpoint.[^control-exp02]
+* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
+  According to the neighbours, he tried to break into a house but was
+  immobilised and beaten by members of the community.[^control-exp02]
 
-[^control-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
-morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
-anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
-que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
-forcada a ter relações sexuais com ele sob ameaça de morte.
+[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade.
 
-* *Treatment 01 - Police ineffectiveness*: A young man between 20 and 25
-  years old was lynched and killed on the 1\textsuperscript{st} of June. He was
-  accused of raping an 11-year-old girl in São Paulo. He was clubbed to death
-  by about 20 residents who heard the girl screaming after she was taken to an
-  empty lot and forced to have sex with him at gunpoint. **One of the
-  residents who took part in the lynching said they did so because "the police
-  never patrols the area"**.[^treat01-exp02]
+* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
+  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
+  house but was immobilised and beaten by members of the community. **One of
+  the residents who took part in the lynching said they had beaten the suspect
+  because "the police never patrols the area"**.[^treat01-exp02]
 
-[^treat01-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
-morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
-anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
-que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
-forçada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
-envolvidos no linchamento disse que eles fizeram isso porque "a polícia nunca
-patrulha o local".**
+[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
+nunca patrulha o local".**
 
-* *Treatment 02 - Criminal justice ineffectiveness*: A young man between 20
-  and 25 years old was lynched and killed on the 1\textsuperscript{st} of June.
-  He was accused of raping an 11-year-old girl in São Paulo. He was clubbed to
-  death by about 20 residents who heard the girl screaming after she was taken
-  to an empty lot and forced to have sex with him at gunpoint. **One of the
-  residents who took part in the lynching said they did so because "the
-  judicial system is too slow"**.[^treat02-exp02]
+* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial system is too slow"**.[^treat02-exp02]
 
-[^treat02-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
-morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
-anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
-que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
-forçada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
-envolvidos no linchamento disse que eles fizeram isso porque "a justiça é muito
-lenta"**.
+[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
+é muito lenta"**.
 
-* *Treatment 03 - Demand for harsher legal punishment*: A young man between 20
-  and 25 years old was lynched and killed on the 1\textsuperscript{st} of June.
-  He was accused of raping an 11-year-old girl in São Paulo. He was clubbed to
-  death by about 20 residents who heard the girl screaming after she was taken
-  to an empty lot and forced to have sex with him at gunpoint. **One of the
-  residents who took part in the lynching said they did so because "the
-  judicial punishment is not harsh enough"**.[^treat03-exp02]
+* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community. **One
+  of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial punishment is not harsh
+  enough"**.[^treat03-exp02]
 
-[^treat03-exp02]: In Portuguese: Um jovem entre 20 e 25 anos foi linchado e
-morto no dia primeiro de junho. Ele foi acusado de estuprar uma menina de 11
-anos em São Paulo. Ele foi atacado e morto à pauladas por cerca de 20 moradores
-que ouviram a menina gritar após ela ter sido levada para um terreno baldio e
-forcada a ter relações sexuais com ele sob ameaça de morte. **Um dos moradores
-envolvidos no linchamento disse que eles fizeram isso porque "a punição da
-justiça não é dura o suficiente"**.
+[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
+da justiça não é dura o suficiente"**.
 
@@
 4) Right-wingers
-5) Had been previously victimised
+5) Individuals who had been previously victimised
 
@@
 attitudes about lynching. More specifically, we will test whether reminding
-respondents about the legal and social consequences of mob violence reduces
+respondents about the legal and social consequences of vigilante justice reduces
 the subjects' level of support for such practice.
 
-The experiment has three treatment conditions plus a control group. In all of
+The experiment has three treatment conditions and a control group. In all of
 them we will present respondents with a short statement affirming that some
@@
 
-\noindent _H1_: Providing information about the criminal consequences of
-lynchings reduces individual support for vigilantism.
+\noindent _H1_: Individuals who receive information about the criminal
+consequences of lynching show lower support for vigilantism that those in the
+control group.
 
@@
 
-\noindent _H2_: Reminding respondents that torture violates human rights does
-not decrease their support for vigilantism.
+\noindent _H2_: Reminding respondents that torture violates human rights has no
+impact on their support for vigilantism.
 
@@
 
-\noindent _H3_: Information about _vendettas_ decrease individual support for
-vigilantism.
+\noindent _H3_: Information about _vendettas_ triggered by lynchings makes
+individuals less likely to support vigilantism in comparison with respondents in
+the control group. The effect of that information is larger than the other
+two treatments.
 
@@
 
-These three hypotheses will allow us to test how respondents react to different
-consequences of extralegal legal and, hopefully, also help policy-makers design
-more effective campaigns against vigilantism in Brazil.
+These three hypotheses allow us to test how respondents react to different
+consequences of extralegal violence. Hopefully, the experiment may also help
+policy-makers design more effective campaigns against vigilantism in Brazil.
 

### 2020-08-11 pre-analysis-plan/freire-skarbek-lynching.Rmd
small edits in pre-analysis plan

@@
 
-[^thanks]: We thank Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
+[^thanks]: We thank Louise Araújo, Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
 
@@
 people were killed by angry mobs, an average of one execution every two days
-[@zechmeister2014political]. According to José Martins, who has studied
-lynchings in Brazil for more than 30 years, those figures are not only the
-highest in the country's history, but also the highest in the world
+[@barbara2015vigilantes; @oliveira2016mob]. According to José Martins, who has
+studied lynchings in Brazil for more than 30 years, those figures are not only
+the highest in the country's history, but also the highest in the world
 [@pearson2018latam]. Victims are generally accused of petty theft, and many are
@@
 also receive less punishment.[^fapesp] Moreover, there is no significant social
-difference between victims and perpetrators, nor black Brazilians are
+difference between victims and perpetrators, nor are black Brazilians 
 particularly targeted by lynch mobs [@oliveira2016mob]. These dynamics pose a
@@
 in which we show respondents different profiles of lynching victims and ask them
-who they believe deserve the punishment. In our second experiment, we test how
+who they believe deserve punishment. In our second experiment, we test how
 ineffective policing, slow criminal justice systems, and demand for hasher legal
@@
 Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
-Race of crime perpetrator & Black; white; native Brazilian; Asian \\ [4pt]
+Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
 Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
@@
 result of the weakness of police institutions is that citizens decide to take
-criminal matters "in their own hands", thus persecuting and punishing the
+criminal matters "into their own hands", thus persecuting and punishing the
 criminals by themselves. A recent statistic indicates that the police
-solves only 10% of the homicides in Brazil, what lends evidence to the link
+solve only 10% of the homicides in Brazil, what lends support to the link
 between weak law enforcement and lynchings [@pearson2018latam].
@@
 Another determinant of support for vigilante justice that is suggested in the
-literature is the lack of trust in the justice system [@godoy2004justice]. This
-is often due to long criminal proceedings, which cause significant anxiety for
-the victims. In Brazil, the penal code allows the accused to appeal each
-decision several times, so it can take decades before a criminal case is closed
-[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
-the criminal is put to trial, he/she will be punished in a timely matter. Note
-that although the police is part of the criminal justice system, we separate the
-two institutions in our experiment.
+literature is the lack of trust in the justice system [@godoy2004justice;
+@smith2019contradictions]. This is often due to long criminal proceedings,
+which cause significant anxiety for the victims. In Brazil, the penal code
+allows the accused to appeal each decision several times, so it can take
+decades before a criminal case is closed [@sousa2005utilizaccao]. In this
+respect, citizens do not believe that, even if the criminal is put to trial,
+he/she will be punished in a timely matter. Note that although the police is
+part of the criminal justice system, we separate the two institutions in our
+experiment.
 

### 2020-08-25 pre-analysis-plan/freire-skarbek-lynching.Rmd
acknowledgement order

@@
 
-[^thanks]: We thank Louise Araújo, Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
+[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
 

### 2020-09-24 pre-analysis-plan/freire-skarbek-lynching.Rmd
typo

@@
 
-[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
+[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto
+Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their valuable comments.
 

### 2020-10-30 pre-analysis-plan/freire-skarbek-lynching.Rmd
add residency category, small edits

@@
 [^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto
-Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their valuable comments.
+Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their
+valuable comments. This pre-analysis plan received IRB approval from Brown
+University in October 2020 (Protocol 2009002803).
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, [`danilofreire@gmail.com`](mailto:danilofreire@gmail.com), <https://danilofreire.github.io>.
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown
+University, 8 Fones Alley, Providence, RI 02912,
+[`danilofreire@gmail.com`](mailto:danilofreire@gmail.com),
+<https://danilofreire.github.io>.
 
-[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, USA, [`david_skarbek@brown.edu`](mailto:david_skarbek@brown.edu), <http://davidskarbek.com>.
+[^skarbek]: The Department of Political Science and the Political Theory
+Project, Brown University, 8 Fones Alley, Providence, RI 02912, USA,
+[`david_skarbek@brown.edu`](mailto:david_skarbek@brown.edu),
+<http://davidskarbek.com>.
 
@@
 violence has decreased in advanced democracies, vigilantism remains widespread
-in the developing world. In particular, Latin America has been severely affected
-by a recent increase in lynchings. Motivated by growing numbers of drug-related
-crime and by police ineffectiveness, citizen violence has surged in the region
-[@mallen2014vigilantes]. Brazil provides a telling example. From 2011 to 2015,
-the country registered about 2,500 lynching episodes, and in 2015 alone 173
-people were killed by angry mobs, an average of one execution every two days
-[@barbara2015vigilantes; @oliveira2016mob]. According to José Martins, who has
-studied lynchings in Brazil for more than 30 years, those figures are not only
-the highest in the country's history, but also the highest in the world
-[@pearson2018latam]. Victims are generally accused of petty theft, and many are
-beaten to death for stealing mobile phones, cooking utensils, or pairs of
-sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men,
+in the developing world. In particular, Latin America has been severely
+affected by a recent increase in lynchings. Motivated by growing numbers of
+drug-related crime and by police ineffectiveness, citizen violence has surged
+in the region [@mallen2014vigilantes]. Brazil provides a telling example. From
+2011 to 2015, the country registered about 2,500 lynching episodes, and in 2015
+alone 173 people were killed by angry mobs, an average of one execution every
+two days [@barbara2015vigilantes; @oliveira2016mob]. According to José Martins,
+who has studied lynchings in Brazil for more than 30 years, those figures are
+not only the highest in the country's history, but also the highest in the
+world [@pearson2018latam]. Victims are generally accused of petty theft, and
+many are beaten to death for stealing mobile phones, cooking utensils, or pairs
+of sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men,
 but they also include female teenagers, elderly women, and even members of
@@
 and related terms as synonyms. We follow @moncada2017varieties [6] and define
-vigilantism as "the collective use or threat of extralegal violence in
-response to an alleged criminal act". While we focus here on vigilantism that
-directly involves physical violence, we make no distinction between lethal and
+vigilantism as "the collective use or threat of extralegal violence in response
+to an alleged criminal act". While we focus here on vigilantism that directly
+involves physical violence, we make no distinction between lethal and
 non-lethal lynching episodes.
@@
 enforcement [@zizumbo2017community], perceived insecurity [@ceobanu2011crime;
-@godoy2004justice], and social inequality [@arias2010violent]. However, approval
-for extrajudicial violence raises important questions about the relationship
-between states and societies in the region [@nivette2016institutional]. First,
-while vigilantism provides social order to vulnerable populations, it also
-undermines the legitimacy of state institutions [@schuberth2013challenging].
-Lynching episodes reinforce the idea that civilians should not wait for legal
-proceedings and that social control is better exerted by the people themselves
-[@black1983crime]. Second, victim characteristics greatly impact the likelihood
-and severity of lynchings. In Brazil, a person is rarely lynched when they
-commit a crime against males, and females that commit the same crimes as males
-also receive less punishment.[^fapesp] Moreover, there is no significant social
-difference between victims and perpetrators, nor are black Brazilians 
-particularly targeted by lynch mobs [@oliveira2016mob]. These dynamics pose a
-puzzle to existing explanations for mob violence support and stand in sharp
-contrast with the American experience [@smaangs2016doing; @wood2011lynching].
+@godoy2004justice], and social inequality [@arias2010violent]. However,
+approval for extrajudicial violence raises important questions about the
+relationship between states and societies in the region
+[@nivette2016institutional]. First, while vigilantism provides social order to
+vulnerable populations, it also undermines the legitimacy of state institutions
+[@schuberth2013challenging]. Lynching episodes reinforce the idea that
+civilians should not wait for legal proceedings and that social control is
+better exerted by the people themselves [@black1983crime]. Second, victim
+characteristics greatly impact the likelihood and severity of lynchings. In
+Brazil, a person is rarely lynched when they commit a crime against males, and
+females that commit the same crimes as males also receive less
+punishment.[^fapesp] Moreover, there is no significant social difference
+between victims and perpetrators, nor are black Brazilians particularly
+targeted by lynch mobs [@oliveira2016mob]. These dynamics pose a puzzle to
+existing explanations for mob violence support and stand in sharp contrast with
+the American experience [@smaangs2016doing; @wood2011lynching].
 
-[^fapesp]: See
-<https://revistapesquisa.fapesp.br/en/mob-injustice>. Access: June, 2020.
+[^fapesp]: See <https://revistapesquisa.fapesp.br/en/mob-injustice>. Access:
+June, 2020.
 
@@
 provision reduce support for mob violence? We design a set of three experiments
-to tackle these issues. Our first experiment consists of a conjoint analysis
-in which we show respondents different profiles of lynching victims and ask them
+to tackle these issues. Our first experiment consists of a conjoint analysis in
+which we show respondents different profiles of lynching victims and ask them
 who they believe deserve punishment. In our second experiment, we test how
-ineffective policing, slow criminal justice systems, and demand for hasher legal
-punishment affect individual propensity to support mob violence. Finally, we
-assess whether citizens become less supportive of vigilantism when they are
-informed about the legal consequences of lynchings, constitutional human rights,
-or the risk of _vendettas_ associated with mob violence. While in this
-pre-analysis plan we present the three experiments as described above,
-their order will be randomised in our survey to mitigate potential order bias.
+ineffective policing, slow criminal justice systems, and demand for hasher
+legal punishment affect individual propensity to support mob violence. Finally,
+we assess whether citizens become less supportive of vigilantism when they are
+informed about the legal consequences of lynchings, constitutional human
+rights, or the risk of _vendettas_ associated with mob violence. While in this
+pre-analysis plan we present the three experiments as described above, we will
+randomised their order in our survey to mitigate potential order bias.
 
@@
 present five pairs of criminal profiles to respondents. Each profile consists
-of seven attributes: 1) gender of the crime perpetrator; 2) age of the crime
-perpetrator; 3) race of the crime perpetrator; 4) offense; 5) gender of the victim
-of the motivating crime; 6) age of the victim of the motivating crime; 7)
-lynching perpetrators. The attributes and levels are displayed in table
-\ref{tab:categories} below.
+of eight attributes: 1) gender of the crime perpetrator; 2) age of the crime
+perpetrator; 3) race of the crime perpetrator; 4) residency of crime
+perpetrator; 5) offense; 6) gender of the victim of the motivating crime; 7)
+age of the victim of the motivating crime; 8) lynching perpetrators. The
+attributes and levels are displayed in table \ref{tab:categories} below.
 
@@
 Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
+Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
 Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
@@
 Respondents have to indicate which profile they prefer for extrajudicial
-punishment. They are are also required to rate each profile on a scale from 1 to
-7, where 1 indicates they definitely believe lynching was not justified and 7
-indicates they definitely believe lynching was justified. We take this measure
-as a robustness check for our main experimental estimate.
+punishment. We will also include a qualitative textbox below each experiment
+for subjects to explain why they selected their case or whether they believe
+neither alternative is appropriate.
 
@@
 
-* Lynchings are often used as social punishment in Brazil. Lynchings are
-  cases in which three or more people physically attack or execute a suspected
-  criminal in public. We are interested in knowing more about how Brazilians see
-  these episodes. In the next five questions, please read the description of two
-  possible lynching victims in Brazil and indicate in which case you believe the
-  punishment is more justified. Even if you are not entirely sure, please select
-  one of the cases.[^portuguese]
+* Lynchings are often used as social punishment in Brazil. Lynchings are cases
+  in which three or more people physically attack or execute a suspected
+  criminal in public. We are interested in knowing more about how Brazilians
+  see these episodes. In the next five questions, please read the description
+  of two possible lynching victims in Brazil and indicate in which case you
+  believe the punishment is more justified. Even if you are not entirely sure,
+  please select one of the cases.[^portuguese]
 
@@
 religion (if any), 8) monthly family income in minimum wages, 9) political
-orientation (left to right), 10) support for death penalty, 11) whether they had
-been victimised in the last year, 12) whether they believe crime has worsened,
-13) whether they believe militias improve law and order, 14) trust in the
-police, 15) trust in the judicial system.
+orientation (left to right), 10) support for death penalty, 11) whether they
+had been victimised in the last year, 12) whether they believe crime has
+worsened, 13) whether they believe militias improve law and order, 14) trust in
+the police, 15) trust in the judicial system.
 
@@
 We will estimate our models with the `cregg` package [@leeper2018cregg] for the
-R statistical language [@rstats2019]. We will report marginal means and 
-average marginal component effects (AMCEs) in our main analysis.
-However, @leeper2018subgroup show that AMCEs can be misleading in subgroup
-comparisons as model results are sensitive to the choice of reference categories in
+R statistical language [@rstats2019]. We will report marginal means and average
+marginal component effects (AMCEs) in our main analysis. However,
+@leeper2018subgroup show that AMCEs can be misleading in subgroup comparisons
+as model results are sensitive to the choice of reference categories in
 interactions. In contrast, marginal means provide a clear description of
-quantities of interest, in our case preferences towards lynching, while allowing
-for easy comparisons between groups of respondents. So while we will include
-both AMCEs and marginal means estimators in our article, we will conduct our
-subgroup analysis using only the latter. We will cluster standard errors by
-respondent.
+quantities of interest, in our case preferences towards lynching, while
+allowing for easy comparisons between groups of respondents. So while we will
+include both AMCEs and marginal means estimators in our article, we will
+conduct our subgroup analysis using only the latter. We will cluster standard
+errors by respondent.
 
@@
 3) Race of crime perpetrator: blacks
-4) Offense: murder
-5) Gender of victim: female 
-6) Age of victim: child
-7) Lynching perpetrators: the family of the victim
+4) Residency of crime perpetrator: outsider
+5) Offense: murder
+6) Gender of victim: female 
+7) Age of victim: child
+8) Lynching perpetrators: the family of the victim
 
@@
 of any age, whites and Asians, pick pocketers, and if the victim of the
-motivating crime is male. Additionally, we expect that respondents see lynchings
-as less legitimate if they are carried out by bystanders, gangs, or the police
-forces. We have no prior beliefs about the size of each coefficient.
+motivating crime is male. Additionally, we expect that respondents see
+lynchings as less legitimate if they are carried out by bystanders, gangs, or
+the police forces. We have no prior beliefs about the size of each coefficient.
 
@@
 criminal matters "into their own hands", thus persecuting and punishing the
-criminals by themselves. A recent statistic indicates that the police
-solve only 10% of the homicides in Brazil, what lends support to the link
-between weak law enforcement and lynchings [@pearson2018latam].
+criminals by themselves. A recent statistic indicates that the police solve
+only 10% of the homicides in Brazil, what lends support to the link between
+weak law enforcement and lynchings [@pearson2018latam].
 
@@
 support for mob violence. In fact, Brazilians are often vocal about their
-preference for repressive legal punishment. In a recent article in
-_The Wall Street Journal_, a bar owner justified the lynching of the local thug
-who killed his son by saying that "_even if he had been put behind bars for 100
+preference for repressive legal punishment. In a recent article in _The Wall
+Street Journal_, a bar owner justified the lynching of the local thug who
+killed his son by saying that "_even if he had been put behind bars for 100
 years it wouldn't have been enough to pay for all his crimes_"
@@
 The experiment consists of three treatment conditions and one control group.
-Respondents will read an excerpt of a news article describing a real
-lynching case. We have slightly edited the original text so that respondents
-have no prior knowledge of the crime.[^jornal] The vignette for the control
-group includes no information about the reasons behind the lynching. We will ask
+Respondents will read an excerpt of a news article describing a real lynching
+case. We have slightly edited the original text so that respondents have no
+prior knowledge of the crime.[^jornal] The vignette for the control group
+includes no information about the reasons behind the lynching. We will ask
 respondents to show their level of support for mob violence using a 0-100
-slider, where 0 means no support and 100 means full support. Respondents in each
-of the three treatment arms will read the same piece, but with one additional
-sentence explaining the motivations behind the lynching. The vignettes are as
-follows:
+slider, where 0 means no support and 100 means full support. Respondents in
+each of the three treatment arms will read the same piece, but with one
+additional sentence explaining the motivations behind the lynching. The
+vignettes are as follows:
 
@@
   **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial system is too slow"**.[^treat02-exp02]
+  suspect because "the judicial system is too slow and the perpetrator is on
+  the street until the case is heard"**.[^treat02-exp02]
 
@@
 envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
-é muito lenta"**.
+é muito lenta e os criminosos ficam soltos até o julgamento"**.
 
@@
   Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community. **One
-  of the residents who took part in the lynching said they had beaten the
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
   suspect because "the judicial punishment is not harsh
@@
 * You will be shown a news article. Please read it carefully. After you read
-  the article, we will ask one question about it.[^vig01-exp02]
+  the article, we will ask you one question about it.[^vig01-exp02]
 
-[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por favor,
-leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta sobre
-ele.
+[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
+favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
+sobre ele.
 

### 2021-01-04 appendix/appendix.Rmd
add data and script

---
title: |
       | Supplementary Materials for "Casting the First Stone: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: yes
    template: template.latex
---

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, <davidskarbek@brown.edu>, <http://davidskarbek.com>.

```{r setup, echo=FALSE}
plotAMCE <-
    function (x, main = "", xlab = "Change in E[Y]",
              ci = 0.95, colors = NULL,
              xlim = NULL, breaks = NULL,
              labels = NULL, attribute.names = NULL,
              level.names = NULL, label.baseline = TRUE,
              text.size = 11,
              text.color = "black",
              point.size = 0.5, dodge.size = 0.9,
              plot.theme = NULL, plot.display = "all",
              facet.names = NULL,
              facet.levels = NULL,
              group.order = NULL, font.family = NULL,
              tblfy = F, ...) {
        amce_obj <- x
        ylim <- xlim
        pe <- NULL
        se <- NULL
        group <- NULL
        lower <- NULL
        upper <- NULL
        var <- NULL
        printvar <- NULL
        facet <- NULL
        raw_attributes <- names(amce_obj$estimates)
        raw_levels <- lapply(amce_obj$estimates, colnames)
        for (effect in names(raw_levels)) {
            effect_elements <- strsplit(effect, ":")[[1]]
            baseline_interactions <- c()
            for (elem in effect_elements) {
                base_coef <- paste(c(elem, amce_obj$baselines[[elem]]),
                                   collapse = "")
                baseline_interactions <- c(baseline_interactions,
                                           base_coef)
            }
            interaction_str <- paste(baseline_interactions, sep = "",
                                     collapse = ":")
            raw_levels[[effect]] <- c(interaction_str, raw_levels[[effect]])
        }
        if (ci < 1 & ci > 0) {
            zscr <- qnorm(1 - ((1 - ci)/2))
        }
        else {
            cat("Invalid confidence interval -- Defaulting to 95%")
            zscr <- qnorm(1 - ((1 - 0.95)/2))
        }
        if (!is.null(attribute.names)) {
            attribute.names <- unique(attribute.names)
            if (length(attribute.names) != length(raw_attributes)) {
                cat(paste("Error: The number of unique elements in attribute.names ",
                          length(attribute.names), " does not match the attributes in amce object for which estimates were obtained: ",
                          paste(raw_attributes, collapse = ", "), "\n",
                          sep = ""))
                cat("Defaulting attribute.names to attribute names in AMCE object\n")
                attribute.names <- NULL
            }
        }
        if (!is.null(level.names)) {
            names(level.names) <- clean.names(names(level.names))
            for (name in names(level.names)) {
                if (name %in% names(raw_levels)) {
                    if (length(level.names[[name]]) != length(raw_levels[[name]])) {
                        cat(paste("Error: level.names lengths do not match levels for attribute ",
                                  name, "\n", sep = ""))
                        cat(paste("Defaulting level.names for attribute ",
                                  name, " to level names in AMCE object", "\n",
                                  sep = ""))
                        level.names[[name]] <- NULL
                    }
                }
                else {
                    cat(paste("Error: level.names entry ", name,
                              " not in AMCE object. Removing level.names for attribute.",
                              "\n", sep = ""))
                    level.names[[name]] <- NULL
                }
            }
        }
        if (is.null(attribute.names)) {
            attribute.names <- c()
            for (attr in names(amce_obj$estimates)) {
                attr_split <- strsplit(attr, ":")[[1]]
                attr_lookup <- paste(unlist(sapply(attr_split, function(x) amce_obj$user.names[x])),
                                     collapse = ":")
                attribute.names <- c(attribute.names, attr_lookup)
            }
        }
        if (is.null(level.names))
            level.names <- list()
        if (any(!names(raw_levels) %in% names(level.names))) {
            for (attr in names(raw_levels)[!names(raw_levels) %in%
                                           names(level.names)]) {
                attr_split <- strsplit(raw_levels[[attr]], ":")
                level.names[[attr]] <- unlist(lapply(attr_split,
                                                     function(x) paste(sapply(x, function(y) amce_obj$user.levels[y]),
                                                                       collapse = ":")))
            }
        }
        plot.display.opts <- c("all", "unconditional", "interaction")
        if (!is.element(plot.display, plot.display.opts)) {
            stop(paste(c("Error-- plot.display must be once of: ",
                         paste(plot.display.opts, collapse = ", ")), collapse = " "))
        }
        if (!is.null(facet.names)) {
            facet.names <- clean.names(facet.names)
        }
        else if (!is.null(facet.levels)) {
            facet.names <- clean.names(names(facet.levels))
        }
        if (!is.null(facet.names)) {
            facet.names.check <- c()
            for (facet.name in facet.names) {
                if (grepl(":", facet.name))
                    stop("Error-- cannot facet by interaction in current version.")
                if (!facet.name %in% names(amce_obj$estimates) &
                    !facet.name %in% names(amce_obj$cond.estimates)) {
                    stop(paste(c("Error-- cannot find facet name",
                                 facet.name, "in AMCE object output."), collapse = " "))
                }
                else {
                    facet.names.check <- c(facet.names.check, facet.name)
                }
            }
            facet.names <- facet.names.check
        }
        if ((is.null(facet.names)) & (length(amce_obj$respondent.varying) >
                                      0) & (plot.display != "unconditional")) {
            facet.names <- amce_obj$respondent.varying
        }
        if (is.null(facet.names) & plot.display == "interaction") {
            warning("Warning: no facet name or respondent varying characteristic provided to calculate conditional estimates. Will display unconditional only")
            plot.display <- "unconditional"
        }
        if (plot.display == "unconditional" & !is.null(facet.names)) {
            warning("Warning-- plot display is set to unconditional, facet names will be ignored")
            facet.names <- NULL
            facet.levels <- NULL
        }
        if (!is.null(facet.levels)) {
            names(facet.levels) <- clean.names(names(facet.levels))
            for (facet.name in names(facet.levels)) {
                if (facet.name %in% names(amce_obj$baselines)) {
                    facet.levels[[facet.name]] <- clean.names(facet.levels[[facet.name]])
                    if (facet.name %in% names(amce_obj$estimates) &&
                        is.element(amce_obj$baselines[[facet.name]],
                                   facet.levels[[facet.name]])) {
                        stop(paste(c("Error: Facet level \"", as.character(amce_obj$baselines[[facet.name]]),
                                     "\" is the baseline level of a profile varying attribute. Please provide alternative facet level or use defaults."),
                                   collapse = ""))
                    }
                    if (is.null(names(facet.levels[[facet.name]]))) {
                        fac.levs <- sapply(facet.levels[[facet.name]],
                                           function(x) paste(facet.name, x, sep = ""))
                        names(facet.levels[[facet.name]]) <- sapply(fac.levs,
                                                                    USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
                    }
                }
                else if (is.null(names(facet.levels[[facet.name]]))) {
                    names(facet.levels[[facet.name]]) <- as.character(facet.levels[[facet.name]])
                }
            }
        }
        if (is.null(facet.levels))
            facet.levels <- list()
        if (any(!facet.names %in% names(facet.levels))) {
            for (facet.name in facet.names[!facet.names %in% names(facet.levels)]) {
                if (facet.name %in% names(amce_obj$baselines)) {
                    if (facet.name %in% names(amce_obj$estimates)) {
                        fac.levs <- colnames(amce_obj$estimates[[facet.name]])
                    }
                    else {
                        fac.levs <- colnames(amce_obj$cond.estimates[[facet.name]])
                    }
                    facet.levels[[facet.name]] <- sub(facet.name,
                                                      "", fac.levs)
                    facet.levels[[facet.name]] <- c(amce_obj$baselines[[facet.name]],
                                                    facet.levels[[facet.name]])
                    fac.levs <- c(paste(facet.name, amce_obj$baselines[[facet.name]],
                                        sep = ""), fac.levs)
                    names(facet.levels[[facet.name]]) <- sapply(fac.levs,
                                                                USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
                }
                else if (facet.name %in% names(amce_obj$continuous)) {
                    facet.levels[[facet.name]] <- amce_obj$continuous[[facet.name]]
                }
            }
        }
        covariate.values <- list()
        for (var in names(facet.levels)) {
            if (var %in% amce_obj$respondent.varying) {
                covariate.values[[var]] <- facet.levels[[var]]
            }
        }
        d <- data.frame(pe = c(), se = c(), upper = c(), lower = c(),
                        var = c(), printvar = c(), group = c(), facet = c())
        if (plot.display != "interaction") {
            if (plot.display == "all") {
                uncond.facet.name <- "Unconditional"
            }
            else {
                uncond.facet.name <- NA
            }
            if (plot.display == "all" && !is.null(facet.names)) {
                attr_remove <- c()
                for (facet.name in facet.names[!is.element(facet.names,
                                                           amce_obj$respondent.varying)]) {
                    attr_remove1 <- raw_attributes[grepl(":", raw_attributes)]
                    attr_remove1 <- attr_remove1[grepl(facet.name,
                                                       attr_remove1)]
                    attr_remove <- c(attr_remove, attr_remove1)
                }
                raw_attributes <- raw_attributes[!is.element(raw_attributes,
                                                             attr_remove)]
            }
            for (i in 1:length(raw_attributes)) {
                attr_name <- raw_attributes[i]
                print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
                                                             raw_attributes[i])]
                d_head <- data.frame(pe = NA, se = NA, upper = NA,
                                     lower = NA, var = attr_name, printvar = paste(print_attr_name,
                                                                                   ":", sep = ""), group = "<NA>", facet = uncond.facet.name)
                d <- rbind(d, d_head)
                for (j in 1:length(raw_levels[[attr_name]])) {
                    level_name <- raw_levels[[attr_name]][j]
                    print_level_name <- level.names[[attr_name]][j]
                    if (j == 1) {
                        if (label.baseline) {
                            print_level_name <- paste("(Baseline = ",
                                                      print_level_name, ")", sep = "")
                        }
                        d_lev <- data.frame(pe = NA, se = NA, upper = NA,
                                            lower = NA, var = level_name, printvar = paste("   ",
                                                                                           print_level_name, sep = ""), group = print_attr_name,
                                            facet = uncond.facet.name)
                    }
                    else {
                        val_pe <- amce_obj$estimates[[attr_name]][1,
                                                                  level_name]
                        val_se <- amce_obj$estimates[[attr_name]][2,
                                                                  level_name]
                        upper_bnd <- val_pe + zscr * val_se
                        lower_bnd <- val_pe - zscr * val_se
                        d_lev <- data.frame(pe = val_pe, se = val_se,
                                            upper = upper_bnd, lower = lower_bnd, var = level_name,
                                            printvar = paste("   ", print_level_name,
                                                             sep = ""), group = print_attr_name, facet = uncond.facet.name)
                    }
                    d <- rbind(d, d_lev)
                }
            }
        }
        if (plot.display != "unconditional" & !is.null(facet.names)) {
            for (facet.name in facet.names) {
                print_facet_name <- amce_obj$user.names[[facet.name]]
                all_req_vars <- attr(terms(amce_obj$formula), "term.labels")
                all_mod <- unlist(sapply(all_req_vars, function(x) {
                    y <- strsplit(x, ":")[[1]]
                    if (any(y == facet.name))
                        x
                }))
                all_mod <- unlist(sapply(all_mod, function(x) {
                    subs <- strsplit(x, ":")[[1]]
                    subs <- subs[is.element(subs, names(amce_obj$estimates))]
                    subs <- subs[subs != facet.name]
                    if (length(subs) > 0)
                        paste(subs, collapse = ":")
                }))
                if (length(all_mod) == 0) {
                    stop(paste(c("Error: Facet variable", facet.name,
                                 "not interacted with profile attributes"),
                               collapse = " "))
                }
                all_mod <- unique(all_mod)
                if (is.element(facet.name, names(amce_obj$estimates))) {
                    facet.start <- 2
                }
                else {
                    facet.start <- 1
                }
                for (k in facet.start:length(facet.levels[[facet.name]])) {
                    facet_lev <- facet.levels[[facet.name]][k]
                    if (is.element(facet.name, names(amce_obj$estimates))) {
                        print_facet_level <- paste(c("ACIE", paste(c(print_facet_name,
                                                                     names(facet.levels[[facet.name]])[k]), collapse = " = ")),
                                                   collapse = "\n")
                    }
                    else {
                        print_facet_level <- paste(c("Conditional on",
                                                     paste(c(print_facet_name, names(facet.levels[[facet.name]])[k]),
                                                           collapse = " = ")), collapse = "\n")
                    }
                    for (mod_var in all_mod) {
                        print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
                                                                     mod_var)]
                        d_head <- data.frame(pe = NA, se = NA, upper = NA,
                                             lower = NA, var = mod_var, printvar = paste(print_attr_name,
                                                                                         ":", sep = ""), group = "<NA>", facet = print_facet_level)
                        d <- rbind(d, d_head)
                        if (facet.name %in% names(amce_obj$estimates)) {
                            inter_coef <- paste(sort(c(mod_var, facet.name)),
                                                collapse = ":")
                            estimate.source <- amce_obj$estimates[[inter_coef]]
                            estimate.source <- estimate.source[, grep(paste0(facet.name,
                                                                             facet_lev), colnames(estimate.source))]
                        }
                        else {
                            estimate.source <- get.conditional.effects(amce_obj,
                                                                       covariate.values, facet.name, facet_lev,
                                                                       mod_var)
                        }
                        mod_vars <- strsplit(mod_var, ":")[[1]]
                        for (p in 1:length(raw_levels[[mod_var]])) {
                            mod_coef <- raw_levels[[mod_var]][p]
                            mod_coefs <- strsplit(mod_coef, ":")[[1]]
                            for (lev in 1:length(mod_coefs)) {
                                mod_lev <- sub(mod_vars[lev], "", mod_coefs[lev])
                            }
                            print_level_name <- level.names[[mod_var]][p]
                            if (p == 1) {
                                if (label.baseline) {
                                    print_level_name <- paste("(Baseline = ",
                                                              print_level_name, ")", sep = "")
                                }
                                d_lev <- data.frame(pe = NA, se = NA, upper = NA,
                                                    lower = NA, var = mod_coef, printvar = paste("   ",
                                                                                                 print_level_name, sep = ""), group = print_attr_name,
                                                    facet = print_facet_level)
                            }
                            else {
                                val_pe <- estimate.source[1, p - 1]
                                if (!is.na(val_pe)) {
                                    val_se <- estimate.source[2, p - 1]
                                    upper_bnd <- val_pe + zscr * val_se
                                    lower_bnd <- val_pe - zscr * val_se
                                }
                                else {
                                    val_se <- upper_bnd <- lower_bnd <- NA
                                }
                                d_lev <- data.frame(pe = val_pe, se = val_se,
                                                    upper = upper_bnd, lower = lower_bnd,
                                                    var = mod_coef, printvar = paste("   ",
                                                                                     print_level_name, sep = ""), group = print_attr_name,
                                                    facet = print_facet_level)
                            }
                            d <- rbind(d, d_lev)
                        }
                    }
                }
            }
        }
        else {
            d <- d[, -which(colnames(d) == "facet")]
        }
        if (is.null(ylim)) {
            max_upper <- max(d$upper, na.rm = T) + 0.05
            min_lower <- min(d$lower, na.rm = T) - 0.05
            ylim <- c(min_lower, max_upper)
            d[is.na(d)] <- max_upper + 100
        }
        else {
            d[is.na(d)] <- max(ylim) + 100
        }
        d$group[d$group == "<NA>"] <- NA
        if (!is.null(facet.names))
            d$facet[d$facet == "<NA>"] <- NA
        d$var <- factor(d$var, levels = unique(d$var)[length(d$var):1])
        if (!is.null(facet.names)) {
            d$facet <- factor(d$facet, levels = unique(d$facet))
        }
        if (!is.null(group.order)) {
            n.row <- length(unique(as.character(d$var)))
            order.var <- vector("character", length = n.row)
            i <- 1
            while (i < n.row) {
                for (j in group.order) {
                    order.var[i] <- unique(as.character(d$var[d$var ==
                                                                  gsub(" ", "", j)]))
                    i <- i + 1
                    temp.d <- d
                    temp.d$group <- gsub(" ", "", temp.d$group)
                    temp.d <- subset(temp.d, group == gsub(" ", "",
                                                           j))
                    temp.var <- unique((as.character(temp.d$var)))
                    order.var[i:(i + length(temp.var) - 1)] <- temp.var
                    i <- i + length(temp.var)
                }
            }
            order.var <- rev(order.var)
            order.df <- data.frame(order.var, 1:length(order.var))
            colnames(order.df) <- c("var", "order")
            d$var <- factor(d$var, levels = order.var)
            d <- merge(d, order.df, by.x = "var", by.y = "var", suffixes = c("",
                                                                             ""))
        }
        levs <- as.character(d$printvar)
        levs <- gsub('organizations', 'organisations', levs)
        d$printvar <- factor(levs, levels = levs)
        if(tblfy) {
            return(d)
        }
        p = ggplot(d, aes(y = pe, x = var, colour = group))
        p = p + coord_flip(ylim = ylim)
        p = p + geom_hline(yintercept = 0, size = 0.5, colour = "black",
                           linetype = "dotted")
        p = p + geom_pointrange(aes(ymin = lower, ymax = upper),
                                position = position_dodge(width = dodge.size), size = point.size)
        if (!is.null(facet.names)) {
            p = p + facet_wrap(~facet)
        }
        if (is.null(breaks) & is.null(labels)) {
            p = p + scale_y_continuous(name = xlab)
        }
        else if (is.null(breaks) & !is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, labels = labels)
        }
        else if (!is.null(breaks) & is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, breaks = breaks)
        }
        else if (!is.null(breaks) & !is.null(labels)) {
            p = p + scale_y_continuous(name = xlab, breaks = breaks,
                                       labels = labels)
        }
        if (!is.null(group.order)) {
            fix.xlabs.df <- d[!duplicated(d$var), ]
            fix.xlabs <- fix.xlabs.df[order(-fix.xlabs.df$order),
                                      ]$printvar
        }
        else {
            fix.xlabs <- as.character(d$printvar)[!duplicated(d$var)]
        }
        p = p + scale_x_discrete(name = "", labels = fix.xlabs[length(fix.xlabs):1])
        if (!is.null(main)) {
            if (main != "") {
                p = p + ggtitle(main)
            }
        }
        if (is.null(colors)) {
            p = p + scale_colour_discrete(" ")
        }
        else if (is.vector(colors)) {
            cPal <- rep(colors, ceiling(length(unique(d$group))/length(colors)))
            p = p + scale_colour_manual(values = cPal)
        }
        else {
            cat("Error: 'colors' must be a vector. Using default colors\n")
            p = p + scale_colour_discrete(" ")
        }
        if (is.null(plot.theme)) {
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else if (is.null(class(plot.theme))) {
            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else if (class(plot.theme)[1] != "theme") {
            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
            theme_bw1 <- function(base_size = text.size, base_family = "") {
                theme_grey(base_size = base_size, base_family = base_family) %+replace%
                    theme(axis.text.x = element_text(size = base_size *
                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
                          axis.text.y = element_text(size = base_size,
                                                     colour = text.color, hjust = 0, vjust = 0.5,
                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
                          axis.title.y = element_text(size = base_size,
                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
                          plot.title = element_text(face = "bold", family = font.family),
                          legend.position = "none")
            }
            p = p + theme_bw1()
            print(p)
        }
        else {
            p = p + plot.theme
            print(p)
        }
        if (length(covariate.values) > 1) {
            resp.message <- c("Note:")
            for (this.var in names(covariate.values)) {
                resp.message <- paste(c(resp.message, " For AMCE and ACIE conditional on ",
                                        this.var, ", "), collapse = "")
                other.vars <- names(covariate.values)[names(covariate.values) !=
                                                          this.var]
                other.levels <- c()
                for (var in other.vars) {
                    other.levels <- c(other.levels, paste(c(var,
                                                            " will be held at level \"", names(covariate.values[[var]])[1],
                                                            "\""), collapse = ""))
                }
                other.levels <- paste(other.levels, collapse = ", and ")
                resp.message <- c(resp.message, other.levels, ".")
                resp.message <- paste(resp.message, collapse = "")
            }
            cat(resp.message, "\n")
        }
    }
```

# Descriptive Statistics
\label{sec:descriptive}

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

From October 1 to December 5, 2018, we ran an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. The survey proceeded in two steps.

We collected information on Latin American elites. The target was:

1. Members of the Executive branch
2. Members of the Legislative branch
3. Civil society
4. Academics

For each profile, in each country, we aimed at surveying:

1. 10 members of the Executive branch
2. 10 members of the Legislative branch
3. 15 Civil society
4. 15 Academics

To do so, we built a prospective respondents dataset with ten times these members for each country. Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other climate
change-related problems.

After finishing this dataset, we started the surveying stage. From November 12 to December 5, we ran the survey by contacting elite members by phone or by email. We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers. Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.

# Descriptive Statistics \label{sec:descstats}

The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

# Country
tab <- data.frame(table(aux$countryOrigin))
names(tab) <- c('Country', 'Frequency')
p<- ggplot(data = tab, aes(x = Country, y = Frequency)) +
  geom_bar(stat = "identity") +
  geom_hline(yintercept = 50, linetype = "dashed", color = "black") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$Country, y = tab$Frequency + 2)
p

# Elite type
tab <- data.frame(table(aux$groupOrigin))
names(tab) <- c('Group Origin', 'Frequency')
p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
  geom_bar(stat = "identity") +
  theme_bw() + annotate(geom = "text", label = tab$Frequency,
                        x = tab$`Group Origin`, y = tab$Frequency + 5)
p
```

As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru. To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.

Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by those from the Executive and Legislative branches. The data collection for members of the Legislative branch was below the original target, but above the minimum mark of 5 for each country. This is expected, given the difficulty of accessing these elite members.

In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities. This is also in line with our expectations, as elite members are assumed to gravitate around capital cities and large urban centers.

# Frequency of Features Selected by Each Attribute \label{sec:features}

The figures below display the feature frequency for each attribute, by each task.

```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
aux <- cj %>%
  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
  unique()

# Who makes the rules
tab <- data.frame(table(aux$`Who makes the rules?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('Who makes the rules?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are conflicts resolved?
tab <- data.frame(table(aux$`How are conflicts resolved?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are conflicts resolved?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 35) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# What punishments do they use?
tab <- data.frame(table(aux$`What punishments do they use?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('What punishments do they use?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 40) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are repeated violations punished?
tab <- data.frame(table(aux$`How are repeated violations punished?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are repeated violations punished?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How are costs distributed?
tab <- data.frame(table(aux$`How are costs distributed?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How are costs distributed?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p

# How often will the agreement be renegotiated?
tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
names(tab) <- c('Levels', 'Frequency')
p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
  geom_bar(stat="identity") +
  theme_bw() + xlab('How often will the agreement be renegotiated?') +
  annotate(geom = "text", label = tab$Frequency,
           x = tab$Levels, y = tab$Frequency + 50) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p
```

The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*. This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.

# Code for the Main Paper

The code for Figure 2 of the paper follows below. We also include the point estimates in companion tables.

```{r codefig2}
## Main plot
# Main estimation equation
fm <- selected ~ `Who makes the rules?` +
  `How are conflicts resolved?` +
  `What punishments do they use?` +
  `How are repeated violations punished?` +
  `How are costs distributed?` +
  `How often will the agreement be renegotiated?`

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0 = 0.5)

myFaces <- c(rep('plain', 5), "bold",
             rep('plain', 4), "bold",
             rep('plain', 3), "bold",
             rep('plain', 4), "bold",
             rep('plain', 5), "bold",
             rep('plain', 5), "bold")

p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) + ggplot2::theme(
    legend.position = "none",
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    axis.text.y = element_text(face=myFaces, size = 11)) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 1, height = 0, na.rm = TRUE,
                            position = ggstance::position_dodgev(height = 1))
p

ggsave(filename = 'MM_all.pdf', plot = p, width = 8, height = 6)

# Table
table_mm <- function(mms, capt) {
  dfr <- data.frame(feature = mms[,c(4)],
             round(mms[,c(5,6,8,9,10)], digits=3))
  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
                'P-Value', 'Lower', 'Upper')
  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
    kable_styling(font_size = 10) %>%
    group_rows('Who makes the rules?', 1, 5) %>%
    group_rows('How are conflicts resolved?', 6, 10) %>%
    group_rows('What punishments do they use?', 11, 14) %>%
    group_rows('How are repeated violations punished?', 15, 17) %>%
    group_rows('How are costs distributed?', 18, 21) %>%
    group_rows('How often will the agreement be renegotiated?', 22, 26))
}

table_mm(mms, capt = 'Marginal Means -- Full Dataset')
```

The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.

\newpage

```{r codefig3}
## Marginal means by Country

# Argentina
arg <- mm(subset(cj, countryOrigin=='Argentina'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(arg, capt = 'Marginal Means -- Argentina Only')
```

\newpage

```{r}
# Bolivia
bol <- mm(subset(cj, countryOrigin=='Bolivia'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
```

\newpage

```{r}
# Brazil
bra <- mm(subset(cj, countryOrigin=='Brazil'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(bra, capt = 'Marginal Means -- Brazil Only')
```

\newpage

```{r}
# Chile
chi <- mm(subset(cj, countryOrigin=='Chile'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(chi, capt = 'Marginal Means -- Chile Only')
```

\newpage

```{r}
# Colombia
col <- mm(subset(cj, countryOrigin=='Colombia'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(col, capt = 'Marginal Means -- Colombia Only')
```

\newpage

```{r}
# Costa Rica
cri <- mm(subset(cj, countryOrigin=='Costa Rica'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
```

\newpage

```{r}
# Ecuador
ecu <- mm(subset(cj, countryOrigin=='Ecuador'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
```

\newpage

```{r}
# Mexico
mex <- mm(subset(cj, countryOrigin=='Mexico'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(mex, capt = 'Marginal Means -- Mexico Only')
```

\newpage

```{r}
# Panama
pan <- mm(subset(cj, countryOrigin=='Panama'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(pan, capt = 'Marginal Means -- Panama Only')
```

\newpage

```{r}
# Peru
per <- mm(subset(cj, countryOrigin=='Peru'),
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(per, capt = 'Marginal Means -- Peru Only')
```

\newpage

```{r, fig.width = 13, fig.height = 13}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot(rbind(arg, bol, bra, chi, col,
              cri, ecu, mex, pan, per),
        group = 'country', vline = 0.5, nr = 10,
        header_fmt = "%s", size = 2) +
  facet_wrap( ~ country, ncol = 5) +
  ggplot2::theme(
    axis.text.y = element_text(face=myFaces, size = 11)) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 1, height = 0, na.rm = TRUE,
                            position = ggstance::position_dodgev(height = 1))

p

ggsave(filename = 'MM_country.pdf',
       plot = p, width = 12, height = 12)
```

The code for Figure 4 of the paper is available below. Tables displaying the point estimates are also included.

```{r}
## Elite type graphs and estimates

# Table for the Executive branch
res1 <- mm(subset(cj, groupOrigin=='Executive'),
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res1, capt = 'Marginal Means -- Executive Only')
```

\newpage

```{r}
# Legislative branch
res2 <- mm(subset(cj, groupOrigin=='Legislative'),
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res2, capt = 'Marginal Means -- Legislative Only')
```

\newpage

```{r}
# Civil society
res3 <- mm(subset(cj, groupOrigin=='Civil Society'),
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
```

\newpage

```{r}
# Academia
res4 <- mm(subset(cj, groupOrigin=='Academia'),
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res4, capt = 'Marginal Means -- Academia Only')

```

\newpage

```{r, fig.width = 10, fig.height = 8}
# Changing labels
res1$MemberType <- 'Executive'
res2$MemberType <- 'Legislative'
res3$MemberType <- 'Civil Society'
res4$MemberType <- 'Academia'

# Plot by Elite Type
p <- plot(rbind(res1, res2, res3, res4),
     group = 'MemberType', vline = 0.5, nr = 4,
        header_fmt = "%s", size = 2) +
  facet_wrap( ~ MemberType, ncol = 4) +
  ggplot2::theme(
    axis.text.y = element_text(face=myFaces, size = 11)) +
    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
                                                xmax = "upper"),
                            size = 1, height = 0, na.rm = TRUE,
                            position = ggstance::position_dodgev(height = 1))
p

ggsave(filename = 'MM_membertype.pdf', plot = p,
       width = 8, height = 6)
```

# APSA Experimental Section Standard Report for Experiments 
\label{sec:apsa}

## Hypotheses

We designed three survey experiments to investigate (i) which criminal profiles
citizens prefer for extralegal punishment, (ii) how individuals justify mob
violence, and (iii) whether information provision reduces support for
vigilantism. First, we run a conjoint experiment to identify criminal
characteristics that are associated with higher likelihood of lynching. In our
second experiment, we show respondents a short article about a real lynching
episode and ask them whether they see the mob's motivations as legitimate.
Lastly, we test whether providing information about the legal consequences of
lynching, human rights guarantees, and the risk of retribution makes
respondents less likely to endorse extralegal violence.

## Subjects and Context

We selected Brazilian nationals over 18 years of age to participate in our
experiments. Our sample consisted of XXXX participants from all 5 Brazilian
regions (Center-West, North, Northeast, Southeast, and South).

We ran our online survey via Qualtrics. The firm recruited participants from
XXXX to XXXX December, 2020. From the XXXX responded contacted by Qualtrics,
XXXX declined to participate in our experiment (XX%), and XXX agreed to our
consent form (XX%).

## Allocation Methods

**Random Assignment:** We created the conjoint experiment using a Python application provided by @strezhnev2013conjoint. We translated the original survey questions (as shown in the text) into Portuguese, then embedded the PHP file with the randomization parameters in a Qualtrics survey. The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <https://github.com/danilofreire/lynching-experiment-brazil/tree/master/conjoint>.

For each attribute, the probability of selecting a given component follows a uniform distribution function. The table below describes the results.

\vspace{.5cm}

| **Attribute**                          | **Values**                                   | **Probabilities** |
|:---------------------------------------|:---------------------------------------------|------------------:|
| **Who makes the rules?**               | International organizations                  | 1/5               |
|                                        | Federal government                           | 1/5               |
|                                        | Local government                             | 1/5               |
|                                        | Local community members                      | 1/5               |
|                                        | Non-governmental organizations               | 1/5               |
|                                        |                                              |                   |
| **Conflict resolution mechanism**      | United Nations                               | 1/5               |
|                                        | Government bureaucracy                       | 1/5               |
|                                        | Local courts                                 | 1/5               |
|                                        | Private arbitration                          | 1/5               |
|                                        | Informal norms                               | 1/5               |
|                                        |                                              |                   |
| **Punishment**                         | Imprisonment                                 | 1/4               |
|                                        | Fines                                        | 1/4               |
|                                        | Blacklist                                    | 1/4               |
|                                        | None                                         | 1/4               |
|                                        |                                              |                   |
| **Punishment for repeated violations** | More penalty                                 | 1/3               |
|                                        | Same                                         | 1/3               |
|                                        | Less penalty                                 | 1/3               |
|                                        |                                              |                   |
| **Agreement costs**                    | Rich countries pay more than poor countries  | 1/4               |
|                                        | Proportional to history of emissions         | 1/4               |
|                                        | Proportional to current emissions            | 1/4               |
|                                        | Only rich countries pay                      | 1/4               |
|                                        |                                              |                   |
| **Renegotiation**                      | Never                                        | 1/5               |
|                                        | Fifty years                                  | 1/5               |
|                                        | Twenty years                                 | 1/5               |
|                                        | Five years                                   | 1/5               |
|                                        | One year                                     | 1/5               |
Table: Conjoint experiment attributes and their respective probabilities.

We added one logical restriction to the set climate change treaties: **Punishment = None** can never appear together with **Punishment for repeated violations = Less penalty**. The number of possible treaties are the product of the attributes ($5\times 5 \times 4 \times 3 \times 4 \times 5 = 6,000$) minus the number of removed possibilities ($5\times 5  \times 4 \times 5 = 500$). The total number of possible treaties is $5,500$.

## Treatments

**Descriptions of the intervention:** Our treatment was the randomization of components in the conjoined climate mitigation treaties. We provided the following description before the conjoint experiment starts, in Spanish and Portuguese:

\vspace{.5cm}

```
For the following questions, read carefully the instructions below.

Imagine that your country would sign an international treaty to mitigate climate change.
A climate mitigation treaty has, in general, the following attributes:

1. Who defines the rules? Which group will define the parameters for the treaty?
2. How are the conflicts that might happen when the treaty begin be resolved?
3. What punishments should be applied to ensure compliance?
4. How will repeated violations be punished?
5. How are costs for implementing the treaty be distributed?
6. How often the treaty has to be renegotiated?

In the following questions, you will see variations in treaties on these six attributes.
Please select the treaty that has the characteristics that you believe are best for your country.
```

\vspace{.5cm}

The conjoint experiment consisted in comparing two treaties that vary in these six attributes, repeating the application for seven times for each respondent.

\noindent \textbf{Software:} To program the PHP randomization device we used the Python application provided by @strezhnev2013conjoint. We used Qualtrics to administer the survey.

\noindent \textbf{Delivery:} We repeated the conjoint experiment seven times, to improve test power.

\noindent \textbf{Dataset description:} Each line in the dataset represents a given treaty, varying for the selection status (selected versus non-selected) for a given respondent. When a respondent finished an entire response set, this adds 14 rows to the dataset. Seven rows with the selected treaties and other seven rows with the non-selected treaties.

\noindent \textbf{Deception:} We used no deception in our experiments.

## Results

\noindent \textbf{Outcome measures and covariates:} The main outcome is a binary indicator for the selection of a given conjoined package. We added two covariates to measure heterogeneous effects: *Country* and *Elite type*.

\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.

\noindent \textbf{Statistical analysis:} We fit a marginal means estimator and an AMCE estimator. The estimation conditions the results within subjects and the presented conjoined packages. The results are available in sections \ref{sec:features} and \ref{sec:amce}.

\noindent \textbf{Missing data and attrition:} Conditional on having started the conjoint experiment, for each task we had the following completion rates:

```{r, fig.width = 7, fig.height = 8}
barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
```

## Other Information

* **IRB**: This research received IRB approval from Brown University (Protocol 2009002803/2020).

* **Pre-registration**: We submitted the study design to EGAP's registry on
  October 30th, 2020. A time-stamped copy of the pre-analysis plan is available
  at
  <https://github.com/danilofreire/lynching-experiment-brazil/tree/master/pre-analysis-plan>

* **Funding**: We received $10,000 from the Department of Political Economy at
  King's College London to conduct this research. The study sponsor did not
  play a role in the design or analysis of the study or in the decision to
  submit for publication.

* **Replication materials**: All scripts and data required to replicate the
  results of our study are available at
  <http://github.com/danilofreire/lynching-experiment-brazil>.

# Session Information
\label{sec:session-info}

```{r session, cache=TRUE}
sessionInfo()
```

# References

### 2021-01-04 pre-analysis-plan/freire-skarbek-lynching.Rmd
add data and script

@@
     number_sections: yes
-    keep_tex: no
+    keep_tex: yes
     toc: no

### 2021-01-04 appendix/lynchings.R

@@ -1,0 +1,1339 @@
+##############################################################
+## "Casting the First Stone: Lynching Attitudes in Brazil"  ##
+## Danilo Freire and David Skarbek                          ##
+## January 2021                                             ##
+##############################################################
+
+# Install and load required packages
+packages <- c("cjoint", "cregg", "kableExtra",
+              "janitor", "stargazer", "tidyverse")
+installed_packages <- packages %in% rownames(installed.packages())
+if (any(installed_packages == FALSE)) {
+  install.packages(packages[!installed_packages])
+}
+invisible(lapply(packages, library, character.only = TRUE))
+
+# Load the dataset, remove unused rows and columns,
+# and convert variable names to snake case
+df <- read_csv("../data/data.csv") %>%
+  clean_names() %>%
+  mutate(response_id            = as.character(response_id),
+         consent                = as.factor(q1),
+         progress               = as.numeric(progress),
+         finished               = as.factor(finished),
+         age                    = as.numeric(q2),
+         gender                 = as.factor(q3),
+         race                   = as.factor(q4),
+         education              = as.factor(q5),
+         region                 = as.factor(q6),
+         household_income       = as.factor(q7),
+         ideology               = as.factor(q8),
+         death_penalty          = as.factor(q9),
+         previous_victim        = as.character(q10),
+         previous_victim_text   = as.character(q10_text),
+         views_police           = as.factor(q11),
+         views_justice          = as.factor(q12),
+         exp02_control          = as.numeric(q18),
+         exp02_police           = as.numeric(q19),
+         exp02_slow_justice     = as.numeric(q20),
+         exp02_small_punishment = as.numeric(q21),
+         exp03_control          = as.numeric(q22),
+         exp03_constitution     = as.numeric(q23),
+         exp03_rights           = as.numeric(q24),
+         exp03_vendetta         = as.numeric(q25)) %>%
+  slice(-1L) %>%
+  select(-c(q1:q12, q18:q25)) %>%
+  relocate(response_id, consent, progress, finished,
+           location_latitude, location_longitude) %>%
+  mutate(across(where(is.character), tolower)) %>%
+  mutate(across(where(is.factor), tolower))
+
+# write_csv(df, "../data/data-portuguese.csv")
+
+# Translate factor values from Portuguese to English
+df <- df %>%
+  mutate(consent = recode(consent,
[…]

### 2021-01-05 appendix/lynchings.R
change conjoint plot colours

@@ -383,7 +383,7 @@ conjoint_data <- conjoint_data %>%
                                               "Police" = "Polícia",
                                               "Neighbors" = "Vizinhos")) %>%
   select(-c(16, 18, 20, 22, 24, 26, 28, 30)) %>%
-  drop_na()
+  mutate(response_id = tolower(response_id))
 
 fm <- selected ~ `Gender of crime perpetrator` +
   `Age of crime perpetrator` + `Race of crime perpetrator` +
@@ -400,12 +400,9 @@ faces <- c(rep("plain", 5), "bold", # from bottom to top!
 
 plot(mm(conjoint_data, fm, id = ~response_id),
      vline = 0.5, header_fmt = "%s") +
-  theme_classic() + 
   theme(legend.position = "none",
         axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-conjoint_data$response_id <- tolower(conjoint_data$response_id)
+  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
 
 # Gender
 cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
@@ -414,10 +411,9 @@ cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
 cjdt$Gender <- factor(cjdt$gender)
 mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", by = ~Gender)
 plot(mm_by, group = "Gender", vline = 0.5, header_fmt = "%s") +
-  theme_classic() +
   theme(legend.position = "bottom",
         axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
+  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
 
 # Education
 cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
@@ -431,10 +427,9 @@ cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
 cjdt$Education <- factor(cjdt$education2)
 mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", by = ~Education)
 plot(mm_by, group = "Education", vline = 0.5, header_fmt = "%s") +
-  theme_classic() +
   theme(legend.position = "bottom",
[…]

### 2021-01-07 appendix/lynchings.R
fix conjoint formula and colours

@@ -374,6 +374,7 @@ conjoint_data <- conjoint_data %>%
                                                " Female" = "Feminino"),
          `Age of crime victim` = fct_recode(`Age of crime victim`,
                                             " Teenager" = "Adolescente",
+                                            " Child"    = "Criança",
                                             " Adult"    = "Adulto(a)",
                                             " Elderly"  = "Idoso(a)"),
          `Lynching perpetrators` = fct_recode(`Lynching perpetrators`,
@@ -388,9 +389,11 @@ conjoint_data <- conjoint_data %>%
 fm <- selected ~ `Gender of crime perpetrator` +
   `Age of crime perpetrator` + `Race of crime perpetrator` +
   `Residency of crime perpetrator` + `Offense` +
-  `Gender of crime victim` + `Lynching perpetrators`
+  `Gender of crime victim` + `Age of crime victim` +
+  `Lynching perpetrators`
 
 faces <- c(rep("plain", 5), "bold", # from bottom to top!
+           rep("plain", 4), "bold",
            rep("plain", 2), "bold",
            rep("plain", 5), "bold",
            rep("plain", 2), "bold",
@@ -402,7 +405,9 @@ plot(mm(conjoint_data, fm, id = ~response_id),
      vline = 0.5, header_fmt = "%s") +
   theme(legend.position = "none",
         axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+mm(conjoint_data, fm, id = ~response_id)
 
 # Gender
 cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
@@ -413,7 +418,7 @@ mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", by = ~Gender)
 plot(mm_by, group = "Gender", vline = 0.5, header_fmt = "%s") +
   theme(legend.position = "bottom",
         axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
 
 # Education
[…]

### 2021-01-28 appendix/appendix.Rmd
add descriptive statistics to appendix

@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.
+[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.
 
@@
 
-```{r setup, echo=FALSE}
-plotAMCE <-
-    function (x, main = "", xlab = "Change in E[Y]",
-              ci = 0.95, colors = NULL,
-              xlim = NULL, breaks = NULL,
-              labels = NULL, attribute.names = NULL,
-              level.names = NULL, label.baseline = TRUE,
-              text.size = 11,
-              text.color = "black",
-              point.size = 0.5, dodge.size = 0.9,
-              plot.theme = NULL, plot.display = "all",
-              facet.names = NULL,
-              facet.levels = NULL,
-              group.order = NULL, font.family = NULL,
-              tblfy = F, ...) {
-        amce_obj <- x
-        ylim <- xlim
-        pe <- NULL
-        se <- NULL
-        group <- NULL
-        lower <- NULL
-        upper <- NULL
-        var <- NULL
-        printvar <- NULL
-        facet <- NULL
-        raw_attributes <- names(amce_obj$estimates)
-        raw_levels <- lapply(amce_obj$estimates, colnames)
-        for (effect in names(raw_levels)) {
-            effect_elements <- strsplit(effect, ":")[[1]]
-            baseline_interactions <- c()
-            for (elem in effect_elements) {
-                base_coef <- paste(c(elem, amce_obj$baselines[[elem]]),
-                                   collapse = "")
-                baseline_interactions <- c(baseline_interactions,
-                                           base_coef)
+\newpage
+
+# Introduction
+
+This appendix contains the `R` code required to replicate the results we
+present in "_Casting the First Stone: Understanding Attitudes towards Lynching
+in Brazil_". This file also includes the descriptive statistics of our sample,
+the average marginal component effects (AMCEs) for our conjoint experiment,
+additional subgroup analyses for all three experiments, and a standard report
+which follows APSA's guidelines for experimental research [@gerber2014reporting].
+
+The code below loads the required datasets and the `R` packages we use in our
+statistical analyses. It also translates the names of the factor variables from
+Portuguese into English.
+
+\footnotesize
+```{r loading, warning=F, error=F, cache=T}
+# Install and load required packages
+packages <- c("cjoint", "cregg", "kableExtra",
+              "janitor", "stargazer", "tidyverse")
+installed_packages <- packages %in% rownames(installed.packages())
+if (any(installed_packages == FALSE)) {
+  install.packages(packages[!installed_packages])
 }
-            interaction_str <- paste(baseline_interactions, sep = "",
-                                     collapse = ":")
-            raw_levels[[effect]] <- c(interaction_str, raw_levels[[effect]])
-        }
-        if (ci < 1 & ci > 0) {
-            zscr <- qnorm(1 - ((1 - ci)/2))
-        }
-        else {
-            cat("Invalid confidence interval -- Defaulting to 95%")
-            zscr <- qnorm(1 - ((1 - 0.95)/2))
-        }
-        if (!is.null(attribute.names)) {
-            attribute.names <- unique(attribute.names)
-            if (length(attribute.names) != length(raw_attributes)) {
-                cat(paste("Error: The number of unique elements in attribute.names ",
-                          length(attribute.names), " does not match the attributes in amce object for which estimates were obtained: ",
-                          paste(raw_attributes, collapse = ", "), "\n",
-                          sep = ""))
-                cat("Defaulting attribute.names to attribute names in AMCE object\n")
-                attribute.names <- NULL
-            }
-        }
-        if (!is.null(level.names)) {
-            names(level.names) <- clean.names(names(level.names))
-            for (name in names(level.names)) {
-                if (name %in% names(raw_levels)) {
-                    if (length(level.names[[name]]) != length(raw_levels[[name]])) {
-                        cat(paste("Error: level.names lengths do not match levels for attribute ",
-                                  name, "\n", sep = ""))
-                        cat(paste("Defaulting level.names for attribute ",
-                                  name, " to level names in AMCE object", "\n",
-                                  sep = ""))
-                        level.names[[name]] <- NULL
-                    }
-                }
-                else {
-                    cat(paste("Error: level.names entry ", name,
-                              " not in AMCE object. Removing level.names for attribute.",
-                              "\n", sep = ""))
-                    level.names[[name]] <- NULL
-                }
-            }
-        }
-        if (is.null(attribute.names)) {
-            attribute.names <- c()
-            for (attr in names(amce_obj$estimates)) {
-                attr_split <- strsplit(attr, ":")[[1]]
-                attr_lookup <- paste(unlist(sapply(attr_split, function(x) amce_obj$user.names[x])),
-                                     collapse = ":")
-                attribute.names <- c(attribute.names, attr_lookup)
-            }
-        }
-        if (is.null(level.names))
-            level.names <- list()
-        if (any(!names(raw_levels) %in% names(level.names))) {
-            for (attr in names(raw_levels)[!names(raw_levels) %in%
-                                           names(level.names)]) {
-                attr_split <- strsplit(raw_levels[[attr]], ":")
-                level.names[[attr]] <- unlist(lapply(attr_split,
-                                                     function(x) paste(sapply(x, function(y) amce_obj$user.levels[y]),
-                                                                       collapse = ":")))
-            }
-        }
-        plot.display.opts <- c("all", "unconditional", "interaction")
-        if (!is.element(plot.display, plot.display.opts)) {
-            stop(paste(c("Error-- plot.display must be once of: ",
-                         paste(plot.display.opts, collapse = ", ")), collapse = " "))
-        }
-        if (!is.null(facet.names)) {
-            facet.names <- clean.names(facet.names)
-        }
-        else if (!is.null(facet.levels)) {
-            facet.names <- clean.names(names(facet.levels))
-        }
-        if (!is.null(facet.names)) {
-            facet.names.check <- c()
-            for (facet.name in facet.names) {
-                if (grepl(":", facet.name))
-                    stop("Error-- cannot facet by interaction in current version.")
-                if (!facet.name %in% names(amce_obj$estimates) &
-                    !facet.name %in% names(amce_obj$cond.estimates)) {
-                    stop(paste(c("Error-- cannot find facet name",
-                                 facet.name, "in AMCE object output."), collapse = " "))
-                }
-                else {
-                    facet.names.check <- c(facet.names.check, facet.name)
-                }
-            }
-            facet.names <- facet.names.check
-        }
-        if ((is.null(facet.names)) & (length(amce_obj$respondent.varying) >
-                                      0) & (plot.display != "unconditional")) {
-            facet.names <- amce_obj$respondent.varying
-        }
-        if (is.null(facet.names) & plot.display == "interaction") {
-            warning("Warning: no facet name or respondent varying characteristic provided to calculate conditional estimates. Will display unconditional only")
-            plot.display <- "unconditional"
-        }
-        if (plot.display == "unconditional" & !is.null(facet.names)) {
-            warning("Warning-- plot display is set to unconditional, facet names will be ignored")
-            facet.names <- NULL
-            facet.levels <- NULL
-        }
-        if (!is.null(facet.levels)) {
-            names(facet.levels) <- clean.names(names(facet.levels))
-            for (facet.name in names(facet.levels)) {
-                if (facet.name %in% names(amce_obj$baselines)) {
-                    facet.levels[[facet.name]] <- clean.names(facet.levels[[facet.name]])
-                    if (facet.name %in% names(amce_obj$estimates) &&
-                        is.element(amce_obj$baselines[[facet.name]],
-                                   facet.levels[[facet.name]])) {
-                        stop(paste(c("Error: Facet level \"", as.character(amce_obj$baselines[[facet.name]]),
-                                     "\" is the baseline level of a profile varying attribute. Please provide alternative facet level or use defaults."),
-                                   collapse = ""))
-                    }
-                    if (is.null(names(facet.levels[[facet.name]]))) {
-                        fac.levs <- sapply(facet.levels[[facet.name]],
-                                           function(x) paste(facet.name, x, sep = ""))
-                        names(facet.levels[[facet.name]]) <- sapply(fac.levs,
-                                                                    USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
-                    }
-                }
-                else if (is.null(names(facet.levels[[facet.name]]))) {
-                    names(facet.levels[[facet.name]]) <- as.character(facet.levels[[facet.name]])
-                }
-            }
-        }
-        if (is.null(facet.levels))
-            facet.levels <- list()
-        if (any(!facet.names %in% names(facet.levels))) {
-            for (facet.name in facet.names[!facet.names %in% names(facet.levels)]) {
-                if (facet.name %in% names(amce_obj$baselines)) {
-                    if (facet.name %in% names(amce_obj$estimates)) {
-                        fac.levs <- colnames(amce_obj$estimates[[facet.name]])
-                    }
-                    else {
-                        fac.levs <- colnames(amce_obj$cond.estimates[[facet.name]])
-                    }
-                    facet.levels[[facet.name]] <- sub(facet.name,
-                                                      "", fac.levs)
-                    facet.levels[[facet.name]] <- c(amce_obj$baselines[[facet.name]],
-                                                    facet.levels[[facet.name]])
-                    fac.levs <- c(paste(facet.name, amce_obj$baselines[[facet.name]],
-                                        sep = ""), fac.levs)
-                    names(facet.levels[[facet.name]]) <- sapply(fac.levs,
-                                                                USE.NAMES = F, function(x) amce_obj$user.levels[[x]])
-                }
-                else if (facet.name %in% names(amce_obj$continuous)) {
-                    facet.levels[[facet.name]] <- amce_obj$continuous[[facet.name]]
-                }
-            }
-        }
-        covariate.values <- list()
-        for (var in names(facet.levels)) {
-            if (var %in% amce_obj$respondent.varying) {
-                covariate.values[[var]] <- facet.levels[[var]]
-            }
-        }
-        d <- data.frame(pe = c(), se = c(), upper = c(), lower = c(),
-                        var = c(), printvar = c(), group = c(), facet = c())
-        if (plot.display != "interaction") {
-            if (plot.display == "all") {
-                uncond.facet.name <- "Unconditional"
-            }
-            else {
-                uncond.facet.name <- NA
-            }
-            if (plot.display == "all" && !is.null(facet.names)) {
-                attr_remove <- c()
-                for (facet.name in facet.names[!is.element(facet.names,
-                                                           amce_obj$respondent.varying)]) {
-                    attr_remove1 <- raw_attributes[grepl(":", raw_attributes)]
-                    attr_remove1 <- attr_remove1[grepl(facet.name,
-                                                       attr_remove1)]
-                    attr_remove <- c(attr_remove, attr_remove1)
-                }
-                raw_attributes <- raw_attributes[!is.element(raw_attributes,
-                                                             attr_remove)]
-            }
-            for (i in 1:length(raw_attributes)) {
-                attr_name <- raw_attributes[i]
-                print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
-                                                             raw_attributes[i])]
-                d_head <- data.frame(pe = NA, se = NA, upper = NA,
-                                     lower = NA, var = attr_name, printvar = paste(print_attr_name,
-                                                                                   ":", sep = ""), group = "<NA>", facet = uncond.facet.name)
-                d <- rbind(d, d_head)
-                for (j in 1:length(raw_levels[[attr_name]])) {
-                    level_name <- raw_levels[[attr_name]][j]
-                    print_level_name <- level.names[[attr_name]][j]
-                    if (j == 1) {
-                        if (label.baseline) {
-                            print_level_name <- paste("(Baseline = ",
-                                                      print_level_name, ")", sep = "")
-                        }
-                        d_lev <- data.frame(pe = NA, se = NA, upper = NA,
-                                            lower = NA, var = level_name, printvar = paste("   ",
-                                                                                           print_level_name, sep = ""), group = print_attr_name,
-                                            facet = uncond.facet.name)
-                    }
-                    else {
-                        val_pe <- amce_obj$estimates[[attr_name]][1,
-                                                                  level_name]
-                        val_se <- amce_obj$estimates[[attr_name]][2,
-                                                                  level_name]
-                        upper_bnd <- val_pe + zscr * val_se
-                        lower_bnd <- val_pe - zscr * val_se
-                        d_lev <- data.frame(pe = val_pe, se = val_se,
-                                            upper = upper_bnd, lower = lower_bnd, var = level_name,
-                                            printvar = paste("   ", print_level_name,
-                                                             sep = ""), group = print_attr_name, facet = uncond.facet.name)
-                    }
-                    d <- rbind(d, d_lev)
-                }
-            }
-        }
-        if (plot.display != "unconditional" & !is.null(facet.names)) {
-            for (facet.name in facet.names) {
-                print_facet_name <- amce_obj$user.names[[facet.name]]
-                all_req_vars <- attr(terms(amce_obj$formula), "term.labels")
-                all_mod <- unlist(sapply(all_req_vars, function(x) {
-                    y <- strsplit(x, ":")[[1]]
-                    if (any(y == facet.name))
-                        x
-                }))
-                all_mod <- unlist(sapply(all_mod, function(x) {
-                    subs <- strsplit(x, ":")[[1]]
-                    subs <- subs[is.element(subs, names(amce_obj$estimates))]
-                    subs <- subs[subs != facet.name]
-                    if (length(subs) > 0)
-                        paste(subs, collapse = ":")
-                }))
-                if (length(all_mod) == 0) {
-                    stop(paste(c("Error: Facet variable", facet.name,
-                                 "not interacted with profile attributes"),
-                               collapse = " "))
-                }
-                all_mod <- unique(all_mod)
-                if (is.element(facet.name, names(amce_obj$estimates))) {
-                    facet.start <- 2
-                }
-                else {
-                    facet.start <- 1
-                }
-                for (k in facet.start:length(facet.levels[[facet.name]])) {
-                    facet_lev <- facet.levels[[facet.name]][k]
-                    if (is.element(facet.name, names(amce_obj$estimates))) {
-                        print_facet_level <- paste(c("ACIE", paste(c(print_facet_name,
-                                                                     names(facet.levels[[facet.name]])[k]), collapse = " = ")),
-                                                   collapse = "\n")
-                    }
-                    else {
-                        print_facet_level <- paste(c("Conditional on",
-                                                     paste(c(print_facet_name, names(facet.levels[[facet.name]])[k]),
-                                                           collapse = " = ")), collapse = "\n")
-                    }
-                    for (mod_var in all_mod) {
-                        print_attr_name <- attribute.names[which(names(amce_obj$estimates) ==
-                                                                     mod_var)]
-                        d_head <- data.frame(pe = NA, se = NA, upper = NA,
-                                             lower = NA, var = mod_var, printvar = paste(print_attr_name,
-                                                                                         ":", sep = ""), group = "<NA>", facet = print_facet_level)
-                        d <- rbind(d, d_head)
-                        if (facet.name %in% names(amce_obj$estimates)) {
-                            inter_coef <- paste(sort(c(mod_var, facet.name)),
-                                                collapse = ":")
-                            estimate.source <- amce_obj$estimates[[inter_coef]]
-                            estimate.source <- estimate.source[, grep(paste0(facet.name,
-                                                                             facet_lev), colnames(estimate.source))]
-                        }
-                        else {
-                            estimate.source <- get.conditional.effects(amce_obj,
-                                                                       covariate.values, facet.name, facet_lev,
-                                                                       mod_var)
-                        }
-                        mod_vars <- strsplit(mod_var, ":")[[1]]
-                        for (p in 1:length(raw_levels[[mod_var]])) {
-                            mod_coef <- raw_levels[[mod_var]][p]
-                            mod_coefs <- strsplit(mod_coef, ":")[[1]]
-                            for (lev in 1:length(mod_coefs)) {
-                                mod_lev <- sub(mod_vars[lev], "", mod_coefs[lev])
-                            }
-                            print_level_name <- level.names[[mod_var]][p]
-                            if (p == 1) {
-                                if (label.baseline) {
-                                    print_level_name <- paste("(Baseline = ",
-                                                              print_level_name, ")", sep = "")
-                                }
-                                d_lev <- data.frame(pe = NA, se = NA, upper = NA,
-                                                    lower = NA, var = mod_coef, printvar = paste("   ",
-                                                                                                 print_level_name, sep = ""), group = print_attr_name,
-                                                    facet = print_facet_level)
-                            }
-                            else {
-                                val_pe <- estimate.source[1, p - 1]
-                                if (!is.na(val_pe)) {
-                                    val_se <- estimate.source[2, p - 1]
-                                    upper_bnd <- val_pe + zscr * val_se
-                                    lower_bnd <- val_pe - zscr * val_se
-                                }
-                                else {
-                                    val_se <- upper_bnd <- lower_bnd <- NA
-                                }
-                                d_lev <- data.frame(pe = val_pe, se = val_se,
-                                                    upper = upper_bnd, lower = lower_bnd,
-                                                    var = mod_coef, printvar = paste("   ",
-                                                                                     print_level_name, sep = ""), group = print_attr_name,
-                                                    facet = print_facet_level)
-                            }
-                            d <- rbind(d, d_lev)
-                        }
-                    }
-                }
-            }
-        }
-        else {
-            d <- d[, -which(colnames(d) == "facet")]
-        }
-        if (is.null(ylim)) {
-            max_upper <- max(d$upper, na.rm = T) + 0.05
-            min_lower <- min(d$lower, na.rm = T) - 0.05
-            ylim <- c(min_lower, max_upper)
-            d[is.na(d)] <- max_upper + 100
-        }
-        else {
-            d[is.na(d)] <- max(ylim) + 100
-        }
-        d$group[d$group == "<NA>"] <- NA
-        if (!is.null(facet.names))
-            d$facet[d$facet == "<NA>"] <- NA
-        d$var <- factor(d$var, levels = unique(d$var)[length(d$var):1])
-        if (!is.null(facet.names)) {
-            d$facet <- factor(d$facet, levels = unique(d$facet))
-        }
-        if (!is.null(group.order)) {
-            n.row <- length(unique(as.character(d$var)))
-            order.var <- vector("character", length = n.row)
-            i <- 1
-            while (i < n.row) {
-                for (j in group.order) {
-                    order.var[i] <- unique(as.character(d$var[d$var ==
-                                                                  gsub(" ", "", j)]))
-                    i <- i + 1
-                    temp.d <- d
-                    temp.d$group <- gsub(" ", "", temp.d$group)
-                    temp.d <- subset(temp.d, group == gsub(" ", "",
-                                                           j))
-                    temp.var <- unique((as.character(temp.d$var)))
-                    order.var[i:(i + length(temp.var) - 1)] <- temp.var
-                    i <- i + length(temp.var)
-                }
-            }
-            order.var <- rev(order.var)
-            order.df <- data.frame(order.var, 1:length(order.var))
-            colnames(order.df) <- c("var", "order")
-            d$var <- factor(d$var, levels = order.var)
-            d <- merge(d, order.df, by.x = "var", by.y = "var", suffixes = c("",
-                                                                             ""))
-        }
-        levs <- as.character(d$printvar)
-        levs <- gsub('organizations', 'organisations', levs)
-        d$printvar <- factor(levs, levels = levs)
-        if(tblfy) {
-            return(d)
-        }
-        p = ggplot(d, aes(y = pe, x = var, colour = group))
-        p = p + coord_flip(ylim = ylim)
-        p = p + geom_hline(yintercept = 0, size = 0.5, colour = "black",
-                           linetype = "dotted")
-        p = p + geom_pointrange(aes(ymin = lower, ymax = upper),
-                                position = position_dodge(width = dodge.size), size = point.size)
-        if (!is.null(facet.names)) {
-            p = p + facet_wrap(~facet)
-        }
-        if (is.null(breaks) & is.null(labels)) {
-            p = p + scale_y_continuous(name = xlab)
-        }
-        else if (is.null(breaks) & !is.null(labels)) {
-            p = p + scale_y_continuous(name = xlab, labels = labels)
-        }
-        else if (!is.null(breaks) & is.null(labels)) {
-            p = p + scale_y_continuous(name = xlab, breaks = breaks)
-        }
-        else if (!is.null(breaks) & !is.null(labels)) {
-            p = p + scale_y_continuous(name = xlab, breaks = breaks,
-                                       labels = labels)
-        }
-        if (!is.null(group.order)) {
-            fix.xlabs.df <- d[!duplicated(d$var), ]
-            fix.xlabs <- fix.xlabs.df[order(-fix.xlabs.df$order),
-                                      ]$printvar
-        }
-        else {
-            fix.xlabs <- as.character(d$printvar)[!duplicated(d$var)]
-        }
-        p = p + scale_x_discrete(name = "", labels = fix.xlabs[length(fix.xlabs):1])
-        if (!is.null(main)) {
-            if (main != "") {
-                p = p + ggtitle(main)
-            }
-        }
-        if (is.null(colors)) {
-            p = p + scale_colour_discrete(" ")
-        }
-        else if (is.vector(colors)) {
-            cPal <- rep(colors, ceiling(length(unique(d$group))/length(colors)))
-            p = p + scale_colour_manual(values = cPal)
-        }
-        else {
-            cat("Error: 'colors' must be a vector. Using default colors\n")
-            p = p + scale_colour_discrete(" ")
-        }
-        if (is.null(plot.theme)) {
-            theme_bw1 <- function(base_size = text.size, base_family = "") {
-                theme_grey(base_size = base_size, base_family = base_family) %+replace%
-                    theme(axis.text.x = element_text(size = base_size *
-                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
-                          axis.text.y = element_text(size = base_size,
-                                                     colour = text.color, hjust = 0, vjust = 0.5,
-                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
-                          axis.title.y = element_text(size = base_size,
-                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
-                          plot.title = element_text(face = "bold", family = font.family),
-                          legend.position = "none")
-            }
-            p = p + theme_bw1()
-            print(p)
-        }
-        else if (is.null(class(plot.theme))) {
-            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
-            theme_bw1 <- function(base_size = text.size, base_family = "") {
-                theme_grey(base_size = base_size, base_family = base_family) %+replace%
-                    theme(axis.text.x = element_text(size = base_size *
-                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
-                          axis.text.y = element_text(size = base_size,
-                                                     colour = text.color, hjust = 0, vjust = 0.5,
-                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
-                          axis.title.y = element_text(size = base_size,
-                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
-                          plot.title = element_text(face = "bold", family = font.family),
-                          legend.position = "none")
-            }
-            p = p + theme_bw1()
-            print(p)
-        }
-        else if (class(plot.theme)[1] != "theme") {
-            cat("Error: 'plot.theme' is not a valid ggplot theme object. Using default theme\n")
-            theme_bw1 <- function(base_size = text.size, base_family = "") {
-                theme_grey(base_size = base_size, base_family = base_family) %+replace%
-                    theme(axis.text.x = element_text(size = base_size *
-                                                         0.9, colour = text.color, hjust = 0.5, vjust = 1),
-                          axis.text.y = element_text(size = base_size,
-                                                     colour = text.color, hjust = 0, vjust = 0.5,
-                                                     family = font.family), axis.ticks = element_line(colour = "grey50"),
-                          axis.title.y = element_text(size = base_size,
-                                                      angle = 90, vjust = 0.01, hjust = 0.1, family = font.family),
-                          plot.title = element_text(face = "bold", family = font.family),
-                          legend.position = "none")
-            }
-            p = p + theme_bw1()
-            print(p)
-        }
-        else {
-            p = p + plot.theme
-            print(p)
-        }
-        if (length(covariate.values) > 1) {
-            resp.message <- c("Note:")
-            for (this.var in names(covariate.values)) {
-                resp.message <- paste(c(resp.message, " For AMCE and ACIE conditional on ",
-                                        this.var, ", "), collapse = "")
-                other.vars <- names(covariate.values)[names(covariate.values) !=
-                                                          this.var]
-                other.levels <- c()
-                for (var in other.vars) {
-                    other.levels <- c(other.levels, paste(c(var,
-                                                            " will be held at level \"", names(covariate.values[[var]])[1],
-                                                            "\""), collapse = ""))
-                }
-                other.levels <- paste(other.levels, collapse = ", and ")
-                resp.message <- c(resp.message, other.levels, ".")
-                resp.message <- paste(resp.message, collapse = "")
-            }
-            cat(resp.message, "\n")
-        }
-    }
+invisible(lapply(packages, library, character.only = TRUE))
+
+# Load the dataset, remove unused rows and columns,
+# and convert variable names to snake case
+df <- read_csv("../data/data.csv") %>%
+  clean_names() %>%
+  mutate(response_id            = as.character(response_id),
+         consent                = as.factor(q1),
+         progress               = as.numeric(progress),
+         finished               = as.factor(finished),
+         age                    = as.numeric(q2),
+         gender                 = as.factor(q3),
+         race                   = as.factor(q4),
+         education              = as.factor(q5),
+         region                 = as.factor(q6),
+         household_income       = as.factor(q7),
+         ideology               = as.factor(q8),
+         death_penalty          = as.factor(q9),
+         previous_victim        = as.character(q10),
+         previous_victim_text   = as.character(q10_text),
+         views_police           = as.factor(q11),
+         views_justice          = as.factor(q12),
+         exp02_control          = as.numeric(q18),
+         exp02_police           = as.numeric(q19),
+         exp02_slow_justice     = as.numeric(q20),
+         exp02_small_punishment = as.numeric(q21),
+         exp03_control          = as.numeric(q22),
+         exp03_constitution     = as.numeric(q23),
+         exp03_rights           = as.numeric(q24),
+         exp03_vendetta         = as.numeric(q25)) %>%
+  slice(-1L) %>%
+  select(-c(q1:q12, q18:q25)) %>%
+  relocate(response_id, consent, progress, finished,
+           location_latitude, location_longitude) %>%
+  mutate(across(where(is.character), tolower)) %>%
+  mutate(across(where(is.factor), tolower))
+
+# Translate factor values from Portuguese to English
+df <- df %>%
+  mutate(consent = recode(consent,
+                          "concordo"     = "Agree",
+                          "não concordo" = "Disagree"),
+         gender = recode(gender,
+                         "feminino"              = "Female",
+                         "masculino"             = "Male",
+                         "outro"                 = "Other",
+                         "prefiro não responder" = "Rather Not Say"),
+         race = recode(race,
+                       "amarela"               = "Asian",
+                       "branca"                = "White",
+                       "indígena"              = "Indigenous",
+                       "outra"                 = "Other",
+                       "parda"                 = "Mixed Race",
+                       "prefiro não responder" = "Rather Not Say",
+                       "preta"                 = "Black"),
+         education = recode(education,
+                            "da 1ª à 4ª série do ensino fundamental (antigo primário)" = "Primary School",
+                            "da 5ª à 8ª série do ensino fundamental (antigo ginásio)"  = "Secondary School",
+                            "ensino médio (antigo 2º grau)"                            = "High School",
+                            "ensino superior"                                          = "College",
+                            "mestrado ou doutorado"                                    = "Graduate School",
+                            "não sei"                                                  = "Don't Know"),
+         region = recode(region,
+                         "centro-oeste" = "Center-West",
+                         "nordeste"     = "Northeast",
+                         "norte"        = "North",
+                         "sudeste"      = "Southeast",
+                         "sul"          = "South"),
+         household_income = recode(household_income,
+                                   "acima de r$ 20.000"       = "Above R$20,000",
+                                   "até r$ 1.000"             = "Up to R$1,000",
+                                   "de r$ 1.001 a r$ 2.000"   = "From R$1,001 to R$2,000",
+                                   "de r$ 10.000 a r$ 20.000" = "From R$10,001 to R$20,000",
+                                   "de r$ 2.001 a r$ 3.000"   = "From R$2,001 to R$3,000",
+                                   "de r$ 3.001 a r$ 5.000"   = "From R$3,001 to R$5,000",
+                                   "de r$ 5.001 a r$ 10.000"  = "From R$5,001 to R$10,000"),
+         ideology = recode(ideology,
+                           "centro"                = "Center",
+                           "centro-direita"        = "Center-Right",
+                           "centro-esquerda"       = "Center-Left",
+                           "direita"               = "Right",
+                           "esquerda"              = "Left",
+                           "não sei"               = "Don't Know",
+                           "prefiro não responder" = "Rather Not Say"),
+         death_penalty = recode(death_penalty,
+                                "não"                   = "No",
+                                "não sei"               = "Don't Know",
+                                "prefiro não responder" = "Rather Not Say",
+                                "sim"                   = "Yes"),
+         views_police = recode(views_police,
+                               "boa"                   = "Good",
+                               "muito boa"             = "Very Good",
+                               "muito ruim"            = "Very Bad",
+                               "não sei"               = "Don't Know",
+                               "prefiro não responder" = "Rather Not Say",
+                               "regular"               = "Regular",
+                               "ruim"                  = "Bad"),
+         views_justice = recode(views_justice,
+                                "boa"                   = "Good",
+                                "muito boa"             = "Very Good",
+                                "muito ruim"            = "Very Bad",
+                                "não sei"               = "Don't Know",
+                                "prefiro não responder" = "Rather Not Say",
+                                "regular"               = "Regular",
+                                "ruim"                  = "Bad"),
+         previous_victim_dummy = recode(previous_victim,
+                                        "nenhum" = "No",
+                                        .missing = NA_character_,
+                                        .default = "Yes")) %>%
+relocate(response_id:previous_victim, previous_victim_dummy,
+         previous_victim_text:f_5_2_8)
+
+# Check for duplicated values
+count(get_dupes(df))
+```
+\normalsize
+
+# Descriptive Statistics
+
+```{r samplesize, echo=F, warning=F, error=F, cache=T}
+df1 <- df %>% filter(consent == "Agree")
 ```
 
-# Descriptive Statistics
-\label{sec:descriptive}
+We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
+sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
+five regions of the country (Center-West, North, Northeast, South, and
+Southeast). We used quotas for gender and region to ensure that our sample was
+similar to the Brazilian population in those characteristics. We also collected
+information about whether the subjects had been victimized in the previous 12
+months, as well as their opinion the Brazilian judicial system and the police
+forces. They follow in the graphs and tables below.
 
-\setlength{\parindent}{1cm}
-\setlength{\parskip}{0pt}
+## Informed Consent
 
-From October 1 to December 5, 2018, we ran an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru.
-The survey proceeded in two steps.
+About 98% of the interviewees agreed to participate in the survey experiment.
+We therefore exclude the remaining cases from the dataset.
 
-We collected information on Latin American elites. The target was:
+\footnotesize
+```{r consent, warning=F, error=F, cache=T}
+df %>%
+  group_by(consent) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 2)) %>%
+  rename(Consent = consent) %>%
+  kbl(., booktabs = TRUE, caption = "Informed Consent") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
 
-1. Members of the Executive branch
-2. Members of the Legislative branch
-3. Civil society
-4. Academics
+# Remove subjects who did not agree with consent form
+df1 <- df %>% filter(consent == "Agree")
+```
+\normalsize
 
-For each profile, in each country, we aimed at surveying:
+## Gender
 
-1. 10 members of the Executive branch
-2. 10 members of the Legislative branch
-3. 15 Civil society
-4. 15 Academics
+The gender distribution of our sample is described below. It closely matches
+the official data from the [Brazilian Census
+Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18320-quantidade-de-homens-e-mulheres.html),
+which states that women are 51.8% of the population and men comprise 48.2%.
 
-To do so, we built a prospective respondents dataset with ten times these members for each country.
-Then, we ran an online and telephone survey where we collected information regarding the climate change agreements and other climate
-change-related problems.
+\footnotesize
+```{r gender, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(gender) %>%
+  filter(!is.na(gender)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Gender = gender) %>%
+  kbl(., booktabs = TRUE, caption = "Gender") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
 
-After finishing this dataset, we started the surveying stage.
-From November 12 to December 5, we ran the survey by contacting elite members by phone or by email.
-We had two teams of enumerators, one based in São Paulo and another based in Rio de Janeiro, Brazil, comprised of Portuguese and Spanish native speakers.
-Although the overall aim of the survey was 500 responses, the teams managed to collect 654 interviews.
+## Age
 
-# Descriptive Statistics \label{sec:descstats}
+The age distribution of our sample is shown below. The median age of the survey
+respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which
+indicates that our sample is older than the Brazilian population (median age $=
+33.4$ years old) [@ciafactbook2020].
 
-The main demographic statistics collected were the country and elite types, and the geolocation of the respondents. They follow in the graphs below.
+\footnotesize
+```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3}
+tibble(` `    = "Age",
+       Median = round(median(df1$age, na.rm = TRUE), 2),
+       Mean   = round(mean(df1$age, na.rm = TRUE), 2),
+       SD     = round(sd(df1$age, na.rm = TRUE), 2),
+       Min    = min(df1$age, na.rm = TRUE),
+       Max    = max(df1$age, na.rm = TRUE),
+       `NA`   = sum(is.na(df1$age))) %>%
+kbl(., booktabs = TRUE, caption = "Age") %>%
+row_spec(0, bold = TRUE) %>%
+kable_styling(latex_options = "hold_position")
 
-```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
-library(plm); library(tidyverse)
-library(haven); library(clusterSEs)
-library(stargazer); library(cjoint)
-library(sp); library(cregg)
-library(kableExtra)
-load('freire-mignozzetti-skarbek.RData')
+ggplot(subset(df1, !is.na(age)), aes(age)) +
+  geom_bar(fill = "#152238") +
+  labs(title = "Age Distribution", x = "Age", y = "Count") +
+  geom_vline(aes(xintercept = mean(age, na.rm = TRUE)),
+            color = "darkred", linetype = 5, size = 0.5) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5))
+```
+\normalsize
 
-aux <- cj %>%
-  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
-  unique()
+## Race
 
-# Country
-tab <- data.frame(table(aux$countryOrigin))
-names(tab) <- c('Country', 'Frequency')
-p<- ggplot(data = tab, aes(x = Country, y = Frequency)) +
-  geom_bar(stat = "identity") +
-  geom_hline(yintercept = 50, linetype = "dashed", color = "black") +
-  theme_bw() + annotate(geom = "text", label = tab$Frequency,
-                        x = tab$Country, y = tab$Frequency + 2)
-p
+The next demographic variable we show here is race. According to the [Brazilian
+Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html), 42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4% as Blacks, and 1,1% as Asians or Indigenous.
+As we see below, our sample includes more Whites and fewer individuals who identify as Mixed Race.
+The number of Blacks roughly coincide with the population statistics.
 
-# Elite type
-tab <- data.frame(table(aux$groupOrigin))
-names(tab) <- c('Group Origin', 'Frequency')
-p<- ggplot(data = tab, aes(x = `Group Origin`, y = Frequency)) +
-  geom_bar(stat = "identity") +
-  theme_bw() + annotate(geom = "text", label = tab$Frequency,
-                        x = tab$`Group Origin`, y = tab$Frequency + 5)
-p
+\footnotesize
+```{r race, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(race) %>%
+  filter(!is.na(race)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Race = race) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Race") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+## Education
+
+```{r educationtext, echo=F, warning=F, error=F, cache=T}
+df2 <- df1 %>%
+  group_by(education) %>%
+  filter(!is.na(education)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Education = education)
 ```
 
-As we can see, we managed to contact more than fifty elite members for all countries but Bolivia and Peru.
-To compensate for the low collection rates in these two countries, note that we exceeded the sample size in all the remaining states.
+As expected, our sample is also more educated than [the Brazilian
+population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
+About `r df2[1, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]`% 
+have graduate school education.
 
-Considering the elite type, note that we have, as expected, more people from academia and the civil society, followed by those from the Executive and Legislative branches.
-The data collection for members of the Legislative branch was below the original target, but above the minimum mark of 5 for each country.
-This is expected, given the difficulty of accessing these elite members.
+\footnotesize
+```{r education, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(education) %>%
+  filter(!is.na(education)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Education = education) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Education") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
 
-In the map, we can see that the answers concentrate on the country's capitals, with some variation within the state, but with sample concentrated in the largest municipalities.
-This is also in line with our expectations, as elite members are assumed to gravitate around capital cities and large urban centers.
+## Household Income
 
-# Frequency of Features Selected by Each Attribute \label{sec:features}
-
-The figures below display the feature frequency for each attribute, by each task.
-
-```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
-aux <- cj %>%
-  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
-  unique()
-
-# Who makes the rules
-tab <- data.frame(table(aux$`Who makes the rules?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('Who makes the rules?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 35) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are conflicts resolved?
-tab <- data.frame(table(aux$`How are conflicts resolved?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are conflicts resolved?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 35) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# What punishments do they use?
-tab <- data.frame(table(aux$`What punishments do they use?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('What punishments do they use?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 40) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are repeated violations punished?
-tab <- data.frame(table(aux$`How are repeated violations punished?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are repeated violations punished?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How are costs distributed?
-tab <- data.frame(table(aux$`How are costs distributed?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How are costs distributed?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
-
-# How often will the agreement be renegotiated?
-tab <- data.frame(table(aux$`How often will the agreement be renegotiated?`))
-names(tab) <- c('Levels', 'Frequency')
-p <- ggplot(data=tab, aes(x = Levels, y = Frequency)) +
-  geom_bar(stat="identity") +
-  theme_bw() + xlab('How often will the agreement be renegotiated?') +
-  annotate(geom = "text", label = tab$Frequency,
-           x = tab$Levels, y = tab$Frequency + 50) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-p
+```{r incometext, echo=F, warning=F, error=F, cache=T}
+df2 <- df1 %>%
+  group_by(household_income) %>%
+  filter(!is.na(household_income)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(`Household Income` = household_income)
 ```
 
-The two remarkable issues are the low frequency of *Less penalty* in the attribute *How are repeated violations punished?* and the low frequency of *None* for the attribute *What punishments do they use?*.
-This because when we draw the level none for the attribute *What punishments do they use?* or the level less penalty for *How are repeated violations punished?*, then it makes no sense to have less penalty than the minimum possible.
+In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
+R\$5,0001 to R\$10,000 per month (US\$920 to US\$1840 as of January 2021), which
+comprise the largest group in our sample. However, the sample also contains 
+`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
+and R\$2,000 (US\$ 185 to US\$370) and `r df2[7, 3]*100`% with household incomes
+up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
+this respect, we have reached participants from all social classes.
 
-# Code for the Main Paper
+\footnotesize
+```{r income, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(household_income) %>%
+  filter(!is.na(household_income)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(`Household Income` = household_income) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Household Income") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
 
-The code for Figure 2 of the paper follows below. We also include the point estimates in companion tables.
+## Political Ideology
 
-```{r codefig2}
-## Main plot
-# Main estimation equation
-fm <- selected ~ `Who makes the rules?` +
-  `How are conflicts resolved?` +
-  `What punishments do they use?` +
-  `How are repeated violations punished?` +
-  `How are costs distributed?` +
-  `How often will the agreement be renegotiated?`
-
-# Plot
-mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0 = 0.5)
-
-myFaces <- c(rep('plain', 5), "bold",
-             rep('plain', 4), "bold",
-             rep('plain', 3), "bold",
-             rep('plain', 4), "bold",
-             rep('plain', 5), "bold",
-             rep('plain', 5), "bold")
-
-p <- plot(mms, vline = 0.5, header_fmt = "%s", size = 2) + ggplot2::theme(
-    legend.position = "none",
-    panel.grid.major = ggplot2::element_blank(),
-    panel.grid.minor = ggplot2::element_blank(),
-    axis.text.y = element_text(face=myFaces, size = 11)) +
-    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
-                                                xmax = "upper"),
-                            size = 1, height = 0, na.rm = TRUE,
-                            position = ggstance::position_dodgev(height = 1))
-p
-
-ggsave(filename = 'MM_all.pdf', plot = p, width = 8, height = 6)
-
-# Table
-table_mm <- function(mms, capt) {
-  dfr <- data.frame(feature = mms[,c(4)],
-             round(mms[,c(5,6,8,9,10)], digits=3))
-  names(dfr) <- c('Feature', 'Estimate', 'Std.Error',
-                'P-Value', 'Lower', 'Upper')
-  return(kable(dfr, "latex", caption = capt, booktabs = T) %>%
-    kable_styling(font_size = 10) %>%
-    group_rows('Who makes the rules?', 1, 5) %>%
-    group_rows('How are conflicts resolved?', 6, 10) %>%
-    group_rows('What punishments do they use?', 11, 14) %>%
-    group_rows('How are repeated violations punished?', 15, 17) %>%
-    group_rows('How are costs distributed?', 18, 21) %>%
-    group_rows('How often will the agreement be renegotiated?', 22, 26))
-}
-
-table_mm(mms, capt = 'Marginal Means -- Full Dataset')
+```{r ideologytext, echo=F, warning=F, error=F, cache=T}
+df2 <- df1 %>%
+  group_by(ideology) %>%
+  filter(!is.na(ideology)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Ideology = ideology)
 ```
 
-The code for Figure 3 of the paper follows below, with also the point estimates in a companion table.
+We have also collected information regarding the subjects' political ideology.
+Most respondents identify themselves as right-wingers (`r df2[7, 3]*100`%),
+followed by left-wingers (`r df2[5, 3]*100`%), and centrists (`r df2[1, 3]*100`%).
+Subjects who do not know their ideology or prefer not to tell their
+political beliefs are also large in number (`r df2[4, 3]*100`% and 
+`r df2[6, 3]*100`%, respectively).
+
+\footnotesize
+```{r ideology, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(ideology) %>%
+  filter(!is.na(ideology)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Ideology = ideology) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Political Ideology") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+## Support for Death Penalty
+
+Below you may find how many respondents support the death penalty.
+
+\footnotesize
+```{r deathpenalty, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(death_penalty) %>%
+  filter(!is.na(death_penalty)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(`Support for Death Penalty` = death_penalty) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Support for Death Penalty") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+## Previous Victimization
+
+We asked subjects whether they had victimized in the previous 12 months, as
+crime victims may be more likely to support lynchings. The responses follow
+below.
+
+\footnotesize
+```{r victimization, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(previous_victim_dummy) %>%
+  filter(!is.na(previous_victim_dummy)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(Victimization = previous_victim_dummy) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Previous Victimization (12 Months)") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+## Opinion on the Police
+
+Here we show the results for our question on how respondents see the police
+forces.
+
+\footnotesize
+```{r police, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(views_police) %>%
+  filter(!is.na(views_police)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(`Opinion on the Police` = views_police) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Opinion on the Police") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+## Opinion on the Judicial System
+
+Lastly, we asked how respondents evaluate their local judiciary. As in the
+previous question, subjects could choose among five options, as well as affirm
+that they do not have an opinion or decline to answer the question.
+
+\footnotesize
+```{r justice, warning=F, error=F, cache=T}
+df1 %>%
+  group_by(views_justice) %>%
+  filter(!is.na(views_justice)) %>%
+  summarise(N = n()) %>%
+  mutate(Frequency = round(N / sum(N), 3)) %>%
+  rename(`Opinion on the Judicial System` = views_justice) %>%
+  kbl(., booktabs = TRUE,  linesep = "",
+      caption = "Opinion on the Judicial System") %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = "hold_position")
+```
+\normalsize
+
+# Experiment 01
 
 \newpage
-
-```{r codefig3}
-## Marginal means by Country
-
-# Argentina
-arg <- mm(subset(cj, countryOrigin=='Argentina'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(arg, capt = 'Marginal Means -- Argentina Only')
-```
-
-\newpage
-
-```{r}
-# Bolivia
-bol <- mm(subset(cj, countryOrigin=='Bolivia'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
-```
-
-\newpage
-
-```{r}
-# Brazil
-bra <- mm(subset(cj, countryOrigin=='Brazil'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(bra, capt = 'Marginal Means -- Brazil Only')
-```
-
-\newpage
-
-```{r}
-# Chile
-chi <- mm(subset(cj, countryOrigin=='Chile'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(chi, capt = 'Marginal Means -- Chile Only')
-```
-
-\newpage
-
-```{r}
-# Colombia
-col <- mm(subset(cj, countryOrigin=='Colombia'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(col, capt = 'Marginal Means -- Colombia Only')
-```
-
-\newpage
-
-```{r}
-# Costa Rica
-cri <- mm(subset(cj, countryOrigin=='Costa Rica'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
-```
-
-\newpage
-
-```{r}
-# Ecuador
-ecu <- mm(subset(cj, countryOrigin=='Ecuador'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
-```
-
-\newpage
-
-```{r}
-# Mexico
-mex <- mm(subset(cj, countryOrigin=='Mexico'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(mex, capt = 'Marginal Means -- Mexico Only')
-```
-
-\newpage
-
-```{r}
-# Panama
-pan <- mm(subset(cj, countryOrigin=='Panama'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(pan, capt = 'Marginal Means -- Panama Only')
-```
-
-\newpage
-
-```{r}
-# Peru
-per <- mm(subset(cj, countryOrigin=='Peru'),
-        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(per, capt = 'Marginal Means -- Peru Only')
-```
-
-\newpage
-
-```{r, fig.width = 13, fig.height = 13}
-# Changing country labels
-arg$country <- 'Argentina'
-bol$country <- 'Bolivia'
-bra$country <- 'Brazil'
-chi$country <- 'Chile'
-col$country <- 'Colombia'
-cri$country <- 'Costa Rica'
-ecu$country <- 'Ecuador'
-mex$country <- 'Mexico'
-pan$country <- 'Panama'
-per$country <- 'Peru'
-# Plot by country
-p <- plot(rbind(arg, bol, bra, chi, col,
-              cri, ecu, mex, pan, per),
-        group = 'country', vline = 0.5, nr = 10,
-        header_fmt = "%s", size = 2) +
-  facet_wrap( ~ country, ncol = 5) +
-  ggplot2::theme(
-    axis.text.y = element_text(face=myFaces, size = 11)) +
-    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
-                                                xmax = "upper"),
-                            size = 1, height = 0, na.rm = TRUE,
-                            position = ggstance::position_dodgev(height = 1))
-
-p
-
-ggsave(filename = 'MM_country.pdf',
-       plot = p, width = 12, height = 12)
-```
-
-The code for Figure 4 of the paper is available below. Tables displaying the point estimates are also included.
-
-```{r}
-## Elite type graphs and estimates
-
-# Table for the Executive branch
-res1 <- mm(subset(cj, groupOrigin=='Executive'),
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res1, capt = 'Marginal Means -- Executive Only')
-```
-
-\newpage
-
-```{r}
-# Legislative branch
-res2 <- mm(subset(cj, groupOrigin=='Legislative'),
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res2, capt = 'Marginal Means -- Legislative Only')
-```
-
-\newpage
-
-```{r}
-# Civil society
-res3 <- mm(subset(cj, groupOrigin=='Civil Society'),
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
-```
-
-\newpage
-
-```{r}
-# Academia
-res4 <- mm(subset(cj, groupOrigin=='Academia'),
-           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
-table_mm(res4, capt = 'Marginal Means -- Academia Only')
-
-```
-
-\newpage
-
-```{r, fig.width = 10, fig.height = 8}
-# Changing labels
-res1$MemberType <- 'Executive'
-res2$MemberType <- 'Legislative'
-res3$MemberType <- 'Civil Society'
-res4$MemberType <- 'Academia'
-
-# Plot by Elite Type
-p <- plot(rbind(res1, res2, res3, res4),
-     group = 'MemberType', vline = 0.5, nr = 4,
-        header_fmt = "%s", size = 2) +
-  facet_wrap( ~ MemberType, ncol = 4) +
-  ggplot2::theme(
-    axis.text.y = element_text(face=myFaces, size = 11)) +
-    ggplot2::geom_errorbarh(ggplot2::aes_string(xmin = "lower",
-                                                xmax = "upper"),
-                            size = 1, height = 0, na.rm = TRUE,
-                            position = ggstance::position_dodgev(height = 1))
-p
-
-ggsave(filename = 'MM_membertype.pdf', plot = p,
-       width = 8, height = 6)
-```
-
-# APSA Experimental Section Standard Report for Experiments 
-\label{sec:apsa}
-
-## Hypotheses
-
-We designed three survey experiments to investigate (i) which criminal profiles
-citizens prefer for extralegal punishment, (ii) how individuals justify mob
-violence, and (iii) whether information provision reduces support for
-vigilantism. First, we run a conjoint experiment to identify criminal
-characteristics that are associated with higher likelihood of lynching. In our
-second experiment, we show respondents a short article about a real lynching
-episode and ask them whether they see the mob's motivations as legitimate.
-Lastly, we test whether providing information about the legal consequences of
-lynching, human rights guarantees, and the risk of retribution makes
-respondents less likely to endorse extralegal violence.
-
-## Subjects and Context
-
-We selected Brazilian nationals over 18 years of age to participate in our
-experiments. Our sample consisted of XXXX participants from all 5 Brazilian
-regions (Center-West, North, Northeast, Southeast, and South).
-
-We ran our online survey via Qualtrics. The firm recruited participants from
-XXXX to XXXX December, 2020. From the XXXX responded contacted by Qualtrics,
-XXXX declined to participate in our experiment (XX%), and XXX agreed to our
-consent form (XX%).
-
-## Allocation Methods
-
-**Random Assignment:** We created the conjoint experiment using a Python application provided by @strezhnev2013conjoint.
-We translated the original survey questions (as shown in the text) into Portuguese, then embedded the PHP file with the randomization parameters in a Qualtrics survey.
-The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <https://github.com/danilofreire/lynching-experiment-brazil/tree/master/conjoint>.
-
-For each attribute, the probability of selecting a given component follows a uniform distribution function. The table below describes the results.
-
-\vspace{.5cm}
-
-| **Attribute**                          | **Values**                                   | **Probabilities** |
-|:---------------------------------------|:---------------------------------------------|------------------:|
-| **Who makes the rules?**               | International organizations                  | 1/5               |
-|                                        | Federal government                           | 1/5               |
-|                                        | Local government                             | 1/5               |
-|                                        | Local community members                      | 1/5               |
-|                                        | Non-governmental organizations               | 1/5               |
-|                                        |                                              |                   |
-| **Conflict resolution mechanism**      | United Nations                               | 1/5               |
-|                                        | Government bureaucracy                       | 1/5               |
-|                                        | Local courts                                 | 1/5               |
-|                                        | Private arbitration                          | 1/5               |
-|                                        | Informal norms                               | 1/5               |
-|                                        |                                              |                   |
-| **Punishment**                         | Imprisonment                                 | 1/4               |
-|                                        | Fines                                        | 1/4               |
-|                                        | Blacklist                                    | 1/4               |
-|                                        | None                                         | 1/4               |
-|                                        |                                              |                   |
-| **Punishment for repeated violations** | More penalty                                 | 1/3               |
-|                                        | Same                                         | 1/3               |
-|                                        | Less penalty                                 | 1/3               |
-|                                        |                                              |                   |
-| **Agreement costs**                    | Rich countries pay more than poor countries  | 1/4               |
-|                                        | Proportional to history of emissions         | 1/4               |
-|                                        | Proportional to current emissions            | 1/4               |
-|                                        | Only rich countries pay                      | 1/4               |
-|                                        |                                              |                   |
-| **Renegotiation**                      | Never                                        | 1/5               |
-|                                        | Fifty years                                  | 1/5               |
-|                                        | Twenty years                                 | 1/5               |
-|                                        | Five years                                   | 1/5               |
-|                                        | One year                                     | 1/5               |
-Table: Conjoint experiment attributes and their respective probabilities.
-
-We added one logical restriction to the set climate change treaties: **Punishment = None** can never appear together with **Punishment for repeated violations = Less penalty**.
-The number of possible treaties are the product of the attributes ($5\times 5 \times 4 \times 3 \times 4 \times 5 = 6,000$) minus the number of removed possibilities ($5\times 5  \times 4 \times 5 = 500$).
-The total number of possible treaties is $5,500$.
-
-## Treatments
-
-**Descriptions of the intervention:** Our treatment was the randomization of components in the conjoined climate mitigation treaties.
-We provided the following description before the conjoint experiment starts, in Spanish and Portuguese:
-
-\vspace{.5cm}
-
-```
-For the following questions, read carefully the instructions below.
-
-Imagine that your country would sign an international treaty to mitigate climate change.
-A climate mitigation treaty has, in general, the following attributes:
-
-1. Who defines the rules? Which group will define the parameters for the treaty?
-2. How are the conflicts that might happen when the treaty begin be resolved?
-3. What punishments should be applied to ensure compliance?
-4. How will repeated violations be punished?
-5. How are costs for implementing the treaty be distributed?
-6. How often the treaty has to be renegotiated?
-
-In the following questions, you will see variations in treaties on these six attributes.
-Please select the treaty that has the characteristics that you believe are best for your country.
-```
-
-\vspace{.5cm}
-
-The conjoint experiment consisted in comparing two treaties that vary in these six attributes, repeating the application for seven times for each respondent.
-
-\noindent \textbf{Software:} To program the PHP randomization device we used the Python application provided by @strezhnev2013conjoint. We used Qualtrics to administer the survey.
-
-\noindent \textbf{Delivery:} We repeated the conjoint experiment seven times, to improve test power.
-
-\noindent \textbf{Dataset description:} Each line in the dataset represents a given treaty, varying for the selection status (selected versus non-selected) for a given respondent.
-When a respondent finished an entire response set, this adds 14 rows to the dataset.
-Seven rows with the selected treaties and other seven rows with the non-selected treaties.
-
-\noindent \textbf{Deception:} We used no deception in our experiments.
-
-## Results
-
-\noindent \textbf{Outcome measures and covariates:} The main outcome is a binary indicator for the selection of a given conjoined package.
-We added two covariates to measure heterogeneous effects: *Country* and *Elite type*.
-
-\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.
-
-\noindent \textbf{Statistical analysis:} We fit a marginal means estimator and an AMCE estimator.
-The estimation conditions the results within subjects and the presented conjoined packages.
-The results are available in sections \ref{sec:features} and \ref{sec:amce}.
-
-\noindent \textbf{Missing data and attrition:} Conditional on having started the conjoint experiment, for each task we had the following completion rates:
-
-```{r, fig.width = 7, fig.height = 8}
-barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
-```
-
-## Other Information
-
-* **IRB**: This research received IRB approval from Brown University (Protocol 2009002803/2020).
-
-* **Pre-registration**: We submitted the study design to EGAP's registry on
-  October 30th, 2020. A time-stamped copy of the pre-analysis plan is available
-  at
-  <https://github.com/danilofreire/lynching-experiment-brazil/tree/master/pre-analysis-plan>
-
-* **Funding**: We received $10,000 from the Department of Political Economy at
-  King's College London to conduct this research. The study sponsor did not
-  play a role in the design or analysis of the study or in the decision to
-  submit for publication.
-
-* **Replication materials**: All scripts and data required to replicate the
-  results of our study are available at
-  <http://github.com/danilofreire/lynching-experiment-brazil>.
 

### 2021-01-28 appendix/lynchings.R

@@ -533,9 +533,24 @@ m4 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
 m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC2"))
 m4se <- sqrt(diag(m4cov))
 
-stargazer(m1, m2, m3, m4,
-          se = list(m1se, m2se, m3se, m4se),
+stargazer(m2, m3, m4, m1,
+          se = list(m2se, m3se, m4se, m1se),
           align = TRUE)
+
+# Effect of covariates on basline levels
+df_exp02_group <- df_exp02 %>%
+  filter(gender == c("Female", "Male"),
+         race %in% c("Asian", "Black", "Mixed Race", "White"),
+         ideology %in% c("Center", "Center-Left", "Center-Right",
+                         "Left", "Right"))
+
+m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
+m2 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
+m3 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
+m4 <- lm(exp02_outcomes ~ gender + race + ideology,
+         data = df_exp02_group)
+
+stargazer(m1, m2, m3, m4, align = TRUE)
 
 ## Subgroup analysis: gender = Female
 table(df_exp02$gender)
@@ -543,16 +558,16 @@ table(df_exp02$gender)
 df_exp02_group <- df_exp02 %>% filter(gender == "Female")
 
 m1 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02_group)
-coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
+m1se <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
 
 m2 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02_group)
-coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
+m2se <- coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
 
 m3 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02_group)
-coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
+m3se <- coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
 
[…]

### 2021-01-28 appendix/appendix.Rmd
add first part exp 01 app

@@
 The next demographic variable we show here is race. According to the [Brazilian
-Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html), 42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4% as Blacks, and 1,1% as Asians or Indigenous.
-As we see below, our sample includes more Whites and fewer individuals who identify as Mixed Race.
-The number of Blacks roughly coincide with the population statistics.
+Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
+42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4%
+as Blacks, and 1,1% as Asians or Indigenous. As we see below, our sample
+includes more Whites and fewer individuals who identify as Mixed Race. The
+number of Blacks roughly coincide with the population statistics.
 
@@
 
+## Description
+
+In our first experiments, we present five pairs of criminal profiles to
+respondents. Each profile consists of eight attributes: 1) gender of the crime
+perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
+4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
+motivating crime; 7) age of the victim of the motivating crime; 8) lynching
+perpetrators. The attributes and levels are displayed in table
+\ref{tab:categories} below.
+
+\vspace{.3cm}
+
+\begin{table}[htpb]
+\small
+\begin{center}
+\caption{\textbf{Attributes and Levels}}
+\label{tab:categories}
+\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
+\Xhline{2\arrayrulewidth}
+\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
+\Xhline{2\arrayrulewidth}
+\small
+Gender of crime perpetrator & Male; female \\ [4pt]
+Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
+Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
+Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
+Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
+Gender of crime victim & Male; female\\ [4pt]
+Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
+Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
+\Xhline{2\arrayrulewidth}
+\end{tabular}
+\end{center}
+\end{table}
+
+Respondents indicated which profile they preferred for extrajudicial
+punishment. They had read the following prompt prior to the experiment:
+
+* `Lynchings are often used as social punishment in Brazil. Lynchings are cases
+  in which three or more people physically attack or execute a suspected
+  criminal in public. We are interested in knowing more about how Brazilians
+  see these episodes. In the next five questions, please read the description
+  of two possible lynching victims in Brazil and indicate in which case you
+  believe the punishment is more justified. Even if you are not entirely sure,
+  please select one of the cases.`[^portuguese]
+
+[^portuguese]: Original text in Portuguese: `Linchamentos são às vezes usados
+como punição social no Brasil. Linchamentos são casos nos quais três ou mais
+pessoas agridem fisicamente ou executam em público um suspeito de um crime.
+Estamos interessados em saber mais sobre como os brasileiros vêem estes
+episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
+possíveis vítimas de linchamento no Brasil e indique em quais delas você
+acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
+por favor, escolha um dos casos.`
+
+## Replication Code
+
+We estimate the conjoint experiments with the `cregg` package
+[@leeper2018cregg] for the `R` statistical language [@rstats2019]. We follow
+@leeper2018subgroup and report marginal means
+
+We will cluster standard errors by
+respondent. The code follows below.
+
+\footnotesize
+```{r conjointfull, warning=F, error=F, cache=T, fig.width=7, fig.height=6}
+conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
+                                responses = c("Q13", "Q14", "Q15",
+                                              "Q16", "Q17"),
+                                covariates = c("ResponseId",
+                                               "Q1", "Q2", "Q3", "Q4",
+                                               "Q5", "Q6", "Q7",
+                                               "Q8", "Q9", "Q10",
+                                               "Q11", "Q12"),
+                                new.format = FALSE, respondentID = NULL)
+
+conjoint_data <- conjoint_data %>%
+  rename(response_id                      = ResponseId,
+         Age                              = Q2,
+         Gender                           = Q3,
+         Race                             = Q4,
+         Education                        = Q5,
+         Region                           = Q6,
+         "Household Income"               = Q7,
+         Ideology                         = Q8,
+         "Support death penalty"          = Q9,
+         "Previous Victimization"         = Q10,
+         "Offense"                        = Crime,
+         "Opinion on Policing"            = Q11,
+         "Opinion on Judiciary"           = Q12,
+         "Gender of crime victim"         = "Gênero.da.vítima",
+         "Gender of crime perpetrator"    = "Gênero.do(a).criminoso(a)",
+         "Age of crime victim"            = "Idade.da.vítima",
+         "Age of crime perpetrator"       = "Idade.do(a).criminoso(a)",
+         "Lynching perpetrators"          = "Linchadores",
+         "Race of crime perpetrator"      = "Raça.do(a).criminoso(a)",
+         "Residency of crime perpetrator" = "Residência.do.criminoso") %>%
+  mutate(`Gender of crime perpetrator` = fct_recode(`Gender of crime perpetrator`,
+                                                    "Male"   = "Masculino",
+                                                    "Female" = "Feminino"),
+         `Age of crime perpetrator` = fct_recode(`Age of crime perpetrator`,
+                                                 "Teenager" = "Adolescente",
+                                                 "Adult"    = "Adulto(a)",
+                                                 "Elderly"  = "Idoso(a)"),
+         `Race of crime perpetrator` = fct_recode(`Race of crime perpetrator`,
+                                                  "Asian"      = "Asiático(a)",
+                                                  "White"      = "Branco(a)",
+                                                  "Indigenous" = "Indígena",
+                                                  "Black"      = "Negro(a)"),
+         `Residency of crime perpetrator` = fct_recode(`Residency of crime perpetrator`,
+                                                       "Another neighborhood" = "Mora em outro bairro",
+                                                       "In the neighborhood"  = "Mora na vizinhança"),
+         `Offense` = fct_recode(`Offense`,
+                                "Murder"         = "Assassinou",
+                                "Pick-pocketing" = "Bateu a carteira",
+                                "Rape"           = "Estuprou",
+                                "Molestation"    = "Molestou",
+                                "Car theft"      = "Roubou o carro"),
+         `Gender of crime victim` = fct_recode(`Gender of crime victim`,
+                                               " Male"   = "Masculino",
+                                               " Female" = "Feminino"),
+         `Age of crime victim` = fct_recode(`Age of crime victim`,
+                                            " Teenager" = "Adolescente",
+                                            " Child"    = "Criança",
+                                            " Adult"    = "Adulto(a)",
+                                            " Elderly"  = "Idoso(a)"),
+         `Lynching perpetrators` = fct_recode(`Lynching perpetrators`,
+                                              "Family of the victim" = "Família da vítima",
+                                              "Gangs" = "Gangues",
+                                              "Bystanders" = "Pedestres",
+                                              "Police" = "Polícia",
+                                              "Neighbors" = "Vizinhos")) %>%
+  select(-c(16, 18, 20, 22, 24, 26, 28, 30)) %>%
+  mutate(response_id = tolower(response_id))
+
+fm <- selected ~ `Gender of crime perpetrator` +
+  `Age of crime perpetrator` + `Race of crime perpetrator` +
+  `Residency of crime perpetrator` + `Offense` +
+  `Gender of crime victim` + `Age of crime victim` +
+  `Lynching perpetrators`
+
+faces <- c(rep("plain", 5), "bold",
+           rep("plain", 4), "bold",
+           rep("plain", 2), "bold",
+           rep("plain", 5), "bold",
+           rep("plain", 2), "bold",
+           rep("plain", 4), "bold",
+           rep("plain", 3), "bold",
+           rep("plain", 2), "bold")
+
+plot(mm(conjoint_data, fm, id = ~response_id),
+     vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "none",
+        axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+```
+\normalsize
+
 \newpage

### 2021-01-30 appendix/appendix.Rmd
add more analyses to experiment 01

@@
     toc: true
-    keep_tex: yes
+    toc_depth: 3
+    keep_tex: no
     template: template.latex
@@
 \footnotesize
-```{r loading, warning=F, error=F, cache=T}
+```{r loading, warning=F, error=F, cache=F}
 # Install and load required packages
@@
   mutate(consent = recode(consent,
-                          "concordo"     = "Agree",
-                          "não concordo" = "Disagree"),
+                          concordo     = "Agree",
+                          `não concordo` = "Disagree"),
          gender = recode(gender,
@@
 
-```{r samplesize, echo=F, warning=F, error=F, cache=T}
+```{r sample-size, echo=F, warning=F, error=F, message=F, cache=T}
 df1 <- df %>% filter(consent == "Agree")
@@
 
-```{r incometext, echo=F, warning=F, error=F, cache=T}
+```{r income-text, echo=F, warning=F, error=F, cache=T}
 df2 <- df1 %>%
@@
 \footnotesize
-```{r deathpenalty, warning=F, error=F, cache=T}
+```{r death-penalty, warning=F, error=F, cache=T}
 df1 %>%
@@
 
+We added three restrictions to the conjoint design to avoid implausible
+scenarios. First, female rapists were excluded from the model, but we did
+include female molesters in the conjoint experiment. Second, when the offense
+was car theft, the victim could not be a child. Lastly, teenagers could not be
+victims of car theft either. All other combinations were allowed. We randomized
+the attributes using a `.php` script, which is available at
+<https://github.com/danilofreire/lynching-experiment-brazil/blob/master/conjoint/portuguese/lynching-conjoint-pt.php>.
+
 Respondents indicated which profile they preferred for extrajudicial
-punishment. They had read the following prompt prior to the experiment:
+punishment. Prior to the experiments, they had read the following prompt:
 
@@
 
-## Replication Code
+## Marginal Means Estimator
 
-We estimate the conjoint experiments with the `cregg` package
-[@leeper2018cregg] for the `R` statistical language [@rstats2019]. We follow
-@leeper2018subgroup and report marginal means
-
-We will cluster standard errors by
-respondent. The code follows below.
+We estimate the conjoint experiment with the `cregg` package [@leeper2018cregg]
+for the `R` statistical language [@rstats2019]. We follow @leeper2020measuring
+and report marginal means as our main estimates. Marginal means are easy to
+interpret and they are not sensitive to choice of the reference category in
+subgroup analyses. The $H_0$ in all models are that the coefficient is equal to
+0.5, that is, that respondents are indifferent to the attribute level. Standard
+errors are clustered by respondent. The code follows below.
 
 \footnotesize
-```{r conjointfull, warning=F, error=F, cache=T, fig.width=7, fig.height=6}
+```{r conjoint-mm, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
 conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
@@
 
+# Model
 fm <- selected ~ `Gender of crime perpetrator` +
@@
 
+mms <- mm(conjoint_data, fm, id = ~response_id, h0 = 0.5)
+
+# Plot
 faces <- c(rep("plain", 5), "bold",
@@
 
-plot(mm(conjoint_data, fm, id = ~response_id),
-     vline = 0.5, header_fmt = "%s") +
+plot(mms, vline = 0.5, header_fmt = "%s") +
   theme(legend.position = "none",
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Table
+table_mm <- function(mms, capt) {
+dfr <- data.frame(feature = mms[, c(4)],
+                  round(mms[, c(5, 6, 8, 9, 10)], digits = 3))
+names(dfr) <- c("Feature", "Estimate", "Std. Error",
+                "P-Value", "Lower", "Upper")
+return(kbl(dfr, "latex", caption = capt, linesep = "",
+           booktabs = TRUE) %>%
+kable_styling(font_size = 12, full_width = TRUE,
+              latex_options = "hold_position") %>%
+pack_rows("Gender of crime perpetrator", 1, 2) %>%
+pack_rows("Age of crime perpetrator", 3, 5) %>%
+pack_rows("Race of crime perpetrator", 6, 9) %>%
+pack_rows("Residency of crime perpetrator", 10, 11) %>%
+pack_rows("Offense", 12, 16) %>%
+pack_rows("Gender of crime victim", 17, 18) %>%
+pack_rows("Age of crime victim", 19, 22) %>%
+pack_rows("Lynching perpetrators", 23, 27) %>%
+column_spec(1, width = "6cm"))
+}
+
+table_mm(mms, capt = "Marginal Means -- Full Model")
+```
+\normalsize
+
+\newpage
+
+## Average Marginal Component Effect (AMCE) Estimator
+
+We also estimate AMCE coefficients for our conjoint experiment. This method
+selects one reference category for each attribute and look at changes from the
+baseline level. The reference category are marked as zero in our models.
+
+\footnotesize
+```{r conjoint-amce, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
+amces <- cj(conjoint_data, fm, id = ~response_id)
+
+plot(amces, vline = 0.0, header_fmt = "%s") +
+  theme(legend.position = "none",
+        axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+table_mm(amces, capt = "Average Marginal Component Effects -- Full Model")
+```
+
+\newpage
+
+## Subgroup Analyses
+
+In this subsection, we test whether our results vary according to individual characteristics, such as gender, age, race, income, support for death penalty, and the respondents' opinions on the judicial system and the police forces.
+All models report marginal means.
+
+### Gender
+
+Results do not seem to vary according to the gender of the respondent. We focus
+here on the differences between males and females and exclude the 11
+observations in which respondents preferred not to say their gender or marked
+"other" in our questionnaire. Across all conjoint experiment attributes, we see
+that an overlap between the 95% confidence intervals for males and females.
+
+\footnotesize
+```{r conjoint-females, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos = "H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(gender) %>%
+  filter(gender == c("Male", "Female"))
+cjdt$Gender <- factor(cjdt$gender)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Gender)
+
+# Plot
+plot(mm_by, group = "Gender", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+table_mm_by <- function(mm_by, capt) {
+dfr <- data.frame(feature = mm_by[, c(5)],
+                  round(mm_by[, c(6, 7, 9, 10, 11)], digits = 3))
+names(dfr) <- c("Feature", "Estimate", "Std. Error",
+                "P-Value", "Lower", "Upper")
+return(kbl(dfr, "latex", caption = capt, linesep = "",
+           booktabs = TRUE) %>%
+kable_styling(font_size = 12, full_width = TRUE,
+              latex_options = "hold_position") %>%
+pack_rows("Gender of crime perpetrator", 1, 2) %>%
+pack_rows("Age of crime perpetrator", 3, 5) %>%
+pack_rows("Race of crime perpetrator", 6, 9) %>%
+pack_rows("Residency of crime perpetrator", 10, 11) %>%
+pack_rows("Offense", 12, 16) %>%
+pack_rows("Gender of crime victim", 17, 18) %>%
+pack_rows("Age of crime victim", 19, 22) %>%
+pack_rows("Lynching perpetrators", 23, 27) %>%
+column_spec(1, width = "6cm"))
+}
+
+mm_females <- mm_by %>% filter(BY == "Female")
+table_mm_by(mm_females, capt = "Marginal Means -- Females")
+```
+
+\newpage
+
+```{r conjoint-males, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_males <- mm_by %>% filter(BY == "Male")
+table_mm_by(mm_males, capt = "Marginal Means -- Males")
+```
+\normalsize
+
+\newpage
+
+### Age
+
+As our age variable is continuous, we divide the data into three age brackets:
+18-34 years old, 35-54 years old, and 55-plus years old. The results show that
+seniors (55-plus) are more likely to select profiles that include murder as an
+offense, and less inclined to choose cases
+
+\footnotesize
+```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.5}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(age) %>%
+  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34",
+                          age >= 35 & age <= 54 ~ "35-54",
+                          age >= 55 ~ "55 plus",
+                                TRUE ~ as.character(age)))
+cjdt$Age <- factor(cjdt$age2)
+mm_by <- cj(cjdt, fm, id = ~response_id, h0 = 0.5,
+            estimate = "mm", by = ~Age)
+
+# Plot
+plot(mm_by, group = "Age", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
+```
+\normalsize
+
+\newpage
+
+### Race
+
+Below are our results when we disaggregate the data by race. We find that they are
+almost identical is all dimensions except for offense. Asian respondents are
+much less likely to select profiles that contain pickpocketing as a crime.
+
+\footnotesize
+```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(race) %>%
+  filter(race == c("Asian", "Black", "Mixed Race", "White"))
+cjdt$Race <- factor(cjdt$race)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Race)
+
+# Plot
+plot(mm_by, group = "Race", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_asian <- mm_by %>% filter(BY == "Asian")
+table_mm_by(mm_asian, capt = "Marginal Means -- Asian")
+mm_black <- mm_by %>% filter(BY == "Black")
+table_mm_by(mm_black, capt = "Marginal Means -- Black")
+mm_mixed <- mm_by %>% filter(BY == "Mixed Race")
+table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
+mm_white <- mm_by %>% filter(BY == "White")
+table_mm_by(mm_white, capt = "Marginal Means -- White")
 ```

### 2021-01-31 appendix/appendix.Rmd
add income and education, improve code

@@
 \footnotesize
-```{r loading, warning=F, error=F, cache=F}
+```{r loading, warning=F, message=F, error=F, cache=T}
 # Install and load required packages
@@
 
+\newpage
+
 ## Household Income
@@
 interpret and they are not sensitive to choice of the reference category in
-subgroup analyses. The $H_0$ in all models are that the coefficient is equal to
-0.5, that is, that respondents are indifferent to the attribute level. Standard
+subgroup analyses. The $H_0$ in all models is that the coefficient is equal to
+0.5, that is, that respondents are indifferent to that attribute level. Standard
 errors are clustered by respondent. The code follows below.
@@
 As our age variable is continuous, we divide the data into three age brackets:
-18-34 years old, 35-54 years old, and 55-plus years old. The results show that
-seniors (55-plus) are more likely to select profiles that include murder as an
-offense, and less inclined to choose cases
+18-34 years old, 35-54 years old, and 55+ years old. The results show that
+seniors (55+) are more likely to select profiles that include murder as an
+offense, and less inclined to choose cases involving molestation. The remaining
+attributes show little variation.
 
 \footnotesize
-```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.5}
+```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
 # Model
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
+
+# Tables
+mm_young <- mm_by %>% filter(BY == "18-34")
+table_mm_by(mm_young, capt = "Marginal Means -- 18-34 Years Old")
+mm_adult <- mm_by %>% filter(BY == "35-54")
+table_mm_by(mm_adult, capt = "Marginal Means -- 35-54 Years Old")
+mm_senior <- mm_by %>% filter(BY == "55 plus")
+table_mm_by(mm_senior, capt = "Marginal Means -- 55+ Years Old")
 ```
@@
 \footnotesize
-```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7}
+```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7, fig.pos="H"}
 # Model
@@
 table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
+```
+
+\newpage
+
+```{r conjoint-white, warning=F, message=F, error=F, cache=T, fig.pos="H"}
 mm_white <- mm_by %>% filter(BY == "White")
@@
 \normalsize
+
+\newpage
+
+### Education
+
+Next, we divide our data according to respondents' level of education. As the
+number of interviewees with primary or secondary education is low, we merge
+them into a single category, while the other levels (high school, college, and
+graduate school) remain the same as in our questionnaire.
+
+\footnotesize
+```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(education) %>%
+  filter(education == c("College", "Graduate School",
+                        "Primary School", "Secondary School",
+                        "High School")) %>%
+  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
+                                education == "Secondary School" ~ "Primary or Secondary School",
+                                TRUE ~ education))
+cjdt$Education <- factor(cjdt$education2)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Education)
+
+# Plot
+plot(mm_by, group = "Education", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
+
+# Tables
+mm_college <- mm_by %>% filter(BY == "College")
+table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
+mm_grad <- mm_by %>% filter(BY == "Graduate School")
+table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
+mm_high <- mm_by %>% filter(BY == "High School")
+table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
+mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
+table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
+```
+\normalsize
+
+\newpage
+
+### Household Income
+
+\footnotesize
+```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(household_income) %>%
+  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
+                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
+                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
+                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
+                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
+                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
+                                       household_income == "Above R$20,000" ~ "Above R$5,000",
+                                       TRUE ~ NA_character_))
+cjdt$Income <- factor(cjdt$household_income2)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Income)
+
+# Plot
+plot(mm_by, group = "Income", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_3k <- mm_by %>% filter(BY == "Up to R$3,000")
+table_mm_by(mm_3k, capt = "Marginal Means -- Up to 3,000 BRL")
+mm_5k <- mm_by %>% filter(BY == "From R$3,001 to R$5,000")
+table_mm_by(mm_5k, capt = "Marginal Means -- From 3,001 to 5,000 BRL")
+mm_abv5k <- mm_by %>% filter(BY == "Above R$5,000")
+table_mm_by(mm_abv5k, capt = "Marginal Means -- Above 5,000 BRL")
+```
+\normalsize
+
+\newpage
 
@@
 ```
-
-# References

### 2021-02-01 appendix/appendix.Rmd
finish experiment 01

@@
 In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
-R\$5,0001 to R\$10,000 per month (US\$920 to US\$1840 as of January 2021), which
+R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
 comprise the largest group in our sample. However, the sample also contains
 `r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
-and R\$2,000 (US\$ 185 to US\$370) and `r df2[7, 3]*100`% with household incomes
+and R\$2,000 (US\$ 184 to US\$368) and `r df2[7, 3]*100`% with household incomes
 up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
@@
 
-In this subsection, we test whether our results vary according to individual characteristics, such as gender, age, race, income, support for death penalty, and the respondents' opinions on the judicial system and the police forces.
-All models report marginal means.
+In this subsection, we test whether our results vary according to individual
+characteristics, such as gender, age, race, income, support for death penalty,
+and the respondents' opinions on the judicial system and the police forces. All
+models report marginal means.
 
@@
 mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
+```
+
+\newpage
+
+```{r conjoint-degree, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
 table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
@@
 
+We also disaggregate the results by monthly household income. As some
+categories have few respondents, we group them into three categories: (i) up to
+R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
+above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
+high-income households. We find no considerable difference amongst them.
+
 \footnotesize
-```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5, fig.pos="H"}
 # Model
@@
 
+### Support for Death Penalty
+
+Here we assess whether subjects who support the death penalty have different
+preferences towards lynching victims. There are fewer respondents who answered
+"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
+from their estimates are larger than the for the other two categories. The
+estimates largely overlap across the four groups, although those who answered "Rather Not Say" are less favorable to lynching Indigenous criminals.
+
+\footnotesize
+```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(death_penalty)
+cjdt$death_penalty <- factor(cjdt$death_penalty)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~death_penalty)
+
+plot(mm_by, group = "death_penalty", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_dk <- mm_by %>% filter(BY == "Don't Know")
+table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
+mm_no <- mm_by %>% filter(BY == "No")
+table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
+```
+
+\newpage
+
+```{r conjoint-deathrns, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
+table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
+```
+
+\newpage
+
+```{r conjoint-deathyes, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
+```
+
+\normalsize
+
+\newpage
+
+### Previous Victimization
+
+Respondents who had been victimized in the past 12 months also do not have
+different preferences towards lynchings victim profiles. The results are
+virtually identical for both groups, as one can see below.
+
+```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id")
+cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
+
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Previous_Victim)
+
+# Plot
+plot(mm_by, group = "Previous_Victim", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_no <- mm_by %>% filter(BY == "No")
+table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
+```
+
+\newpage
+
+```{r conjoint-victimizationyes, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
+```
+\normalsize
+
+\newpage
+
+### Opinion on the Police
+
+Experimental results do not change when we break the responses according to how
+subjects view the police forces.
+
+\footnotesize
+```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
+                                   views_police == "Don't Know" ~ NA_character_,
+                                   TRUE ~ views_police)) %>% drop_na(views_police2)
+cjdt$Police <- factor(cjdt$views_police2)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
+            h0 = 0.5, by = ~Police)
+
+# Plot
+plot(mm_by, group = "Police", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
+mm_good <- mm_by %>% filter(BY == "Good")
+table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
+mm_regular <- mm_by %>% filter(BY == "Regular")
+table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
+```
+
+\newpage
+
+```{r conjoint-polvbad, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_vbad <- mm_by %>% filter(BY == "Very Bad")
+table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
+```
+\newpage
+
+```{r conjoint-polvgood, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
+```
+\normalsize
+
+\newpage
+
+### Opinion on the Judicial System
+
+Lastly, we analyze whether personal beliefs about the judicial system affect
+the type of lynching victim respondents select.
+
+\footnotesize
+```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
+                                   views_justice == "Don't Know" ~ NA_character_,
+                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
+cjdt$Judiciary <- factor(cjdt$views_justice2)
+
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", 
+            h0 = 0.5, by = ~Judiciary)
+
+# Plot
+plot(mm_by, group = "Judiciary", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
+mm_good <- mm_by %>% filter(BY == "Good")
+table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
+mm_regular <- mm_by %>% filter(BY == "Regular")
+table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
+```
+
+\newpage
+
+```{r conjoint-justicevbad, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_vbad <- mm_by %>% filter(BY == "Very Bad")
+table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
+```
+
+\newpage
+
+```{r conjoint-justicevgood, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
+```
+\normalsize
+
+\newpage
+
+# Experiment 02
+
 \newpage

### 2021-02-02 appendix/appendix.Rmd
change spacing exp01, add main results exp02

--- 2021-01-31 appendix/appendix.Rmd
@@
 
-In our first experiments, we present five pairs of criminal profiles to
+In our first experiment, we present five pairs of criminal profiles to
 respondents. Each profile consists of eight attributes: 1) gender of the crime
@@
 
-* `Lynchings are often used as social punishment in Brazil. Lynchings are cases
+* Lynchings are often used as social punishment in Brazil. Lynchings are cases
   in which three or more people physically attack or execute a suspected
@@
   believe the punishment is more justified. Even if you are not entirely sure,
-  please select one of the cases.`[^portuguese]
-
-[^portuguese]: Original text in Portuguese: `Linchamentos são às vezes usados
+  please select one of the cases.[^portuguese]
+
+[^portuguese]: Original text in Portuguese: Linchamentos são às vezes usados
 como punição social no Brasil. Linchamentos são casos nos quais três ou mais
@@
 acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
-por favor, escolha um dos casos.`
+por favor, escolha um dos casos.
 
@@
 cjdt$Gender <- factor(cjdt$gender)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
-            h0 = 0.5, by = ~Gender)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Gender)
 
@@
 table_mm_by(mm_females, capt = "Marginal Means -- Females")
-```
-
-\newpage
-
-```{r conjoint-males, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
 mm_males <- mm_by %>% filter(BY == "Male")
@@
 
-\newpage
+\clearpage
 
@@
 \footnotesize
-```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.2, fig.pos="H"}
 # Model
@@
   drop_na(age) %>%
-  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34",
-                          age >= 35 & age <= 54 ~ "35-54",
-                          age >= 55 ~ "55 plus",
-                          TRUE ~ as.character(age)))
+  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
+                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
 cjdt$Age <- factor(cjdt$age2)
-mm_by <- cj(cjdt, fm, id = ~response_id, h0 = 0.5,
-            estimate = "mm", by = ~Age)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Age)
 
@@
 \footnotesize
-```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7, fig.pos="H"}
+```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.4, fig.pos="H"}
 # Model
@@
 cjdt$Race <- factor(cjdt$race)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
-            h0 = 0.5, by = ~Race)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Race)
 
@@
 table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
-```
-
-\newpage
-
-```{r conjoint-white, warning=F, message=F, error=F, cache=T, fig.pos="H"}
 mm_white <- mm_by %>% filter(BY == "White")
@@
 \footnotesize
-```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
+```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
 # Model
@@
 cjdt$Education <- factor(cjdt$education2)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
-            h0 = 0.5, by = ~Education)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)
 
@@
 
-\footnotesize
-```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=6, fig.pos="H"}
+We also disaggregate the results by monthly household income. As some
+categories have few respondents, we group them into three categories: (i) up to
+R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
+above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
+high-income households. We find no considerable difference amongst them.
+
+\footnotesize
+```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
 # Model
@@
 cjdt$Income <- factor(cjdt$household_income2)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
-            h0 = 0.5, by = ~Income)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Income)
 
@@
 
-\newpage
+\clearpage
+
+### Support for Death Penalty
+
+Here we assess whether subjects who support the death penalty have different
+preferences towards lynching victims. There are fewer respondents who answered
+"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
+from their estimates are larger than the for the other two categories. The
+estimates largely overlap across the four groups, although those who answered "Rather Not Say" are less favorable to lynching Indigenous criminals.
+
+\footnotesize
+```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(death_penalty)
+cjdt$Death_Penalty <- factor(cjdt$death_penalty)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Death_Penalty)
+
+# Plot
+plot(mm_by, group = "Death_Penalty", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_dk <- mm_by %>% filter(BY == "Don't Know")
+table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
+mm_no <- mm_by %>% filter(BY == "No")
+table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
+mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
+table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
+```
+\normalsize
+
+\clearpage
+
+### Previous Victimization
+
+Respondents who had been victimized in the past 12 months also do not have
+different preferences towards lynchings victim profiles. The results are
+virtually identical for both groups, as one can see below.
+
+\footnotesize
+```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id")
+cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Previous_Victim)
+
+# Plot
+plot(mm_by, group = "Previous_Victim", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_no <- mm_by %>% filter(BY == "No")
+table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
+```
+\normalsize
+
+\clearpage
+
+### Opinion on the Police
+
+Experimental results do not change when we break the responses according to how
+subjects view the police forces.
+
+\footnotesize
+```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
+                                   views_police == "Don't Know" ~ NA_character_,
+                                   TRUE ~ views_police)) %>% drop_na(views_police2)
+cjdt$Police <- factor(cjdt$views_police2)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)
+
+# Plot
+plot(mm_by, group = "Police", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
+mm_good <- mm_by %>% filter(BY == "Good")
+table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
+mm_regular <- mm_by %>% filter(BY == "Regular")
+table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
+mm_vbad <- mm_by %>% filter(BY == "Very Bad")
+table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
+```
+\normalsize
+
+\clearpage
+
+### Opinion on the Judicial System
+
+Lastly, we analyze whether personal beliefs about the judicial system affect
+the type of lynching victim respondents select.
+
+\footnotesize
+```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
+                                    views_justice == "Don't Know" ~ NA_character_,
+                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
+cjdt$Judiciary <- factor(cjdt$views_justice2)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)
+
+# Plot
+plot(mm_by, group = "Judiciary", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
+mm_good <- mm_by %>% filter(BY == "Good")
+table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
+mm_regular <- mm_by %>% filter(BY == "Regular")
+table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
+mm_vbad <- mm_by %>% filter(BY == "Very Bad")
+table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
+```
+\normalsize
+
+\clearpage
+
+# Experiment 02
+
+## Description
+
+In our second experiment, we analyze how respondents justify their preferences
+towards extralegal violence. We assess the impact of three factors that have
+been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
+criminal justice; 3) demand for harsher punishment for criminals. Below, we
+discuss them in further detail.
+
+Research shows that police ineffectiveness frequently appears as a strong
+predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
+result of the weakness of police institutions is that citizens decide to take
+criminal matters "into their own hands", thus persecuting and punishing the
+criminals by themselves. A recent statistic indicates that the police solves
+only 10% of the homicides in Brazil, which lends support to the link between
+weak law enforcement and lynchings [@pearson2018latam].
+
+Another possible determinant of lynching support is lack of trust in the
+justice system [@godoy2004justice; @smith2019contradictions]. This is often due
+to long criminal proceedings, which cause significant anxiety for the victims.
+In Brazil, the penal code allows the accused to appeal each decision several
+times, so it can take decades before a criminal case is closed
+[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
+the criminal is put to trial, he/she will be punished in a timely matter. Note
+that although the police is technically part of the criminal justice system, we
+analyze the two institutions separately in our experiment.
+
+Lastly, we evaluate whether respondents think that the legal punishment
+assigned to criminals is not proportional to the severity of their crimes. In
+particular, we intend to gauge the demand for iron-fisted criminal justice in
+Brazil. Although this treatment arm is related to the previous ones, it
+addresses not the efficiency of the institutions, but their legitimacy
+[@nivette2016institutional]. In fact, Brazilians are often vocal about their
+preference for repressive legal punishment. In a recent article in _The Wall
+Street Journal_, a bar owner justified the lynching of the local thug who
+killed his son by saying that "_even if he had been put behind bars for 100
+years it wouldn't have been enough to pay for all his crimes_"
+[@pearson2018latam]. We hypothesize that many Brazilians also share this view.
+
+The experiment consists of three treatment conditions and one control group.
+Respondents read an excerpt of a news article describing a real lynching case.
+We have slightly edited the original text so that respondents have no prior
+knowledge of the crime.[^jornal] The vignette for the control group includes no
+information about the reasons behind the lynching. We ask respondents to show
+their level of lynching support using a 0-100 slider, where 0 means no support
+and 100 means full support. Respondents in each of the three treatment arms
+read the same piece, but with one additional sentence explaining the
+motivations behind the lynching. The vignettes are as follows:
+
+[^jornal]: The original article is available at the following address:
+<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
+Access: August 2020.
+
+* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
+  According to the neighbours, he tried to break into a house but was
+  immobilised and beaten by members of the community.[^control-exp02]
+
+[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade.
+
+* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
+  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
+  house but was immobilised and beaten by members of the community. **One of
+  the residents who took part in the lynching said they had beaten the suspect
+  because "the police never patrols the area"**.[^treat01-exp02]
+
+[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
+nunca patrulha o local".**
+
+* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial system is too slow and the perpetrator is on
+  the street until the case is heard"**.[^treat02-exp02]
+
+[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
+é muito lenta e os criminosos ficam soltos até o julgamento"**.
+
+* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial punishment is not harsh
+  enough"**.[^treat03-exp02]
+
+[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
+da justiça não é dura o suficiente"**.
+
+Before each vignette, respondents will read the following text:
+
+* You will be shown a news article. Please read it carefully. After you read
+  the article, we will ask you one question about it.[^vig01-exp02]
+
+[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
+favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
+sobre ele.
+
+After the vignette, respondents will be presented with this question:
+
+* Would you think that the lynching was justified? Please use the slider below
+  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
+  use 51 to 100. Please use 50 if you neither agree nor
+  disagree.[^vig02-exp02]
+
+[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
+favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
+49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
+discordar.
+
+## Main Results
+
+Table \ref{tab:exp02main} summarizes our results.
+
+\footnotesize
+```{r exp02-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp02 <- df1 %>%
+  mutate(exp02_outcomes = coalesce(exp02_control, exp02_police,
+                                   exp02_slow_justice, exp02_small_punishment),
+  exp02_any_treat = case_when(!is.na(exp02_control) ~ "0",
+                              !is.na(exp02_police) ~ "1",
+                              !is.na(exp02_slow_justice) ~ "1",
+                              !is.na(exp02_small_punishment) ~ "1",
+                              TRUE ~ NA_character_),
+         exp02_police_treat = case_when(!is.na(exp02_control) ~ "0",
+                                        !is.na(exp02_police) ~ "1"),
+         exp02_slow_justice_treat = case_when(!is.na(exp02_control) ~ "0",
+                                              !is.na(exp02_slow_justice) ~ "1"),
+         exp02_small_punishment_treat = case_when(!is.na(exp02_control) ~ "0",
+                                                  !is.na(exp02_small_punishment) ~ "1"))
+
+m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
+m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
+m1se <- sqrt(diag(m1cov))
+
+m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
+m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
+m2se <- sqrt(diag(m2cov))
+
+m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
+m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
+m3se <- sqrt(diag(m3cov))
+
+m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
+m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC2"))
+m4se <- sqrt(diag(m4cov))
+
+stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
+title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
+dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
+covariate.labels = c("Police does not patrol area", "Justice too slow",
+"Punishment not harsh enough", "Combined treatments"),
+column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
+keep.stat = c("n", "rsq"), no.space = TRUE)
+```
+\normalsize
 
@@
 
+\footnotesize
 ```{r session, cache=TRUE}
@@
 ```
+\normalsize
+
+\clearpage

### 2021-02-04 appendix/appendix.Rmd
reorder factors exp01, add code exp02

@@
                        "preta"                 = "Black"),
+         race = fct_relevel(race, "Other", "Rather Not Say", after = Inf),
          education = recode(education,
@@
                             "não sei"                                                  = "Don't Know"),
+         education = fct_relevel(education, "Primary School", "Secondary School", "High School",
+                                 "College", "Graduate School", "Don't Know"),
          region = recode(region,
@@
                                    "de r$ 5.001 a r$ 10.000"  = "From R$5,001 to R$10,000"),
+         household_income = fct_relevel(household_income, "Up to R$1,000",
+                                        "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
+                                        "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
+                                        "From R$10,001 to R$20,000", "Above R$20,000"),
          ideology = recode(ideology,
@@
                            "prefiro não responder" = "Rather Not Say"),
+         ideology = fct_relevel(ideology, "Left", "Center-Left", "Center",
+                                "Center-Right", "Right", "Don't Know",
+                                "Rather Not Say"),
          death_penalty = recode(death_penalty,
@@
                                 "sim"                   = "Yes"),
+         death_penalty = fct_relevel(death_penalty, "Don't Know",
+                                     "Rather Not Say", after = Inf),
          views_police = recode(views_police,
@@
                                "ruim"                  = "Bad"),
+         views_police = fct_relevel(views_police, "Very Good", "Good", "Regular",
+                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),
          views_justice = recode(views_justice,
@@
                                 "ruim"                  = "Bad"),
+         views_justice = fct_relevel(views_justice, "Very Good", "Good", "Regular",
+                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),
          previous_victim_dummy = recode(previous_victim,
@@
   rename(Race = race) %>%
+  mutate(Race = fct_relevel(Race, "Other", "Rather Not Say", after = Inf)) %>%
   kbl(., booktabs = TRUE,  linesep = "",
@@
 population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
-About `r df2[1, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]`%
+About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[5, 3]`%
 have graduate school education.
@@
 
-In terms of household income, `r df2[6, 3]*100`% of the respondents earns from
+In terms of household income, `r df2[5, 3]*100`% of the respondents earn from
 R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
@@
 `r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
-and R\$2,000 (US\$ 184 to US\$368) and `r df2[7, 3]*100`% with household incomes
+and R\$2,000 (US\$ 184 to US\$368) and `r df2[1, 3]*100`% with household incomes
 up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
@@
 We have also collected information regarding the subjects' political ideology.
-Most respondents identify themselves as right-wingers (`r df2[7, 3]*100`%),
-followed by left-wingers (`r df2[5, 3]*100`%), and centrists (`r df2[1, 3]*100`%).
+Most respondents identify themselves as right-wingers (`r df2[5, 3]*100`%),
+followed by left-wingers (`r df2[1, 3]*100`%), and centrists (`r df2[3, 3]*100`%).
 Subjects who do not know their ideology or prefer not to tell their
-political beliefs are also large in number (`r df2[4, 3]*100`% and
-`r df2[6, 3]*100`%, respectively).
+political beliefs are also large in number (`r df2[6, 3]*100`% and
+`r df2[7, 3]*100`%, respectively).
 
@@
 \footnotesize
-```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
+```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
 # Model
@@
                                 education == "Secondary School" ~ "Primary or Secondary School",
-                                TRUE ~ education))
+                                TRUE ~ education),
+         education2 = fct_relevel(education2, "Primary or Secondary School",
+                                  "High School", "College", "Graduate School"))
 cjdt$Education <- factor(cjdt$education2)
@@
 # Tables
+mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
+table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
+mm_high <- mm_by %>% filter(BY == "High School")
+table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
 mm_college <- mm_by %>% filter(BY == "College")
@@
 table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
-mm_high <- mm_by %>% filter(BY == "High School")
-table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
-mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
-table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
 ```
@@
 \footnotesize
-```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
+```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
 # Model
@@
                                        household_income == "Above R$20,000" ~ "Above R$5,000",
-                                       TRUE ~ NA_character_))
+                                       TRUE ~ NA_character_),
+         household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
+                                         "Above R$5,000"))
 cjdt$Income <- factor(cjdt$household_income2)
@@
 from their estimates are larger than the for the other two categories. The
-estimates largely overlap across the four groups, although those who answered "Rather Not Say" are less favorable to lynching Indigenous criminals.
+estimates largely overlap across the four groups, although those who answered
+"Rather Not Say" are less favorable to lynching Indigenous criminals.
 
@@
 cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
-  drop_na(death_penalty)
+  drop_na(death_penalty) %>%
+  mutate(death_penalty = fct_relevel(death_penalty, "Yes", "No",
+                                     "Don't Know", "Rather Not Say"))
 cjdt$Death_Penalty <- factor(cjdt$death_penalty)
@@
 # Tables
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
+mm_no <- mm_by %>% filter(BY == "No")
+table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
 mm_dk <- mm_by %>% filter(BY == "Don't Know")
 table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
-mm_no <- mm_by %>% filter(BY == "No")
-table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
 mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
 table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
-mm_yes <- mm_by %>% filter(BY == "Yes")
-table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
 ```
@@
 # Model
-cjdt <- full_join(conjoint_data, df1, by = "response_id")
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  mutate(previous_victim_dummy, "Yes", "No")
 cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
@@
 # Tables
+mm_yes <- mm_by %>% filter(BY == "Yes")
+table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
 mm_no <- mm_by %>% filter(BY == "No")
 table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
-mm_yes <- mm_by %>% filter(BY == "Yes")
-table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
 ```
@@
 \footnotesize
-```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.7, fig.pos="H"}
+```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
 # Model
@@
                                    views_police == "Don't Know" ~ NA_character_,
-                                   TRUE ~ views_police)) %>% drop_na(views_police2)
+                                   TRUE ~ views_police),
+         views_police2 = fct_relevel(views_police2, "Very Good", "Good",
+                                     "Regular", "Bad", "Very Bad")) %>%
+  drop_na(views_police2)
 cjdt$Police <- factor(cjdt$views_police2)
@@
 # Tables
-mm_bad <- mm_by %>% filter(BY == "Bad")
-table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
 mm_good <- mm_by %>% filter(BY == "Good")
@@
 table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
 mm_vbad <- mm_by %>% filter(BY == "Very Bad")
 table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
-mm_vgood <- mm_by %>% filter(BY == "Very Good")
-table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
 ```
@@
 \footnotesize
-```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
+```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
 # Model
@@
                                     views_justice == "Don't Know" ~ NA_character_,
-                                   TRUE ~ views_justice)) %>% drop_na(views_justice2)
+                                   TRUE ~ views_justice),
+         views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
+                                      "Regular", "Bad", "Very Bad")) %>%
+  drop_na(views_justice2)
 cjdt$Judiciary <- factor(cjdt$views_justice2)
@@
 # Tables
-mm_bad <- mm_by %>% filter(BY == "Bad")
-table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
+mm_vgood <- mm_by %>% filter(BY == "Very Good")
+table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
 mm_good <- mm_by %>% filter(BY == "Good")
@@
 table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
+mm_bad <- mm_by %>% filter(BY == "Bad")
+table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
 mm_vbad <- mm_by %>% filter(BY == "Very Bad")
 table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
-mm_vgood <- mm_by %>% filter(BY == "Very Good")
-table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
 ```
@@
 
-Table \ref{tab:exp02main} summarizes our results.
+Table \ref{tab:exp02main} summarizes our results. As we see, none of the
+treatment effects are statistically significant at conventional levels. This
+indicates that institutional factors do not affect lynching support in our
+sample.
 
@@
 m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
-m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
+m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
 m1se <- sqrt(diag(m1cov))
@@
 m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
-m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC2"))
+m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
 m2se <- sqrt(diag(m2cov))
@@
 m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
-m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC2"))
+m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
 m3se <- sqrt(diag(m3cov))
@@
 m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
-m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC2"))
+m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
 m4se <- sqrt(diag(m4cov))
@@
           column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
+          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
+```
+\normalsize
+
+\clearpage
+
+## Demographic Characteristics and Lynching Support
+
+Here we evaluate the impact of individual characteristics on lynching support.
+We combine all treatment and control groups and measure whether demographic
+information, which we collected in our questionnaire, changes baseline levels.
+
+```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp02_group <- df_exp02 %>%
+  filter(gender == c("Female", "Male"),
+         race %in% c("Asian", "Black", "Mixed Race", "White"),
+         education %in% c("College", "Graduate School",
+                          "Primary School", "Secondary School", "High School")) %>%
+  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
+                                education == "Secondary School" ~ "Primary or Secondary School",
+                                TRUE ~ as.character(education))) %>%
+  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
+                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
+                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
+                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
+                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
+                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
+                                       household_income == "Above R$20,000" ~ "Above R$5,000",
+                                       TRUE ~ NA_character_))
+
+m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
+m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
+m1se <- sqrt(diag(m1cov))
+
+m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
+m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
+m2se <- sqrt(diag(m2cov))
+
+m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
+m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
+m3se <- sqrt(diag(m3cov))
+
+m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
+m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
+m4se <- sqrt(diag(m4cov))
+
+m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
+m5cov <- coeftest(m5, vcov = vcovHC(m5, type = "HC1"))
+m5se <- sqrt(diag(m5cov))
+
+m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
+m6cov <- coeftest(m6, vcov = vcovHC(m6, type = "HC1"))
+m6se <- sqrt(diag(m6cov))
+
+m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
+m7cov <- coeftest(m7, vcov = vcovHC(m7, type = "HC1"))
+m7se <- sqrt(diag(m7cov))
+
+m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
+m8cov <- coeftest(m8, vcov = vcovHC(m8, type = "HC1"))
+m8se <- sqrt(diag(m8cov))
+
+m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)
+m9cov <- coeftest(m9, vcov = vcovHC(m9, type = "HC1"))
+m9se <- sqrt(diag(m9cov))
+
+stargazer(m1, m2, m3, m4, m5, se = list(m1se, m2se, m3se, m4se, m5se), header = FALSE,
+          align = TRUE, label = "exp02demo1",
+          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
+          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
+          covariate.labels = c("Male", "Age (years)", "Black", "Mixed Race",
+                               "White", "Graduate School", "High School",
+                               "Primary or Secondary School", ""),
+          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
           keep.stat = c("n", "rsq"), no.space = TRUE)
-```
-\normalsize
+
+stargazer(m6, m7, m8, m9, se = list(m6se, m7se, m8se, m9se), header = FALSE,
+          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
+dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
+column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
+keep.stat = c("n", "rsq"), no.space = TRUE)
+```
 

### 2021-02-04 appendix/lynchings.R

@@ -517,6 +517,10 @@ df_exp02 <- df1 %>%
          exp02_small_punishment_treat = case_when(!is.na(exp02_control) ~ "0",
                                                   !is.na(exp02_small_punishment) ~ "1"))
 
+df_exp02 <- df_exp02 %>% mutate(dummy = case_when(exp02_outcomes >= 50 ~ 1,
+                                                  exp02_outcomes < 50 ~ 0,
+                                                  TRUE ~ NA_real_))
+
 m1 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
 m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC2"))
 m1se <- sqrt(diag(m1cov))

### 2021-02-07 appendix/appendix.Rmd
change tables, add some models

@@
 # Install and load required packages
-packages <- c("cjoint", "cregg", "kableExtra",
+packages <- c("cjoint", "cregg", "estimatr", "kableExtra",
               "janitor", "stargazer", "tidyverse")
@@
 m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
-m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
-m1se <- sqrt(diag(m1cov))
-
 m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
-m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
-m2se <- sqrt(diag(m2cov))
-
 m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
-m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
-m3se <- sqrt(diag(m3cov))
-
 m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
-m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
-m4se <- sqrt(diag(m4cov))
-
-stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
-          title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
-          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
+
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
+          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
+          header = FALSE, align = TRUE, label = "exp02main",
+          title = "Experiment 02 -- Main Results", style = "apsr",
+          dep.var.labels = "Lynching Support",
           covariate.labels = c("Police does not patrol area", "Justice too slow",
                                "Punishment not harsh enough", "Combined treatments"),
-          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
-          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
+          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
+          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
 ```
@@
 \clearpage
+
+## Subgroup Analyses
 
@@
 
+\footnotesize
 ```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
@@
   filter(gender == c("Female", "Male"),
-         race %in% c("Asian", "Black", "Mixed Race", "White"),
-         education %in% c("College", "Graduate School",
-                          "Primary School", "Secondary School", "High School")) %>%
+         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
+         education %in% c("College", "Graduate School", "Primary School",
+                          "Secondary School", "High School")) %>%
+  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
+                            "Indigenous")) %>%
   mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                 education == "Secondary School" ~ "Primary or Secondary School",
-                                TRUE ~ as.character(education))) %>%
+                                TRUE ~ as.character(education)),
+         education2 = fct_relevel(education2, "Primary or Secondary School",
+                                  "High School", "College", "Graduate School")) %>%
+  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
+                                    "Bad", "Very Bad")) %>%
+  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good", 
+                                    "Bad", "Very Bad")) %>%
+  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
+                                "Center-Right", "Right", "Don't Know",
+                                "Rather Not Say")) %>%
   mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
@@
                                        household_income == "Above R$20,000" ~ "Above R$5,000",
-                                       TRUE ~ NA_character_))
-
+                                       TRUE ~ NA_character_),
+  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
+                                  "Above R$5,000"))
+
+# Models
 m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
-m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
-m1se <- sqrt(diag(m1cov))
-
 m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
-m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
-m2se <- sqrt(diag(m2cov))
-
 m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
-m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
-m3se <- sqrt(diag(m3cov))
-
 m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
-m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
-m4se <- sqrt(diag(m4cov))
-
 m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
-m5cov <- coeftest(m5, vcov = vcovHC(m5, type = "HC1"))
-m5se <- sqrt(diag(m5cov))
-
 m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
-m6cov <- coeftest(m6, vcov = vcovHC(m6, type = "HC1"))
-m6se <- sqrt(diag(m6cov))
-
 m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
-m7cov <- coeftest(m7, vcov = vcovHC(m7, type = "HC1"))
-m7se <- sqrt(diag(m7cov))
-
 m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
-m8cov <- coeftest(m8, vcov = vcovHC(m8, type = "HC1"))
-m8se <- sqrt(diag(m8cov))
-
 m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)
-m9cov <- coeftest(m9, vcov = vcovHC(m9, type = "HC1"))
-m9se <- sqrt(diag(m9cov))
-
-stargazer(m1, m2, m3, m4, m5, se = list(m1se, m2se, m3se, m4se, m5se), header = FALSE,
-          align = TRUE, label = "exp02demo1",
-          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
-          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
-          covariate.labels = c("Male", "Age (years)", "Black", "Mixed Race",
-                               "White", "Graduate School", "High School",
-                               "Primary or Secondary School", ""),
-          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
-          keep.stat = c("n", "rsq"), no.space = TRUE)
-
-stargazer(m6, m7, m8, m9, se = list(m6se, m7se, m8se, m9se), header = FALSE,
-          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
-dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
-column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
-keep.stat = c("n", "rsq"), no.space = TRUE)
-```
+
+# Tables (robust standard errors from estimatr)
+stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
+          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
+          header = FALSE, align = TRUE, label = "exp02demo1",
+          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
+          dep.var.labels = "Lynching Support",
+          covariate.labels = c("Male", "Age (years)", "Black", "Mixed race",
+                               "Asian", "Indigenous", "High school", "College",
+                               "Graduate school", "3,001 to 5,000 BRL",
+                               "5,000+ BRL"), style = "apsr",
+          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female; 
+                                              Model 3: White; Model 4: Primary or secondary school;",
+                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
+                                              parentheses."),
+          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
+
+stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
+          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
+          header = FALSE, align = TRUE, label = "exp02demo2",
+          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
+          dep.var.labels = "Lynching Support", style = "apsr",
+          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right")
+          column.sep.width = "2pt", notes = "Robust standard error in parentheses.",
+          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
+```
+\normalsize
 

### 2021-02-08 appendix/appendix.Rmd
add text analysis exp01

@@
 # Install and load required packages
-packages <- c("cjoint", "cregg", "estimatr", "kableExtra",
-              "janitor", "stargazer", "tidyverse")
+packages <- c("cjoint", "cregg", "estimatr", "grf", "kableExtra", "janitor",
+              "quanteda", "seededlda", "stargazer", "tidyverse")
 installed_packages <- packages %in% rownames(installed.packages())
@@
 ```
-
-\newpage
+\normalsize
+
+\clearpage
 
@@
 and the respondents' opinions on the judicial system and the police forces. All
-models report marginal means.
+models report marginal means. As we shall see, the results are very robust
+across all model specifications.
 
@@
 
+## Text Analysis
+
+In addition to the conjoint experiments, we also asked respondents to justify
+their profile choices. We added a textbook after each conjoint and informed
+subjects that their responses were optional.
+However, we obtained `r (nrow(df1) - sum(is.na(df1$q13_text))) + (nrow(df1) - sum(is.na(df1$q14_text))) + (nrow(df1) - sum(is.na(df1$q15_text))) + (nrow(df1) - sum(is.na(df1$q16_text))) + (nrow(df1) - sum(is.na(df1$q17_text)))` responses
+in our survey, which we analyze here.
+
+First, we concatenate all text responses into a single vector. Then we tokenize
+the sentences, remove Portuguese stop words and punctuation, and select the
+words that appear most frequently in the texts.
+
+The graphs shows that _crime_ (same as in English), _porque_ (because),
+_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
+often. This is expected as subjects were asked to justify their choices. The
+next words in the list are related to victim or crime characteristics, such as
+_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
+(victim). Indeed, they provide evidence our previous findings and confirm that
+respondents select lynching victim profiles according to these two factors.
+Criminal characteristics, such as age or race, do not seem to be particularly
+relevant, as respondents do not mention them as much. The next words are
+_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
+(have to), and _justiça_ (justice). We believe these words correspond to cases
+where respondents wanted to affirm they do not have any preference regarding
+the lynching profiles, or that they would rather not have chosen any of the
+alternatives.
+
+\footnotesize
+```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles"}
+dfmat <- df1 %>%
+  select(q13_text, q14_text, q15_text, q16_text, q17_text) %>%
+  gather() %>%
+  drop_na() %>%
+  corpus(text_field = "value") %>%
+  tokens(remove_punct = TRUE, remove_numbers = TRUE,
+         remove_symbol = TRUE) %>%
+  dfm() %>%
+  dfm_remove(., pattern = c(stopwords("pt", source = "snowball"),
+                            "é", "ser"))
+
+# Plot
+dfmat %>%
+  textstat_frequency(n = 15) %>%
+  ggplot(aes(x = reorder(feature, frequency), y = frequency)) +
+  geom_point(colour = "#152238") +
+  coord_flip() +
+  labs(x = NULL, y = "Frequency") +
+  theme_minimal()
+```
+\normalsize
+
+We also construct a feature co-occurrence matrix (FCM) that shows which words
+appear together in the responses we collected. Again, the results confirm the
+findings of the conjoint experiment. As suggested in the previous graph, we see
+a central cluster that describe crime and victim characteristics and includes
+the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
+_criança_ (child), _assassinato_ (murder), and _vítima_ (victim). This
+highlights that these are the most important reasons why respondents choose
+lynching profiles.
+
+We also note that there is another word cluster on the left. It contains words
+that indicate that some respondents do not support lynchings, such as _não_
+(no), _opção_ (choice), _nada_ (nothing), _justifica_ (justifies),
+_justificável_ (justifiable), and _escolher_ (choose).
+
+\footnotesize
+```{r conjoint-fcm, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Semantic network analysis"}
+fcmat <- fcm(dfmat)
+feat <- names(topfeatures(fcmat, 70))
+fcmat_select <- fcm_select(fcmat, pattern = feat, selection = "keep")
+size <- log(colSums(dfm_select(dfmat, feat, selection = "keep")))
+
+# Plot
+set.seed(144)
+textplot_network(fcmat_select, min_freq = 0.8, vertex_size = size / max(size) * 3, max.overlaps = 30)
+```
+\normalsize
+
+Lastly, we estimate a latent Dirichlet allocation (LDA) model to identify the
+three most important topics in our corpus. The first topic includes words that
+describes lynching perpetrators, as it contains the words like _polícia_
+(police), _pessoas_ (people), and _família_ (family). The second topic
+identifies the same words we associate with respondents who are against
+lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
+(against). The last topic, in contrast, refer to victim and crime
+characteristics, which have also appeared in our previous estimations. Some of
+the most common words in this group are _crime_ (crime), _criança_ (child),
+_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
+_grave_ (serious), and _molestar_ (molest).
+
+As our results show, respondents decide which individual deserves punishment
+based on factors related to the crime he/she committed, specially the crime
+victim. There is also a group of respondents that oppose lynchings in
+principle, who affirm that lynchings are not justified.
+
+\footnotesize
+```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
+# Latent Dirichlet allocation
+tmod_lda <- textmodel_lda(dfmat, k = 3)
+terms(tmod_lda, 10)
+```
+\normalsize
+
 # Experiment 02
@@
           p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "exp02main",
+          header = FALSE, align = TRUE, label = "tab:exp02main",
           title = "Experiment 02 -- Main Results", style = "apsr",
-          dep.var.labels = "Lynching Support",
+          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
           covariate.labels = c("Police does not patrol area", "Justice too slow",
@@
 
-## Subgroup Analyses
-
 ## Demographic Characteristics and Lynching Support
@@
 df_exp02_group <- df_exp02 %>%
-  filter(gender == c("Female", "Male"),
+  filter(gender %in% c("Female", "Male"),
          race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
@@
           p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "exp02demo1",
+          header = FALSE, align = TRUE, label = "tab:exp02demo1",
           title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
-          dep.var.labels = "Lynching Support",
-          covariate.labels = c("Male", "Age (years)", "Black", "Mixed race",
-                               "Asian", "Indigenous", "High school", "College",
-                               "Graduate school", "3,001 to 5,000 BRL",
-                               "5,000+ BRL"), style = "apsr",
+          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
+          column.labels = c("Gender", "Age", "Race", "Education", "Income"),
+          covariate.labels = c("Male", "Years", "Black", "Mixed Race",
+                               "Asian", "Indigenous", "High School", "College",
+                               "Graduate School", "3,001 to 5,000 BRL", "5,000+ BRL"),
           column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female;
@@
 
+```
+\clearpage
+
+```{r exp02-demographics2, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
 stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
           p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "exp02demo2",
+          header = FALSE, align = TRUE, label = "tab:exp02demo2",
           title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
-          dep.var.labels = "Lynching Support", style = "apsr",
-          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right")
-          column.sep.width = "2pt", notes = "Robust standard error in parentheses.",
-          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
-```
-\normalsize
+          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
+          column.labels = c("Ideology", "Previous Victimization", "Police",
+                            "Judiciary"),
+          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right",
+                               "Don't Know", "Rather Not Say", "Yes",
+                               "Very Good", "Good", "Bad", "Very Bad",
+                               "Don't Know", "Rather Not Say",
+                               "Very Good", "Good", "Bad", "Very Bad",
+                               "Don't Know", "Rather Not Say"),
+          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Center;
+                                              Model 2: No; Model 3: Regular; Model 4: Regular.",
+                                              "Robust standard errors in parentheses."),
+          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
+```
+\normalsize
+
+## Subgroup Analyses
+
+\footnotesize
+```{r exp02-forest, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6, eval=F}
+df_exp02_police <- df_exp02_group %>%
+  select(exp02_outcomes, exp02_police_treat, gender, age, race, education, household_income2, ideology, views_police, views_justice) %>%
+  mutate(exp02_police_treat = as.numeric(exp02_police_treat))
+
+  drop_na()
+
+library(FindIt)
+F1 <-FindIt(model.treat = exp02_outcomes ~ exp02_police_treat,
+            model.main = ~ race,
+            model.int = ~ race,
+            data = df_exp02_police,
+            type = "binary",
+            treat.type = "single")
+
+F1 <-FindIt(model.treat= outcome ~ treat,
+            model.main= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75,
+            model.int= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75, data = LaLonde, type="binary", treat.type="single")
+
+cases <- sample(seq_len(nrow(df_exp02_police)), round(nrow(df_exp02_police) * .6))
+train <- df_exp02_police[cases, ]
+test <- df_exp02_police[-cases, ]
+
+x <- c("age")
+g <- c("gender", "race", "education", "household_income2",
+"ideology", "views_police", "views_justice")
+X2 <- model.matrix(~ 0 + ., train[c(x, g)])
+
+cf <- causal_forest(
+  X = X2,
+  Y = as.numeric(train$exp02_outcomes),
+  W = as.integer(train$exp02_police_treat),
+  num.trees = 1000,
+  seed = 1839
+)
+
+cf %>%
+  variable_importance() %>%
+  as.data.frame() %>%
+  mutate(variable = colnames(cf$X.orig)) %>%
+  arrange(desc(V1))
+
+preds <- predict(
+  object = cf,
+  newdata = model.matrix(~ ., data = test[, 3:ncol(train)]),
+  estimate.variance = TRUE
+)
+
+test$preds <- preds$predictions
+
+ggplot(test, aes(x = views_justice, y = preds)) +
+  geom_point() +
+  geom_smooth(method = "loess", span = 1) +
+  theme_light()
+
+average_treatment_effect(cf, target.sample = "all")
+tree <- get_tree(cf, 1)
+plot(tree)
+
+dr_scores <- double_robust_scores(cf)
+tree <- policy_tree(X2, dr_scores, 3)
+plot(tree)
+plot_htes(preds, ci = TRUE)
+```
 

### 2021-02-09 appendix/appendix.Rmd
add het effects exp02, description exp03

@@
 # Install and load required packages
-packages <- c("cjoint", "cregg", "estimatr", "grf", "kableExtra", "janitor",
-              "quanteda", "seededlda", "stargazer", "tidyverse")
+packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
+              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
 installed_packages <- packages %in% rownames(installed.packages())
@@
 
-\newpage
-
 ## Household Income
@@
 
-We also note that there is another word cluster on the left. It contains words
+We note that there is another word cluster on the left. It contains words
 that indicate that some respondents do not support lynchings, such as _não_
@@
 
-Lastly, we estimate a latent Dirichlet allocation (LDA) model to identify the
+We estimate a latent Dirichlet allocation (LDA) model to identify the
 three most important topics in our corpus. The first topic includes words that
@@
 
+# Models
 m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
@@
 
+# Table
 stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
@@
           column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
-```
-\normalsize
-
-\clearpage
-
-## Demographic Characteristics and Lynching Support
-
-Here we evaluate the impact of individual characteristics on lynching support.
-We combine all treatment and control groups and measure whether demographic
-information, which we collected in our questionnaire, changes baseline levels.
-
-\footnotesize
-```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-df_exp02_group <- df_exp02 %>%
-  filter(gender %in% c("Female", "Male"),
-         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
-         education %in% c("College", "Graduate School", "Primary School",
-                          "Secondary School", "High School")) %>%
+          keep.stat = "n", no.space = TRUE)
+```
+\normalsize
+
+\newpage
+
+## Heterogeneous Effects
+
+We estimate heterogeneous effects for our experiment using Bayesian Additive
+Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
+allow users to detect non-linear interactions and are insensitive to the choice
+of tuning parameters, so they are well-suited to analyze observational and
+experimental data [@green2012modeling]. More specifically, we employ the
+`bartCause` package, which is designed to estimate causal inference models.
+
+### Treatment 01: Police Ineffectiveness
+
+Our results indicate that the effects for this treatment arm is null in every
+model specification. We find no evidence of heterogeneous effects.
+
+\footnotesize
+```{r exp02-bart01, warning=F, error=F, message=F, cache=T}
+df_exp02_het <- df_exp02 %>%
+  filter(gender %in% c("Female", "Male")) %>%
   mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
-                            "Indigenous")) %>%
-  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
-                                education == "Secondary School" ~ "Primary or Secondary School",
-                                TRUE ~ as.character(education)),
-         education2 = fct_relevel(education2, "Primary or Secondary School",
-                                  "High School", "College", "Graduate School")) %>%
-  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad")) %>%
-  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad")) %>%
-  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
-                                "Center-Right", "Right", "Don't Know",
-                                "Rather Not Say")) %>%
-  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
-                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
-                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
-                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
-                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
-                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
-                                       household_income == "Above R$20,000" ~ "Above R$5,000",
-                                       TRUE ~ NA_character_),
-  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
-                                  "Above R$5,000"))
-
-# Models
-m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
-m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
-m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
-m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
-m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
-m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
-m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
-m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
-m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)
-
-# Tables (robust standard errors from estimatr)
-stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
-          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp02demo1",
-          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
-          column.labels = c("Gender", "Age", "Race", "Education", "Income"),
-          covariate.labels = c("Male", "Years", "Black", "Mixed Race",
-                               "Asian", "Indigenous", "High School", "College",
-                               "Graduate School", "3,001 to 5,000 BRL", "5,000+ BRL"),
-          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female;
-                                              Model 3: White; Model 4: Primary or secondary school;",
-                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
-                                              parentheses."),
-          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
-
-```
-\clearpage
-
-```{r exp02-demographics2, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
-          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp02demo2",
-          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}", style = "apsr",
-          column.labels = c("Ideology", "Previous Victimization", "Police",
-                            "Judiciary"),
-          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right",
-                               "Don't Know", "Rather Not Say", "Yes",
-                               "Very Good", "Good", "Bad", "Very Bad",
-                               "Don't Know", "Rather Not Say",
-                               "Very Good", "Good", "Bad", "Very Bad",
-                               "Don't Know", "Rather Not Say"),
-          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Center;
-                                              Model 2: No; Model 3: Regular; Model 4: Regular.",
-                                              "Robust standard errors in parentheses."),
-          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
-```
-\normalsize
-
-## Subgroup Analyses
-
-\footnotesize
-```{r exp02-forest, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6, eval=F}
-df_exp02_police <- df_exp02_group %>%
-  select(exp02_outcomes, exp02_police_treat, gender, age, race, education, household_income2, ideology, views_police, views_justice) %>%
-  mutate(exp02_police_treat = as.numeric(exp02_police_treat))
-
-  drop_na()
-
-library(FindIt)
-F1 <-FindIt(model.treat = exp02_outcomes ~ exp02_police_treat,
-            model.main = ~ race,
-            model.int = ~ race,
-            data = df_exp02_police,
-            type = "binary",
-            treat.type = "single")
-
-F1 <-FindIt(model.treat= outcome ~ treat,
-            model.main= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75,
-            model.int= ~ age+educ+black+hisp+white+marr+nodegr+log.re75+u75, data = LaLonde, type="binary", treat.type="single")
-
-cases <- sample(seq_len(nrow(df_exp02_police)), round(nrow(df_exp02_police) * .6))
-train <- df_exp02_police[cases, ]
-test <- df_exp02_police[-cases, ]
-
-x <- c("age")
-g <- c("gender", "race", "education", "household_income2",
-"ideology", "views_police", "views_justice")
-X2 <- model.matrix(~ 0 + ., train[c(x, g)])
-
-cf <- causal_forest(
-  X = X2,
-  Y = as.numeric(train$exp02_outcomes),
-  W = as.integer(train$exp02_police_treat),
-  num.trees = 1000,
-  seed = 1839
-)
-
-cf %>%
-  variable_importance() %>%
-  as.data.frame() %>%
-  mutate(variable = colnames(cf$X.orig)) %>%
-  arrange(desc(V1))
-
-preds <- predict(
-  object = cf,
-  newdata = model.matrix(~ ., data = test[, 3:ncol(train)]),
-  estimate.variance = TRUE
-)
-
-test$preds <- preds$predictions
-
-ggplot(test, aes(x = views_justice, y = preds)) +
-  geom_point() +
-  geom_smooth(method = "loess", span = 1) +
-  theme_light()
-
-average_treatment_effect(cf, target.sample = "all")
-tree <- get_tree(cf, 1)
-plot(tree)
-
-dr_scores <- double_robust_scores(cf)
-tree <- policy_tree(X2, dr_scores, 3)
-plot(tree)
-plot_htes(preds, ci = TRUE)
-```
-
-\newpage
+                            "Indigenous"),
+         education = fct_relevel(education, "Primary School", "Secondary School",
+                                  "High School", "College", "Graduate School"),
+         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
+                                    "Bad", "Very Bad"),
+         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
+                                     "Bad", "Very Bad"),
+         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
+                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
+         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
+                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
+                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
+                                         "Above R$20,000"),
+         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
+         death_penalty = fct_relevel(death_penalty, "Yes", "No"))
+
+df_exp02_police <- df_exp02_het %>%
+  mutate(exp02_police_treat = as.numeric(exp02_police_treat)) %>%
+  drop_na(exp02_police_treat)
+
+# Gender
+summary(bartc(exp02_outcomes, exp02_police_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp02_outcomes, exp02_police_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp02_outcomes, exp02_police_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp02_outcomes, exp02_police_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp02_outcomes, exp02_police_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp02_outcomes, exp02_police_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp02_outcomes, exp02_police_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp02_outcomes, exp02_police_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 02: Criminal Justice Ineffectiveness
+
+We do not find any evidence of heterogeneous treatment effects in this
+condition either.
+
+\footnotesize
+```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
+df_exp02_slow_justice <- df_exp02_het %>%
+  mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
+  drop_na(exp02_slow_justice_treat)
+
+# Gender
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Race
+# summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
+              # group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
+              # n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 03: Demand for Harsher Legal Punishment
+
+As in the last two series of models, our results show no evidence of
+heterogeneous treatment effects.
+
+\footnotesize
+```{r exp02-bart03, warning=F, error=F, message=F, cache=T}
+df_exp02_small_punishment <- df_exp02_het %>%
+  mutate(exp02_small_punishment_treat = as.numeric(exp02_small_punishment_treat)) %>%
+  drop_na(exp02_small_punishment_treat)
+
+# Gender
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income2,
+              group.by = household_income2, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+# Experiment 03
+
+## Description
+
+Our last experiment measures the effect of information provision on attitudes
+about lynching. In particular, we test whether reminding respondents
+about the legal and social consequences of vigilante justice reduces the
+subjects' level of support for such practice.
+
+The experiment has three treatment conditions and a control group. In all of
+them we present respondents with a short statement affirming that some
+Brazilians support vigilantism under certain conditions. Respondents were asked
+to use 0 to 49 if they disagree, 50 if they neither agree nor disagree, and
+50-100 if they agree with the sentence.
+
+Each of the three treatment groups received a different message about the
+legal or social consequences of lynching in Brazil. In the first treatment
+arm, we informed subjects about how the Brazilian constitution and penal code
+punishes civilian violence. The second treatment group was notified about
+the human rights guarantees enshrined in Brazil's legal framework. The last
+group read a vignette that mentions how lynchings can spark _vendettas_ and
+initiate a cycle of violence in the community. Subjects in the control group
+received no information about the consequences of lynchings. The text shown
+to the control and treatment groups can be read below.
+
+* *Control group*: In Brazil, some people believe that lynching may be
+  justified under certain conditions. To what degree do you agree or disagree
+  that lynching can be justified? Please use the slider below to indicate your
+  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
+  Please use 50 if you neither agree nor disagree.[^control-exp03]
+
+[^control-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
+linchamentos são justificados sob certas condições. O quanto você concorda ou
+discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo
+para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para
+concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem
+discorde.
+
+* *Treatment 01 - Legal punishment for lynching perpetrators*: In Brazil,
+  some people believe that lynching may be justified under certain conditions.
+  **However, the Brazilian constitution and penal code strictly forbid
+  lynching and those involved can be accused of torture or murder**. To what
+  degree do you agree or disagree that lynching can be justified? Please use
+  the slider below to indicate your preference. For disagreement, use 0 to 49;
+  for agreement, use 51 to 100. Please use 50 if you neither agree nor
+  disagree.[^treat01-exp03]
+
+[^treat01-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
+linchamentos são justificados sob certas condições. **Entretanto, a
+constituição e o código penal do Brasil proíbem estritamente os linchamentos e
+os envolvidos podem ser acusados de tortura ou assassinato.** O quanto você
+concorda ou discorda que linchamentos podem ser justificados? Por favor, use a
+barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0
+a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
+nem discorde.
+
+* *Treatment 02 - Human rights*: In Brazil, some people believe that lynching
+  may be justified under certain conditions. **However, the Brazilian
+  constitution states that all individuals have the right of not being
+  tortured, including criminals**. To what degree do you agree or disagree that
+  lynching can be justified? Please use the slider below to indicate your
+  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
+  Please use 50 if you neither agree nor disagree.[^treat02-exp03]
+
+[^treat02-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
+linchamentos são justificados sob certas condições. **Entretanto, a
+constituição do Brasil afirma que todos os indivíduos têm o direito de não
+serem torturados, inclusive criminosos**. O quanto você concorda ou discorda que
+linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar
+sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use
+de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.
+
+* *Treatment 03 - Vendettas*: In Brazil, some people believe that lynching
+  may be justified under certain conditions. **However, lynchings can trigger
+  a new cycle of violence as the family or friends of the victim may retaliate
+  the community**. To what degree do you agree or disagree that lynching can be
+  justified? Please use the slider below to indicate your preference. For
+  disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you
+  neither agree nor disagree.[^treat03-exp03]
+
+[^treat03-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
+linchamentos são justificados sob certas condições. **Entretanto, linchamentos
+podem iniciar um ciclo de violência pois a família ou amigos da vítima podem
+retaliar a comunidade**. O quanto você concorda ou discorda que linchamentos
+podem ser justificados? Por favor, use a barra abaixo para indicar sua
+preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de
+51 a 100. Por favor, use 50 caso você não concorde nem discorde.
+
+## Main Results
+
+Our results are available in table XXX below.
 

### 2021-02-09 appendix/appendix.Rmd
add het fx exp02 and exp03, small edits

@@
 the average marginal component effects (AMCEs) for our conjoint experiment,
-additional subgroup analyses for all three experiments, and a standard report
-which follows APSA's guidelines for experimental research [@gerber2014reporting].
+and additional subgroup analyses for all three experiments.
 
@@
 
-We estimate a latent Dirichlet allocation (LDA) model to identify the
-three most important topics in our corpus. The first topic includes words that
-describes lynching perpetrators, as it contains the words like _polícia_
-(police), _pessoas_ (people), and _família_ (family). The second topic
-identifies the same words we associate with respondents who are against
-lynchings, such as _nenhum_ (none), _opção_ (choice), _não_ (no), and _contra_
-(against). The last topic, in contrast, refer to victim and crime
-characteristics, which have also appeared in our previous estimations. Some of
-the most common words in this group are _crime_ (crime), _criança_ (child),
-_estupro_ (rape), _vítima_ (victim), _porque_ (because), _idoso_ (elderly),
-_grave_ (serious), and _molestar_ (molest).
-
-As our results show, respondents decide which individual deserves punishment
-based on factors related to the crime he/she committed, specially the crime
-victim. There is also a group of respondents that oppose lynchings in
-principle, who affirm that lynchings are not justified.
+We estimate a latent Dirichlet allocation (LDA) model to identify the three
+most important topics in our corpus. The first topic includes words that refer
+to victim and crime characteristics, many of which have also appeared in our
+previous estimations. Some of the most common words in this group are _crime_
+(crime), _criança_ (child), _estupro_ (rape), _vítima_ (victim), _porque_
+(because), _idoso_ (elderly), _grave_ (serious), and _molestar_ (molest). When
+we count the number of topics in the corpus, we see that this is the
+predominant one. The second topic identified by the model describes lynching
+perpetrators, as it contains the words like _polícia_ (police), _pessoas_
+(people), and _família_ (family). The third topic identifies the same words we
+associate with respondents who are against lynchings, such as _nenhum_ (none),
+_opção_ (choice), _não_ (no), and _contra_ (against). As our results show,
+respondents decide which individual deserves punishment based on factors
+related to the crime he/she committed, specially the crime victim. There is
+also a group of respondents that oppose lynchings in principle, who affirm that
+lynchings are never justified.
 
@@
 terms(tmod_lda, 10)
+table(topics(tmod_lda))
 ```
@@
 
+# Previous Victimization
+df_exp02_police2 <- df_exp02_police %>% drop_na(previous_victim_dummy)
+summary(bartc(exp02_outcomes, exp02_police_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_police2,
+              n.chains = 5L, seed = 144))
+
 # Opinion on the Police
@@
 ```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
+# Remove "Indigenous" and "Other" from `race` as they only
+# have 1 observation each. The model cannot be estimated otherwise.
 df_exp02_slow_justice <- df_exp02_het %>%
+  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
   mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
@@
 # Race
-# summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
-              # group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
-              # n.chains = 5L, seed = 144))
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
 
@@
               group.by = death_penalty, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp02_slow_justice2 <- df_exp02_slow_justice %>% drop_na(previous_victim_dummy)
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_slow_justice2,
               n.chains = 5L, seed = 144))
@@
 # Household Income
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income2,
-              group.by = household_income2, group.effects = TRUE, data = df_exp02_small_punishment,
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp02_small_punishment,
               n.chains = 5L, seed = 144))
@@
               group.by = death_penalty, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(previous_victim_dummy)
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_small_punishment2,
               n.chains = 5L, seed = 144))
@@
 
-Our results are available in table XXX below.
+Our results are available in table \ref{tab:exp03main}. Reminding respondents
+of the legal consequences of lynchings has a strong, negative effect on
+individual levels of lynching support. We see a reduction of about 4.5%, which
+corresponds to an 11% change when compared to the baseline levels. Our second
+treatment condition, reminding subjects of human rights guarantees, has no
+statistically significant effect. Informing respondents that lynchings can
+trigger a cycle of violence also has a large negative effect. It decreases
+lynching support by 3%, which is an 8% reduction in comparison with the control
+group. When we combine all treatments, we still detect a negative impact of the
+treatment conditions.
+
+\footnotesize
+```{r exp03-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp03 <- df1 %>%
+  mutate(exp03_outcomes = coalesce(exp03_control, exp03_constitution,
+                                   exp03_rights, exp03_vendetta),
+         exp03_any_treat = case_when(!is.na(exp03_control) ~ "0",
+                                     !is.na(exp03_constitution) ~ "1",
+                                     !is.na(exp03_rights) ~ "1",
+                                     !is.na(exp03_vendetta) ~ "1",
+                                     TRUE ~ NA_character_),
+         exp03_constitution_treat = case_when(!is.na(exp03_control) ~ "0",
+                                              !is.na(exp03_constitution) ~ "1"),
+         exp03_rights_treat = case_when(!is.na(exp03_control) ~ "0",
+                                        !is.na(exp03_rights) ~ "1"),
+         exp03_vendetta_treat = case_when(!is.na(exp03_control) ~ "0",
+                                          !is.na(exp03_vendetta) ~ "1"))
+
+m1 <- lm(exp03_outcomes ~ exp03_constitution_treat, data = df_exp03)
+m2 <- lm(exp03_outcomes ~ exp03_rights_treat, data = df_exp03)
+m3 <- lm(exp03_outcomes ~ exp03_vendetta_treat, data = df_exp03)
+m4 <- lm(exp03_outcomes ~ exp03_any_treat, data = df_exp03)
+
+# Table
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
+          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp03main",
+          title = "Experiment 03 -- Main Results", style = "apsr",
+          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+          covariate.labels = c("Constitution and penal code", "Human rights",
+                               "Vendettas", "Combined treatments"),
+          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
+          keep.stat = "n", no.space = TRUE)
+```
+\normalsize
+
+## Heterogeneous Effects
+
+In this section, we explore whether our pre-treatment covariates impact the
+treatment effect. We use the same flexible approach we employed in the previous
+experiment, and estimate all models using Bayesian Additive Regression Trees
+(BART). The algorithm produces average treatment effects for each category in
+the moderator variables.
+
+### Treatment 01: Legal Punishment for Lynching Perpetrators
+
+We find no evidence of heterogeneous effects in this treatment condition. All
+coefficients are largely similar across all model specifications.
+
+\footnotesize
+```{r exp03-bart01, warning=F, error=F, message=F, cache=T}
+df_exp03_het <- df_exp03 %>%
+  filter(gender %in% c("Female", "Male")) %>%
+  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
+                            "Indigenous"),
+         education = fct_relevel(education, "Primary School", "Secondary School",
+                                  "High School", "College", "Graduate School"),
+         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
+                                    "Bad", "Very Bad"),
+         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
+                                     "Bad", "Very Bad"),
+         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
+                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
+         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
+                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
+                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
+                                         "Above R$20,000"),
+         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
+         death_penalty = fct_relevel(death_penalty, "Yes", "No"))
+
+df_exp03_constitution <- df_exp03_het %>%
+  mutate(exp03_constitution_treat = as.numeric(exp03_constitution_treat)) %>%
+  drop_na(exp03_constitution_treat)
+
+# Gender
+summary(bartc(exp03_outcomes, exp03_constitution_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp03_outcomes, exp03_constitution_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp03_outcomes, exp03_constitution_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp03_outcomes, exp03_constitution_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp03_outcomes, exp03_constitution_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp03_outcomes, exp03_constitution_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(previous_victim_dummy)
+summary(bartc(exp03_outcomes, exp03_constitution_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_constitution2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp03_outcomes, exp03_constitution_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp03_outcomes, exp03_constitution_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 02: Human Rights
+
+Our results show no presence of heterogeneous effects.
+
+\footnotesize
+```{r exp03-bart02, warning=F, error=F, message=F, cache=T}
+df_exp03_rights <- df_exp03_het %>%
+  mutate(exp03_rights_treat = as.numeric(exp03_rights_treat)) %>%
+  drop_na(exp03_rights_treat)
+
+# Gender
+summary(bartc(exp03_outcomes, exp03_rights_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp03_outcomes, exp03_rights_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp03_outcomes, exp03_rights_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp03_outcomes, exp03_rights_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp03_outcomes, exp03_rights_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp03_outcomes, exp03_rights_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp03_rights2 <- df_exp03_rights %>% drop_na(previous_victim_dummy)
+summary(bartc(exp03_outcomes, exp03_rights_treat, previous_victim_dummy, 
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_rights2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp03_outcomes, exp03_rights_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp03_outcomes, exp03_rights_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 03: Vendettas
+
+We do not find considerable heterogeneity in the these results. Overall, the
+three treatment conditions are very stable, thus we are confident that the
+main results are not driven by any particular group.
+
+\footnotesize
+```{r exp03-bart03, warning=F, error=F, message=F, cache=T}
+df_exp03_vendetta <- df_exp03_het %>%
+  mutate(exp03_vendetta_treat = as.numeric(exp03_vendetta_treat)) %>%
+  drop_na(exp03_vendetta_treat)
+
+# Gender
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(previous_victim_dummy)
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, previous_victim_dummy, 
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_vendetta2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+\newpage
 
 # Session Information
-\label{sec:session-info}
 
@@
 \normalsize
-
-\clearpage

### 2021-02-10 appendix/appendix.Rmd
reorder factors desc stats, add age het fx exp02 exp03

@@
 df1 %>%
-  group_by(race) %>%
-  filter(!is.na(race)) %>%
+  rename(Race = race) %>%
+  mutate(Race = fct_relevel(Race, "White", "Other", "Rather Not Say", after = Inf)) %>%
+  group_by(Race) %>%
+  filter(!is.na(Race)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(Race = race) %>%
-  mutate(Race = fct_relevel(Race, "Other", "Rather Not Say", after = Inf)) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Race") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Race") %>%
   row_spec(0, bold = TRUE) %>%
@@
 population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
-About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[5, 3]`%
+About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]*100`%
 have graduate school education.
@@
 df1 %>%
-  group_by(education) %>%
-  filter(!is.na(education)) %>%
+  rename(Education = education) %>%
+  mutate(Education = fct_relevel(Education, "Primary School", "Secondary School",
+                                 "High School", "College", "Graduate School")) %>%
+  group_by(Education) %>%
+  filter(!is.na(Education)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(Education = education) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Education") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Education") %>%
   row_spec(0, bold = TRUE) %>%
@@
 df1 %>%
-  group_by(household_income) %>%
-  filter(!is.na(household_income)) %>%
+  rename(`Household Income` = household_income) %>%
+  mutate(`Household Income` = fct_relevel(`Household Income`, "Up to R$1,000",
+                                          "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
+                                          "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
+                                          "From R$10,001 to R$20,000", "Above R$20,000")) %>%
+  group_by(`Household Income`) %>%
+  filter(!is.na(`Household Income`)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(`Household Income` = household_income) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Household Income") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Household Income") %>%
   row_spec(0, bold = TRUE) %>%
@@
   filter(!is.na(ideology)) %>%
+  mutate(ideology = fct_relevel(ideology, "Left")) %>%
   summarise(N = n()) %>%
@@
 df1 %>%
-  group_by(ideology) %>%
-  filter(!is.na(ideology)) %>%
+  rename(Ideology = ideology) %>%
+  mutate(Ideology = fct_relevel(Ideology, "Left", "Center-Left", "Center",
+                                "Center-Right", "Right")) %>%
+  group_by(Ideology) %>%
+  filter(!is.na(Ideology)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(Ideology = ideology) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Political Ideology") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Political Ideology") %>%
   row_spec(0, bold = TRUE) %>%
@@
 
+\newpage
+
 ## Support for Death Penalty
@@
 df1 %>%
-  group_by(death_penalty) %>%
-  filter(!is.na(death_penalty)) %>%
+  rename(`Support for Death Penalty` = death_penalty) %>%
+  mutate(`Support for Death Penalty` = fct_relevel(`Support for Death Penalty`, "Yes", "No")) %>%
+  group_by(`Support for Death Penalty`) %>%
+  filter(!is.na(`Support for Death Penalty`)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(`Support for Death Penalty` = death_penalty) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Support for Death Penalty") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Support for Death Penalty") %>%
   row_spec(0, bold = TRUE) %>%
@@
 df1 %>%
-  group_by(previous_victim_dummy) %>%
-  filter(!is.na(previous_victim_dummy)) %>%
+  rename(Victimization = previous_victim_dummy) %>%
+  mutate(Victimization = fct_relevel(Victimization, "Yes", "No")) %>%
+  group_by(Victimization) %>%
+  filter(!is.na(Victimization)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(Victimization = previous_victim_dummy) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Previous Victimization (12 Months)") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Previous Victimization (12 Months)") %>%
   row_spec(0, bold = TRUE) %>%
@@
 df1 %>%
-  group_by(views_police) %>%
-  filter(!is.na(views_police)) %>%
+  rename(`Opinion on the Police` = views_police) %>%
+  mutate(`Opinion on the Police` = fct_relevel(`Opinion on the Police`, "Very Good", "Good",
+                                               "Regular", "Bad", "Very Bad")) %>%
+  group_by(`Opinion on the Police`) %>%
+  filter(!is.na(`Opinion on the Police`)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(`Opinion on the Police` = views_police) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Opinion on the Police") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Police") %>%
   row_spec(0, bold = TRUE) %>%
@@
 \normalsize
+
+\newpage
 
@@
 df1 %>%
-  group_by(views_justice) %>%
-  filter(!is.na(views_justice)) %>%
+  rename(`Opinion on the Justice System` = views_justice) %>%
+  mutate(`Opinion on the Justice System` = fct_relevel(`Opinion on the Justice System`, "Very Good",
+                                                       "Good", "Regular", "Bad", "Very Bad")) %>%
+  group_by(`Opinion on the Justice System`) %>%
+  filter(!is.na(`Opinion on the Justice System`)) %>%
   summarise(N = n()) %>%
   mutate(Frequency = round(N / sum(N), 3)) %>%
-  rename(`Opinion on the Judicial System` = views_justice) %>%
-  kbl(., booktabs = TRUE,  linesep = "",
-      caption = "Opinion on the Judicial System") %>%
+  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Justice System") %>%
   row_spec(0, bold = TRUE) %>%
@@
 plot(mms, vline = 0.5, header_fmt = "%s") +
-  theme(legend.position = "none",
-        axis.text.y = element_text(face = faces, size = 10)) +
+  theme(legend.position = "none", axis.text.y = element_text(face = faces, size = 10)) +
   scale_colour_viridis_d(option = "inferno", end = 0.8)
@@
 Criminal characteristics, such as age or race, do not seem to be particularly
-relevant, as respondents do not mention them as much. The next words are
+relevant, as respondents do not mention them as much. The following terms are
 _nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
@@
          previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
-         death_penalty = fct_relevel(death_penalty, "Yes", "No"))
+         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
+         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
+                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
 
@@
               group.by = gender, group.effects = TRUE, data = df_exp02_police,
+              n.chains = 5L, seed = 144))
+
+# Age
+summary(bartc(exp02_outcomes, exp02_police_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp02_police,
               n.chains = 5L, seed = 144))
@@
 
+# Age
+summary(bartc(exp02_outcomes, exp02_slow_justice_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp02_slow_justice,
+              n.chains = 5L, seed = 144))
+
 # Race
@@
               group.by = gender, group.effects = TRUE, data = df_exp02_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Age
+df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(age2)
+summary(bartc(exp02_outcomes, exp02_small_punishment_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp02_small_punishment2,
               n.chains = 5L, seed = 144))
@@
 df_exp03 <- df1 %>%
-  mutate(exp03_outcomes = coalesce(exp03_control, exp03_constitution,
-                                   exp03_rights, exp03_vendetta),
-         exp03_any_treat = case_when(!is.na(exp03_control) ~ "0",
-                                     !is.na(exp03_constitution) ~ "1",
-                                     !is.na(exp03_rights) ~ "1",
-                                     !is.na(exp03_vendetta) ~ "1",
+  mutate(exp03_outcomes = coalesce(exp03_control, exp03_constitution, exp03_rights, exp03_vendetta),
+         exp03_any_treat = case_when(!is.na(exp03_control) ~ "0", !is.na(exp03_constitution) ~ "1",
+                                     !is.na(exp03_rights) ~ "1", !is.na(exp03_vendetta) ~ "1",
                                      TRUE ~ NA_character_),
@@
 # Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE, align = TRUE,
           p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp03main",
-          title = "Experiment 03 -- Main Results", style = "apsr",
+          title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",
           dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
@@
               group.by = gender, group.effects = TRUE, data = df_exp03_constitution,
+              n.chains = 5L, seed = 144))
+
+# Age
+df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(age2)
+summary(bartc(exp03_outcomes, exp03_constitution_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp03_constitution2,
               n.chains = 5L, seed = 144))
@@
 
+# Age
+df_exp03_rights2 <- df_exp03_rights %>% drop_na(age2)
+summary(bartc(exp03_outcomes, exp03_rights_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp03_rights2,
+              n.chains = 5L, seed = 144))
+
 # Race
@@
 
+# Age
+df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(age2)
+summary(bartc(exp03_outcomes, exp03_vendetta_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp03_vendetta2,
+              n.chains = 5L, seed = 144))
+
 # Race
@@
 
-\newpage
-
 # Session Information

### 2021-02-14 appendix/appendix.Rmd
add seeded lda model

@@
 \footnotesize
-```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
-# Latent Dirichlet allocation
+```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
+# Unsupervised LDA
 tmod_lda <- textmodel_lda(dfmat, k = 3)
@@
 table(topics(tmod_lda))
+```
+\normalsize
+
+Our last model is a semisupervised LDA, in which we include a series of
+keywords to measure how frequently some pre-defined topics appear often in the
+responses. We adopt a conservative approach and only include words that we have
+a high degree of confidence that are not ambiguous. There are four pre-defined
+topics in this estimation. The first refers to victims, and include words for
+children, life, and victim (along with possible variations). The second topic
+describes crime characteristics with words such as murder, rape, kill, molest,
+and steal. The next group has four keywords that describe lynching
+perpetrators, and they are gangs, family, bystanders, and police. The fourth
+topic includes terms to identify respondents who are against lynchings, and we
+added against, none, do not agree, and choice as the seed terms. We see that
+these groups have a large number of terms each, and that crime characteristics
+is the topic that shows more often when our terms are applied.
+
+\footnotesize
+```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
+# Semisupervised LDA
+keywords <- dictionary(list(Victim      = c("crian*", "vida*", "v*tima*"),
+                            Crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
+                            Perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
+                            Against     = c("contra", "nenhum*", "n*o concord*", "op**o")))
+
+slda <- textmodel_seededlda(dfmat, keywords, residual = TRUE)
+terms(slda, 10)
+table(topics(slda))
 ```

### 2021-02-14 appendix/appendix.Rmd
small changes to seeded lda model

@@
 a high degree of confidence that are not ambiguous. There are four pre-defined
-topics in this estimation. The first refers to victims, and include words for
-children, life, and victim (along with possible variations). The second topic
-describes crime characteristics with words such as murder, rape, kill, molest,
-and steal. The next group has four keywords that describe lynching
-perpetrators, and they are gangs, family, bystanders, and police. The fourth
-topic includes terms to identify respondents who are against lynchings, and we
-added against, none, do not agree, and choice as the seed terms. We see that
-these groups have a large number of terms each, and that crime characteristics
-is the topic that shows more often when our terms are applied.
+topics in this estimation. The first refers to victims, and include the
+Portuguese words for _children_, _life_, and _victim_ (along with possible
+variations). The second topic describes crime characteristics with words such
+as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
+keywords that describe lynching perpetrators, and they are _gangs_, _family_,
+_bystanders_, and _police_. The fourth topic includes terms to identify
+respondents who are against lynchings, and we added _against_, _none_, _do not
+agree_, and _choice_ as the seed terms. We see that these groups have a large
+number of terms each, and that crime characteristics is the topic that shows
+more often when our terms are applied.
 
@@
 # Semisupervised LDA
-keywords <- dictionary(list(Victim      = c("crian*", "vida*", "v*tima*"),
-                            Crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
-                            Perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
-                            Against     = c("contra", "nenhum*", "n*o concord*", "op**o")))
+keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
+                            crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
+                            perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
+                            against     = c("contra", "escolha", "nenhum*", "n*o concord*", "op**o")))
 

### 2021-02-14 appendix/appendix.Rmd
small changes in the text

@@
 information about whether the subjects had been victimized in the previous 12
-months, as well as their opinion the Brazilian judicial system and the police
-forces. They follow in the graphs and tables below.
+months, as well as their opinion of the Brazilian judicial system and the
+police forces. They follow in the graphs and tables below.
 
@@
 About 98% of the interviewees agreed to participate in the survey experiment.
-We therefore exclude the remaining cases from the dataset.
+We excluded respondents who did not give their consent from the dataset.
 
@@
 
-We asked subjects whether they had victimized in the previous 12 months, as
-crime victims may be more likely to support lynchings. The responses follow
+We asked subjects whether they had been victimized in the previous 12 months,
+as crime victims may be more likely to support lynchings. The responses follow
 below.
@@
 We also estimate AMCE coefficients for our conjoint experiment. This method
-selects one reference category for each attribute and look at changes from the
-baseline level. The reference category are marked as zero in our models.
+selects one reference category for each attribute and looks at changes from the
+baseline level. The reference categories are marked as zero in our models.
 
@@
 "other" in our questionnaire. Across all conjoint experiment attributes, we see
-that an overlap between the 95% confidence intervals for males and females.
+an overlap between the 95% confidence intervals for males and females.
 
@@
 above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
-high-income households. We find no considerable difference amongst them.
+high-income households. We find no considerable differences among them.
 
@@
 "Don't Know" or "Rather Not Say" to our question, so the confidence intervals
-from their estimates are larger than the for the other two categories. The
+from their estimates are larger than for the other two categories. The
 estimates largely overlap across the four groups, although those who answered
@@
 
-Experimental results do not change when we break the responses according to how
-subjects view the police forces.
+Experimental results do not change when we break down the responses according
+to how subjects view the police forces.
 
@@
 In addition to the conjoint experiments, we also asked respondents to justify
-their profile choices. We added a textbook after each conjoint and informed
+their profile choices. We added a text box after each conjoint and informed
 subjects that their responses were optional.
@@
 findings of the conjoint experiment. As suggested in the previous graph, we see
-a central cluster that describe crime and victim characteristics and includes
+a central cluster that describes crime and victim characteristics and includes
 the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
@@
 respondents decide which individual deserves punishment based on factors
-related to the crime he/she committed, specially the crime victim. There is
+related to the crime he/she committed, especially the crime victim. There is
 also a group of respondents that oppose lynchings in principle, who affirm that
@@
 
-Before each vignette, respondents will read the following text:
+Before each vignette, respondents read the following text:
 
@@
 
-After the vignette, respondents will be presented with this question:
-
-* Would you think that the lynching was justified? Please use the slider below
+After the vignette, respondents were presented with this question:
+
+* Do you think that the lynching was justified? Please use the slider below
   to indicate your opinion. For disagreement, use 0 to 49; for agreement,
@@
 treatment effects are statistically significant at conventional levels. This
-indicates that institutional factors do not affect lynching support in our
+suggests that institutional factors do not affect lynching support in our
 sample.
@@
 
-We do not find considerable heterogeneity in the these results. Overall, the
+We do not find considerable heterogeneity in the results. Overall, the
 three treatment conditions are very stable, thus we are confident that the

### 2021-02-15 appendix/appendix.Rmd
copyediting appendix text

@@
 About 98% of the interviewees agreed to participate in the survey experiment.
-We excluded respondents who did not give their consent from the dataset.
+We excluded the remaining 2% from our analyses.
 
@@
 _criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
-(victim). Indeed, they provide evidence our previous findings and confirm that
-respondents select lynching victim profiles according to these two factors.
-Criminal characteristics, such as age or race, do not seem to be particularly
-relevant, as respondents do not mention them as much. The following terms are
-_nenhum_ (none), _contra_ (against), _acho_ (I think), _casos_ (cases), _ter_
-(have to), and _justiça_ (justice). We believe these words correspond to cases
-where respondents wanted to affirm they do not have any preference regarding
-the lynching profiles, or that they would rather not have chosen any of the
-alternatives.
+(victim). Indeed, they provide evidence for our previous findings and confirm
+that respondents select lynching victim profiles according to these two
+factors. Criminal characteristics, such as age or race, do not seem to be
+particularly relevant, as respondents do not mention them as much. The
+following terms are _nenhum_ (none), _contra_ (against), _acho_ (I think),
+_casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe these
+words correspond to cases where respondents wanted to affirm that they do not
+have any preference regarding the lynching profiles, or that they would rather
+not have chosen any of the alternatives.
 
@@
 respondents who are against lynchings, and we added _against_, _none_, _do not
-agree_, and _choice_ as the seed terms. We see that these groups have a large
-number of terms each, and that crime characteristics is the topic that shows
-more often when our terms are applied.
+agree_, and _choice_ as seed terms. We see that the topic describing crime
+characteristics is the one that appears more often.
 

### 2021-02-16 appendix/appendix.Rmd
add robust se with starprep function

@@
 stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
-          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
+          p = starprep(m1, m2, m3, m4, stat = "p.value"),
           header = FALSE, align = TRUE, label = "tab:exp02main",
@@
 \normalsize
-
-\newpage
 
@@
 # Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE, align = TRUE,
-          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE,
+          p = starprep(m1, m2, m3, m4, stat = "p.value"), align = TRUE,
           title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",

### 2021-05-19 appendix/appendix.Rmd
add updated appendix

@@
 title: |
-       | Supplementary Materials for "Casting the First Stone: Understanding Attitudes towards Lynching in Brazil"
+       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
 author:
@@
     number_sections: yes
+    highlight: haddock
     toc: true
@@
 
-[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.
-
-[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, <davidskarbek@brown.edu>, <http://davidskarbek.com>.
+[^freire]: School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <http://danilofreire.github.io>.
+
+[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, <davidskarbek@brown.edu>, <http://davidskarbek.com>.
 
@@
 This appendix contains the `R` code required to replicate the results we
-present in "_Casting the First Stone: Understanding Attitudes towards Lynching
-in Brazil_". This file also includes the descriptive statistics of our sample,
-the average marginal component effects (AMCEs) for our conjoint experiment,
-and additional subgroup analyses for all three experiments.
+present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
+towards Lynching in Brazil_". This file also includes the descriptive
+statistics of our sample, the average marginal component effects (AMCEs) for
+our conjoint experiment, and additional subgroup analyses for all three
+experiments.
 
@@
          views_justice          = as.factor(q12),
-         exp02_control          = as.numeric(q18),
-         exp02_police           = as.numeric(q19),
-         exp02_slow_justice     = as.numeric(q20),
-         exp02_small_punishment = as.numeric(q21),
+         exp01_control          = as.numeric(q18),
+         exp01_police           = as.numeric(q19),
+         exp01_slow_justice     = as.numeric(q20),
+         exp01_small_punishment = as.numeric(q21),
          exp03_control          = as.numeric(q22),
@@
 
-In our first experiment, we present five pairs of criminal profiles to
+In our first experiment, we analyze how respondents justify their preferences
+towards extralegal violence. We assess the impact of three factors that have
+been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
+criminal justice; 3) demand for harsher punishment for criminals. Below, we
+discuss them in further detail.
+
+Research shows that police ineffectiveness frequently appears as a strong
+predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
+result of the weakness of police institutions is that citizens decide to take
+criminal matters "into their own hands", thus persecuting and punishing the
+criminals by themselves. A recent statistic indicates that the police solves
+only 10% of the homicides in Brazil, which lends support to the link between
+weak law enforcement and lynchings [@pearson2018latam].
+
+Another possible determinant of lynching support is lack of trust in the
+justice system [@godoy2004justice; @smith2019contradictions]. This is often due
+to long criminal proceedings, which cause significant anxiety for the victims.
+In Brazil, the penal code allows the accused to appeal each decision several
+times, so it can take decades before a criminal case is closed
+[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
+the criminal is put to trial, he/she will be punished in a timely matter. Note
+that although the police is technically part of the criminal justice system, we
+analyze the two institutions separately in our experiment.
+
+Lastly, we evaluate whether respondents think that the legal punishment
+assigned to criminals is not proportional to the severity of their crimes. In
+particular, we intend to gauge the demand for iron-fisted criminal justice in
+Brazil. Although this treatment arm is related to the previous ones, it
+addresses not the efficiency of the institutions, but their legitimacy
+[@nivette2016institutional]. In fact, Brazilians are often vocal about their
+preference for repressive legal punishment. In a recent article in _The Wall
+Street Journal_, a bar owner justified the lynching of the local thug who
+killed his son by saying that "_even if he had been put behind bars for 100
+years it wouldn't have been enough to pay for all his crimes_"
+[@pearson2018latam]. We hypothesize that many Brazilians also share this view.
+
+The experiment consists of three treatment conditions and one control group.
+Respondents read an excerpt of a news article describing a real lynching case.
+We have slightly edited the original text so that respondents have no prior
+knowledge of the crime.[^jornal] The vignette for the control group includes no
+information about the reasons behind the lynching. We ask respondents to show
+their level of lynching support using a 0-100 slider, where 0 means no support
+and 100 means full support. Respondents in each of the three treatment arms
+read the same piece, but with one additional sentence explaining the
+motivations behind the lynching. The vignettes are as follows:
+
+[^jornal]: The original article is available at the following address:
+<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
+Access: August 2020.
+
+* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
+  According to the neighbours, he tried to break into a house but was
+  immobilised and beaten by members of the community.[^control-exp01]
+
+[^control-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade.
+
+* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
+  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
+  house but was immobilised and beaten by members of the community. **One of
+  the residents who took part in the lynching said they had beaten the suspect
+  because "the police never patrols the area"**.[^treat01-exp01]
+
+[^treat01-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
+nunca patrulha o local".**
+
+* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial system is too slow and the perpetrator is on
+  the street until the case is heard"**.[^treat02-exp01]
+
+[^treat02-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
+é muito lenta e os criminosos ficam soltos até o julgamento"**.
+
+* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
+  into a house but was immobilised and beaten by members of the community.
+  **One of the residents who took part in the lynching said they had beaten the
+  suspect because "the judicial punishment is not harsh
+  enough"**.[^treat03-exp01]
+
+[^treat03-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
+Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
+envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
+da justiça não é dura o suficiente"**.
+
+Before each vignette, respondents read the following text:
+
+* You will be shown a news article. Please read it carefully. After you read
+  the article, we will ask you one question about it.[^vig01-exp01]
+
+[^vig01-exp01]: In Portuguese: Uma notícia será apresentada para você. Por
+favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
+sobre ele.
+
+After the vignette, respondents were presented with this question:
+
+* Do you think that the lynching was justified? Please use the slider below
+  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
+  use 51 to 100. Please use 50 if you neither agree nor
+  disagree.[^vig02-exp01]
+
+[^vig02-exp01]: In Portuguese: Você acha que o linchamento foi correto? Por
+favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
+49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
+discordar.
+
+## Main Results
+
+Table \ref{tab:exp01main} summarizes our results. As we see, none of the
+treatment effects are statistically significant at conventional levels. This
+suggests that institutional factors do not affect lynching support in our
+sample.
+
+\footnotesize
+```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp01 <- df1 %>%
+  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
+                                   exp01_slow_justice, exp01_small_punishment),
+         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
+                                     !is.na(exp01_police) ~ "1",
+                                     !is.na(exp01_slow_justice) ~ "1",
+                                     !is.na(exp01_small_punishment) ~ "1",
+                                     TRUE ~ NA_character_),
+         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
+                                        !is.na(exp01_police) ~ "1"),
+         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
+                                              !is.na(exp01_slow_justice) ~ "1"),
+         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
+                                                  !is.na(exp01_small_punishment) ~ "1"))
+
+# Models
+m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
+m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
+m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
+m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)
+
+# Table
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
+          p = starprep(m1, m2, m3, m4, stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp01main",
+          title = "Experiment 01 -- Main Results", style = "apsr",
+          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+          covariate.labels = c("Police does not patrol area", "Justice too slow",
+                               "Punishment not harsh enough", "Combined treatments"),
+          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
+          keep.stat = "n", no.space = TRUE)
+```
+\normalsize
+
+## Determinants of Baseline Levels
+
+Here we estimate the effect of gender, race, and political ideology on
+lynching support. We find that males, blacks, and mixed race individuals are
+more likely to endorse lynchings when compared to females and whites,
+respectively. Left and center-left voters, in contrast, show lower support for
+lynchings when compared to centrists.
+
+\footnotesize
+```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp01_group <- df_exp01 %>%
+  filter(gender == c("Female", "Male"),
+         race %in% c("Asian", "Black", "Mixed Race", "White"),
+         ideology %in% c("Center", "Center-Left", "Center-Right",
+                         "Left", "Right"))
+
+m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
+m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
+m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
+m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
+         relevel(ideology, ref = "Center"), data = df_exp01_group)
+
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp01baseline",
+          title = "Experiment 01 -- Determinants of Baseline Levels of
+          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
+                               "Left", "Center-Left", "Center-Right", "Right"),
+          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
+          keep.stat = "n", no.space = TRUE)
+```
+\normalsize
+
+## Heterogeneous Effects
+
+We estimate heterogeneous effects for our experiment using Bayesian Additive
+Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
+allow users to detect non-linear interactions and are insensitive to the choice
+of tuning parameters, so they are well-suited to analyze observational and
+experimental data [@green2012modeling]. More specifically, we employ the
+`bartCause` package, which is designed to estimate causal inference models.
+
+### Treatment 01: Police Ineffectiveness
+
+Our results indicate that the effects for this treatment arm is null in every
+model specification. We find no evidence of heterogeneous effects.
+
+\footnotesize
+```{r exp01-bart01, warning=F, error=F, message=F, cache=T}
+df_exp01_het <- df_exp01 %>%
+  filter(gender %in% c("Female", "Male")) %>%
+  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
+                            "Indigenous"),
+         education = fct_relevel(education, "Primary School", "Secondary School",
+                                  "High School", "College", "Graduate School"),
+         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
+                                    "Bad", "Very Bad"),
+         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
+                                     "Bad", "Very Bad"),
+         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
+                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
+         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
+                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
+                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
+                                         "Above R$20,000"),
+         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
+         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
+         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
+                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
+
+df_exp01_police <- df_exp01_het %>%
+  mutate(exp01_police_treat = as.numeric(exp01_police_treat)) %>%
+  drop_na(exp01_police_treat)
+
+# Gender
+summary(bartc(exp01_outcomes, exp01_police_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Age
+summary(bartc(exp01_outcomes, exp01_police_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp01_outcomes, exp01_police_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp01_outcomes, exp01_police_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp01_outcomes, exp01_police_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp01_outcomes, exp01_police_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp01_outcomes, exp01_police_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp01_police2 <- df_exp01_police %>% drop_na(previous_victim_dummy)
+summary(bartc(exp01_outcomes, exp01_police_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_police2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp01_outcomes, exp01_police_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp01_outcomes, exp01_police_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 02: Criminal Justice Ineffectiveness
+
+We do not find any evidence of heterogeneous treatment effects in this
+condition either.
+
+\footnotesize
+```{r exp01-bart02, warning=F, error=F, message=F, cache=T}
+# Remove "Indigenous" and "Other" from `race` as they only
+# have 1 observation each. The model cannot be estimated otherwise.
+df_exp01_slow_justice <- df_exp01_het %>%
+  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
+  mutate(exp01_slow_justice_treat = as.numeric(exp01_slow_justice_treat)) %>%
+  drop_na(exp01_slow_justice_treat)
+
+# Gender
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Age
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp01_slow_justice2 <- df_exp01_slow_justice %>% drop_na(previous_victim_dummy)
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_slow_justice2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+### Treatment 03: Demand for Harsher Legal Punishment
+
+As in the last two series of models, our results show no evidence of
+heterogeneous treatment effects.
+
+\footnotesize
+```{r exp01-bart03, warning=F, error=F, message=F, cache=T}
+df_exp01_small_punishment <- df_exp01_het %>%
+  mutate(exp01_small_punishment_treat = as.numeric(exp01_small_punishment_treat)) %>%
+  drop_na(exp01_small_punishment_treat)
+
+# Gender
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, gender,
+              group.by = gender, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Age
+df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(age2)
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, age2,
+              group.by = age2, group.effects = TRUE, data = df_exp01_small_punishment2,
+              n.chains = 5L, seed = 144))
+
+# Race
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, race,
+              group.by = race, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Education
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, education,
+              group.by = education, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Household Income
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, household_income,
+              group.by = household_income, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Political Ideology
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, ideology,
+              group.by = ideology, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Support for Death Penalty
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, death_penalty,
+              group.by = death_penalty, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Previous Victimization
+df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(previous_victim_dummy)
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, previous_victim_dummy,
+              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_small_punishment2,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Police
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_police,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+
+# Opinion on the Judicial System
+summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_justice,
+              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
+              n.chains = 5L, seed = 144))
+```
+\normalsize
+
+\newpage
+
+# Experiment 02
+
+## Description
+
+In our second experiment, we present five pairs of criminal profiles to
 respondents. Each profile consists of eight attributes: 1) gender of the crime
@@
                                 education == "Secondary School" ~ "Primary or Secondary School",
-                                TRUE ~ education),
+                                TRUE ~ as.character(education)),
          education2 = fct_relevel(education2, "Primary or Secondary School",
@@
                                    views_police == "Don't Know" ~ NA_character_,
-                                   TRUE ~ views_police),
+                                   TRUE ~ as.character(views_police)),
          views_police2 = fct_relevel(views_police2, "Very Good", "Good",
@@
                                     views_justice == "Don't Know" ~ NA_character_,
-                                   TRUE ~ views_justice),
+                                   TRUE ~ as.character(views_justice)),
          views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
@@
   gather() %>%
-  drop_na() %>%
   corpus(text_field = "value") %>%
@@
 
-# Experiment 02
-
-## Description
-
-In our second experiment, we analyze how respondents justify their preferences
-towards extralegal violence. We assess the impact of three factors that have
-been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
-criminal justice; 3) demand for harsher punishment for criminals. Below, we
-discuss them in further detail.
-
-Research shows that police ineffectiveness frequently appears as a strong
-predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
-result of the weakness of police institutions is that citizens decide to take
-criminal matters "into their own hands", thus persecuting and punishing the
-criminals by themselves. A recent statistic indicates that the police solves
-only 10% of the homicides in Brazil, which lends support to the link between
-weak law enforcement and lynchings [@pearson2018latam].
-
-Another possible determinant of lynching support is lack of trust in the
-justice system [@godoy2004justice; @smith2019contradictions]. This is often due
-to long criminal proceedings, which cause significant anxiety for the victims.
-In Brazil, the penal code allows the accused to appeal each decision several
-times, so it can take decades before a criminal case is closed
-[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
-the criminal is put to trial, he/she will be punished in a timely matter. Note
-that although the police is technically part of the criminal justice system, we
-analyze the two institutions separately in our experiment.
-
-Lastly, we evaluate whether respondents think that the legal punishment
-assigned to criminals is not proportional to the severity of their crimes. In
-particular, we intend to gauge the demand for iron-fisted criminal justice in
-Brazil. Although this treatment arm is related to the previous ones, it
-addresses not the efficiency of the institutions, but their legitimacy
-[@nivette2016institutional]. In fact, Brazilians are often vocal about their
-preference for repressive legal punishment. In a recent article in _The Wall
-Street Journal_, a bar owner justified the lynching of the local thug who
-killed his son by saying that "_even if he had been put behind bars for 100
-years it wouldn't have been enough to pay for all his crimes_"
-[@pearson2018latam]. We hypothesize that many Brazilians also share this view.
-
-The experiment consists of three treatment conditions and one control group.
-Respondents read an excerpt of a news article describing a real lynching case.
-We have slightly edited the original text so that respondents have no prior
-knowledge of the crime.[^jornal] The vignette for the control group includes no
-information about the reasons behind the lynching. We ask respondents to show
-their level of lynching support using a 0-100 slider, where 0 means no support
-and 100 means full support. Respondents in each of the three treatment arms
-read the same piece, but with one additional sentence explaining the
-motivations behind the lynching. The vignettes are as follows:
-
-[^jornal]: The original article is available at the following address:
-<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
-Access: August 2020.
-
-* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
-  According to the neighbours, he tried to break into a house but was
-  immobilised and beaten by members of the community.[^control-exp02]
-
-[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade.
-
-* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
-  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
-  house but was immobilised and beaten by members of the community. **One of
-  the residents who took part in the lynching said they had beaten the suspect
-  because "the police never patrols the area"**.[^treat01-exp02]
-
-[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
-nunca patrulha o local".**
-
-* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial system is too slow and the perpetrator is on
-  the street until the case is heard"**.[^treat02-exp02]
-
-[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
-é muito lenta e os criminosos ficam soltos até o julgamento"**.
-
-* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial punishment is not harsh
-  enough"**.[^treat03-exp02]
-
-[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
-da justiça não é dura o suficiente"**.
-
-Before each vignette, respondents read the following text:
-
-* You will be shown a news article. Please read it carefully. After you read
-  the article, we will ask you one question about it.[^vig01-exp02]
-
-[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
-favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
-sobre ele.
-
-After the vignette, respondents were presented with this question:
-
-* Do you think that the lynching was justified? Please use the slider below
-  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
-  use 51 to 100. Please use 50 if you neither agree nor
-  disagree.[^vig02-exp02]
-
-[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
-favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
-49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
-discordar.
-
-## Main Results
-
-Table \ref{tab:exp02main} summarizes our results. As we see, none of the
-treatment effects are statistically significant at conventional levels. This
-suggests that institutional factors do not affect lynching support in our
-sample.
-
-\footnotesize
-```{r exp02-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-df_exp02 <- df1 %>%
-  mutate(exp02_outcomes = coalesce(exp02_control, exp02_police,
-                                   exp02_slow_justice, exp02_small_punishment),
-         exp02_any_treat = case_when(!is.na(exp02_control) ~ "0",
-                                     !is.na(exp02_police) ~ "1",
-                                     !is.na(exp02_slow_justice) ~ "1",
-                                     !is.na(exp02_small_punishment) ~ "1",
-                                     TRUE ~ NA_character_),
-         exp02_police_treat = case_when(!is.na(exp02_control) ~ "0",
-                                        !is.na(exp02_police) ~ "1"),
-         exp02_slow_justice_treat = case_when(!is.na(exp02_control) ~ "0",
-                                              !is.na(exp02_slow_justice) ~ "1"),
-         exp02_small_punishment_treat = case_when(!is.na(exp02_control) ~ "0",
-                                                  !is.na(exp02_small_punishment) ~ "1"))
-
-# Models
-m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
-m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
-m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
-m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
-
-# Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
-          p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp02main",
-          title = "Experiment 02 -- Main Results", style = "apsr",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Police does not patrol area", "Justice too slow",
-                               "Punishment not harsh enough", "Combined treatments"),
-          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
-
-## Heterogeneous Effects
-
-We estimate heterogeneous effects for our experiment using Bayesian Additive
-Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
-allow users to detect non-linear interactions and are insensitive to the choice
-of tuning parameters, so they are well-suited to analyze observational and
-experimental data [@green2012modeling]. More specifically, we employ the
-`bartCause` package, which is designed to estimate causal inference models.
-
-### Treatment 01: Police Ineffectiveness
-
-Our results indicate that the effects for this treatment arm is null in every
-model specification. We find no evidence of heterogeneous effects.
-
-\footnotesize
-```{r exp02-bart01, warning=F, error=F, message=F, cache=T}
-df_exp02_het <- df_exp02 %>%
-  filter(gender %in% c("Female", "Male")) %>%
-  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
-                            "Indigenous"),
-         education = fct_relevel(education, "Primary School", "Secondary School",
-                                  "High School", "College", "Graduate School"),
-         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad"),
-         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
-                                     "Bad", "Very Bad"),
-         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
-                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
-         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
-                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
-                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
-                                         "Above R$20,000"),
-         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
-         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
-         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
-                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
-
-df_exp02_police <- df_exp02_het %>%
-  mutate(exp02_police_treat = as.numeric(exp02_police_treat)) %>%
-  drop_na(exp02_police_treat)
-
-# Gender
-summary(bartc(exp02_outcomes, exp02_police_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp02_outcomes, exp02_police_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp02_outcomes, exp02_police_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp02_outcomes, exp02_police_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp02_outcomes, exp02_police_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp02_outcomes, exp02_police_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp02_outcomes, exp02_police_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp02_police2 <- df_exp02_police %>% drop_na(previous_victim_dummy)
-summary(bartc(exp02_outcomes, exp02_police_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_police2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp02_outcomes, exp02_police_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp02_outcomes, exp02_police_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_police,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-### Treatment 02: Criminal Justice Ineffectiveness
-
-We do not find any evidence of heterogeneous treatment effects in this
-condition either.
-
-\footnotesize
-```{r exp02-bart02, warning=F, error=F, message=F, cache=T}
-# Remove "Indigenous" and "Other" from `race` as they only
-# have 1 observation each. The model cannot be estimated otherwise.
-df_exp02_slow_justice <- df_exp02_het %>%
-  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
-  mutate(exp02_slow_justice_treat = as.numeric(exp02_slow_justice_treat)) %>%
-  drop_na(exp02_slow_justice_treat)
-
-# Gender
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp02_slow_justice2 <- df_exp02_slow_justice %>% drop_na(previous_victim_dummy)
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_slow_justice2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp02_outcomes, exp02_slow_justice_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_slow_justice,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-### Treatment 03: Demand for Harsher Legal Punishment
-
-As in the last two series of models, our results show no evidence of
-heterogeneous treatment effects.
-
-\footnotesize
-```{r exp02-bart03, warning=F, error=F, message=F, cache=T}
-df_exp02_small_punishment <- df_exp02_het %>%
-  mutate(exp02_small_punishment_treat = as.numeric(exp02_small_punishment_treat)) %>%
-  drop_na(exp02_small_punishment_treat)
-
-# Gender
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(age2)
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp02_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp02_small_punishment2 <- df_exp02_small_punishment %>% drop_na(previous_victim_dummy)
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp02_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp02_outcomes, exp02_small_punishment_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp02_small_punishment,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
 # Experiment 03
@@
 \footnotesize
-```{r session, cache=TRUE}
+```{r session, cache=T}
 sessionInfo()

### 2021-05-19 pre-analysis-plan/freire-skarbek-lynching.tex
add pdfs and translations

--- 2020-10-30 pre-analysis-plan/freire-skarbek-lynching.Rmd
@@
----
-title:  |
-        | Pre-Analysis Plan:
-        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil[^thanks]
-author:
-  - Danilo Freire[^freire]
-  - David Skarbek[^skarbek]
-date: \today
-abstract: "Why do citizens support extrajudicial violence?
-While endorsement for vigilantism has significantly decreased in advanced democracies, lynchings remain tolerated throughout the developing world.
-In this pre-analysis plan, we propose three survey experiments to investigate (i) which criminal profiles citizens prefer for extralegal punishment, (ii) how individuals justify mob violence, and (iii) whether information provision reduces support for vigilantism.
-First, we run a conjoint experiment to identify criminal characteristics that are associated with higher likelihood of lynching.
-In our second experiment, we show respondents a short article about a real lynching episode and ask them whether they see the mob's motivations as legitimate.
-Lastly, we test whether providing information about the legal consequences of lynching, human rights guarantees, and the risk of retribution makes respondents less likely to endorse extralegal violence.
-We will run the experiments in Brazil, a country which has seen a sharp rise in vigilante attacks and currently experiences one lynching attempt per day.
-Our survey will be conducted online and include 2,000 participants."
-abstractspacing: double
-keywords: Brazil, crime, extralegal violence, lynching, vigilantism
-fontsize: 12pt
-margin: 2cm
-urlcolor: darkblue
-linkcolor: Mahogany
-citecolor: Mahogany
-spacing: double
-papersize: a4paper
-bibliography: references.bib
-biblio-style: apalike
-output:
-  pdf_document:
-    citation_package: natbib
-    fig_caption: yes
-    number_sections: yes
-    keep_tex: no
-    toc: no
-    toc_depth: 3
-    template: template.latex
----
+% !TEX program = XeLaTeX
+\documentclass[12pt,a4paper,]{article}
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-# If you need to install any package while knitting the document
-r <- getOption("repos")
-r["CRAN"] <- "https://cran.rstudio.com/"
-options(repos = r)
-if (!require("kableExtra")) {
-    install.packages("kableExtra")
+% Fonts
+\usepackage{libertine}
+% This is a nice mathfont, it fits well with Libertine
+% Comment the line if you want to use a different one
+\usepackage[libertine]{newtxmath}
+% The default monofont 
+% Again, comment the line below if you want to change it
+\usepackage[scaled=.95]{inconsolata}
+
+% Add the following packages to support kableExtra
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{etoolbox}
+\usepackage{tocloft}
+
+% Dots in toc
+\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
+
+% Colours
+\usepackage[usenames,dvipsnames]{xcolor}
+\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
+
+% Spacing
+\usepackage{setspace}
+
+% Margin
+\usepackage[margin=2cm]{geometry}
+
+% Packages I've been using for different reasons...
+\usepackage{hyperref}
+\usepackage{dcolumn}
+\usepackage{graphicx}
+\usepackage{float}
+\floatplacement{figure}{H}
+\usepackage{pgf}
+\usepackage{tikz}
+\usetikzlibrary{arrows}
+\usetikzlibrary{positioning}
+\usepackage{mathtools}
+\usepackage{caption}
+
+% UK English
+\usepackage[UKenglish]{babel}
+\usepackage[UKenglish]{isodate}
+\cleanlookdateon
+
+% Penalties
+\exhyphenpenalty=1000
+\hyphenpenalty=1000
+\widowpenalty=1000
+\clubpenalty=1000
+
+% Hypersetup
+\hypersetup{
+  linkcolor=Mahogany,
+  citecolor=Mahogany,
+  urlcolor=darkblue, 
+  breaklinks=true, 
+  colorlinks=true,
+      pdfauthor={Danilo Freire; David Skarbek},
+      pdfkeywords={Brazil, crime, extralegal violence, lynching, vigilantism},
   }
-```
 
-[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto
-Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their
-valuable comments. This pre-analysis plan received IRB approval from Brown
-University in October 2020 (Protocol 2009002803).
+% If XeTex, LuaLaTeX, etc
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{amssymb,amsmath}
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown
-University, 8 Fones Alley, Providence, RI 02912,
-[`danilofreire@gmail.com`](mailto:danilofreire@gmail.com),
-<https://danilofreire.github.io>.
+% Language
 
-[^skarbek]: The Department of Political Science and the Political Theory
-Project, Brown University, 8 Fones Alley, Providence, RI 02912, USA,
-[`david_skarbek@brown.edu`](mailto:david_skarbek@brown.edu),
-<http://davidskarbek.com>.
+% Bibliography
+\usepackage{natbib}
+\bibliographystyle{apalike}
+\makeatletter
+% Remove comma after author
+\setcitestyle{aysep={}}
+\patchcmd{\NAT@citex}
+	  {\@citea\NAT@hyper@{%
+		 \NAT@nmfmt{\NAT@nm}%
+		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+		 \NAT@date}}
+	  {\@citea\NAT@nmfmt{\NAT@nm}%
+	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+	\patchcmd{\NAT@citex}
+	  {\@citea\NAT@hyper@{%
+		 \NAT@nmfmt{\NAT@nm}%
+		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+		   {\@citeb\@extra@b@citeb}%
+		 \NAT@date}}
+	  {\@citea\NAT@nmfmt{\NAT@nm}%
+	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+	  {}{}
+% Patch case where name and year are separated by aysep
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+% Patch case where name and year are separated by opening bracket
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+       {\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+  {}{}
+\makeatother
 
+% Listings
+
+% Verbatim
+
+% Tables
+
+% Graphics
+
+% Make links footnotes instead of hotlinks:
+%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
+ \providecommand{\tightlist}{%
+   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Numbered sections
+\setcounter{secnumdepth}{5}
+% % % Redefines (sub)paragraphs to behave more like sections
+% \ifx\paragraph\undefined\else
+% \let\oldparagraph\paragraph
+% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+% \fi
+% \ifx\subparagraph\undefined\else
+% \let\oldsubparagraph\subparagraph
+% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+% \fi
+% 
+% Spacing
+\doublespacing
+
+% Title
+\title{Pre-Analysis Plan:\\
+Casting the First Stone: Understanding Attitudes towards Lynching in
+Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Miriam Golden,
+  Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco
+  for their valuable comments. This pre-analysis plan received IRB
+  approval from Brown University in October 2020 (Protocol 2009002803).}}
+
+% Author
+\author{Danilo Freire\footnote{Postdoctoral Research Associate, The Political
+  Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912,
+  \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}},
+  \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{The Department of Political Science and the
+  Political Theory Project, Brown University, 8 Fones Alley, Providence,
+  RI 02912, USA,
+  \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}},
+  \url{http://davidskarbek.com}.}}
+
+% Date
+\date{\today}
+
+% Begin document
+\begin{document}
+\maketitle
+
+% Abstract
+\begin{abstract}
+\doublespacing \noindent Why do citizens support extrajudicial violence? While endorsement for
+vigilantism has significantly decreased in advanced democracies,
+lynchings remain tolerated throughout the developing world. In this
+pre-analysis plan, we propose three survey experiments to investigate
+(i) which criminal profiles citizens prefer for extralegal punishment,
+(ii) how individuals justify mob violence, and (iii) whether information
+provision reduces support for vigilantism. First, we run a conjoint
+experiment to identify criminal characteristics that are associated with
+higher likelihood of lynching. In our second experiment, we show
+respondents a short article about a real lynching episode and ask them
+whether they see the mob's motivations as legitimate. Lastly, we test
+whether providing information about the legal consequences of lynching,
+human rights guarantees, and the risk of retribution makes respondents
+less likely to endorse extralegal violence. We will run the experiments
+in Brazil, a country which has seen a sharp rise in vigilante attacks
+and currently experiences one lynching attempt per day. Our survey will
+be conducted online and include 2,000 participants.
+\vspace{.25cm}
+
+\noindent \textbf{Keywords}: Brazil, crime, extralegal violence, lynching, vigilantism
+\vspace{.25cm}
+
+\end{abstract}
+
+% Table of Contents
 \newpage
 
-# Motivation
+\hypertarget{motivation}{%
+\section{Motivation}\label{motivation}}
+
 \label{sec:motivation}
@@
 
-Why do citizens endorse extralegal punishment?[^definitions] Although mob
-violence has decreased in advanced democracies, vigilantism remains widespread
-in the developing world. In particular, Latin America has been severely
-affected by a recent increase in lynchings. Motivated by growing numbers of
-drug-related crime and by police ineffectiveness, citizen violence has surged
-in the region [@mallen2014vigilantes]. Brazil provides a telling example. From
-2011 to 2015, the country registered about 2,500 lynching episodes, and in 2015
-alone 173 people were killed by angry mobs, an average of one execution every
-two days [@barbara2015vigilantes; @oliveira2016mob]. According to José Martins,
-who has studied lynchings in Brazil for more than 30 years, those figures are
-not only the highest in the country's history, but also the highest in the
-world [@pearson2018latam]. Victims are generally accused of petty theft, and
-many are beaten to death for stealing mobile phones, cooking utensils, or pairs
-of sandals [@barbara2015vigilantes]. Lynching perpetrators are often young men,
-but they also include female teenagers, elderly women, and even members of
-local police forces [@moura2017linchamentos; @oliveira2016mob].
+Why do citizens endorse extralegal punishment?\footnote{Here we consider
+  extralegal violence, vigilantism, lynching, and related terms as
+  synonyms. We follow \citet[6]{moncada2017varieties} and define
+  vigilantism as ``the collective use or threat of extralegal violence
+  in response to an alleged criminal act''. While we focus here on
+  vigilantism that directly involves physical violence, we make no
+  distinction between lethal and non-lethal lynching episodes.} Although
+mob violence has decreased in advanced democracies, vigilantism remains
+widespread in the developing world. In particular, Latin America has
+been severely affected by a recent increase in lynchings. Motivated by
+growing numbers of drug-related crime and by police ineffectiveness,
+citizen violence has surged in the region \citep{mallen2014vigilantes}.
+Brazil provides a telling example. From 2011 to 2015, the country
+registered about 2,500 lynching episodes, and in 2015 alone 173 people
+were killed by angry mobs, an average of one execution every two days
+\citep{barbara2015vigilantes, oliveira2016mob}. According to José
+Martins, who has studied lynchings in Brazil for more than 30 years,
+those figures are not only the highest in the country's history, but
+also the highest in the world \citep{pearson2018latam}. Victims are
+generally accused of petty theft, and many are beaten to death for
+stealing mobile phones, cooking utensils, or pairs of sandals
+\citep{barbara2015vigilantes}. Lynching perpetrators are often young
+men, but they also include female teenagers, elderly women, and even
+members of local police forces
+\citep{moura2017linchamentos, oliveira2016mob}.
 
-[^definitions]: Here we consider extralegal violence, vigilantism, lynching,
-and related terms as synonyms. We follow @moncada2017varieties [6] and define
-vigilantism as "the collective use or threat of extralegal violence in response
-to an alleged criminal act". While we focus here on vigilantism that directly
-involves physical violence, we make no distinction between lethal and
-non-lethal lynching episodes.
+Recent research suggests that support for vigilantism in Latin America
+is associated with exposure to violence \citep{garcia2019anger},
+untrustworthy law enforcement \citep{zizumbo2017community}, perceived
+insecurity \citep{ceobanu2011crime, godoy2004justice}, and social
+inequality \citep{arias2010violent}. However, approval for extrajudicial
+violence raises important questions about the relationship between
+states and societies in the region \citep{nivette2016institutional}.
+First, while vigilantism provides social order to vulnerable
+populations, it also undermines the legitimacy of state institutions
+\citep{schuberth2013challenging}. Lynching episodes reinforce the idea
+that civilians should not wait for legal proceedings and that social
+control is better exerted by the people themselves
+\citep{black1983crime}. Second, victim characteristics greatly impact
+the likelihood and severity of lynchings. In Brazil, a person is rarely
+lynched when they commit a crime against males, and females that commit
+the same crimes as males also receive less punishment.\footnote{See
+  \url{https://revistapesquisa.fapesp.br/en/mob-injustice}. Access:
+  June, 2020.} Moreover, there is no significant social difference
+between victims and perpetrators, nor are black Brazilians particularly
+targeted by lynch mobs \citep{oliveira2016mob}. These dynamics pose a
+puzzle to existing explanations for mob violence support and stand in
+sharp contrast with the American experience
+\citep{smaangs2016doing, wood2011lynching}.
 
-Recent research suggests that support for vigilantism in Latin America is
-associated with exposure to violence [@garcia2019anger], untrustworthy law
-enforcement [@zizumbo2017community], perceived insecurity [@ceobanu2011crime;
-@godoy2004justice], and social inequality [@arias2010violent]. However,
-approval for extrajudicial violence raises important questions about the
-relationship between states and societies in the region
-[@nivette2016institutional]. First, while vigilantism provides social order to
-vulnerable populations, it also undermines the legitimacy of state institutions
-[@schuberth2013challenging]. Lynching episodes reinforce the idea that
-civilians should not wait for legal proceedings and that social control is
-better exerted by the people themselves [@black1983crime]. Second, victim
-characteristics greatly impact the likelihood and severity of lynchings. In
-Brazil, a person is rarely lynched when they commit a crime against males, and
-females that commit the same crimes as males also receive less
-punishment.[^fapesp] Moreover, there is no significant social difference
-between victims and perpetrators, nor are black Brazilians particularly
-targeted by lynch mobs [@oliveira2016mob]. These dynamics pose a puzzle to
-existing explanations for mob violence support and stand in sharp contrast with
-the American experience [@smaangs2016doing; @wood2011lynching].
+In this study, we endeavour to answer the following questions: 1) which
+victim characteristics increase individual support for extralegal
+punishment?; 2) how do individuals justify their approval for
+vigilantism?; and 3) can information provision reduce support for mob
+violence? We design a set of three experiments to tackle these issues.
+Our first experiment consists of a conjoint analysis in which we show
+respondents different profiles of lynching victims and ask them who they
+believe deserve punishment. In our second experiment, we test how
+ineffective policing, slow criminal justice systems, and demand for
+hasher legal punishment affect individual propensity to support mob
+violence. Finally, we assess whether citizens become less supportive of
+vigilantism when they are informed about the legal consequences of
+lynchings, constitutional human rights, or the risk of \emph{vendettas}
+associated with mob violence. While in this pre-analysis plan we present
+the three experiments as described above, we will randomised their order
+in our survey to mitigate potential order bias.
 
-[^fapesp]: See <https://revistapesquisa.fapesp.br/en/mob-injustice>. Access:
-June, 2020.
+\hypertarget{experiment-01}{%
+\section{Experiment 01}\label{experiment-01}}
 
-In this study, we endeavour to answer the following questions: 1) which victim
-characteristics increase individual support for extralegal punishment?; 2) how
-do individuals justify their approval for vigilantism?; and 3) can information
-provision reduce support for mob violence? We design a set of three experiments
-to tackle these issues. Our first experiment consists of a conjoint analysis in
-which we show respondents different profiles of lynching victims and ask them
-who they believe deserve punishment. In our second experiment, we test how
-ineffective policing, slow criminal justice systems, and demand for hasher
-legal punishment affect individual propensity to support mob violence. Finally,
-we assess whether citizens become less supportive of vigilantism when they are
-informed about the legal consequences of lynchings, constitutional human
-rights, or the risk of _vendettas_ associated with mob violence. While in this
-pre-analysis plan we present the three experiments as described above, we will
-randomised their order in our survey to mitigate potential order bias.
-
-# Experiment 01
 \label{sub:exp01}
 
-We start our analysis with a choice-based conjoint experimental design. We will
-present five pairs of criminal profiles to respondents. Each profile consists
-of eight attributes: 1) gender of the crime perpetrator; 2) age of the crime
-perpetrator; 3) race of the crime perpetrator; 4) residency of crime
-perpetrator; 5) offense; 6) gender of the victim of the motivating crime; 7)
-age of the victim of the motivating crime; 8) lynching perpetrators. The
-attributes and levels are displayed in table \ref{tab:categories} below.
+We start our analysis with a choice-based conjoint experimental design.
+We will present five pairs of criminal profiles to respondents. Each
+profile consists of eight attributes: 1) gender of the crime
+perpetrator; 2) age of the crime perpetrator; 3) race of the crime
+perpetrator; 4) residency of crime perpetrator; 5) offense; 6) gender of
+the victim of the motivating crime; 7) age of the victim of the
+motivating crime; 8) lynching perpetrators. The attributes and levels
+are displayed in table \ref{tab:categories} below.
 
@@
 Respondents have to indicate which profile they prefer for extrajudicial
-punishment. We will also include a qualitative textbox below each experiment
-for subjects to explain why they selected their case or whether they believe
-neither alternative is appropriate.
+punishment. We will also include a qualitative textbox below each
+experiment for subjects to explain why they selected their case or
+whether they believe neither alternative is appropriate.
 
-Respondents will read the following prompt before they start the experiment:
+Respondents will read the following prompt before they start the
+experiment:
 
-* Lynchings are often used as social punishment in Brazil. Lynchings are cases
-  in which three or more people physically attack or execute a suspected
-  criminal in public. We are interested in knowing more about how Brazilians
-  see these episodes. In the next five questions, please read the description
-  of two possible lynching victims in Brazil and indicate in which case you
-  believe the punishment is more justified. Even if you are not entirely sure,
-  please select one of the cases.[^portuguese]
+\begin{itemize}
+\tightlist
+\item
+  Lynchings are often used as social punishment in Brazil. Lynchings are
+  cases in which three or more people physically attack or execute a
+  suspected criminal in public. We are interested in knowing more about
+  how Brazilians see these episodes. In the next five questions, please
+  read the description of two possible lynching victims in Brazil and
+  indicate in which case you believe the punishment is more justified.
+  Even if you are not entirely sure, please select one of the
+  cases.\footnote{We will conduct the survey experiments in Portuguese.
+    The translation for the first experiment is as follows: Linchamentos
+    são às vezes usados como punição social no Brasil. Linchamentos são
+    casos nos quais três ou mais pessoas agridem fisicamente ou executam
+    em público um suspeito de um crime. Estamos interessados em saber
+    mais sobre como os brasileiros vêem estes episódios. Nas próximas
+    cinco questões, por favor, leia a descrição de duas possíveis
+    vítimas de linchamento no Brasil e indique em quais delas você
+    acredita que a punição é mais justificada. Mesmo que você não tenha
+    certeza, por favor, escolha um dos casos.}
+\end{itemize}
 
-[^portuguese]: We will conduct the survey experiments in Portuguese. The
-translation for the first experiment is as follows: Linchamentos são às vezes
-usados como punição social no Brasil. Linchamentos são casos nos quais três ou
-mais pessoas agridem fisicamente ou executam em público um suspeito de um
-crime. Estamos interessados em saber mais sobre como os brasileiros vêem estes
-episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
-possíveis vítimas de linchamento no Brasil e indique em quais delas você
-acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
-por favor, escolha um dos casos.
+\hypertarget{sample}{%
+\subsection{Sample}\label{sample}}
 
-## Sample
 \label{sub:sample}
@@
 We invite respondents from all regions of Brazil to participate in our
-experiment. Qualtrics will recruit 2,000 adult Brazilian citizens to take part
-in our survey experiment.
+experiment. Qualtrics will recruit 2,000 adult Brazilian citizens to
+take part in our survey experiment.
 
-We will also include 15 questions on demographics that we believe may influence
-the results. The questions are: 1) the respondent's age, 2) gender, 3) state of
-birth, 4) state they currently live in, 5) ethnicity, 6) level of education, 7)
-religion (if any), 8) monthly family income in minimum wages, 9) political
-orientation (left to right), 10) support for death penalty, 11) whether they
-had been victimised in the last year, 12) whether they believe crime has
-worsened, 13) whether they believe militias improve law and order, 14) trust in
-the police, 15) trust in the judicial system.
+We will also include 15 questions on demographics that we believe may
+influence the results. The questions are: 1) the respondent's age, 2)
+gender, 3) state of birth, 4) state they currently live in, 5)
+ethnicity, 6) level of education, 7) religion (if any), 8) monthly
+family income in minimum wages, 9) political orientation (left to
+right), 10) support for death penalty, 11) whether they had been
+victimised in the last year, 12) whether they believe crime has
+worsened, 13) whether they believe militias improve law and order, 14)
+trust in the police, 15) trust in the judicial system.
 
-## Estimation
+\hypertarget{estimation}{%
+\subsection{Estimation}\label{estimation}}
+
 \label{sub:estimation}
 
-We will estimate our models with the `cregg` package [@leeper2018cregg] for the
-R statistical language [@rstats2019]. We will report marginal means and average
-marginal component effects (AMCEs) in our main analysis. However,
-@leeper2018subgroup show that AMCEs can be misleading in subgroup comparisons
-as model results are sensitive to the choice of reference categories in
-interactions. In contrast, marginal means provide a clear description of
-quantities of interest, in our case preferences towards lynching, while
-allowing for easy comparisons between groups of respondents. So while we will
-include both AMCEs and marginal means estimators in our article, we will
-conduct our subgroup analysis using only the latter. We will cluster standard
-errors by respondent.
+We will estimate our models with the \texttt{cregg} package
+\citep{leeper2018cregg} for the R statistical language
+\citep{rstats2019}. We will report marginal means and average marginal
+component effects (AMCEs) in our main analysis. However,
+\citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup
+comparisons as model results are sensitive to the choice of reference
+categories in interactions. In contrast, marginal means provide a clear
+description of quantities of interest, in our case preferences towards
+lynching, while allowing for easy comparisons between groups of
+respondents. So while we will include both AMCEs and marginal means
+estimators in our article, we will conduct our subgroup analysis using
+only the latter. We will cluster standard errors by respondent.
 
-## Hypotheses
+\hypertarget{hypotheses}{%
+\subsection{Hypotheses}\label{hypotheses}}
+
 \label{sec:hypotheses}
 
-We expect that, on average, respondents are more likely to select profiles with
-the following attributes levels:
+We expect that, on average, respondents are more likely to select
+profiles with the following attributes levels:
 
-1) Gender of crime perpetrator: male 
-2) Age of crime perpetrator: teenager
-3) Race of crime perpetrator: blacks
-4) Residency of crime perpetrator: outsider
-5) Offense: murder
-6) Gender of victim: female 
-7) Age of victim: child
-8) Lynching perpetrators: the family of the victim
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Gender of crime perpetrator: male
+\item
+  Age of crime perpetrator: teenager
+\item
+  Race of crime perpetrator: blacks
+\item
+  Residency of crime perpetrator: outsider
+\item
+  Offense: murder
+\item
+  Gender of victim: female
+\item
+  Age of victim: child
+\item
+  Lynching perpetrators: the family of the victim
+\end{enumerate}
 
-We also expect that support for extralegal punishment will be lower for females
-of any age, whites and Asians, pick pocketers, and if the victim of the
-motivating crime is male. Additionally, we expect that respondents see
-lynchings as less legitimate if they are carried out by bystanders, gangs, or
-the police forces. We have no prior beliefs about the size of each coefficient.
+We also expect that support for extralegal punishment will be lower for
+females of any age, whites and Asians, pick pocketers, and if the victim
+of the motivating crime is male. Additionally, we expect that
+respondents see lynchings as less legitimate if they are carried out by
+bystanders, gangs, or the police forces. We have no prior beliefs about
+the size of each coefficient.
 
-## Heterogeneous Effects
+\hypertarget{heterogeneous-effects}{%
+\subsection{Heterogeneous Effects}\label{heterogeneous-effects}}
+
 \label{sub:het01}
@@
 We also intend to run subgroup analysis in our sample. We believe that
-preferences towards lynching may vary according to age, gender, race, level of
-education, political ideology, and previous victimisation. In particular, we
-hypothesise that:
+preferences towards lynching may vary according to age, gender, race,
+level of education, political ideology, and previous victimisation. In
+particular, we hypothesise that:
 
-* Younger respondents believe that lynchings by the police are less justified.
+\begin{itemize}
+\item
+  Younger respondents believe that lynchings by the police are less
+  justified.
+\item
+  Female respondents believe that lynchings against females are less
+  justified.
+\item
+  Respondents of a particular race are less likely to choose individuals
+  of the same race as lynching victims.
+\item
+  More educated individuals show less support for lynchings against
+  petty criminals.
+\item
+  Political ideology has no effect on support for lynchings when the
+  victim is female.
+\item
+  Right-wingers show stronger support for lynchings against males than
+  left-wingers.
+\item
+  Respondents who were victimised in the last year are more likely to
+  support lynchings by neighbours and the police.
+\end{itemize}
 
-* Female respondents believe that lynchings against females are less justified.
+\hypertarget{experiment-02}{%
+\section{Experiment 02}\label{experiment-02}}
 
-* Respondents of a particular race are less likely to choose individuals of
-  the same race as lynching victims.
+In our second experiment, we analyse how respondents justify their
+preferences for extralegal violence. We assess the impact of three
+factors that have been cited as major drivers of vigilante justice in
+Brazil: 1) police ineffectiveness; 2) slow criminal justice; 3) demand
+for harsher punishment for criminals. Below, we discuss them in further
+detail.
 
-* More educated individuals show less support for lynchings against petty
-  criminals.
+Research shows that police ineffectiveness frequently appears as a
+strong predictor for vigilantism
+\citep{cruz2019determinants, garcia2019anger}. The direct result of the
+weakness of police institutions is that citizens decide to take criminal
+matters ``into their own hands'', thus persecuting and punishing the
+criminals by themselves. A recent statistic indicates that the police
+solve only 10\% of the homicides in Brazil, what lends support to the
+link between weak law enforcement and lynchings
+\citep{pearson2018latam}.
 
-* Political ideology has no effect on support for lynchings when the victim is
-  female.
-
-* Right-wingers show stronger support for lynchings against males than
-  left-wingers.
-
-* Respondents who were victimised in the last year are more likely to support
-  lynchings by neighbours and the police.
-
-# Experiment 02
-
-In our second experiment, we analyse how respondents justify their preferences
-for extralegal violence. We assess the impact of three factors that have been
-cited as major drivers of vigilante justice in Brazil: 1) police
-ineffectiveness; 2) slow criminal justice; 3) demand for harsher punishment for
-criminals. Below, we discuss them in further detail.
-
-Research shows that police ineffectiveness frequently appears as a strong
-predictor for vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
-result of the weakness of police institutions is that citizens decide to take
-criminal matters "into their own hands", thus persecuting and punishing the
-criminals by themselves. A recent statistic indicates that the police solve
-only 10% of the homicides in Brazil, what lends support to the link between
-weak law enforcement and lynchings [@pearson2018latam].
-
-Another determinant of support for vigilante justice that is suggested in the
-literature is the lack of trust in the justice system [@godoy2004justice;
-@smith2019contradictions]. This is often due to long criminal proceedings,
-which cause significant anxiety for the victims. In Brazil, the penal code
-allows the accused to appeal each decision several times, so it can take
-decades before a criminal case is closed [@sousa2005utilizaccao]. In this
-respect, citizens do not believe that, even if the criminal is put to trial,
-he/she will be punished in a timely matter. Note that although the police is
-part of the criminal justice system, we separate the two institutions in our
+Another determinant of support for vigilante justice that is suggested
+in the literature is the lack of trust in the justice system
+\citep{godoy2004justice, smith2019contradictions}. This is often due to
+long criminal proceedings, which cause significant anxiety for the
+victims. In Brazil, the penal code allows the accused to appeal each
+decision several times, so it can take decades before a criminal case is
+closed \citep{sousa2005utilizaccao}. In this respect, citizens do not
+believe that, even if the criminal is put to trial, he/she will be
+punished in a timely matter. Note that although the police is part of
+the criminal justice system, we separate the two institutions in our
 experiment.
@@
 Lastly, we evaluate whether respondents think that the legal punishment
-assigned to criminals is not proportional to the severity of their crimes. In
-particular, we hope to gauge the demand for iron-fisted criminal justice in
-Brazil. Although this treatment arm is related to the previous ones, it
-addresses not the efficiency of the institutions, but their legitimacy
-[@nivette2016institutional]. We believe that the demand for harsher laws is on
-the rise in Brazil, and this may be a major reason why citizens justify their
-support for mob violence. In fact, Brazilians are often vocal about their
-preference for repressive legal punishment. In a recent article in _The Wall
-Street Journal_, a bar owner justified the lynching of the local thug who
-killed his son by saying that "_even if he had been put behind bars for 100
-years it wouldn't have been enough to pay for all his crimes_"
-[@pearson2018latam]. We hypothesise that many Brazilians also share this view.
+assigned to criminals is not proportional to the severity of their
+crimes. In particular, we hope to gauge the demand for iron-fisted
+criminal justice in Brazil. Although this treatment arm is related to
+the previous ones, it addresses not the efficiency of the institutions,
+but their legitimacy \citep{nivette2016institutional}. We believe that
+the demand for harsher laws is on the rise in Brazil, and this may be a
+major reason why citizens justify their support for mob violence. In
+fact, Brazilians are often vocal about their preference for repressive
+legal punishment. In a recent article in \emph{The Wall Street Journal},
+a bar owner justified the lynching of the local thug who killed his son
+by saying that ``\emph{even if he had been put behind bars for 100 years
+it wouldn't have been enough to pay for all his crimes}''
+\citep{pearson2018latam}. We hypothesise that many Brazilians also share
+this view.
 
-The experiment consists of three treatment conditions and one control group.
-Respondents will read an excerpt of a news article describing a real lynching
-case. We have slightly edited the original text so that respondents have no
-prior knowledge of the crime.[^jornal] The vignette for the control group
-includes no information about the reasons behind the lynching. We will ask
-respondents to show their level of support for mob violence using a 0-100
-slider, where 0 means no support and 100 means full support. Respondents in
-each of the three treatment arms will read the same piece, but with one
-additional sentence explaining the motivations behind the lynching. The
-vignettes are as follows:
+The experiment consists of three treatment conditions and one control
+group. Respondents will read an excerpt of a news article describing a
+real lynching case. We have slightly edited the original text so that
+respondents have no prior knowledge of the crime.\footnote{The original
+  article is available at the following address:
+  \url{https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso}.
+  Access: August 2020.} The vignette for the control group includes no
+information about the reasons behind the lynching. We will ask
+respondents to show their level of support for mob violence using a
+0-100 slider, where 0 means no support and 100 means full support.
+Respondents in each of the three treatment arms will read the same
+piece, but with one additional sentence explaining the motivations
+behind the lynching. The vignettes are as follows:
 
-[^jornal]: The original article is available at the following address:
-<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
-Access: August 2020.
+\begin{itemize}
+\tightlist
+\item
+  \emph{Control group}: A man was lynched last Friday in Jundiaí, São
+  Paulo. According to the neighbours, he tried to break into a house but
+  was immobilised and beaten by members of the community.\footnote{In
+    Portuguese: Um homem foi linchado na última sexta-feira em Jundiaí,
+    São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+    mas foi imobilizado e agredido por membros da comunidade.}
+\end{itemize}
 
-* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
-  According to the neighbours, he tried to break into a house but was
-  immobilised and beaten by members of the community.[^control-exp02]
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 01 - Police ineffectiveness}: A man was lynched last
+  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to
+  break into a house but was immobilised and beaten by members of the
+  community. \textbf{One of the residents who took part in the lynching
+  said they had beaten the suspect because ``the police never patrols
+  the area''}.\footnote{In Portuguese: Um homem foi linchado na última
+    sexta-feira em Jundiaí, São Paulo. De acordo com vizinhos, ele
+    tentou invadir uma residência mas foi imobilizado e agredido por
+    membros da comunidade. \textbf{Um dos moradores envolvidos no
+    linchamento disse que eles agrediram o suspeito porque ``a polícia
+    nunca patrulha o local''.}}
+\end{itemize}
 
-[^control-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade.
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 02 - Criminal justice ineffectiveness}: A man was
+  lynched last Friday in Jundiaí, São Paulo. According to the
+  neighbours, he tried to break into a house but was immobilised and
+  beaten by members of the community. \textbf{One of the residents who
+  took part in the lynching said they had beaten the suspect because
+  ``the judicial system is too slow and the perpetrator is on the street
+  until the case is heard''}.\footnote{In Portuguese: Um homem foi
+    linchado na última sexta-feira em Jundiaí, São Paulo. De acordo com
+    vizinhos, ele tentou invadir uma residência mas foi imobilizado e
+    agredido por membros da comunidade. \textbf{Um dos moradores
+    envolvidos no linchamento disse que eles agrediram o suspeito porque
+    ``a justiça é muito lenta e os criminosos ficam soltos até o
+    julgamento''}.}
+\end{itemize}
 
-* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
-  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
-  house but was immobilised and beaten by members of the community. **One of
-  the residents who took part in the lynching said they had beaten the suspect
-  because "the police never patrols the area"**.[^treat01-exp02]
-
-[^treat01-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
-nunca patrulha o local".**
-
-* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial system is too slow and the perpetrator is on
-  the street until the case is heard"**.[^treat02-exp02]
-
-[^treat02-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
-é muito lenta e os criminosos ficam soltos até o julgamento"**.
-
-* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial punishment is not harsh
-  enough"**.[^treat03-exp02]
-
-[^treat03-exp02]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
-da justiça não é dura o suficiente"**.
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 03 - Demand for harsher legal punishment}: A man was
+  lynched last Friday in Jundiaí, São Paulo. According to the
+  neighbours, he tried to break into a house but was immobilised and
+  beaten by members of the community. \textbf{One of the residents who
+  took part in the lynching said they had beaten the suspect because
+  ``the judicial punishment is not harsh enough''}.\footnote{In
+    Portuguese: Um homem foi linchado na última sexta-feira em Jundiaí,
+    São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
+    mas foi imobilizado e agredido por membros da comunidade. \textbf{Um
+    dos moradores envolvidos no linchamento disse que eles agrediram o
+    suspeito porque ``a punição da justiça não é dura o suficiente''}.}
+\end{itemize}
 
@@
 
-* You will be shown a news article. Please read it carefully. After you read
-  the article, we will ask you one question about it.[^vig01-exp02]
-
-[^vig01-exp02]: In Portuguese: Uma notícia será apresentada para você. Por
-favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
-sobre ele.
+\begin{itemize}
+\tightlist
+\item
+  You will be shown a news article. Please read it carefully. After you
+  read the article, we will ask you one question about it.\footnote{In
+    Portuguese: Uma notícia será apresentada para você. Por favor, leia
+    a notícia com atenção. Após você ler o artigo, faremos uma pergunta
+    sobre ele.}
+\end{itemize}
 
@@
 
-* Would you think that the lynching was justified? Please use the slider below
-  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
-  use 51 to 100. Please use 50 if you neither agree nor
-  disagree.[^vig02-exp02]
+\begin{itemize}
+\tightlist
+\item
+  Would you think that the lynching was justified? Please use the slider
+  below to indicate your opinion. For disagreement, use 0 to 49; for
+  agreement, use 51 to 100. Please use 50 if you neither agree nor
+  disagree.\footnote{In Portuguese: Você acha que o linchamento foi
+    correto? Por favor, use a barra abaixo para indicar sua opinião.
+    Para discordar, use de 0 a 49; para concordar, use de 51 a 100. Por
+    favor, use 50 para não concordar nem discordar.}
+\end{itemize}
 
-[^vig02-exp02]: In Portuguese: Você acha que o linchamento foi correto? Por
-favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
-49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
-discordar.
+\hypertarget{sample-1}{%
+\subsection{Sample}\label{sample-1}}
 
-## Sample
+We will randomise the treatment and control conditions to the entire
+respondent pool. The randomisation procedure here is independent of that
+of the previous experiment.
 
-We will randomise the treatment and control conditions to the entire respondent
-pool. The randomisation procedure here is independent of that of the previous
-experiment.
+\hypertarget{estimation-1}{%
+\subsection{Estimation}\label{estimation-1}}
 
-## Estimation
+We will carry out our hypothesis tests with OLS. We will compare the
+average score given by the control group with the average score
+attributed by respondents in each treatment condition. We will use
+robust standard errors for all the models.
 
-We will carry out our hypothesis tests with OLS. We will compare the average
-score given by the control group with the average score attributed by
-respondents in each treatment condition. We will use robust standard errors for
-all the models.
-
-## Hypotheses
+\hypertarget{hypotheses-1}{%
+\subsection{Hypotheses}\label{hypotheses-1}}
 
@@
 
-\noindent _H1_: Respondents assigned to the _police ineffectiveness_ treatment
-group will show stronger support for lynchings when compared to the control
-group. We believe that the effect will be smaller than for the other two
-treatment conditions.
+\noindent \emph{H1}: Respondents assigned to the \emph{police
+ineffectiveness} treatment group will show stronger support for
+lynchings when compared to the control group. We believe that the effect
+will be smaller than for the other two treatment conditions.
 
@@
 
-\noindent _H2_: Respondents assigned to the _criminal justice ineffectiveness_
-treatment group will show stronger support for lynchings when compared to the
-control group. We hypothesise that the effect for this group will be higher
-than that of the first treatment condition but lower than that of the third
-treatment group.
+\noindent \emph{H2}: Respondents assigned to the \emph{criminal justice
+ineffectiveness} treatment group will show stronger support for
+lynchings when compared to the control group. We hypothesise that the
+effect for this group will be higher than that of the first treatment
+condition but lower than that of the third treatment group.
 
@@
 
-\noindent _H3_: Respondents assigned to the _demand for harsher punishment_
-treatment group will show the strongest support for lynchings.
+\noindent \emph{H3}: Respondents assigned to the \emph{demand for
+harsher punishment} treatment group will show the strongest support for
+lynchings.
 
-## Heterogeneous Effects
+\hypertarget{heterogeneous-effects-1}{%
+\subsection{Heterogeneous Effects}\label{heterogeneous-effects-1}}
 
-We hypothesise that these respondents are more likely to agree that lynchings
-are justified:
+We hypothesise that these respondents are more likely to agree that
+lynchings are justified:
 
-1) Older citizens
-2) White
-3) Low levels of education
-4) Right-wingers
-5) Individuals who had been previously victimised
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Older citizens
+\item
+  White
+\item
+  Low levels of education
+\item
+  Right-wingers
+\item
+  Individuals who had been previously victimised
+\end{enumerate}
 
-# Experiment 03
+\hypertarget{experiment-03}{%
+\section{Experiment 03}\label{experiment-03}}
 
-Our last experiment aims to measure the effect of information provision on
-attitudes about lynching. More specifically, we will test whether reminding
-respondents about the legal and social consequences of vigilante justice reduces
-the subjects' level of support for such practice.
+Our last experiment aims to measure the effect of information provision
+on attitudes about lynching. More specifically, we will test whether
+reminding respondents about the legal and social consequences of
+vigilante justice reduces the subjects' level of support for such
+practice.
 
-The experiment has three treatment conditions and a control group. In all of
-them we will present respondents with a short statement affirming that some
-Brazilians support vigilantism under certain conditions. The control group will
-be asked to rate their agreement with the statement with a 0-100 slider where
-100 indicates full agreement with the statement and 0 indicates no agreement.
-Respondents will be asked to use 0 to 49 if they disagree, 50 if they neither
-agree nor disagree, and 50-100 if they agree with the sentence.
+The experiment has three treatment conditions and a control group. In
+all of them we will present respondents with a short statement affirming
+that some Brazilians support vigilantism under certain conditions. The
+control group will be asked to rate their agreement with the statement
+with a 0-100 slider where 100 indicates full agreement with the
+statement and 0 indicates no agreement. Respondents will be asked to use
+0 to 49 if they disagree, 50 if they neither agree nor disagree, and
+50-100 if they agree with the sentence.
 
-Each of the three treatment groups will receive a different message about the
-legal or social consequences of lynching in Brazil. In the first treatment
-arm, we will inform subjects about how the Brazilian constitution and penal code
-punishes civilian violence. The second treatment group will be notified about
-the human rights guarantees enshrined in Brazil's legal framework. The last
-group will read a vignette that mentions how lynchings can spark _vendettas_ and
-initiate a cycle of violence in the community. Subjects in the control group
-will receive no information about the consequences of lynchings. The text shown
-to the control and treatment groups can be read below.
+Each of the three treatment groups will receive a different message
+about the legal or social consequences of lynching in Brazil. In the
+first treatment arm, we will inform subjects about how the Brazilian
+constitution and penal code punishes civilian violence. The second
+treatment group will be notified about the human rights guarantees
+enshrined in Brazil's legal framework. The last group will read a
+vignette that mentions how lynchings can spark \emph{vendettas} and
+initiate a cycle of violence in the community. Subjects in the control
+group will receive no information about the consequences of lynchings.
+The text shown to the control and treatment groups can be read below.
 
-* *Control group*: In Brazil, some people believe that lynching may be
-  justified under certain conditions. To what degree do you agree or disagree
-  that lynching can be justified? Please use the slider below to indicate your
-  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
-  Please use 50 if you neither agree nor disagree.[^control-exp03]
+\begin{itemize}
+\tightlist
+\item
+  \emph{Control group}: In Brazil, some people believe that lynching may
+  be justified under certain conditions. To what degree do you agree or
+  disagree that lynching can be justified? Please use the slider below
+  to indicate your preference. For disagreement, use 0 to 49; for
+  agreement, use 51 to 100. Please use 50 if you neither agree nor
+  disagree.\footnote{In Portuguese: No Brasil, algumas pessoas acreditam
+    que linchamentos são justificados sob certas condições. O quanto
+    você concorda ou discorda que linchamentos podem ser justificados?
+    Por favor, use a barra abaixo para indicar sua preferência. Para
+    indicar que discorda, use de 0 a 49; para concordar, use de 51 a
+    100. Por favor, use 50 caso você não concorde nem discorde.}
+\end{itemize}
 
-[^control-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
-linchamentos são justificados sob certas condições. O quanto você concorda ou
-discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo
-para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para
-concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem
-discorde.
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 01 - Legal punishment for lynching perpetrators}: In
+  Brazil, some people believe that lynching may be justified under
+  certain conditions. \textbf{However, the Brazilian constitution and
+  penal code strictly forbid lynching and those involved can be accused
+  of torture or murder}. To what degree do you agree or disagree that
+  lynching can be justified? Please use the slider below to indicate
+  your preference. For disagreement, use 0 to 49; for agreement, use 51
+  to 100. Please use 50 if you neither agree nor disagree.\footnote{In
+    Portuguese: No Brasil, algumas pessoas acreditam que linchamentos
+    são justificados sob certas condições. \textbf{Entretanto, a
+    constituição e o código penal do Brasil proíbem estritamente os
+    linchamentos e os envolvidos podem ser acusados de tortura ou
+    assassinato.} O quanto você concorda ou discorda que linchamentos
+    podem ser justificados? Por favor, use a barra abaixo para indicar
+    sua preferência. Para indicar que discorda, use de 0 a 49; para
+    concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
+    nem discorde.}
+\end{itemize}
 
-* *Treatment 01 - Legal punishment for lynching perpetrators*: In Brazil,
-  some people believe that lynching may be justified under certain conditions.
-  **However, the Brazilian constitution and penal code strictly forbid
-  lynching and those involved can be accused of torture or murder**. To what
-  degree do you agree or disagree that lynching can be justified? Please use
-  the slider below to indicate your preference. For disagreement, use 0 to 49;
-  for agreement, use 51 to 100. Please use 50 if you neither agree nor
-  disagree.[^treat01-exp03]
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 02 - Human rights}: In Brazil, some people believe
+  that lynching may be justified under certain conditions.
+  \textbf{However, the Brazilian constitution states that all
+  individuals have the right of not being tortured, including
+  criminals}. To what degree do you agree or disagree that lynching can
+  be justified? Please use the slider below to indicate your preference.
+  For disagreement, use 0 to 49; for agreement, use 51 to 100. Please
+  use 50 if you neither agree nor disagree.\footnote{In Portuguese: No
+    Brasil, algumas pessoas acreditam que linchamentos são justificados
+    sob certas condições. \textbf{Entretanto, a constituição do Brasil
+    afirma que todos os indivíduos têm o direito de não serem
+    torturados, inclusive criminosos}. O quanto você concorda ou
+    discorda que linchamentos podem ser justificados? Por favor, use a
+    barra abaixo para indicar sua preferência. Para indicar que
+    discorda, use de 0 a 49; para concordar, use de 51 a 100. Por favor,
+    use 50 caso você não concorde nem discorde.}
+\end{itemize}
 
-[^treat01-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
-linchamentos são justificados sob certas condições. **Entretanto, a
-constituição e o código penal do Brasil proíbem estritamente os linchamentos e
-os envolvidos podem ser acusados de tortura ou assassinato.** O quanto você
-concorda ou discorda que linchamentos podem ser justificados? Por favor, use a
-barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0
-a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
-nem discorde.
+\begin{itemize}
+\tightlist
+\item
+  \emph{Treatment 03 - Vendettas}: In Brazil, some people believe that
+  lynching may be justified under certain conditions. \textbf{However,
+  lynchings can trigger a new cycle of violence as the family or friends
+  of the victim may retaliate the community}. To what degree do you
+  agree or disagree that lynching can be justified? Please use the
+  slider below to indicate your preference. For disagreement, use 0 to
+  49; for agreement, use 51 to 100. Please use 50 if you neither agree
+  nor disagree.\footnote{In Portuguese: No Brasil, algumas pessoas
+    acreditam que linchamentos são justificados sob certas condições.
+    \textbf{Entretanto, linchamentos podem iniciar um ciclo de violência
+    pois a família ou amigos da vítima podem retaliar a comunidade}. O
+    quanto você concorda ou discorda que linchamentos podem ser
+    justificados? Por favor, use a barra abaixo para indicar sua
+    preferência. Para indicar que discorda, use de 0 a 49; para
+    concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
+    nem discorde.}
+\end{itemize}
 
-* *Treatment 02 - Human rights*: In Brazil, some people believe that lynching
-  may be justified under certain conditions. **However, the Brazilian
-  constitution states that all individuals have the right of not being
-  tortured, including criminals**. To what degree do you agree or disagree that
-  lynching can be justified? Please use the slider below to indicate your
-  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
-  Please use 50 if you neither agree nor disagree.[^treat02-exp03]
+\hypertarget{sample-2}{%
+\subsection{Sample}\label{sample-2}}
 
-[^treat02-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
-linchamentos são justificados sob certas condições. **Entretanto, a
-constituição do Brasil afirma que todos os indivíduos têm o direito de não
-serem torturados, inclusive criminosos**. O quanto você concorda ou discorda que
-linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar
-sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use
-de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.
+We will randomise the treatment and control conditions to all subjects
+included in our sample. The treatment assignment here is independent of
+that of the previous two experiments.
 
-* *Treatment 03 - Vendettas*: In Brazil, some people believe that lynching
-  may be justified under certain conditions. **However, lynchings can trigger
-  a new cycle of violence as the family or friends of the victim may retaliate
-  the community**. To what degree do you agree or disagree that lynching can be
-  justified? Please use the slider below to indicate your preference. For
-  disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you
-  neither agree nor disagree.[^treat03-exp03]
+\hypertarget{estimation-2}{%
+\subsection{Estimation}\label{estimation-2}}
 
-[^treat03-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
-linchamentos são justificados sob certas condições. **Entretanto, linchamentos
-podem iniciar um ciclo de violência pois a família ou amigos da vítima podem
-retaliar a comunidade**. O quanto você concorda ou discorda que linchamentos
-podem ser justificados? Por favor, use a barra abaixo para indicar sua
-preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de
-51 a 100. Por favor, use 50 caso você não concorde nem discorde.
+We are interested in the difference between the average score assigned
+by each of the treatment groups minus the average score assigned by the
+control group. We will estimate average treatment effects using OLS with
+dummy indicators for the treatment groups.
 
-## Sample
-
-We will randomise the treatment and control conditions to all subjects included
-in our sample. The treatment assignment here is independent of that of the
-previous two experiments.
-
-## Estimation
-
-We are interested in the difference between the average score assigned by each
-of the treatment groups minus the average score assigned by the control group.
-We will estimate average treatment effects using OLS with dummy indicators for
-the treatment groups.
-
-## Hypotheses
+\hypertarget{hypotheses-2}{%
+\subsection{Hypotheses}\label{hypotheses-2}}
 
@@
 
-\noindent _H1_: Individuals who receive information about the criminal
-consequences of lynching show lower support for vigilantism that those in the
-control group.
+\noindent \emph{H1}: Individuals who receive information about the
+criminal consequences of lynching show lower support for vigilantism
+that those in the control group.
 
@@
 
-\noindent _H2_: Reminding respondents that torture violates human rights has no
-impact on their support for vigilantism.
+\noindent \emph{H2}: Reminding respondents that torture violates human
+rights has no impact on their support for vigilantism.
 
@@
 
-\noindent _H3_: Information about _vendettas_ triggered by lynchings makes
-individuals less likely to support vigilantism in comparison with respondents in
-the control group. The effect of that information is larger than the other
-two treatments.
+\noindent \emph{H3}: Information about \emph{vendettas} triggered by
+lynchings makes individuals less likely to support vigilantism in
+comparison with respondents in the control group. The effect of that
+information is larger than the other two treatments.
 
@@
 
-These three hypotheses allow us to test how respondents react to different
-consequences of extralegal violence. Hopefully, the experiment may also help
-policy-makers design more effective campaigns against vigilantism in Brazil.
+These three hypotheses allow us to test how respondents react to
+different consequences of extralegal violence. Hopefully, the experiment
+may also help policy-makers design more effective campaigns against
+vigilantism in Brazil.
 
-## Heterogeneous Effects
+\hypertarget{heterogeneous-effects-2}{%
+\subsection{Heterogeneous Effects}\label{heterogeneous-effects-2}}
 
-As with the previous two experiments, we will measure whether our treatments
-have heterogeneous effects. The same demographic characteristics we describe
-above -- age, gender, race, education level, political ideology, and previous
-victimisation -- will also be used here.
+As with the previous two experiments, we will measure whether our
+treatments have heterogeneous effects. The same demographic
+characteristics we describe above -- age, gender, race, education level,
+political ideology, and previous victimisation -- will also be used
+here.
 
@@
 \setlength{\parskip}{5pt}
+
+% More bibliography
+\bibliography{references.bib}
+
+\end{document}

### 2021-06-16 appendix/appendix-short.Rmd
first draft

--- 2021-05-19 appendix/appendix.Rmd
@@
 title: |
-       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
+       | Supplementary Material for "Vigilantism, Institutions, and Honor Culture: Understanding Attitudes toward Lynching in Brazil"
 author:
@@
 bibliography: ../article/references.bib
-biblio-style: apalike
+biblio-style: ../article/chicago-ff.bst
 output:
@@
 
-\newpage
-
-# Introduction
-
-This appendix contains the `R` code required to replicate the results we
-present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
-towards Lynching in Brazil_". This file also includes the descriptive
-statistics of our sample, the average marginal component effects (AMCEs) for
-our conjoint experiment, and additional subgroup analyses for all three
-experiments.
-
-The code below loads the required datasets and the `R` packages we use in our
-statistical analyses. It also translates the names of the factor variables from
-Portuguese into English.
-
-\footnotesize
-```{r loading, warning=F, message=F, error=F, cache=T}
+\appendix
+
+# Descriptive Statistics
+
+```{r loading, warning=F, message=F, error=F, cache=T, echo=F}
 # Install and load required packages
@@
 
-# Check for duplicated values
-count(get_dupes(df))
-```
-\normalsize
-
-# Descriptive Statistics
-
-```{r sample-size, echo=F, warning=F, error=F, message=F, cache=T}
 df1 <- df %>% filter(consent == "Agree")
 ```
+
+This appendix contains additional tables and graphs that complement the results
+we present in "_Vigilantism, Institutions, and Honor Culture: Understanding
+Attitudes towards Lynching in Brazil_". An extended version of this file, which
+includes further tests for heterogeneous effects and `R` code, is available at
+[_redacted for peer review_]. The repository also contains our pre-analysis
+plan and the `php` scripts we used in our conjoint experiment.
 
@@
 five regions of the country (Center-West, North, Northeast, South, and
-Southeast). We used quotas for gender and region to ensure that our sample was
-similar to the Brazilian population in those characteristics. We also collected
-information about whether the subjects had been victimized in the previous 12
-months, as well as their opinion of the Brazilian judicial system and the
-police forces. They follow in the graphs and tables below.
-
-## Informed Consent
-
-About 98% of the interviewees agreed to participate in the survey experiment.
-We excluded the remaining 2% from our analyses.
-
-\footnotesize
-```{r consent, warning=F, error=F, cache=T}
-df %>%
-  group_by(consent) %>%
-  summarise(N = n()) %>%
-  mutate(Frequency = round(N / sum(N), 2)) %>%
-  rename(Consent = consent) %>%
-  kbl(., booktabs = TRUE, caption = "Informed Consent") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = "hold_position")
-
-# Remove subjects who did not agree with consent form
-df1 <- df %>% filter(consent == "Agree")
-```
-\normalsize
+Southeast).
 
@@
 
-The gender distribution of our sample is described below. It closely matches
+The gender distribution of our sample closely matches
 the official data from the [Brazilian Census
@@
 \footnotesize
-```{r gender, warning=F, error=F, cache=T}
+```{r gender, warning=F, error=F, cache=T, echo=F}
 df1 %>%
@@
 \footnotesize
-```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3}
+```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3, echo=F}
 tibble(` `    = "Age",
@@
 \footnotesize
-```{r race, warning=F, error=F, cache=T}
+```{r race, warning=F, error=F, cache=T, echo=F}
 df1 %>%
@@
 
-```{r educationtext, echo=F, warning=F, error=F, cache=T}
+```{r educationtext, echo=F, warning=F, error=F, cache=T, echo=F}
 df2 <- df1 %>%
@@
 \footnotesize
-```{r education, warning=F, error=F, cache=T}
+```{r education, warning=F, error=F, cache=T, echo=F}
 df1 %>%
@@
 
-```{r income-text, echo=F, warning=F, error=F, cache=T}
+```{r income-text, echo=F, warning=F, error=F, cache=T, echo=F}
 df2 <- df1 %>%
@@
 \footnotesize
-```{r income, warning=F, error=F, cache=T}
+```{r income, warning=F, error=F, cache=T, echo=F}
 df1 %>%
@@
 
-```{r ideologytext, echo=F, warning=F, error=F, cache=T}
+```{r ideologytext, echo=F, warning=F, error=F, cache=T, echo=F}
 df2 <- df1 %>%
@@
 \footnotesize
-```{r ideology, warning=F, error=F, cache=T}
+```{r ideology, warning=F, error=F, cache=T, echo=F}
 df1 %>%
@@
 
-\newpage
-
-## Support for Death Penalty
-
-Below you may find how many respondents support the death penalty.
-
-\footnotesize
-```{r death-penalty, warning=F, error=F, cache=T}
-df1 %>%
-  rename(`Support for Death Penalty` = death_penalty) %>%
-  mutate(`Support for Death Penalty` = fct_relevel(`Support for Death Penalty`, "Yes", "No")) %>%
-  group_by(`Support for Death Penalty`) %>%
-  filter(!is.na(`Support for Death Penalty`)) %>%
-  summarise(N = n()) %>%
-  mutate(Frequency = round(N / sum(N), 3)) %>%
-  kbl(., booktabs = TRUE,  linesep = "", caption = "Support for Death Penalty") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = "hold_position")
-```
-\normalsize
-
-## Previous Victimization
-
-We asked subjects whether they had been victimized in the previous 12 months,
-as crime victims may be more likely to support lynchings. The responses follow
-below.
-
-\footnotesize
-```{r victimization, warning=F, error=F, cache=T}
-df1 %>%
-  rename(Victimization = previous_victim_dummy) %>%
-  mutate(Victimization = fct_relevel(Victimization, "Yes", "No")) %>%
-  group_by(Victimization) %>%
-  filter(!is.na(Victimization)) %>%
-  summarise(N = n()) %>%
-  mutate(Frequency = round(N / sum(N), 3)) %>%
-  kbl(., booktabs = TRUE,  linesep = "", caption = "Previous Victimization (12 Months)") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = "hold_position")
-```
-\normalsize
-
-## Opinion on the Police
-
-Here we show the results for our question on how respondents see the police
-forces.
-
-\footnotesize
-```{r police, warning=F, error=F, cache=T}
-df1 %>%
-  rename(`Opinion on the Police` = views_police) %>%
-  mutate(`Opinion on the Police` = fct_relevel(`Opinion on the Police`, "Very Good", "Good",
-                                               "Regular", "Bad", "Very Bad")) %>%
-  group_by(`Opinion on the Police`) %>%
-  filter(!is.na(`Opinion on the Police`)) %>%
-  summarise(N = n()) %>%
-  mutate(Frequency = round(N / sum(N), 3)) %>%
-  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Police") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = "hold_position")
-```
-\normalsize
-
-\newpage
-
-## Opinion on the Judicial System
-
-Lastly, we asked how respondents evaluate their local judiciary. As in the
-previous question, subjects could choose among five options, as well as affirm
-that they do not have an opinion or decline to answer the question.
-
-\footnotesize
-```{r justice, warning=F, error=F, cache=T}
-df1 %>%
-  rename(`Opinion on the Justice System` = views_justice) %>%
-  mutate(`Opinion on the Justice System` = fct_relevel(`Opinion on the Justice System`, "Very Good",
-                                                       "Good", "Regular", "Bad", "Very Bad")) %>%
-  group_by(`Opinion on the Justice System`) %>%
-  filter(!is.na(`Opinion on the Justice System`)) %>%
-  summarise(N = n()) %>%
-  mutate(Frequency = round(N / sum(N), 3)) %>%
-  kbl(., booktabs = TRUE,  linesep = "", caption = "Opinion on the Justice System") %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = "hold_position")
-```
-\normalsize
-
 # Experiment 01
@@
 Research shows that police ineffectiveness frequently appears as a strong
-predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
-result of the weakness of police institutions is that citizens decide to take
-criminal matters "into their own hands", thus persecuting and punishing the
-criminals by themselves. A recent statistic indicates that the police solves
-only 10% of the homicides in Brazil, which lends support to the link between
-weak law enforcement and lynchings [@pearson2018latam].
+predictor of vigilantism [@garcia2019anger]. The direct result of the weakness
+of police institutions is that citizens decide to take criminal matters "into
+their own hands", thus persecuting and punishing the criminals by themselves. A
+recent statistic indicates that the police solves only 10% of the homicides in
+Brazil, which lends support to the link between weak law enforcement and
+lynchings [@pearson2018latam].
 
 Another possible determinant of lynching support is lack of trust in the
-justice system [@godoy2004justice; @smith2019contradictions]. This is often due
-to long criminal proceedings, which cause significant anxiety for the victims.
-In Brazil, the penal code allows the accused to appeal each decision several
-times, so it can take decades before a criminal case is closed
-[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
-the criminal is put to trial, he/she will be punished in a timely matter. Note
-that although the police is technically part of the criminal justice system, we
-analyze the two institutions separately in our experiment.
+justice system [@smith2019contradictions]. This is often due to long criminal
+proceedings, which cause significant anxiety for the victims. In Brazil, the
+penal code allows the accused to appeal each decision several times, so it can
+take decades before a criminal case is closed [@sousa2005utilizaccao]. In this
+respect, citizens do not believe that, even if the criminal is put to trial,
+he/she will be punished in a timely matter. Note that although the police is
+technically part of the criminal justice system, we analyze the two
+institutions separately in our experiment.
 
@@
 
-## Main Results
-
-Table \ref{tab:exp01main} summarizes our results. As we see, none of the
-treatment effects are statistically significant at conventional levels. This
-suggests that institutional factors do not affect lynching support in our
-sample.
-
-\footnotesize
-```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis', echo=F}
 df_exp01 <- df1 %>%
@@
 
-# Models
 m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
@@
 m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)
-
-# Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
-          p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp01main",
-          title = "Experiment 01 -- Main Results", style = "apsr",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Police does not patrol area", "Justice too slow",
-                               "Punishment not harsh enough", "Combined treatments"),
-          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
-
-## Determinants of Baseline Levels
-
-Here we estimate the effect of gender, race, and political ideology on
-lynching support. We find that males, blacks, and mixed race individuals are
-more likely to endorse lynchings when compared to females and whites,
-respectively. Left and center-left voters, in contrast, show lower support for
-lynchings when compared to centrists.
-
-\footnotesize
-```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-df_exp01_group <- df_exp01 %>%
-  filter(gender == c("Female", "Male"),
-         race %in% c("Asian", "Black", "Mixed Race", "White"),
-         ideology %in% c("Center", "Center-Left", "Center-Right",
-                         "Left", "Right"))
-
-m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
-m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
-m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
-m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
-         relevel(ideology, ref = "Center"), data = df_exp01_group)
-
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp01baseline",
-          title = "Experiment 01 -- Determinants of Baseline Levels of
-          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
-                               "Left", "Center-Left", "Center-Right", "Right"),
-          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
+```
 
@@
 experimental data [@green2012modeling]. More specifically, we employ the
-`bartCause` package, which is designed to estimate causal inference models.
+`bartCause` package, which is designed to estimate causal inference models. The
+results are based on 800 posterior samples times 5 chains.
+
+Results vary little in all of our estimations. We find that the personal
+characteristics of the respondents have no impact on our main models, which we
+report in table 1 in the article. Below we present heterogeneous effects for
+the three treatment conditions we included in our experiment. We run one model
+for each covariate, namely gender, age, race, education, household income, and
+political ideology. To save space, here we only show the average treatment
+effect within each group, but the complete results are available in section 3.4
+of the extended version of the appendix ([_redacted for peer review_]).
 
@@
 
-\footnotesize
-```{r exp01-bart01, warning=F, error=F, message=F, cache=T}
-df_exp01_het <- df_exp01 %>%
-  filter(gender %in% c("Female", "Male")) %>%
-  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
-                            "Indigenous"),
-         education = fct_relevel(education, "Primary School", "Secondary School",
-                                  "High School", "College", "Graduate School"),
-         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad"),
-         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
-                                     "Bad", "Very Bad"),
-         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
-                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
-         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
-                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
-                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
-                                         "Above R$20,000"),
-         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
-         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
-         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
-                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
-
-df_exp01_police <- df_exp01_het %>%
-  mutate(exp01_police_treat = as.numeric(exp01_police_treat)) %>%
-  drop_na(exp01_police_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_police_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp01_outcomes, exp01_police_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_police_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_police_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_police_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_police_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_police_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_police2 <- df_exp01_police %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_police_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_police2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_police_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_police_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-```
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 1: Police Ineffectiveness}
+  \label{tab:exp01het01}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & 0.9729 &  &  & & & \\
+  & (2.293) &  &  & & & \\
+  Age &  & 1.180 &  & & & \\
+  &  & (2.266) &  &  \\
+  Race &  &  & 1.0668 & & &  \\
+  &  &  & (2.261) & & & \\
+  Education &  &  &  & 1.1463 & & \\
+  &  &  &  & (2.277) & & \\
+  Household Income &  &  &  & & 1.1459 & \\
+  &  &  &  & & (2.290) & \\
+  Political Ideology &  &  &  & & & 1.3693 \\
+  &  &  &  & & & (2.225) \\
+ N & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} \\
+\hline \\[-1.8ex]
+\end{tabular}
+\end{table}
 \normalsize
@@
 
-\footnotesize
-```{r exp01-bart02, warning=F, error=F, message=F, cache=T}
-# Remove "Indigenous" and "Other" from `race` as they only
-# have 1 observation each. The model cannot be estimated otherwise.
-df_exp01_slow_justice <- df_exp01_het %>%
-  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
-  mutate(exp01_slow_justice_treat = as.numeric(exp01_slow_justice_treat)) %>%
-  drop_na(exp01_slow_justice_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_slow_justice2 <- df_exp01_slow_justice %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_slow_justice2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-```
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 2: Criminal Justice
+  Ineffectiveness}
+  \label{tab:exp01het02}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & -0.0752 &  &  & & & \\
+  & (2.372) &  &  & & & \\
+  Age &  & -0.2788 &  & & & \\
+  &  & (2.379) &  &  \\
+  Race &  &  & NA & & &  \\
+  &  &  & (NA) & & & \\
+  Education &  &  &  & 0.2204 & & \\
+  &  &  &  & (2.347) & & \\
+  Household Income &  &  &  & & -0.0295 & \\
+  &  &  &  & & (2.331) & \\
+  Political Ideology &  &  &  & & & -0.0936 \\
+  &  &  &  & & & (2.339) \\
+ N & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} \\
+\hline \\[-1.8ex]
+\multicolumn{5}{l}{\textbf{Note}: There are no estimates for race because some
+groups have no observations.}
+\end{tabular}
+\end{table}
 \normalsize
@@
 
-As in the last two series of models, our results show no evidence of
-heterogeneous treatment effects.
-
-\footnotesize
-```{r exp01-bart03, warning=F, error=F, message=F, cache=T}
-df_exp01_small_punishment <- df_exp01_het %>%
-  mutate(exp01_small_punishment_treat = as.numeric(exp01_small_punishment_treat)) %>%
-  drop_na(exp01_small_punishment_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(age2)
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-```
+As in our previous estimations, we find no evidence of heterogeneous treatment effects.
+
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 3: Demand for Harsher Legal
+  Punishment}
+  \label{tab:exp01het03}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & 0.4202 &  &  & & & \\
+  & (2.331) &  &  & & & \\
+  Age &  & 0.7766 &  & & & \\
+  &  & (2.316) &  &  \\
+  Race &  &  & 0.6672 & & &  \\
+  &  &  & (2.367) & & & \\
+  Education &  &  &  & 0.50238 & & \\
+  &  &  &  & (2.337) & & \\
+  Household Income &  &  &  & & 0.5526 & \\
+  &  &  &  & & (2.307) & \\
+  Political Ideology &  &  &  & & & 0.61041 \\
+  &  &  &  & & & (2.298) \\
+ N & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} \\
+\hline \\[-1.8ex]
+\end{tabular}
+\end{table}
 \normalsize
@@
 motivating crime; 7) age of the victim of the motivating crime; 8) lynching
-perpetrators. The attributes and levels are displayed in table
-\ref{tab:categories} below.
-
-\vspace{.3cm}
-
-\begin{table}[htpb]
-\small
-\begin{center}
-\caption{\textbf{Attributes and Levels}}
-\label{tab:categories}
-\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
-\Xhline{2\arrayrulewidth}
-\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
-\Xhline{2\arrayrulewidth}
-\small
-Gender of crime perpetrator & Male; female \\ [4pt]
-Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
-Race of crime perpetrator & Black; White; Native Brazilian; Asian \\ [4pt]
-Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
-Offense & Picks the pocket; steals the car; molests; rapes; murders \\ [4pt]
-Gender of crime victim & Male; female\\ [4pt]
-Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
-Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
-\Xhline{2\arrayrulewidth}
-\end{tabular}
-\end{center}
-\end{table}
+perpetrators.
 
@@
 victims of car theft either. All other combinations were allowed. We randomized
-the attributes using a `.php` script, which is available at
-<https://github.com/danilofreire/lynching-experiment-brazil/blob/master/conjoint/portuguese/lynching-conjoint-pt.php>.
+the attributes using a `php` script, which is available at
+[_redacted for peer review_].
 
@@
 
-## Marginal Means Estimator
-
-We estimate the conjoint experiment with the `cregg` package [@leeper2018cregg]
-for the `R` statistical language [@rstats2019]. We follow @leeper2020measuring
-and report marginal means as our main estimates. Marginal means are easy to
-interpret and they are not sensitive to choice of the reference category in
-subgroup analyses. The $H_0$ in all models is that the coefficient is equal to
-0.5, that is, that respondents are indifferent to that attribute level. Standard
-errors are clustered by respondent. The code follows below.
-
-\footnotesize
-```{r conjoint-mm, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
+```{r conjoint-mm, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=5, echo=F, results = "hide"}
 conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
@@
 
-plot(mms, vline = 0.5, header_fmt = "%s") +
-  theme(legend.position = "none", axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
-
 # Table
@@
 }
-
-table_mm(mms, capt = "Marginal Means -- Full Model")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-We also estimate AMCE coefficients for our conjoint experiment. This method
-selects one reference category for each attribute and looks at changes from the
-baseline level. The reference categories are marked as zero in our models.
-
-\footnotesize
-```{r conjoint-amce, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
+In the article, we estimate the conjoint experiment with the `cregg` package
+[@leeper2018cregg] for the `R` statistical language [@rstats2019]. Here we also
+present AMCE coefficients for the same experiment. This method selects one
+reference category for each attribute and looks at changes from the baseline
+level. The reference categories are marked as zero in our models.
+
+\vspace{.3cm}
+
+```{r conjoint-amce, warning=F, error=F, message=F, cache=T, fig.width=8, fig.height=5, echo=F, echo=F}
 amces <- cj(conjoint_data, fm, id = ~response_id)
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-table_mm(amces, capt = "Average Marginal Component Effects -- Full Model")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-females, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos = "H"}
+\vspace{.3cm}
+```{r conjoint-females, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos = "H", echo=F}
 # Model
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-table_mm_by <- function(mm_by, capt) {
-dfr <- data.frame(feature = mm_by[, c(5)],
-                  round(mm_by[, c(6, 7, 9, 10, 11)], digits = 3))
-names(dfr) <- c("Feature", "Estimate", "Std. Error",
-                "P-Value", "Lower", "Upper")
-return(kbl(dfr, "latex", caption = capt, linesep = "",
-           booktabs = TRUE) %>%
-kable_styling(font_size = 12, full_width = TRUE,
-              latex_options = "hold_position") %>%
-pack_rows("Gender of crime perpetrator", 1, 2) %>%
-pack_rows("Age of crime perpetrator", 3, 5) %>%
-pack_rows("Race of crime perpetrator", 6, 9) %>%
-pack_rows("Residency of crime perpetrator", 10, 11) %>%
-pack_rows("Offense", 12, 16) %>%
-pack_rows("Gender of crime victim", 17, 18) %>%
-pack_rows("Age of crime victim", 19, 22) %>%
-pack_rows("Lynching perpetrators", 23, 27) %>%
-column_spec(1, width = "6cm"))
-}
-
-mm_females <- mm_by %>% filter(BY == "Female")
-table_mm_by(mm_females, capt = "Marginal Means -- Females")
-mm_males <- mm_by %>% filter(BY == "Male")
-table_mm_by(mm_males, capt = "Marginal Means -- Males")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.2, fig.pos="H"}
+\vspace{.3cm}
+```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.6, fig.pos="H", echo=F}
 # Model
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
-
-# Tables
-mm_young <- mm_by %>% filter(BY == "18-34")
-table_mm_by(mm_young, capt = "Marginal Means -- 18-34 Years Old")
-mm_adult <- mm_by %>% filter(BY == "35-54")
-table_mm_by(mm_adult, capt = "Marginal Means -- 35-54 Years Old")
-mm_senior <- mm_by %>% filter(BY == "55 plus")
-table_mm_by(mm_senior, capt = "Marginal Means -- 55+ Years Old")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.4, fig.pos="H"}
+\vspace{.3cm}
+```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos="H", echo=F}
 # Model
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_asian <- mm_by %>% filter(BY == "Asian")
-table_mm_by(mm_asian, capt = "Marginal Means -- Asian")
-mm_black <- mm_by %>% filter(BY == "Black")
-table_mm_by(mm_black, capt = "Marginal Means -- Black")
-mm_mixed <- mm_by %>% filter(BY == "Mixed Race")
-table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
-mm_white <- mm_by %>% filter(BY == "White")
-table_mm_by(mm_white, capt = "Marginal Means -- White")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
+\vspace{.5cm}
+```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos="H", echo=F}
 # Model
@@
 
-# Tables
-mm_pri_sec <- mm_by %>% filter(BY == "Primary or Secondary School")
-table_mm_by(mm_pri_sec, capt = "Marginal Means -- Primary or Secondary School Degree")
-mm_high <- mm_by %>% filter(BY == "High School")
-table_mm_by(mm_high, capt = "Marginal Means -- High School Degree")
-mm_college <- mm_by %>% filter(BY == "College")
-table_mm_by(mm_college, capt = "Marginal Means -- College Degree")
-mm_grad <- mm_by %>% filter(BY == "Graduate School")
-table_mm_by(mm_grad, capt = "Marginal Means -- Graduate School Degree")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
+\vspace{.3cm}
+```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.5, fig.pos="H", echo=F}
 # Model
@@
   scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_3k <- mm_by %>% filter(BY == "Up to R$3,000")
-table_mm_by(mm_3k, capt = "Marginal Means -- Up to 3,000 BRL")
-mm_5k <- mm_by %>% filter(BY == "From R$3,001 to R$5,000")
-table_mm_by(mm_5k, capt = "Marginal Means -- From 3,001 to 5,000 BRL")
-mm_abv5k <- mm_by %>% filter(BY == "Above R$5,000")
-table_mm_by(mm_abv5k, capt = "Marginal Means -- Above 5,000 BRL")
-```
-\normalsize
-
-\clearpage
-
-### Support for Death Penalty
-
-Here we assess whether subjects who support the death penalty have different
-preferences towards lynching victims. There are fewer respondents who answered
-"Don't Know" or "Rather Not Say" to our question, so the confidence intervals
-from their estimates are larger than for the other two categories. The
-estimates largely overlap across the four groups, although those who answered
-"Rather Not Say" are less favorable to lynching Indigenous criminals.
-
-\footnotesize
-```{r conjoint-penalty, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos="H"}
+```
+
+### Political Ideology
+
+Here we disaggregate the results according to political ideology. We see that
+political views do not change the overall responses.
+
+\vspace{.5cm}
+```{r conjoint-ideology, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.2, fig.pos="H", echo=F}
 # Model
 cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
-  drop_na(death_penalty) %>%
-  mutate(death_penalty = fct_relevel(death_penalty, "Yes", "No",
-                                     "Don't Know", "Rather Not Say"))
-cjdt$Death_Penalty <- factor(cjdt$death_penalty)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Death_Penalty)
+  drop_na(ideology)
+cjdt$Ideology <- factor(cjdt$ideology)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by =
+            ~Ideology)
 
 # Plot
-plot(mm_by, group = "Death_Penalty", vline = 0.5, header_fmt = "%s") +
+plot(mm_by, group = "Ideology", vline = 0.5, header_fmt = "%s") +
   theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
   scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_yes <- mm_by %>% filter(BY == "Yes")
-table_mm_by(mm_yes, capt = "Marginal Means -- Support for Death Penalty: Yes")
-mm_no <- mm_by %>% filter(BY == "No")
-table_mm_by(mm_no, capt = "Marginal Means -- Support for Death Penalty: No")
-mm_dk <- mm_by %>% filter(BY == "Don't Know")
-table_mm_by(mm_dk, capt = "Marginal Means -- Support for Death Penalty: Do Not Know")
-mm_rns <- mm_by %>% filter(BY == "Rather Not Say")
-table_mm_by(mm_rns, capt = "Marginal Means -- Support for Death Penalty: Rather Not Say")
-```
-\normalsize
-
-\clearpage
-
-### Previous Victimization
-
-Respondents who had been victimized in the past 12 months also do not have
-different preferences towards lynchings victim profiles. The results are
-virtually identical for both groups, as one can see below.
-
-\footnotesize
-```{r conjoint-victimization, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.6, fig.pos="H"}
-# Model
-cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
-  mutate(previous_victim_dummy, "Yes", "No")
-cjdt$Previous_Victim <- factor(cjdt$previous_victim_dummy)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Previous_Victim)
-
-# Plot
-plot(mm_by, group = "Previous_Victim", vline = 0.5, header_fmt = "%s") +
-  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_yes <- mm_by %>% filter(BY == "Yes")
-table_mm_by(mm_yes, capt = "Marginal Means -- Previous Victimization (12 Months): Yes")
-mm_no <- mm_by %>% filter(BY == "No")
-table_mm_by(mm_no, capt = "Marginal Means -- Previous Victimization (12 Months): No")
-```
-\normalsize
-
-\clearpage
-
-### Opinion on the Police
-
-Experimental results do not change when we break down the responses according
-to how subjects view the police forces.
-
-\footnotesize
-```{r conjoint-policing, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=6, fig.pos="H"}
-# Model
-cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
-  mutate(views_police2 = case_when(views_police == "Rather Not Say" ~ NA_character_,
-                                   views_police == "Don't Know" ~ NA_character_,
-                                   TRUE ~ as.character(views_police)),
-         views_police2 = fct_relevel(views_police2, "Very Good", "Good",
-                                     "Regular", "Bad", "Very Bad")) %>%
-  drop_na(views_police2)
-cjdt$Police <- factor(cjdt$views_police2)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Police)
-
-# Plot
-plot(mm_by, group = "Police", vline = 0.5, header_fmt = "%s") +
-  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_vgood <- mm_by %>% filter(BY == "Very Good")
-table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Police: Very Good")
-mm_good <- mm_by %>% filter(BY == "Good")
-table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Police: Good")
-mm_regular <- mm_by %>% filter(BY == "Regular")
-table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Police: Regular")
-mm_bad <- mm_by %>% filter(BY == "Bad")
-table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Police: Bad")
-mm_vbad <- mm_by %>% filter(BY == "Very Bad")
-table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Police: Very Bad")
-```
-\normalsize
-
-\clearpage
-
-### Opinion on the Judicial System
-
-Lastly, we analyze whether personal beliefs about the judicial system affect
-the type of lynching victim respondents select.
-
-\footnotesize
-```{r conjoint-justice, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
-# Model
-cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
-  mutate(views_justice2 = case_when(views_justice == "Rather Not Say" ~ NA_character_,
-                                    views_justice == "Don't Know" ~ NA_character_,
-                                   TRUE ~ as.character(views_justice)),
-         views_justice2 = fct_relevel(views_justice2, "Very Good", "Good",
-                                      "Regular", "Bad", "Very Bad")) %>%
-  drop_na(views_justice2)
-cjdt$Judiciary <- factor(cjdt$views_justice2)
-mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Judiciary)
-
-# Plot
-plot(mm_by, group = "Judiciary", vline = 0.5, header_fmt = "%s") +
-  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
-  scale_colour_viridis_d(option = "inferno", end = 0.8)
-
-# Tables
-mm_vgood <- mm_by %>% filter(BY == "Very Good")
-table_mm_by(mm_vgood, capt = "Marginal Means -- Opinion on the Judicial System: Very Good")
-mm_good <- mm_by %>% filter(BY == "Good")
-table_mm_by(mm_good, capt = "Marginal Means -- Opinion on the Judicial System: Good")
-mm_regular <- mm_by %>% filter(BY == "Regular")
-table_mm_by(mm_regular, capt = "Marginal Means -- Opinion on the Judicial System: Regular")
-mm_bad <- mm_by %>% filter(BY == "Bad")
-table_mm_by(mm_bad, capt = "Marginal Means -- Opinion on the Judicial System: Bad")
-mm_vbad <- mm_by %>% filter(BY == "Very Bad")
-table_mm_by(mm_vbad, capt = "Marginal Means -- Opinion on the Judicial System: Very Bad")
-```
-\normalsize
-
-\clearpage
+```
 
@@
 
-\footnotesize
-```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles"}
+\vspace{.3cm}
+```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.5, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles", echo=F}
 dfmat <- df1 %>%
@@
                             "é", "ser"))
-
-# Plot
 dfmat %>%
@@
 ```
-\normalsize
 
@@
 
-\footnotesize
-```{r conjoint-fcm, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H", fig.cap = "Semantic network analysis"}
+\vspace{.3cm}
+```{r conjoint-fcm, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=3, fig.pos="H", fig.cap = "Semantic network analysis", echo=F}
 fcmat <- fcm(dfmat)
@@
 \footnotesize
-```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
+```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H", echo=F}
 # Unsupervised LDA
@@
 
-Our last model is a semisupervised LDA, in which we include a series of
+Our last model is a semisupervized LDA, in which we include a series of
 keywords to measure how frequently some pre-defined topics appear often in the
@@
 \footnotesize
-```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
+```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H", echo=F}
 # Semisupervised LDA
@@
 
-## Main Results
-
-Our results are available in table \ref{tab:exp03main}. Reminding respondents
-of the legal consequences of lynchings has a strong, negative effect on
-individual levels of lynching support. We see a reduction of about 4.5%, which
-corresponds to an 11% change when compared to the baseline levels. Our second
-treatment condition, reminding subjects of human rights guarantees, has no
-statistically significant effect. Informing respondents that lynchings can
-trigger a cycle of violence also has a large negative effect. It decreases
-lynching support by 3%, which is an 8% reduction in comparison with the control
-group. When we combine all treatments, we still detect a negative impact of the
-treatment conditions.
-
-\footnotesize
-```{r exp03-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+```{r exp03-main, warning=F, message=F, error=F, cache=T, echo=F}
 df_exp03 <- df1 %>%
@@
 m4 <- lm(exp03_outcomes ~ exp03_any_treat, data = df_exp03)
-
-# Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE,
-          p = starprep(m1, m2, m3, m4, stat = "p.value"), align = TRUE,
-          title = "Experiment 03 -- Main Results", style = "apsr", label = "tab:exp03main",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Constitution and penal code", "Human rights",
-                               "Vendettas", "Combined treatments"),
+```
+\normalsize
+
+## Determinants of Baseline Levels
+
+As we did in the first experiment, we evaluate how individual characteristics
+impact lynching support. The results are similar to those presented in table
+\ref{tab:exp03baseline}, with the exception that the coefficient for white
+respondents is negative in two estimations, and the coefficient for male does
+not reach statistical significance in the last model ($p$-value = 0.11).
+
+```{r exp03-baseline, warning=F, message=F, error=F, cache=T, fig.pos="ht", results='asis', echo=F}
+df_exp03_group <- df_exp03 %>%
+  filter(gender == c("Female", "Male"),
+         race %in% c("Asian", "Black", "Mixed Race", "White"),
+         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))
+
+df_exp03_gender <- df_exp03 %>% filter(gender == c("Female", "Male"))
+df_exp03_race <- df_exp03 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
+  mutate(race = fct_relevel(race, "Black"))
+df_exp03_ideology <- df_exp03 %>%
+         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+         mutate(ideology = fct_relevel(ideology, "Center"))
+
+m1 <- lm(exp03_outcomes ~ gender, data = df_exp03_gender)
+m2 <- lm(exp03_outcomes ~ race, data = df_exp03_race)
+m3 <- lm(exp03_outcomes ~ ideology, data = df_exp03_ideology)
+m4 <- lm(exp03_outcomes ~ gender + race + ideology, data = df_exp03_group)
+
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp03baseline",
+          title = "Experiment 01 -- Determinants of Baseline Levels of
+          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
+                               "Left", "Center-Left", "Center-Right", "Right"),
           column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
+          keep.stat = "n", no.space = TRUE, 
+          table.placement = "ht")
+```
 
@@
 
-\footnotesize
-```{r exp03-bart01, warning=F, error=F, message=F, cache=T}
-df_exp03_het <- df_exp03 %>%
-  filter(gender %in% c("Female", "Male")) %>%
-  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
-                            "Indigenous"),
-         education = fct_relevel(education, "Primary School", "Secondary School",
-                                  "High School", "College", "Graduate School"),
-         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad"),
-         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
-                                     "Bad", "Very Bad"),
-         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
-                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
-         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
-                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
-                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
-                                         "Above R$20,000"),
-         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
-         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
-         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
-                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
-
-df_exp03_constitution <- df_exp03_het %>%
-  mutate(exp03_constitution_treat = as.numeric(exp03_constitution_treat)) %>%
-  drop_na(exp03_constitution_treat)
-
-# Gender
-summary(bartc(exp03_outcomes, exp03_constitution_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(age2)
-summary(bartc(exp03_outcomes, exp03_constitution_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp03_constitution2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp03_outcomes, exp03_constitution_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp03_outcomes, exp03_constitution_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp03_outcomes, exp03_constitution_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp03_outcomes, exp03_constitution_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp03_outcomes, exp03_constitution_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp03_constitution2 <- df_exp03_constitution %>% drop_na(previous_victim_dummy)
-summary(bartc(exp03_outcomes, exp03_constitution_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_constitution2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp03_outcomes, exp03_constitution_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp03_outcomes, exp03_constitution_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_constitution,
-              n.chains = 5L, seed = 144))
-```
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 1: Legal Punishment for Lynching Perpetrators}
+  \label{tab:exp03het01}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & -4.454 &  &  & & & \\
+  & (2.234) &  &  & & & \\
+  Age &  & -4.459 &  & & & \\
+  &  & (2.208) &  &  \\
+  Race &  &  & -4.3069 & & &  \\
+  &  &  & (2.220) & & & \\
+  Education &  &  &  & -4.486 & & \\
+  &  &  &  & (2.190) & & \\
+  Household Income &  &  &  & & -4.520 & \\
+  &  &  &  & & (2.206) & \\
+  Political Ideology &  &  &  & & & -4.5719 \\
+  &  &  &  & & & (2.175) \\
+ N & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} \\
+\hline \\[-1.8ex]
+\end{tabular}
+\end{table}
 \normalsize
@@
 
-\footnotesize
-```{r exp03-bart02, warning=F, error=F, message=F, cache=T}
-df_exp03_rights <- df_exp03_het %>%
-  mutate(exp03_rights_treat = as.numeric(exp03_rights_treat)) %>%
-  drop_na(exp03_rights_treat)
-
-# Gender
-summary(bartc(exp03_outcomes, exp03_rights_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp03_rights2 <- df_exp03_rights %>% drop_na(age2)
-summary(bartc(exp03_outcomes, exp03_rights_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp03_rights2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp03_outcomes, exp03_rights_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp03_outcomes, exp03_rights_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp03_outcomes, exp03_rights_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp03_outcomes, exp03_rights_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp03_outcomes, exp03_rights_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp03_rights2 <- df_exp03_rights %>% drop_na(previous_victim_dummy)
-summary(bartc(exp03_outcomes, exp03_rights_treat, previous_victim_dummy, 
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_rights2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp03_outcomes, exp03_rights_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp03_outcomes, exp03_rights_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_rights,
-              n.chains = 5L, seed = 144))
-```
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 2: Human Rights}
+  \label{tab:exp03het02}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & -1.598 &  &  & & & \\
+  & (2.228) &  &  & & & \\
+  Age &  & -1.5594 &  & & & \\
+  &  & (2.196) &  &  \\
+  Race &  &  & -1.533 & & &  \\
+  &  &  & (2.209) & & & \\
+  Education &  &  &  & -1.5033 & & \\
+  &  &  &  & (2.188) & & \\
+  Household Income &  &  &  & & -1.3378 & \\
+  &  &  &  & & (2.184) & \\
+  Political Ideology &  &  &  & & & -1.4722 \\
+  &  &  &  & & & (2.155) \\
+ N & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} \\
+\hline \\[-1.8ex]
+\end{tabular}
+\end{table}
 \normalsize
@@
 
-We do not find considerable heterogeneity in the results. Overall, the
-three treatment conditions are very stable, thus we are confident that the
-main results are not driven by any particular group.
-
-\footnotesize
-```{r exp03-bart03, warning=F, error=F, message=F, cache=T}
-df_exp03_vendetta <- df_exp03_het %>%
-  mutate(exp03_vendetta_treat = as.numeric(exp03_vendetta_treat)) %>%
-  drop_na(exp03_vendetta_treat)
-
-# Gender
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(age2)
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp03_vendetta2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp03_vendetta2 <- df_exp03_vendetta %>% drop_na(previous_victim_dummy)
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, previous_victim_dummy, 
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp03_vendetta2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp03_outcomes, exp03_vendetta_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp03_vendetta,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-# Session Information
-
-\footnotesize
-```{r session, cache=T}
-sessionInfo()
-```
-\normalsize
+We do not find considerable heterogeneity in these last results. Overall, the
+three treatment conditions are very stable, thus we are confident that the main
+results are not driven by any particular group.
+
+\begin{table}[!htbp] \centering
+\small
+  \caption{Heterogeneous Effects for Treatment 3: Vendettas}
+  \label{tab:exp03het03}
+\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
+\\[-1.8ex]\hline \\[-1.8ex]
+\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
+\hline \\[-1.8ex]
+ Gender & -3.114 &  &  & & & \\
+  & (2.356) &  &  & & & \\
+  Age &  & -2.574 &  & & & \\
+  &  & (2.303) &  &  \\
+  Race &  &  & -3.0267 & & &  \\
+  &  &  & (2.291) & & & \\
+  Education &  &  &  & -3.076 & & \\
+  &  &  &  & (2.271) & & \\
+  Household Income &  &  &  & & -2.738 & \\
+  &  &  &  & & (2.295) & \\
+  Political Ideology &  &  &  & & & -2.8907 \\
+  &  &  &  & & & (2.265) \\
+ N & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} \\
+\hline \\[-1.8ex]
+\end{tabular}
+\end{table}
+\normalsize
+
+\newpage
+
+# Ethics Statement
+
+We adhered to the ethical guidelines provided by the Institutional Review Board
+at Brown University and APSA's Principles and Guidance. To facilitate
+transparency, we comment here on a few aspects of our research design. First,
+we worked with the Brown University IRB to reduce the risk of harm for
+participants taking the survey. This included consultation with a cultural
+expert to inform the phrasing of the survey. Second, respondents received
+compensation via Qualtrics, which paid respondents directly after they completed
+the questionnaire. Each subject in Qualtrics' online panel received the
+equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
+not finish the survey will not receive compensation. The compensation is
+appropriate for the participant population. As of August 17, 2020, Brazil's
+monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
+working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
+survey takes about 20 minutes to complete and respondents received 2.5 USD,
+therefore subjects will receive a monetary compensation that is 6 times higher
+than the local minimum wage. Third, we do not see any potential or perceived
+conflicts of interest in carrying out this research. We received a grant of
+$10,000 to conduct this research from the Centre for the Study of Governance &
+Society at King’s College London, which receives support from the Templeton
+Foundation. We are aware of no conflicts of interest from either source. All of
+the code and data will be made publicly available.
+
+\newpage

### 2021-06-16 article/main.tex
first draft

% !TEX program = XeLaTeX
\documentclass[12pt,ansiapaper]{article}

% Fonts
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=.8]{Fira Mono}

% KableExtra support
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{etoolbox}
\usepackage{tocloft}

% Dots in toc
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}

% Spacing
\usepackage{setspace}

% Margins
\usepackage[margin=2cm]{geometry}

% Packages I've been using for different reasons
\usepackage{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

% English
\usepackage[english]{babel}
\usepackage[english]{isodate}
\cleanlookdateon

% Penalties
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; David Skarbek},
      pdfkeywords={Brazil, crime, extralegal violence, lynching, vigilantism},
  }

% Bibliography
\usepackage{natbib}
\bibliographystyle{chicago-ff}
\makeatletter
% Remove comma after author
\setcitestyle{aysep={}}
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

% Make links footnotes instead of hotlinks:
%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Numbered sections
\setcounter{secnumdepth}{5}
% % % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
% \let\oldparagraph\paragraph
% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
% \let\oldsubparagraph\subparagraph
% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi

% Spacing
\doublespacing

% Title
\title{Vigilantism, Institutions, and Honor Culture:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J. D'Amico, Miriam Golden, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J. Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, and Georg Vanberg for their valuable comments. We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington. This study received IRB approval from Brown University in October 2020 (Protocol 2009002803). Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}. We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.}}

% Author
\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}

% Date
\date{June 16, 2021}

% Begin document
\begin{document}
\maketitle

% Abstract
\begin{abstract}
\doublespacing \noindent Why do people support extrajudicial violence? In this paper, we identify an important role for cultural norms in explaining attitudes toward lynching. In a series of survey experiments with respondents in Brazil, we examine how people view different motivations for lynchings, which characteristics of lynching scenarios garner greater support for lynching, and whether providing different types of information about lynching reduces support for it. We find  that people do not believe that criminal justice institutions should be relied on to solve serious crimes and do believe that in such instances, community members have the right to take vengeance. In particular, our analysis finds that people strongly support the use of extrajudicial violence by families of victims against men who sexually assault and murder women and children. 
\vspace{.25cm}

\noindent \textbf{Keywords:} extralegal violence, vigilantism, lynching, Brazil, crime 
\vspace{.25cm}

\end{abstract}

\newpage

\section{Introduction}
\label{sec:introduction}

\doublespacing

The regulation of violence is one of the most important functions of the state. When states control violence effectively, markets, politics, and civil society can flourish. However, in many places, violence is poorly regulated and nonstate armed actors---ranging from residents to rebel groups---use violence at their own discretion. The extralegal use of violence is also a clear violation of the rule of law \citep[48-49]{blair2020peacekeeping}. More generally, the challenge of monopolizing violence is at the heart of the Weberian definition of the state, and it is arguably one of the most fundamental questions of political economy. While political scientists have written extensively on civil wars, rebel governance, and criminal violence \citep{arjona2016rebelocracy, trejo2021high, barnes2017criminal}, they have written far less about vigilante violence. In this paper, we use survey experiments to better understand people's attitudes toward the use of extralegal violence.

Although lynchings and mob violence more generally have decreased in advanced democracies, it remains widespread in many parts of the world. Based on US State Department reports, \citet[33]{jung2020lynching} find that between 1976 and 2018, lynchings occurred in all regions of the world and in more than a hundred countries. In particular, Latin America has been severely affected by a recent increase in lynchings. Such a surge in citizen-led violence has reportedly been motivated by growing numbers of drug-related crimes and by police ineffectiveness \citep{mallen2014vigilantes}. Brazil provides a telling example. From 2011 to 2015, the country registered about 2,500 lynching episodes. In 2015, 173 people were killed by angry mobs---nearly one execution every two days \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for more than thirty years, these figures are not only the highest in the country's history, but among the highest in the world. The people who participate in lynchings are typically  young men, but they also sometimes include teenage women and girls, elderly women, and even members of the local police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São Paulo kill hundreds of people every year in a way that looks similar to vigilantism \citep{willis2015killing}. Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas extralegally \citep{magaloni2020killing}.}

There is no strong consensus about what factors explain people's participation in vigilantism. Some of the most common explanations focus on the role of state-based institutions. People living in places with weak or failed states might engage in vigilante activity to control crime and to enforce social order \citep{bancroft1887works}. However, others argue that it is growth in state capacity that motivates people to take justice into their own hands out of fear that the state will not punish perpetrators or will do so too lightly \citep{smith2019contradictions}. In Latin America in particular, vigilantism has been found to be associated with previous exposure to violence \citep{garcia2019anger}, untrustworthy law enforcement \citep{zizumbo2017community}, perceived insecurity \citep{ceobanu2011crime, godoy2004justice}, and economic and social inequality \citep{phillips2017inequality,godoy2006popular,arias2010violent}.

Part of the reason for the proliferation of findings is that studying vigilantism empirically presents a substantial challenge. Many studies focus on vigilantism along the American frontier in the mid-nineteenth century, drawing on archival and historical documents  \citep{brown1975strain, courtwright2009violent, obert2018six}. However, much relevant evidence needed to test competing theories has been lost to history. Qualitative and ethnographic research provides deep insights into the motivations and emotions surrounding social disorder, violence, and vigilantism \citep{godoy2002lynchings}. Yet, like all research approaches, this method has shortcomings, including recall bias and social desirability bias. Quantitative approaches that rely on observational data are likewise often limited in important ways, including that relevant data may be absent, data may imperfectly map onto theoretical concepts, and data may be collected and aggregated at a level of analysis far removed from the studied phenomenon. Finally, while a credible identification strategy is not necessary for making causal claims, it can often solve issues that arise from poor-quality data. Unfortunately, credible identification strategies are often not available.  As \citet[17]{bateson2020politics} notes, ``Field experiments on vigilantism would raise serious ethical concerns, and natural experiments are rare.''

In this paper, we use survey experiments to better understand individual perceptions of vigilantism. Based on the existing literature, we designed three survey experiments to understand lynchings in Brazil in particular. This empirical approach offers several distinct advantages. First, the data we collected come from the same level of analysis as the phenomenon itself: local residents. Second, online surveys are less susceptible to social desirability bias, and survey experiments help to elicit sensitive information---an especially important benefit in researching this topic \citep{grimm2010social}. Third, the experimental nature of the approach allows us to estimate the size of effects. Finally, we can also control for confounding, which is a potential concern with more qualitative methods.

One obvious downside to survey experiments is the difficulty in making inferences about the external validity of findings. \citet[17-18]{bateson2020politics} suggests that the closer that a fictional survey prompt matches the real world, the better the external validity. Accordingly, our first experiment is based on an actual account of a lynching in Jundia\'{i}, Brazil. In the second experiment, we include a wide range of lynching-scenario characteristics that allow respondents to consider detailed, realistic examples. Our third experiment examines whether providing different types of information can affect respondents' perceptions of lynchings. Our strategy here is similar to that of public marketing campaigns that governments often use to change public opinion. In this experiment, we provide information akin to government messaging to the general public. Many theories of vigilantism presume that public beliefs and public opinion establish norms about lynchings. Even if none of our respondents have participated or will participate in lynchings, they are part of the community that creates norms about lynching.

In the first experiment, we attempt to understand how the underlying motivation for a lynching affects support for it. In particular, we test whether police absence, the slowness of the legal process, and the belief that punishment will not be harsh enough affect support. We find no effect for any treatment. Instead, combined with existing data on measures of police ineffectiveness and state capacity, we argue that the evidence is consistent with the claim that respondents simply do not view the police as a genuine source of assistance for serious crimes. Our second experiment is a conjoint experiment designed to see which characteristics of a lynching lead people to believe it is more or less justified. We find evidence that is consistent with aspects of an honor culture  \citep{nisbett2018culture,grosjean2014history}. In such cultures, people believe that the victims of crimes or their family members have the right to seek revenge, especially for heinous or otherwise serious crimes. People often see crimes such as forcible rape and murder as stains on the social standing of the victim and their family, and they believe it is not the proper role of the state to respond. In the final experiment, we provide information to respondents to attempt to reduce support for lynching. We remind respondents that lynching is a crime, that all citizens have human rights, and that lynchings can prompt violent vendettas. We find large negative effects of reminding respondents that lynching is a crime and that lynchings carry the risk of vendettas. Taken together, these findings are consistent with the argument that people are more likely to support vigilantism when the state cannot be relied on for crime control and when certain aspects of an honor culture are present.

In studying lynching, this  paper contributes to several debates. First, we provide causal estimates of why Brazilians justify lynching, how vigilantes' motivation affects the justification, and how to reduce support for lynchings. Second, we provide evidence that is consistent with the common argument that vigilantism is driven by state absence or weakness. However, state absence or weakness alone is not enough to explain support for vigilantism. Like \cite{jung2020lynching}, we argue that people's beliefs and cultural norms are crucial to whether vigilantism is perceived to be justified. It is not simply the fact that the state is unavailable to enforce the law that leads people to support lynchings. Instead, it is the belief that it is not the proper role of the police to do so and that the response should instead be carried out by the family of the victim. Third, the insight we gain into the relationship between formal and informal enforcement helps us understand political development or lack thereof. Even when legal institutions are present and effective, norms  can undermine people's reliance on them. This is a major challenge in establishing the rule of law in developing countries, where residents often prefer informal solutions to crime over state-based solutions \citep[10]{blair2020peacekeeping}. As a result, the prevalence of lynchings undermines political development and state capacity, which can fall into a self-reinforcing cycle \citep{jung2020lynching}. Solving the problem of discretionary, extrajudicial use of violence is crucial for understanding political and economic development more generally.

\section{Theory and Hypotheses}
\label{sec:theory}

In an important recent article, Regina Bateson \citeyearpar{bateson2020politics} conceptualizes vigilantism and defines it as ``the extralegal prevention, investigation, or punishment of offenses'' (3). She identifies five key characteristics of vigilantism, each of which varies along a continuum (11--14). First, vigilantism can be carried out by an individual or by a group of people. Second, vigilantism ranges from nonviolent interventions to extremely violent ones, including even the torture and murder of someone who is suspected of committing a crime. Third, it can occur in private or public, and some acts of vigilantism are intentionally carried out in elaborate, public displays. Fourth, vigilantism can arise spontaneously or it can be highly organized and institutionalized. Finally, vigilantism can operate to prevent crime in the first place or to respond to crime during or after its occurrence (what Bateson calls ``defensive'' and ``offensive'' vigilantism). In this paper, we focus on lynchings, a form of vigilantism that is carried out by groups, with violence, in public, spontaneously, and in response to crime being committed.\footnote{Different types of vigilantism might arise for different reasons. For example, highly organized and institutionalized ``vigilance committees'' might be caused by entirely different social forces than are spontaneous lynchings. Accordingly, we focus on a single, specific type of vigilantism---lynching---throughout the paper.}

The study of vigilantism has a long and multidisciplinary history. Both classic works and contemporary research draw from a variety of fields and methods, including anthropology, criminology, history, sociology, and, more recently, political science \citep{moncada2017varieties}. These studies rely on historical, archival, observational, and statistical empirical approaches. This work---which strongly informs our survey design---offers several theories to explain variation in the prevalence of vigilantism.\footnote{We are obviously not testing all existing theories of vigilantism. This is partly because of constraints facing survey-based research. For example,  recent work shows that economic inequality drives Mexican \textit{autodefensa} activity \citep{phillips2017inequality}. Likewise, there are  long-run historical determinants that explain variation in armed resistance \citep{Osorio2019mexico}. Surveys are not especially conducive to testing those types of variables and theories. Instead, we focus on theories based on state presence, perceptions of legitimacy, and cultural norms, which are well suited to survey research.}  First, many scholars argue that vigilantism arises in response to the inability of states to effectively control crime and enforce social order \citep{bancroft1887works}. Historical studies of California identify state absence or weakness as a major cause of the emergence of vigilance committees and miners' courts during the gold rush (1848--55) \citep{hunt1920committees,rohrbough1997days,couttenier2017wild}.\footnote{There is substantial debate about the effectiveness of these activities \citep{clay2003order}. More generally, on extralegal institutions along the nineteenth-century frontier, see \cite{murtazashvili2013political}.} While gold miners often pursued justice in loose, disorganized, and fleeting ways \citep{mcdowell2002commons,mcdowell2007criminal}, some of these vigilance committees were highly organized and semipermanent \citep{bancroft1887works}.\footnote{\citet{taniguchi2016dirty} argues that the committee's actions in 1856 were not a response to a need for order, but instead a land grab from people who acquired land rights when Mexico controlled the region.} Outside of the United States, many studies likewise find that a desire for security and safety drive vigilantism. In Ghana, for example, the lack of criminal justice resources and the presence of corruption among security actors have been blamed for a rise of vigilantism between 1990 and 2000 \citep[416]{adinkrah2005vigilante}. Similarly, in  Guatemala since 1996, lack of effective state-based crime control was partly responsible for the rise of vigilantism \citep{godoy2006popular}. This research suggests the first hypothesis:

\begin{itemize}
  \item \textbf{Hypothesis 1:} Support for vigilantism will increase if people believe they cannot rely on the state to control crime and enforce social order.
\end{itemize}

One challenge to the hypothesis in the context of the US frontier is that vigilante activity was also widespread during roughly the same time along the East Coast and in the South, where states were far more established than along the Western frontier. In response, one theory argues that vigilantism in these locations instead arose along ``social frontiers'' \citep{obert2018keeping}. These are places where social relationships and social standing were ambiguous among different racial, ethnic, and class-based groups. If the state was not strong or stable enough to eliminate these ambiguities, then vigilantism emerged as a way to create and entrench social and political identities. Black Americans, in particular, were lynched in shocking numbers and at shocking frequency across the South well into the twentieth century \citep{dray2003hands,seguin2019national}. Likewise, based on studies of executions of Muslim men in Bosnia and a lynching in Jim Crow--era Maryland, Lee Ann Fujii \citeyearpar{fujii2017talk} argues that lynchings serve as ``violent displays'' that send signals to observers in the community and entrench social hierarchies and political identities.

While the racial prejudice that drove violence in the United States is clear, vigilantism more generally need not be driven primarily by racial tensions. For example, \citet{martins2015linchamentos} writes that lynchings in Brazil are not mainly due to racial prejudice. Local accounts report no significant social difference between victims and perpetrators; nor are Black Brazilians particularly targeted by lynch mobs \citep{band2015rocinha, pearson2018latam, sinhoretto2009linchamentos}. These events might be driven by racism, but they do not reproduce the stark, racially disparate patterns that existed in the United States historically \citep[23]{martins2015linchamentos}. \citet[8]{jung2020lynching} likewise note that ``\textit{racist} social control'' is a unique property of American vigilantism. Brazil's patterns thus pose a puzzle for existing explanations for mob violence and stand in sharp contrast to the American experience \citep{smaangs2016doing, wood2011lynching}.

Recent research has shown that the relationship between states and vigilantism is more complicated than some early studies assumed. Based on extensive interviews and fieldwork in post-apartheid South Africa, Nicholas Rush \citet{smith2019contradictions} finds strong support for the idea that people participate in vigilantism because the state is seen to be \textit{too} strong. Residents perceive a strengthening of the state, fuller support for human rights, and a stronger rule of law. As a result of these perceived changes, crime victims and other community members feel that the state will take too long to arrest, charge, and convict a perpetrator. If the perpetrator is released before trial, they might harm others or intimidate witnesses. Finally, people in South Africa fear that any punishment eventually received will not be severe enough. Accordingly, many South Africans believe it is right for people to take justice into their own hands. In a tragic twist of fate, achieving legal reform and a  closer adherence to the rule of law actually sparks greater use of extrajudicial violence. This suggests a second hypothesis:

\begin{itemize}
  \item \textbf{Hypothesis 2:} Support for vigilantism will increase if people believe states provide too much protection for offenders' rights. 
  \end{itemize}

The studies thus far reviewed tend to focus on state activity. Recent work suggests that residents' perceptions of the state are also important. In a study of Haiti, Danielle F. Jung and Dara Kay Cohen \citeyearpar[3]{jung2020lynching} argue that lynchings are correlated not with state presence, but instead with residents' \textit{views} about the state. They find that perceptions of state legitimacy are far more important in explaining vigilantism than whether state actors are merely present. Residents perceive groups (both state and nonstate actors) as more legitimate if they govern and provide social services. When people view the state as illegitimate because it does not govern, they believe it is their right to participate in vigilantism. This suggests that to explain vigilantism, we must understand both state activity and residents' perceptions of community-state relationships.

Studies of vigilantism in Africa likewise find that culture, norms, and religion are powerful forces shaping the emergence and operation of vigilante groups. In Nigeria, vigilantism takes a variety of shapes, including Hisbah (shari'a enforcement groups), the Bakassi Boys, the Egbusu Boys, and the O'odua People's Congress \citep{pratten2008thief,last2008search, fourchard2008new}. An increase in the influence of neoliberalism (alongside other political changes) also drove vigilantism \citep[5]{pratten2008politics}. In Ghana, nearly 20 percent of the lynchings between 1990 and 2000 happened because people believed that someone (usually an older woman) had used ``mystical powers'' to wound someone's genitals or to cause other health problems  \citep[414]{adinkrah2005vigilante}. Given a relatively weak state, beliefs, culture, and norms shape whether and how vigilante activity happens.

In our study, we find that an honor culture shapes Brazilian beliefs about lynchings. In honor cultures, the reputation and social standing of a person or group is paramount \citep{nisbett2018culture,crowder2017new, vandello2008us, Cao2021honor}. Offenses that threaten to reduce one's standing are seen to give the victim the right (and often the obligation) to respond extralegally \citep{brown2016honor}. Honor cultures are often described as embracing ``a self-protection ethic'' and operate as a system of ``self-help justice'' \citep[1287, 1290]{grosjean2014history}. The offenses need not be serious, as ``everyday challenges, large and small, can undermine an individual's status and reputation, thus rendering his or her honor malleable and uncertain'' \citep[522]{crowder2017new}. However, gendered norms play an important role in honor societies, making heinous crimes especially important to respond to. Being the victim of a serious crime, such as forcible rape, is often seen as tarnishing the reputation of the victim and their family. As a result, as with dueling practices, failure to respond to a harm can affect one's social standing \citep{allen2006duel}. Finally, many honor cultures also follow \textit{lex talionis}, the idea that justice demands an eye for an eye. In places where an honor culture puts the onus to avenge wrongs on local community members, people view state enforcement as less desirable and less legitimate than vigilantism. They see honor as not restored if the state intervenes.

While some of the most prominent studies of honor cultures focus on the history of Scotch-Irish people in the American South \citep[for example,][662-668]{fischer1989albion}, honor cultures still exist in many places today. In the United States, honor cultures exist in some American neighborhoods and are nearly universal in men's prisons across the country \citep{anderson2000code,fleisher2009myth}. Likewise, honor cultures have been a crucial part of clan, tribal, and customary societies in many parts of the world throughout history \citep{weiner2013rule}. As in such societies, it appears that honor cultures tend to emerge in places where people cannot rely on strong and effective states.\footnote{There is a large literature in law and economics that studies how reputation mechanisms can provide order without law \citep{bernstein1992opting,ellickson1991order,greif2006institutions, leeson2014anarchy}.} Cultures of violence can have remarkably long-run effects \citep{vandello2008us}. For example, in the American South, the presence of Scotch-Irish populations in the eighteenth century explains nearly 20 percent of the difference between homicide rates in the North and South today \citep[1286]{grosjean2014history}. An honor culture, and its emphasis on retaliatory norms and violence, did not emerge in the North because the region developed effective formal institutions more quickly. Taken together, the lesson from these studies is that when people cannot rely on state-based institutions to regulate violence, elements of an honor culture can emerge and produce self-help norms, which in turn increase support for vigilantism. This suggests a third hypothesis:

\begin{itemize}
  \item \textbf{Hypothesis 3:} Support for vigilantism will increase if people accept the norms associated with an honor culture.  
  \end{itemize}

In our three experiments, we directly and indirectly tested these hypotheses. We argue that respondents do not believe that state-based legal institutions are the primary way to respond to serious crime. We find that people's attitudes toward vigilantism are shaped strongly by the characteristics of the incident that gives rise to it. In particular, people strongly support lynching by the family of a victim of a sexual offense or murder. Finally, although honor cultures can persist for many decades, our third experiment shows that support for lynchings can be reduced by reminding people of the penalties for lynching and of the risk of sparking vendettas.

%%%%%%%%%%%%%

\section{What Motivates Support for Lynching?}
\label{sub:exp02}
We invited respondents from all regions of Brazil to participate in our experiment. Qualtrics recruited 2,406 adult Brazilian citizens in 2020 between October 30 and December 22 to take part in our survey experiment.\footnote{Our ethics statement is available in Section E of the supplementary material.} We included ten questions on demographics and other information that might influence the results. These include the respondent's age, gender, ethnicity, level of education, monthly family income relative to the minimum wage, political orientation (left to right), support for the death penalty, whether they had been victimized in the last year, their trust in the police, and their trust in the judicial system. We used these measures to disentangle heterogeneous effects in the main responses.

In our first experiment, we examined how the stated motivation for a lynching affects respondents' views about whether it is justified. In particular, we assessed the impact of three factors that have been cited as major drivers of vigilante justice: (1) police ineffectiveness; (2) slow response by the criminal legal system; and (3) demand for harsher punishment for offenders. Belief in the ineffectiveness of policing appears to be a strong predictor of vigilantism \citep{cruz2019determinants, garcia2019anger}. If police cannot or will not stop crime, then people often believe they have a right to do so themselves. Related to this, within the academic literature, lack of trust in the criminal legal system often motivates vigilantism \citep{godoy2004justice, smith2019contradictions}. This is often because of long criminal proceedings, which cause significant anxiety for the victims. Finally, we examined whether respondents believe that the legal punishment given to offenders is severe enough. In particular, we wanted to assess whether respondents are motivated by a desire for harsher penalties in Brazil's criminal legal system.

The experiment consisted of three treatment conditions and one control group. Respondents read an excerpt of a news article describing a real lynching case in Jundia\'{i}, Brazil. Jundia\'{i} is a well-known metropolitan city of about four hundred thousand residents in the state of S\~{a}o Paulo, and we chose it because it is not a particularly distinctive, violent, or unusual city. We slightly edited the original text so that respondents had no prior knowledge of the crime.\footnote{The original article is available at \url{https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso}. Access: August 2020.} Consistent with Bateson's \citeyearpar[3]{bateson2020politics} emphasis on vigilantism as including ``prevention, investigation, or punishment of offenses,'' the vignette for the control group explains that the lynching took place while a crime was occurring. We asked respondents to show their level of support for mob violence using a 0--100 slider, where 0 means no support and 100 means full support.\footnote{We chose not to describe an especially heinous crime, such as murder or sexual assault, because we wanted people to respond to the treatment rather than the crime itself. By focusing on a less serious crime, the treatment is more salient. As shown in the second experiment, there is strong support for lynching for more serious crimes. The baseline of support for lynching in this vignette is about 36 percent (on a scale of 0 to 100), so the crime discussed appears sufficiently serious to justify lynching to a significant number of people.} Respondents in each of the three treatments read the same piece, but with one additional sentence explaining the motivations behind the lynching. Treatment 1 (which is motivated by Hypothesis 1) aimed to test the state-absence explanation. Hypothesis 2 claims that greater protection of offenders' rights increases vigilantism. Treatments 2 and 3 tested two versions of that hypothesis, in the form of slower judicial processes and insufficiently harsh punishments. The vignettes are as follows:

\begin{itemize}
\tightlist
\item
  \emph{Control group}: A man was lynched last Friday in Jundiaí, São Paulo. According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community.\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade.''}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 1 (Police ineffectiveness)}: A man was lynched last Friday in Jundiaí, São Paulo. According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community. \textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the police never patrol the area.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade. \textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque `a polícia nunca patrulha o local.'''}}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 2 (Slow criminal legal system)}: A man was lynched last Friday in Jundiaí, São Paulo. According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community. \textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the judicial system is too slow and the perpetrator is on the street until the case is heard.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade. \textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque ``a justiça é muito lenta e os criminosos ficam soltos até o julgamento.'''}}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 3 (Demand for harsher legal punishment)}: A man was lynched last Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break into a house but was immobilised and beaten by members of the community. \textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the judicial punishment is not harsh enough.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade. \textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque `a punição da justiça não é dura o suficiente.'''}}
\end{itemize}

Before each vignette, respondents read the following text:

\begin{itemize}
\tightlist
\item
  You will be shown a news article. Please read it carefully. After you read the article, we will ask you one question about it.\footnote{In Portuguese: ``Uma notícia será apresentada para você. Por favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta sobre ele.''}
\end{itemize}

After the vignette, respondents were presented with this question:

\begin{itemize}
\tightlist
\item
  Do you think that the lynching was justified? Please use the slider below to indicate your opinion. For disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``Você acha que o linchamento foi correto? Por favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a 49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem discordar.''}
\end{itemize}

\begin{table}[htbp] \centering
  \caption{Average treatment effects for experiment 1}
  \label{tab:exp01main}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
\hline \\[-1.8ex]
 Police do not patrol area & 1.115 &  &  &  \\
  & (1.861) &  &  &  \\
  Justice too slow &  & -0.289 &  &  \\
  &  & (1.927) &  &  \\
  Punishment not harsh enough &  &  & 0.438 &  \\
  &  &  & (1.921) &  \\
  Combined treatments &  &  &  & 0.443 \\
  &  &  &  & (1.545) \\
  Constant & 36.300^{***} & 36.300^{***} & 36.300^{***} & 36.300^{***} \\
  & (1.332) & (1.332) & (1.332) & (1.332) \\
 N & \multicolumn{1}{c}{1,161} & \multicolumn{1}{c}{1,111} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{2,215} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
\end{tabular}
\end{table}

We randomized the treatment and control conditions for the entire respondent pool. This randomization procedure was independent of that of the other experiments. We carried out our hypothesis tests with OLS. We compared the average score given by the control group with the average score given by respondents in each treatment condition.

The first piece of evidence that the experiment provides concerns how baseline levels of support for lynching vary according to individual characteristics. Table \ref{tab:exp01-baselines} shows the impact of gender, race, and ideology on the subjects' tolerance of lynchings. Our dependent variable ranges from 0 to 100. We observed that men are more likely to support lynchings when compared with women. This is in contrast to research in Uganda, Tanzania, and South Africa, where women support mob vigilantism more than men do because they believe that they are less likely to be subject to false accusations \citep{wilke2021gender}.\footnote{On the relationships between gender and violence, see \citet{kadera2018gendered} and related papers.} In line with \citet{martins2015linchamentos}, we found little evidence that support for lynchings is driven primarily by racial prejudice.\footnote{We recognize that race is socially-constructed and that racial categories can be codified in multiple ways. We adopt the racial classification used by the Brazilian Census Bureau (IBGE) as it is widely employed in social research \citep[e.g.][24]{lapop2018brazil} and intuitive to our respondents. Nevertheless, our findings are also consistent with research that uses different, and often more nuanced, conceptions of race \citep{monk2016consequences, schwartzman2020colour}. } Ideology is strongly correlated with support for lynching, with a negative coefficient for citizens who identify as being on the center left or left.\footnote{The results are very similar when we estimated the models using data from our third experiment. Please refer to Section D.2 in the supplementary material for the more information.}

\begin{table}[ht] \centering
  \caption{Determinants of baseline levels of lynching support}
  \label{tab:exp01-baselines}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
\hline \\[-1.8ex]
 Male & 5.124^{***} &  &  & 4.945^{**} \\
  (\textit{Reference: female}) & (1.828) &  &  & (2.165) \\ \\
  Asian &  & 1.119 &  & -6.050 \\
  &  & (4.646) &  & (7.288) \\
  Mixed race &  & 0.724 &  & -5.256 \\
  &  & (2.467) &  & (4.026) \\
  White &  & -1.283 &  & -9.877^{***} \\
  (\textit{Reference: Black}) &  & (2.288) &  & (3.672) \\ \\
  Left &  &  & -11.895^{***} & -10.108^{***} \\
  &  &  & (2.388) & (3.199) \\
  Center left &  &  & -14.707^{***} & -17.484^{***} \\
  &  &  & (2.673) & (3.575) \\
  Center right &  &  & -3.019 & -5.047 \\
  &  &  & (2.881) & (3.838) \\
  Right &  &  & 0.610 & 2.722 \\
  (\textit{Reference: center}) &  &  & (2.328) & (3.235) \\ \\
  Constant & 33.105^{***} & 37.122^{***} & 41.804^{***} & 45.738^{***} \\
  & (1.251) & (2.109) & (1.793) & (4.160) \\
 N & \multicolumn{1}{c}{1,142} & \multicolumn{1}{c}{2,186} & \multicolumn{1}{c}{1,632} & \multicolumn{1}{c}{838} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
\end{tabular}
\end{table}

One interpretation of the null findings for the treatment effects is that state presence and activity have no influence on attitudes toward lynching. If that interpretation is correct, we should reject Hypotheses 1 and 2. However, given the extensive literature discussed above and the qualitative evidence collected in the next experiment (discussed in Section \ref{sec:exp01}), we instead argue that the null results reflect the fact that respondents simply have little to no faith in the criminal legal system in general, and addressing the issues implied in the treatment conditions would have no substantial effect on its perceived effectiveness. Three pieces of evidence support this interpretation. First, many crimes in Brazil are never solved. For example, a recent statistic indicates that the police only solve about 10 percent of the homicides in Brazil, suggesting that even for serious crimes, the police provide little help \citep{pearson2018latam}. Second, Brazilian police forces themselves carry out a substantial number of unjustified killings of people from disadvantaged and minority communities, which undermines their legitimacy and the sense that they can be relied on \citep{willis2015killing}.\footnote{Recent work on Mexico shows that implementing rule of law reforms can reduce police violence \citep{magaloni2020institutionalized}.} In 2019, police killed more than 1,800 people in Rio de Janeiro alone. Third, the Brazilian penal code allows an accused person to appeal each decision several times, so it can take several years (and sometimes more than a decade) before a criminal case is closed \citep{sousa2005utilizaccao}. Given this, people do not believe that a perpetrator will be punished in a timely matter even if put on trial. Finally, along with the rise of Jair Bolsonaro---the far-right president who has publicly called for people to take the law into their own hands \citep{brant2021armas, uol2021bolsonaro}---survey evidence suggests that people have grown considerably more punitive \citep{datafolha2018penademorte}. Taken together, attitudes about lynchings do not seem to be driven by beliefs about \textit{how} the state provides justice. Instead, they reflect the fact that respondents do not, in general, believe that it \textit{can} provide it. In addition, in our next experiment, we found evidence that people who support an honor culture do not think that the state \textit{should} provide justice in certain circumstances.

\section{When Is Lynching Perceived as More Justified?}
\label{sec:exp01}

In the second experiment, we used a choice-based conjoint experimental design. We presented respondents with five pairs of profiles. Each profile consisted of eight attributes: (1) gender of the crime perpetrator; (2) age of the crime perpetrator; (3) race of the crime perpetrator; (4) residency of the crime perpetrator (local or nonlocal); (5) type of offense; (6) gender of the victim of the crime; (7) age of the crime victim; (8) type of lynching perpetrator. The attributes and levels are displayed in table \ref{tab:categories}.\footnote{Limits to the length of the survey mean that many possible attributes and levels could not be included. We chose these particular ones based on a reading of the existing literature and to ensure wide variation in the nature of the lynching scenario.}

\vspace{.3cm}

\begin{table}[htpb]
\begin{center}
\caption{Attributes and levels}
\label{tab:categories}
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Levels}} \\
\Xhline{2\arrayrulewidth}
Gender of crime perpetrator & Male; female \\ [4pt]
Age of crime perpetrator & Teenager; adult; elderly \\ [4pt]
Race of crime perpetrator & Black; white; Native Brazilian; Asian \\ [4pt]
Residency of crime perpetrator & Resident in the community; outsider \\ [4pt]
Offense & Picks pockets; steals cars; molests; rapes; murders \\ [4pt]
Gender of crime victim & Male; female\\ [4pt]
Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
Lynching perpetrators & Bystanders; neighbors; family of the victim; gangs; police \\
\Xhline{2\arrayrulewidth}
\end{tabular}
\end{center}
\end{table}

Respondents were asked to indicate in which scenario in each pair they thought that extrajudicial punishment was more justified. We also included a text box below each experiment for subjects to explain why they selected a particular case and whether they believed lynching was justified in neither case. Respondents read the following prompt before they started the experiment:

\begin{itemize}
\tightlist
\item
  Lynchings are often used as social punishment in Brazil. Lynchings are cases in which three or more people physically attack or execute a suspected criminal in public. We are interested in knowing more about how Brazilians see these episodes. In the next five questions, please read the description of two possible lynching victims in Brazil and indicate in which case you believe the punishment is more justified. Even if you are not entirely sure, please select one of the cases.\footnote{In Portuguese: ``Linchamentos são às vezes usados como punição social no Brasil. Linchamentos são casos nos quais três ou mais pessoas agridem fisicamente ou executam em público um suspeito de um crime. Estamos interessados em saber mais sobre como os brasileiros vêem estes episódios. Nas próximas cinco questões, por favor, leia a descrição de duas possíveis vítimas de linchamento no Brasil e indique em quais delas você acredita que a punição é mais justificada. Mesmo que você não tenha certeza, por favor, escolha um dos casos.''}
\end{itemize}

We estimated our conjoint experiments with the \texttt{cregg} package \citep{leeper2018cregg} for the R statistical language \citep{rstats2019}. We report marginal means in our main analysis instead of average marginal component effects (AMCEs). \citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup comparisons as model results are sensitive to the choice of reference categories in interactions. In contrast, marginal means allow for a clear description of quantities of interest, in our case preferences about lynching, while also allowing for easy comparisons between groups of respondents. In a forced-choice experiment such as this one, marginal means are interpreted as probabilities. A marginal-means estimate of 0.5 indicates that respondents are indifferent to this attribute vis-à-vis other attributes. When the coefficient is lower than 0.5, respondents dislike profiles with this attribute. Conversely, when the point estimate is higher than 0.5, respondents prefer profiles containing a given attribute.

Figure \ref{fig:exp01} shows the main results for the conjoint experiment. The graph illustrates the preference associated with each attribute of the hypothetical lynching episode. Dots with horizontal bars represent point estimates and 95 percent confidence intervals from linear regressions with robust standard errors clustered at the respondent level.\footnote{This was a forced-choice experiment, so respondents had to choose one of the scenarios as more justified. To see whether this was problematic, we included an optional open-text box inviting respondents to explain their choices. Based on a semisupervized Dirichlet allocation model, we estimated about 20 percent of respondents were opposed to lynchings in general. Please refer to Section C.4 of the supplementary material for further information.}

\begin{figure}[ht]
\includegraphics[width=17cm]{conjoint-black.pdf}
\caption{Relative preferences for lynching-episode attributes (marginal means)}
\centering
\label{fig:exp01}
\end{figure}

Respondents selected male offenders (0.548, SE = 0.003, $p$-value $<$ 0.001) as preferred lynching victims more often than female offenders (0.438, SE = 0.004, $p$-value $<$ 0.001). We found identical results in our subgroup analyses, in which we disaggregated our sample according to respondents' gender, income, race, support for the death penalty, and views on the police and judiciary. In all cases, men and teenage boys were more likely to be selected as more justified victims of lynching. Compared with the attributes we discuss below, the gender of the crime perpetrator had one of the largest effects in our experiment. With regard to the age of the crime perpetrator, respondents tolerated the lynching of adults (0.520, SE = 0.005, $p$-value $<$ 0.001) more than attacks against teenagers (0.498, SE = 0.005, $p$-value = 0.650) or the elderly (0.483, SE = 0.005, $p$-value $<$ 0.001). More precisely, subjects were indifferent toward teenagers but reacted positively to lynching of adults and negatively to lynching of elderly people.

When we analyzed the effect of the race of the crime perpetrator, in contrast with the American experience, respondents favored the lynching of white perpetrators (0.512, SE = 0.006, $p$-value = 0.050) the most. Of all the racial identities that we included in the experiment, Black people were the least likely to be chosen as a more justified lynching victim (0.490, SE = 0.006, $p$-value = 0.092), although the 95 percent confidence intervals overlap with the remaining categories. The effect is also robust for most subgroups, including white respondents. Asian respondents, however, rated fellow Asians as their least preferred choice. Taken together, the results provide experimental evidence that support for lynchings in Brazil does not resemble the typical racial patterns scholars have observed in the United States \citep{dray2003hands,seguin2019national,obert2018keeping}. These findings are consistent with recent research on vigilantism in Haiti \citep{jung2020lynching} and with journalistic observations. They further suggest that the US experience with lynchings might be distinct from vigilantism in other places and times \citep{oliveira2016mob}.

The residency of the perpetrator is not a significant driver of support for lynching. Subjects were indifferent as to whether the crime perpetrator lives in the area (0.498, SE = 0.004, $p$-value = 0.668) or in another neighborhood (0.502, SE = 0.004, $p$-value = 0.668). In this sense, it is possible that subjects see lynchings not as a means to protect the area in which they live, which we commonly suppose vigilante groups do, but rather as retribution in specific cases.

The next attribute is type of offense. Rape was by far the most significant attribute in our model (0.719, SE = 0.009, $p$-value $<$ 0.001), followed by murder (0.608, SE = 0.006, $p$-value $<$ 0.001) and molestation (0.538, SE = 0.006, $p$-value $<$ 0.001). It is not surprising that murder was an important offense mentioned by respondents, and the fact that rape appeared as subjects' first choice is not entirely unexpected either. Among incarcerated populations, sex offenders are near-universally seen as having the lowest standing in the community and typically are subject to more violence than most other incarcerated people \citep{fleisher2009myth}. These findings support Hypothesis 3, in that honor cultures tend to view heinous and sex crimes as warranting an extrajudicial response. Overall, we found that respondents do not believe that property crimes, such as car theft (0.351, SE = 0.009, $p$-value $<$ 0.001) and pickpocketing (0.314, SE = 0.006, $p$-value $<$ 0.001), provide justification for lynching. When we analyzed the data by groups, we also saw that poorer respondents, whose household income is less than R\$3,000 (US\$650) per month, are more likely to support the lynching of individuals who commit a property crime.

Consistent with Hypothesis 3, when we analyzed the gender of the crime victim, we found that respondents support lynchings more strongly when the victim is a woman or teenage girl (0.511, SE = 0.004, $p$-value = 0.002) and less strongly when the lynching victim is a man or teenage boy (0.489, SE = 0.004, $p$-value = 0.002). The difference here is smaller than when we considered the gender of the crime perpetrator, but as in the previous estimation the 95 percent confidence intervals of each attribute did not overlap.

For age, we observed that respondents were particularly concerned about children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this attribute is strongly correlated with support for lynchings. Respondents also thought lynchings are more justified when the victim is a teenager (0.505, SE = 0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$ 0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001). Together, these facts lend credence to the idea that citizens see lynchings as a valid punishment when the victims have little chance of defending themselves.

Lastly, we examined who respondents believed are more legitimate perpetrators of lynchings. Consistent with a key aspect of an honor culture, respondents considered the family to be the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$ 0.001). Again, the intervals here did not overlap with those of any other category. Bystanders (0.505, SE = 0.007, $p$-value = 0.450), gangs (0.502, SE = 0.007, $p$-value = 0.815), and neighbors (0.492, SE = 0.007, $p$-value = 0.262) do not increase or decrease respondents attitudes about lynching. If the police carry out a lynching, that reduced the perceived justification (0.467, SE = 0.007, $p$-value $<$ 0.001). In sum, respondents did not believe that lynchings should be carried out by the state but did believe they should be used as a tool for individual or family retribution.

Respondents were given the opportunity to explain the reason why they answered as they did. We analyzed a random sample of nearly 17 percent of the answers. Three major themes emerge that are consistent with the argument that elements of an honor culture played an important role. First, respondents felt that crimes that were especially heinous deserved a response, and often one that would follow lex talionis. For example, one respondent explained their choice of a particular case as more justified by noting, ``Eye for an eye, it's absolutely fair.'' A second  theme is the injustice of victimizing vulnerable populations. Two quotes representative of this theme are: ``The victim is an elderly person, it's okay to lynch the criminal,'' and ``If the victim is a child, lynchings are not enough, they deserve more.'' Finally, a third theme is that families have a special right to vengeance. One respondent explained their choice by saying, ``The family was appalled and did justice with their own hands!'' These open-ended answers are consistent with the quantitative results about \textit{what} people believe, but they also provide additional evidence about \textit{why} they hold their beliefs. Elements of an honor culture matter.

%%%%%%%%%%%%%%%%%%%%%
\section{How to Reduce Support for Lynchings}
\label{sec:exp03}

Even if people view lynchings as a legitimate activity, that does not mean that this norm cannot be changed \citep{weaver2019judge}. In the third experiment, we measured the effect of information provision on attitudes about lynching. More specifically, we tested whether reminding respondents about the legal and social consequences of vigilante justice reduces subjects' support for it. The experiment included three treatment conditions and a control group. In all of them we presented respondents with a short statement affirming that some Brazilians support vigilantism under certain conditions. We asked the control group to rate their agreement with the statement. Respondents were asked to use 0 to 49 if they disagreed, 50 if they neither agreed nor disagreed, and 50--100 if they agreed with the statement.

Each of the three treatment groups received a different message about the legal or social consequences of lynching in Brazil. In the first treatment, we informed subjects about how the Brazilian constitution and penal code punishes civilian violence. The second treatment group was notified about the human rights guarantees enshrined in Brazil's legal framework. The last treatment noted that lynchings can spark vendettas and initiate a cycle of violence in the community. Subjects in the control group received no information about the consequences of lynchings. The text shown to the control and treatment groups can be read below.

\begin{itemize}
\tightlist
\item
  \emph{Control group:} In Brazil, some people believe that lynching may be justified under certain conditions. To what degree do you agree or disagree that lynching can be justified? Please use the slider below to indicate your preference. For disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições. O quanto você concorda ou discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.''}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 1 (Legal punishment for lynching perpetrators):} In Brazil, some people believe that lynching may be justified under certain conditions. \textbf{However, the Brazilian constitution and penal code strictly forbid lynching and those involved can be accused of torture or murder}. To what degree do you agree or disagree that lynching can be justified? Please use the slider below to indicate your preference. For disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições. \textbf{Entretanto, a constituição e o código penal do Brasil proíbem estritamente os linchamentos e os envolvidos podem ser acusados de tortura ou assassinato.} O quanto você concorda ou discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.''}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 2 (Human rights):} In Brazil, some people believe that lynching may be justified under certain conditions. \textbf{However, the Brazilian constitution states that all individuals have the right of not being tortured, including criminals}. To what degree do you agree or disagree that lynching can be justified? Please use the slider below to indicate your preference. For disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições. \textbf{Entretanto, a constituição do Brasil afirma que todos os indivíduos têm o direito de não serem torturados, inclusive criminosos}. O quanto você concorda ou discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.''}
\end{itemize}

\begin{itemize}
\tightlist
\item
  \emph{Treatment 3 (Vendettas):} In Brazil, some people believe that lynching may be justified under certain conditions. \textbf{However, lynchings can trigger a new cycle of violence as the family or friends of the victim may retaliate against the community}. To what degree do you agree or disagree that lynching can be justified? Please use the slider below to indicate your preference. For disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições. \textbf{Entretanto, linchamentos podem iniciar um ciclo de violência pois a família ou amigos da vítima podem retaliar a comunidade}. O quanto você concorda ou discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.''}
\end{itemize}

We are interested in the difference between the average score given by each of the treatment groups and the average score given by the control group.\footnote{As we did in the previous experiment, we randomized the treatment and control conditions to all subjects included in our sample. The treatment assignment here was independent of that of the previous two experiments.} We estimate average treatment effects using OLS with dummy indicators for the treatment groups.

\vspace{.5cm}

\begin{table}[ht] \centering
  \caption{Average treatment effects for experiment 3}
  \label{tab:exp03main}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
\hline \\[-1.8ex]
 Constitution and penal code & -4.509^{**} &  &  &  \\
  & (1.805) &  &  &  \\
  Human rights &  & -1.571 &  &  \\
  &  & (1.801) &  &  \\
  Vendettas &  &  & -3.156^{*} &  \\
  &  &  & (1.879) &  \\
  Combined treatments &  &  &  & -3.023^{**} \\
  &  &  &  & (1.493) \\
  Constant & 40.823^{***} & 40.823^{***} & 40.823^{***} & 40.823^{***} \\
  & (1.293) & (1.293) & (1.293) & (1.293) \\
 N & \multicolumn{1}{c}{1,114} & \multicolumn{1}{c}{1,173} & \multicolumn{1}{c}{1,092} & \multicolumn{1}{c}{2,215} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
\end{tabular}
\end{table}
\normalsize

Table \ref{tab:exp03main} summarizes our main results for this experiment. We find that when respondents are reminded of legal punishments associated with lynchings, their support for lynching decreases by about 11 percent. This result is consistent with the idea that respondents will support an activity less if they perceive it to be more costly. The next treatment group was told the human rights message. The result is not statistically significant and indicates that appeals to individual liberties and the rule of law are likely to fall short. This finding has practical implications, as many campaigns against violent crimes are conducted by human rights groups, which tend to emphasize this type of message. However, in an honor culture, participants do not generally believe that offenders have human rights. Accordingly, we have little reason to believe that such messaging is effective. By contrast, Treatment 1 reminds respondents that perpetrators of lynching potentially face a high personal cost from doing so.

Our last treatment, which raises the possibility of sparking vendettas, exerts a large, negative effect on support for lynchings. Mentioning that lynchings trigger cycles of violence has a negative effect of about 8 percent when compared with the control group. While we expected that the coefficient for this treatment condition would be larger than that for the treatment on legal punishments, the means of both groups are not statistically different from each other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). As with the other experiments, the results remain stable when we conduct subgroup analyses.

In sum, reminding respondents of human rights guarantees does not reduce support for lynchings, but affirming that they can be punished for their acts, either by the state or by individuals, can change their opinions.

\section{Conclusion}
\label{conclusion}

Regulating violence is one of the most fundamental responsibilities of the state, and in many places in the world today, states are failing to do so. In Brazil, lynchings are commonplace and are only one form of vigilantism and extralegal violence plaguing the country. Many favelas are dominated by organized crime groups that engage in violence and wield the threat of violence extralegally \citep{arias2006dynamics,barnes2017criminal}. In this paper, we used survey experiments to examine people's attitudes toward lynching to better understand what makes people feel some instances are more justified, which reasons for doing so gain support, and how to reduce support for lynchings. If people felt like they cannot rely on the state to provide effective regulation of serious violence, then they were more likely to develop beliefs and norms that legitimate the extrajudicial use of violence. More specifically, we found evidence that elements of an honor culture influence how and why extrajudicial violence is used and legitimated. People found lynchings more justifiable when they were in response to especially heinous crimes and when the crimes were perpetrated against vulnerable populations, and they viewed the family as having a distinctive duty for carrying out vengeance. Nevertheless, we were able to reduce support for lynchings by reminding respondents that lynchings are a criminal act and that lynchings risk igniting vendettas.

This paper highlights the importance of ideas, norms, and culture in shaping the prevalence of extrajudicial violence. Most directly, our data show that an honor culture affects when and where lynchings are believed to be justified. Yet, ideas, norms, and culture also affect whether the phenomenon continues. In the United States, for example, Southern lynchings were supported tacitly and openly well into the early twentieth century. Lynching did not decline until newspapers in other parts of the country began to notice, publicize, and criticize the practice \citep{weaver2019judge}.\footnote{On the history and decline of lynching in the United States, see also \citet{wood2011lynching} and \citet{rushdy2012american}.} Local elites could not control these narratives, and these outside voices helped to delegitimize lynchings. Our findings support the argument that norms of legitimacy are crucial to understand the patterns and practices of vigilante violence.

Extrajudicial violence also has profound consequences on political development and the rule of law. First, extensive reliance on extrajudicial violence undermines legal and judicial reform because people feel informal, local dispute resolution is preferable to state-based institutions \citep{blair2020peacekeeping}. This prevents the state from becoming the focal body to resolve criminal and civil conflicts. Second, and related, this has the potential to create a feedback effect in which more vigilantism leads to people viewing the state as less effective and less legitimate, which then leads to more vigilantism and less state effectiveness \citep{jung2020lynching}. Third, a legacy of lynchings can have detrimental effects on political participation. In the United States, for instance, racist lynchings reduced local Black voter turnout substantially \citep{jones2017political}. Given the prevalence of vigilantism in places with precarious electoral systems and substantial ethnic diversity, vigilantism is likely to undermine many forms of political participation. Finally, improving institutions often has negative, unintended consequences that are difficult to ameliorate. This is well documented in the case of rule-of-law reform and vigilantism in South Africa \citep{smith2019contradictions}, but we also see it in the push for democratization in Mexico \citep{trejo2021high} and attempts to reduce gang control of Brazilian favelas \citep{magaloni2020killing}. Outcomes often worsen on important margins when people seek to improve judicial practice, reduce corruption, or reduce the use of extrajudicial violence. 
Developing effective political institutions is one of the state's most important responsibilities, and vigilante violence presents a substantial challenge to doing so.

\newpage

\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

% Bibliography
\bibliography{references.bib}

\end{document}

### 2021-06-16 pre-analysis-plan/pre-analysis-plan-august-2020.Rmd
first draft

--- 2020-09-24 pre-analysis-plan/freire-skarbek-lynching.Rmd
@@
         | Pre-Analysis Plan:
-        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil[^thanks]
+        | Casting the First Stone: Understanding Attitudes towards Lynching in Brazil
 author:
-  - Danilo Freire[^freire]
-  - David Skarbek[^skarbek]
-date: \today
+date: 10 August, 2020
 abstract: "Why do citizens support extrajudicial violence?
@@
 
-[^thanks]: We thank Rosario Aguilar, Louise Araújo, Miriam Golden, Umberto
-Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Scacco for their valuable comments.
+[^thanks]: We thank Louise Araújo, Rosario Aguilar, Miriam Golden, Umberto Mignozzetti, Irfan Nooruddin, Catarina Roman, and Alex Sacco for their valuable comments.
 

### 2022-05-01 article/main.tex
create develop branch

@@
 % !TEX program = XeLaTeX
-\documentclass[12pt,ansiapaper]{article}
+\documentclass[12pt,a4paper]{article}
 
@@
 \usepackage[english]{babel}
-\usepackage[english]{isodate}
-\cleanlookdateon
+% \usepackage[english]{isodate}
+% \cleanlookdateon
 
@@
   colorlinks=true,
-      pdfauthor={Danilo Freire; David Skarbek},
+      pdfauthor={},
       pdfkeywords={Brazil, crime, extralegal violence, lynching, vigilantism},
@@
 % Author
-\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
+\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:dfreire@lincoln.ac.uk}{\texttt{dfreire@lincoln.ac.uk}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
 
 % Date
-\date{June 16, 2021}
+\date{\today}
 
@@
 The regulation of violence is one of the most important functions of the state.
-When states control violence effectively, markets, politics, and civil society can flourish.
-However, in many places, violence is poorly regulated and nonstate armed actors---ranging from residents to rebel groups---use violence at their own discretion.
-The extralegal use of violence is also a clear violation of the rule of law \citep[48-49]{blair2020peacekeeping}.
-More generally, the challenge of monopolizing violence is at the heart of the Weberian definition of the state, and it is arguably one of the most fundamental questions of political economy.
-While political scientists have written extensively on civil wars, rebel governance, and criminal violence \citep{arjona2016rebelocracy, trejo2021high, barnes2017criminal}, they have written far less about vigilante violence.
-In this paper, we use survey experiments to better understand people's attitudes toward the use of extralegal violence.
+When states control violence effectively, markets, politics, and civil society
+can flourish. However, in many places, violence is poorly regulated and
+nonstate armed actors---ranging from residents to rebel groups---use violence
+at their own discretion. The extralegal use of violence is also a clear
+violation of the rule of law \citep[48-49]{blair2020peacekeeping}. More
+generally, the challenge of monopolizing violence is at the heart of the
+Weberian definition of the state, and it is arguably one of the most
+fundamental questions of political economy. While political scientists have
+written extensively on civil wars, rebel governance, and criminal violence
+\citep{arjona2016rebelocracy, trejo2021high, barnes2017criminal}, they have
+written far less about vigilante violence. In this paper, we use survey
+experiments to better understand people's attitudes toward the use of
+extralegal violence.
 
-Although lynchings and mob violence more generally have decreased in advanced democracies, it remains widespread in many parts of the world.
-Based on US State Department reports, \citet[33]{jung2020lynching} find that between 1976 and 2018, lynchings occurred in all regions of the world and in more than a hundred countries.
-In particular, Latin America has been severely affected by a recent increase in lynchings.
-Such a surge in citizen-led violence has reportedly been motivated by growing numbers of drug-related crimes and by police ineffectiveness \citep{mallen2014vigilantes}.
-Brazil provides a telling example.
-From 2011 to 2015, the country registered about 2,500 lynching episodes.
-In 2015, 173 people were killed by angry mobs---nearly one execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
-According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for more than thirty years, these figures are not only the highest in the country's history, but among the highest in the world.
-The people who participate in lynchings are typically  young men, but they also sometimes include teenage women and girls, elderly women, and even members of the local police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São Paulo kill hundreds of people every year in a way that looks similar to vigilantism \citep{willis2015killing}.
-Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas extralegally \citep{magaloni2020killing}.}
+Although lynchings and mob violence more generally have decreased in advanced
+democracies, it remains widespread in many parts of the world. Based on US
+State Department reports, \citet[33]{jung2020lynching} find that between 1976
+and 2018, lynchings occurred in all regions of the world and in more than a
+hundred countries. In particular, Latin America has been severely affected by a
+recent increase in lynchings \citep{godoy2004justice, kloppe2020vortex}.
+Such a surge in citizen-led violence has reportedly been motivated by growing
+numbers of drug-related crimes and by police ineffectiveness
+\citep{mallen2014vigilantes}. Brazil provides a telling example. From 2011 to
+2015, the country registered about 2,500 lynching episodes. In 2015, 173 people
+were killed by angry mobs---nearly one execution every two days
+\citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
+Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
+Brazil for more than thirty years, these figures are not only the highest in
+the country's history, but among the highest in the world. The people who
+participate in lynchings are typically young men, but they also sometimes
+include teenage women and girls, elderly women, and even members of the local
+police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São
+  Paulo kill hundreds of people every year in a way that looks similar to
+vigilantism \citep{willis2015killing}. Recent work also documents how organized
+crime groups in Brazil use extralegal violence in the process of governing
+favelas extralegally \citep{magaloni2020killing}.}
 
-There is no strong consensus about what factors explain people's participation in vigilantism.
-Some of the most common explanations focus on the role of state-based institutions.
-People living in places with weak or failed states might engage in vigilante activity to control crime and to enforce social order \citep{bancroft1887works}.
-However, others argue that it is growth in state capacity that motivates people to take justice into their own hands out of fear that the state will not punish perpetrators or will do so too lightly \citep{smith2019contradictions}.
-In Latin America in particular, vigilantism has been found to be associated with previous exposure to violence \citep{garcia2019anger}, untrustworthy law enforcement \citep{zizumbo2017community}, perceived insecurity \citep{ceobanu2011crime, godoy2004justice}, and economic and social inequality \citep{phillips2017inequality,godoy2006popular,arias2010violent}.
+There is no strong consensus about what factors explain people's participation
+in vigilantism. Some of the most common explanations focus on the role of
+state-based institutions. People living in places with weak or failed states
+might engage in vigilante activity to control crime and to enforce social order
+\citep{bancroft1887works}. However, others argue that it is growth in state
+capacity that motivates people to take justice into their own hands out of fear
+that the state will not punish perpetrators or will do so too lightly
+\citep{smith2019contradictions}. In Latin America in particular, vigilantism
+has been found to be associated with previous exposure to violence
+\citep{garcia2019anger}, untrustworthy law enforcement
+\citep{zizumbo2017community}, perceived insecurity \citep{ceobanu2011crime,
+godoy2004justice}, and economic and social inequality
+\citep{phillips2017inequality,godoy2006popular,arias2010violent}.
 
-Part of the reason for the proliferation of findings is that studying vigilantism empirically presents a substantial challenge.
-Many studies focus on vigilantism along the American frontier in the mid-nineteenth century, drawing on archival and historical documents  \citep{brown1975strain, courtwright2009violent, obert2018six}.
-However, much relevant evidence needed to test competing theories has been lost to history.
-Qualitative and ethnographic research provides deep insights into the motivations and emotions surrounding social disorder, violence, and vigilantism \citep{godoy2002lynchings}.
-Yet, like all research approaches, this method has shortcomings, including recall bias and social desirability bias.
-Quantitative approaches that rely on observational data are likewise often limited in important ways, including that relevant data may be absent, data may imperfectly map onto theoretical concepts, and data may be collected and aggregated at a level of analysis far removed from the studied phenomenon.
-Finally, while a credible identification strategy is not necessary for making causal claims, it can often solve issues that arise from poor-quality data.
-Unfortunately, credible identification strategies are often not available.
-As \citet[17]{bateson2020politics} notes, ``Field experiments on vigilantism would raise serious ethical concerns, and natural experiments are rare.''
+Part of the reason for the proliferation of findings is that studying
+vigilantism empirically presents a substantial challenge. Many studies focus on
+vigilantism along the American frontier in the mid-nineteenth century, drawing
+on archival and historical documents  \citep{brown1975strain,
+courtwright2009violent, obert2018six}. However, much relevant evidence needed
+to test competing theories has been lost to history. Qualitative and
+ethnographic research provides deep insights into the motivations and emotions
+surrounding social disorder, violence, and vigilantism
+\citep{godoy2002lynchings}. Yet, like all research approaches, this method has
+shortcomings, including recall bias and social desirability bias. Quantitative
+approaches that rely on observational data are likewise often limited in
+important ways, including that relevant data may be absent, data may
+imperfectly map onto theoretical concepts, and data may be collected and
+aggregated at a level of analysis far removed from the studied phenomenon.
+Finally, while a credible identification strategy is not necessary for making
+causal claims, it can often solve issues that arise from poor-quality data.
+Unfortunately, credible identification strategies are often not available.  As
+\citet[17]{bateson2020politics} notes, ``Field experiments on vigilantism would
+raise serious ethical concerns, and natural experiments are rare.''
 
-In this paper, we use survey experiments to better understand individual perceptions of vigilantism.
-Based on the existing literature, we designed three survey experiments to understand lynchings in Brazil in particular.
-This empirical approach offers several distinct advantages.
-First, the data we collected come from the same level of analysis as the phenomenon itself: local residents.
-Second, online surveys are less susceptible to social desirability bias, and survey experiments help to elicit sensitive information---an especially important benefit in researching this topic \citep{grimm2010social}.
-Third, the experimental nature of the approach allows us to estimate the size of effects.
-Finally, we can also control for confounding, which is a potential concern with more qualitative methods.
+In this paper, we use survey experiments to better understand individual
+perceptions of vigilantism. Based on the existing literature, we designed three
+survey experiments to understand lynchings in Brazil in particular. This
+empirical approach offers several distinct advantages. First, the data we
+collected come from the same level of analysis as the phenomenon itself: local
+residents. Second, online surveys are less susceptible to social desirability
+bias, and survey experiments help to elicit sensitive information---an
+especially important benefit in researching this topic \citep{grimm2010social}.
+Third, the experimental nature of the approach allows us to estimate the size
+of effects. Finally, we can also control for confounding, which is a potential
+concern with more qualitative methods.
 
-One obvious downside to survey experiments is the difficulty in making inferences about the external validity of findings.
-\citet[17-18]{bateson2020politics} suggests that the closer that a fictional survey prompt matches the real world, the better the external validity.
-Accordingly, our first experiment is based on an actual account of a lynching in Jundia\'{i}, Brazil.
-In the second experiment, we include a wide range of lynching-scenario characteristics that allow respondents to consider detailed, realistic examples.
-Our third experiment examines whether providing different types of information can affect respondents' perceptions of lynchings.
-Our strategy here is similar to that of public marketing campaigns that governments often use to change public opinion.
-In this experiment, we provide information akin to government messaging to the general public.
-Many theories of vigilantism presume that public beliefs and public opinion establish norms about lynchings.
-Even if none of our respondents have participated or will participate in lynchings, they are part of the community that creates norms about lynching.
+One obvious downside to survey experiments is the difficulty in making
+inferences about the external validity of findings.
+\citet[17-18]{bateson2020politics} suggests that the closer that a fictional
+survey prompt matches the real world, the better the external validity.
+Accordingly, our first experiment is based on an actual account of a lynching
+in Jundia\'{i}, Brazil. In the second experiment, we include a wide range of
+lynching-scenario characteristics that allow respondents to consider detailed,
+realistic examples. Our third experiment examines whether providing different
+types of information can affect respondents' perceptions of lynchings. Our
+strategy here is similar to that of public marketing campaigns that governments
+often use to change public opinion. In this experiment, we provide information
+akin to government messaging to the general public. Many theories of
+vigilantism presume that public beliefs and public opinion establish norms
+about lynchings. Even if none of our respondents have participated or will
+participate in lynchings, they are part of the community that creates norms
+about lynching.
 

### 2022-06-15 appendix/appendix-short.Rmd
update paper and appendix

@@
 title: |
-       | Supplementary Material for "Vigilantism, Institutions, and Honor Culture: Understanding Attitudes toward Lynching in Brazil"
+       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
 author:
@@
 - "David Skarbek[^skarbek]"
-date: \today
+date: 14 June 2022
 fontfamily: libertine
@@
 This appendix contains additional tables and graphs that complement the results
-we present in "_Vigilantism, Institutions, and Honor Culture: Understanding
-Attitudes towards Lynching in Brazil_". An extended version of this file, which
-includes further tests for heterogeneous effects and `R` code, is available at
-[_redacted for peer review_]. The repository also contains our pre-analysis
-plan and the `php` scripts we used in our conjoint experiment.
+we present in "_Vigilantism and Institutions: Understanding Attitudes towards
+Lynching in Brazil_". An extended version of this file, which includes further
+tests for heterogeneous effects and `R` code, is available at [_redacted for
+peer review_]. The repository also contains our pre-analysis plan and the `php`
+scripts we used in our conjoint experiment.
 

### 2022-06-15 appendix/appendix.Rmd
update paper and appendix

@@
 title: |
-       | Supplementary Materials for "Vigilantism, Institutions, and Culture: Understanding Attitudes towards Lynching in Brazil"
+       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
 author:
@@
 
+\appendix
+
 # Introduction
@@
 This appendix contains the `R` code required to replicate the results we
-present in "_Vigilantism, Institutions, and Culture: Understanding Attitudes
-towards Lynching in Brazil_". This file also includes the descriptive
-statistics of our sample, the average marginal component effects (AMCEs) for
-our conjoint experiment, and additional subgroup analyses for all three
-experiments.
+present in "_Vigilantism and Institutions: Understanding Attitudes towards
+Lynching in Brazil_". This file also includes the descriptive statistics of our
+sample, the average marginal component effects (AMCEs) for our conjoint
+experiment, and additional subgroup analyses for all three experiments.
 
@@
 
-# Table
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
-          p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp01main",
-          title = "Experiment 01 -- Main Results", style = "apsr",
-          dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp01main", title = "Experiment 01 -- Main Results",
+          style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
           covariate.labels = c("Police does not patrol area", "Justice too slow",
@@
 
-Here we estimate the effect of gender, race, and political ideology on
-lynching support. We find that males, blacks, and mixed race individuals are
-more likely to endorse lynchings when compared to females and whites,
-respectively. Left and center-left voters, in contrast, show lower support for
-lynchings when compared to centrists.
+Here we estimate the effect of gender, race, and political ideology on lynching
+support. We find that males are more likely to tolerate lynchings, whereas left
+and center-left voters oppose lynchings more strongly than centrists. In our
+second model, we find no effect for race, and in the last column we see that
+white respondents are less supportive of lynchings.
 
@@
          race %in% c("Asian", "Black", "Mixed Race", "White"),
-         ideology %in% c("Center", "Center-Left", "Center-Right",
-                         "Left", "Right"))
-
-m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_group)
-m2 <- lm(exp01_outcomes ~ relevel(race, ref = "White"), data = df_exp01_group)
-m3 <- lm(exp01_outcomes ~ relevel(ideology, ref = "Center"), data = df_exp01_group)
-m4 <- lm(exp01_outcomes ~ gender + relevel(race, ref = "White") +
-         relevel(ideology, ref = "Center"), data = df_exp01_group)
+         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))
+
+df_exp01_gender <- df_exp01 %>% filter(gender == c("Female", "Male"))
+df_exp01_race <- df_exp01 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
+  mutate(race = fct_relevel(race, "Black"))
+df_exp01_ideology <- df_exp01 %>%
+         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+         mutate(ideology = fct_relevel(ideology, "Center"))
+
+m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_gender)
+m2 <- lm(exp01_outcomes ~ race, data = df_exp01_race)
+m3 <- lm(exp01_outcomes ~ ideology, data = df_exp01_ideology)
+m4 <- lm(exp01_outcomes ~ gender + race + ideology, data = df_exp01_group)
 
@@
           Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Male", "Asian", "Black", "Mixed Race",
+          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
                                "Left", "Center-Left", "Center-Right", "Right"),
@@
 
+### Political Ideology
+
+Here we disaggregate the results according to political ideology. We see that
+political views do not change the overall responses.
+
+\footnotesize
+```{r conjoint-ideology, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.2, fig.pos="H"}
+# Model
+cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
+  drop_na(ideology)
+cjdt$Ideology <- factor(cjdt$ideology)
+mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by =
+            ~Ideology)
+
+# Plot
+plot(mm_by, group = "Ideology", vline = 0.5, header_fmt = "%s") +
+  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
+  scale_colour_viridis_d(option = "inferno", end = 0.8)
+
+# Tables
+mm_left <- mm_by %>% filter(BY == "Left")
+table_mm_by(mm_left, capt = "Marginal Means -- Left")
+mm_center_left <- mm_by %>% filter(BY == "Center-Left")
+table_mm_by(mm_center_left, capt = "Marginal Means -- Center-Left")
+mm_center <- mm_by %>% filter(BY == "Center")
+table_mm_by(mm_center, capt = "Marginal Means -- Center")
+mm_center_right <- mm_by %>% filter(BY == "Center-Right")
+table_mm_by(mm_center_right, capt = "Marginal Means -- Center-Right")
+mm_right <- mm_by %>% filter(BY == "Right")
+table_mm_by(mm_right, capt = "Marginal Means -- Right")
+mm_dont_know <- mm_by %>% filter(BY == "Don't Know")
+table_mm_by(mm_dont_know, capt = "Marginal Means -- Don't Know")
+mm_not_say <- mm_by %>% filter(BY == "Rather Not Say")
+table_mm_by(mm_not_say, capt = "Marginal Means -- Rather Not Say")
+```
+\normalsize
+
+\clearpage
+
 ### Support for Death Penalty
@@
 ```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
-# Unsupervised LDA
+# Unsupervized LDA
 tmod_lda <- textmodel_lda(dfmat, k = 3)
@@
 ```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
-# Semisupervised LDA
+# Semisupervized LDA
 keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
@@
 
-# Table
 stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), header = FALSE,
@@
                                "Vendettas", "Combined treatments"),
+          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
+          keep.stat = "n", no.space = TRUE)
+
+```
+\normalsize
+
+## Determinants of Baseline Levels
+
+As we did in the first experiment, we evaluate how individual characteristics
+impact lynching support. The results are similar to those presented in table
+\ref{tab:exp01baseline}, with the exception that the coefficient for white
+respondents is negative in two estimations, and the coefficient for male does
+not reach statistical significance in the last model ($p$-value = 0.11).
+
+\footnotesize
+```{r exp03-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
+df_exp03_group <- df_exp03 %>%
+  filter(gender == c("Female", "Male"),
+         race %in% c("Asian", "Black", "Mixed Race", "White"),
+         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))
+
+df_exp03_gender <- df_exp03 %>% filter(gender == c("Female", "Male"))
+df_exp03_race <- df_exp03 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
+  mutate(race = fct_relevel(race, "Black"))
+df_exp03_ideology <- df_exp03 %>%
+         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
+         mutate(ideology = fct_relevel(ideology, "Center"))
+
+m1 <- lm(exp03_outcomes ~ gender, data = df_exp03_gender)
+m2 <- lm(exp03_outcomes ~ race, data = df_exp03_race)
+m3 <- lm(exp03_outcomes ~ ideology, data = df_exp03_ideology)
+m4 <- lm(exp03_outcomes ~ gender + race + ideology, data = df_exp03_group)
+
+stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
+          header = FALSE, align = TRUE, label = "tab:exp03baseline",
+          title = "Experiment 01 -- Determinants of Baseline Levels of
+          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
+          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
+                               "Left", "Center-Left", "Center-Right", "Right"),
           column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
@@
 
+# Ethics Statement
+
+We adhered to the ethical guidelines provided by the Institutional Review Board
+at Brown University and APSA's Principles and Guidance. To facilitate
+transparency, we comment here on a few aspects of our research design. First,
+we worked with the Brown University IRB to reduce the risk of harm for
+participants taking the survey. This included consultation with a cultural
+expert to inform the phrasing of the survey. Second, respondents received
+compensation via Qualtrics, which paid respondents directly after they completed
+the questionnaire. Each subject in Qualtrics' online panel received the
+equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
+not finish the survey will not receive compensation. The compensation is
+appropriate for the participant population. As of August 17, 2020, Brazil's
+monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
+working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
+survey takes about 20 minutes to complete and respondents received 2.5 USD,
+therefore subjects will receive a monetary compensation that is 6 times higher
+than the local minimum wage. Third, we do not see any potential or perceived
+conflicts of interest in carrying out this research. We received a grant of
+$10,000 to conduct this research from the Centre for the Study of Governance &
+Society at King’s College London, which receives support from the Templeton
+Foundation. We are aware of no conflicts of interest from either source. All of
+the code and data will be made publicly available.
+
 # Session Information

### 2022-06-15 article/main.tex
update paper and appendix

--- 2021-06-16 article/main.tex
@@
 % Title
-\title{Vigilantism, Institutions, and Honor Culture:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
+\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
 D'Amico, Miriam Golden, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
 Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, and Georg Vanberg for their valuable comments.
-We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington.
+We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington.
 This study received IRB approval from Brown University in October 2020 (Protocol 2009002803).
@@
 % Author
-\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science and the Political Theory Project, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
+\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
 
 % Date
-\date{June 16, 2021}
+\date{\today}
 
@@
 \doublespacing \noindent Why do people support extrajudicial violence?
-In this paper, we identify an important role for cultural norms in explaining attitudes toward lynching.
 In a series of survey experiments with respondents in Brazil, we examine how people view different motivations for lynchings, which characteristics of lynching scenarios garner greater support for lynching, and whether providing different types of information about lynching reduces support for it.
@@
 The people who participate in lynchings are typically  young men, but they also sometimes include teenage women and girls, elderly women, and even members of the local police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São Paulo kill hundreds of people every year in a way that looks similar to vigilantism \citep{willis2015killing}.
-Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas extralegally \citep{magaloni2020killing}.}
+Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas  \citep{magaloni2020killing}.}
 
@@
 In this experiment, we provide information akin to government messaging to the general public.
-Many theories of vigilantism presume that public beliefs and public opinion establish norms about lynchings.
-Even if none of our respondents have participated or will participate in lynchings, they are part of the community that creates norms about lynching.
 
@@
 Our second experiment is a conjoint experiment designed to see which characteristics of a lynching lead people to believe it is more or less justified.
-We find evidence that is consistent with aspects of an honor culture  \citep{nisbett2018culture,grosjean2014history}.
-In such cultures, people believe that the victims of crimes or their family members have the right to seek revenge, especially for heinous or otherwise serious crimes.
-People often see crimes such as forcible rape and murder as stains on the social standing of the victim and their family, and they believe it is not the proper role of the state to respond.
+People believe that the victims of crimes or their family members have the right to seek revenge, especially for heinous or otherwise serious crimes.
+People see crimes such as forcible rape and murder as especially suitable for extrajudicial violence.
 In the final experiment, we provide information to respondents to attempt to reduce support for lynching.
@@
 We find large negative effects of reminding respondents that lynching is a crime and that lynchings carry the risk of vendettas.
-Taken together, these findings are consistent with the argument that people are more likely to support vigilantism when the state cannot be relied on for crime control and when certain aspects of an honor culture are present.
 
@@
 Instead, it is the belief that it is not the proper role of the police to do so and that the response should instead be carried out by the family of the victim.
-Third, the insight we gain into the relationship between formal and informal enforcement helps us understand political development or lack thereof.
-Even when legal institutions are present and effective, norms  can undermine people's reliance on them.
+Third, our findings inform the relationship between political development and informal norms.
+Even when legal institutions are present, norms  can undermine people's reliance on them.
 This is a major challenge in establishing the rule of law in developing countries, where residents often prefer informal solutions to crime over state-based solutions \citep[10]{blair2020peacekeeping}.
 As a result, the prevalence of lynchings undermines political development and state capacity, which can fall into a self-reinforcing cycle \citep{jung2020lynching}.
-Solving the problem of discretionary, extrajudicial use of violence is crucial for understanding political and economic development more generally.
+As such, solving the problem of discretionary, extrajudicial use of violence is crucial for understanding political and economic development more generally.
 
-\section{Theory and Hypotheses}
+\section{Literature Review and Hypotheses}
 \label{sec:theory}
@@
 If the state was not strong or stable enough to eliminate these ambiguities, then vigilantism emerged as a way to create and entrench social and political identities.
-Black Americans, in particular, were lynched in shocking numbers and at shocking frequency across the South well into the twentieth century \citep{dray2003hands,seguin2019national}.
+Black Americans, in particular, were lynched in shocking numbers and frequency across the South well into the twentieth century \citep{dray2003hands,seguin2019national}.
 Likewise, based on studies of executions of Muslim men in Bosnia and a lynching in Jim Crow--era Maryland, Lee Ann Fujii \citeyearpar{fujii2017talk} argues that lynchings serve as ``violent displays'' that send signals to observers in the community and entrench social hierarchies and political identities.
@@
 \citet[8]{jung2020lynching} likewise note that ``\textit{racist} social control'' is a unique property of American vigilantism.
-Brazil's patterns thus pose a puzzle for existing explanations for mob violence and stand in sharp contrast to the American experience \citep{smaangs2016doing, wood2011lynching}.
+Brazil's patterns thus pose a puzzle for existing explanations for mob violence and stand in contrast to the American experience \citep{smaangs2016doing, wood2011lynching}.
 
 Recent research has shown that the relationship between states and vigilantism is more complicated than some early studies assumed.
-Based on extensive interviews and fieldwork in post-apartheid South Africa, Nicholas Rush \citet{smith2019contradictions} finds strong support for the idea that people participate in vigilantism because the state is seen to be \textit{too} strong.
+Based on extensive interviews and fieldwork in post-apartheid South Africa, Nicholas Rush \citet{smith2019contradictions} finds that people participate in vigilantism because the state is seen to be \textit{too} strong.
 Residents perceive a strengthening of the state, fuller support for human rights, and a stronger rule of law.
@@
 Accordingly, many South Africans believe it is right for people to take justice into their own hands.
-In a tragic twist of fate, achieving legal reform and a  closer adherence to the rule of law actually sparks greater use of extrajudicial violence.
+As a result, achieving legal reform and a  closer adherence to the rule of law can actually sparks greater use of extrajudicial violence.
 This suggests a second hypothesis:
@@
 
-The studies thus far reviewed tend to focus on state activity.
-Recent work suggests that residents' perceptions of the state are also important.
-In a study of Haiti, Danielle F.
-Jung and Dara Kay Cohen \citeyearpar[3]{jung2020lynching} argue that lynchings are correlated not with state presence, but instead with residents' \textit{views} about the state.
-They find that perceptions of state legitimacy are far more important in explaining vigilantism than whether state actors are merely present.
-Residents perceive groups (both state and nonstate actors) as more legitimate if they govern and provide social services.
-When people view the state as illegitimate because it does not govern, they believe it is their right to participate in vigilantism.
-This suggests that to explain vigilantism, we must understand both state activity and residents' perceptions of community-state relationships.
-
-Studies of vigilantism in Africa likewise find that culture, norms, and religion are powerful forces shaping the emergence and operation of vigilante groups.
-In Nigeria, vigilantism takes a variety of shapes, including Hisbah (shari'a enforcement groups), the Bakassi Boys, the Egbusu Boys, and the O'odua People's Congress \citep{pratten2008thief,last2008search, fourchard2008new}.
-An increase in the influence of neoliberalism (alongside other political changes) also drove vigilantism \citep[5]{pratten2008politics}.
+Studies of vigilantism in Africa likewise find that religion, norms, and gender are powerful forces shaping the emergence and operation of vigilante groups.
+For example, in Nigeria, an increase in the influence of neoliberalism (alongside other political changes) drove vigilantism \citep[5]{pratten2008politics}.
 In Ghana, nearly 20 percent of the lynchings between 1990 and 2000 happened because people believed that someone (usually an older woman) had used ``mystical powers'' to wound someone's genitals or to cause other health problems  \citep[414]{adinkrah2005vigilante}.
-Given a relatively weak state, beliefs, culture, and norms shape whether and how vigilante activity happens.
-
-In our study, we find that an honor culture shapes Brazilian beliefs about lynchings.
-In honor cultures, the reputation and social standing of a person or group is paramount \citep{nisbett2018culture,crowder2017new, vandello2008us, Cao2021honor}.
-Offenses that threaten to reduce one's standing are seen to give the victim the right (and often the obligation) to respond extralegally \citep{brown2016honor}.
-Honor cultures are often described as embracing ``a self-protection ethic'' and operate as a system of ``self-help justice'' \citep[1287, 1290]{grosjean2014history}.
-The offenses need not be serious, as ``everyday challenges, large and small, can undermine an individual's status and reputation, thus rendering his or her honor malleable and uncertain'' \citep[522]{crowder2017new}.
-However, gendered norms play an important role in honor societies, making heinous crimes especially important to respond to.
-Being the victim of a serious crime, such as forcible rape, is often seen as tarnishing the reputation of the victim and their family.
-As a result, as with dueling practices, failure to respond to a harm can affect one's social standing \citep{allen2006duel}.
-Finally, many honor cultures also follow \textit{lex talionis}, the idea that justice demands an eye for an eye.
-In places where an honor culture puts the onus to avenge wrongs on local community members, people view state enforcement as less desirable and less legitimate than vigilantism.
-They see honor as not restored if the state intervenes.
-
-While some of the most prominent studies of honor cultures focus on the history of Scotch-Irish people in the American South \citep[for example,][662-668]{fischer1989albion}, honor cultures still exist in many places today.
-In the United States, honor cultures exist in some American neighborhoods and are nearly universal in men's prisons across the country \citep{anderson2000code,fleisher2009myth}.
-Likewise, honor cultures have been a crucial part of clan, tribal, and customary societies in many parts of the world throughout history \citep{weiner2013rule}.
-As in such societies, it appears that honor cultures tend to emerge in places where people cannot rely on strong and effective states.\footnote{There is a large literature in law and economics that studies how reputation mechanisms can provide order without law \citep{bernstein1992opting,ellickson1991order,greif2006institutions, leeson2014anarchy}.} Cultures of violence can have remarkably long-run effects \citep{vandello2008us}.
-For example, in the American South, the presence of Scotch-Irish populations in the eighteenth century explains nearly 20 percent of the difference between homicide rates in the North and South today \citep[1286]{grosjean2014history}.
-An honor culture, and its emphasis on retaliatory norms and violence, did not emerge in the North because the region developed effective formal institutions more quickly.
-Taken together, the lesson from these studies is that when people cannot rely on state-based institutions to regulate violence, elements of an honor culture can emerge and produce self-help norms, which in turn increase support for vigilantism.
+More generally, gender norms play an important role in the use of extrajudicial violence.
+The family members of people who are victims of a serious crime, such as forcible rape, often believe it tarnishes the reputation of the victim and their family.
+As a result, they believe they have the right to punish the offender.
 This suggests a third hypothesis:
@@
 \begin{itemize}
-  \item \textbf{Hypothesis 3:} Support for vigilantism will increase if people accept the norms associated with an honor culture.  
+  \item \textbf{Hypothesis 3:} Support for vigilantism will increase when victims are female and their family carries out retribution.  
   \end{itemize}
 
-In our three experiments, we directly and indirectly tested these hypotheses.
-We argue that respondents do not believe that state-based legal institutions are the primary way to respond to serious crime.
+In our three experiments, we argue that respondents do not believe that state-based legal institutions are the primary way to respond to serious crime.
 We find that people's attitudes toward vigilantism are shaped strongly by the characteristics of the incident that gives rise to it.
 In particular, people strongly support lynching by the family of a victim of a sexual offense or murder.
-Finally, although honor cultures can persist for many decades, our third experiment shows that support for lynchings can be reduced by reminding people of the penalties for lynching and of the risk of sparking vendettas.
+Finally, our third experiment shows that support for lynchings can be reduced by reminding people of the penalties for lynching and of the risk of sparking vendettas.
 
@@
 We observed that men are more likely to support lynchings when compared with women.
-This is in contrast to research in Uganda, Tanzania, and South Africa, where women support mob vigilantism more than men do because they believe that they are less likely to be subject to false accusations \citep{wilke2021gender}.\footnote{On the relationships between gender and violence, see \citet{kadera2018gendered} and related papers.} In line with \citet{martins2015linchamentos}, we found little evidence that support for lynchings is driven primarily by racial prejudice.\footnote{We recognize that race is socially-constructed and that racial categories can be codified in multiple ways.
+This is in contrast to research in Uganda, Tanzania, and South Africa, where women support mob vigilantism more than men do because they believe that they are less likely to be subject to false accusations \citep{wilke2021gender}.\footnote{On the relationships between gender and violence, see \citet{kadera2018gendered} and related papers.} In line with \citet{martins2015linchamentos}, we found little evidence that support for lynchings is driven primarily by outright racial prejudice.\footnote{We recognize that race is socially-constructed and that racial categories can be codified in multiple ways.
 We adopt the racial classification used by the Brazilian Census Bureau (IBGE) as it is widely employed in social research \citep[e.g.][24]{lapop2018brazil} and intuitive to our respondents.
@@
 
-One interpretation of the null findings for the treatment effects is that state presence and activity have no influence on attitudes toward lynching.
+There were no significant effects on any of the treatments.
+One possible interpretation of the null findings is that state presence and activity have no influence on attitudes toward lynching.
 If that interpretation is correct, we should reject Hypotheses 1 and 2.
-However, given the extensive literature discussed above and the qualitative evidence collected in the next experiment (discussed in Section \ref{sec:exp01}), we instead argue that the null results reflect the fact that respondents simply have little to no faith in the criminal legal system in general, and addressing the issues implied in the treatment conditions would have no substantial effect on its perceived effectiveness.
-Three pieces of evidence support this interpretation.
+
+Given the extensive literature discussed above and the qualitative evidence collected in the next experiment (discussed in Section \ref{sec:exp01}), an alternative explanation is that the null results reflect the fact that respondents simply have little to no faith in the criminal legal system in general.
+Several pieces of evidence support this interpretation.
 First, many crimes in Brazil are never solved.
@@
 Finally, along with the rise of Jair Bolsonaro---the far-right president who has publicly called for people to take the law into their own hands \citep{brant2021armas, uol2021bolsonaro}---survey evidence suggests that people have grown considerably more punitive \citep{datafolha2018penademorte}.
-Taken together, attitudes about lynchings do not seem to be driven by beliefs about \textit{how} the state provides justice.
-Instead, they reflect the fact that respondents do not, in general, believe that it \textit{can} provide it.
-In addition, in our next experiment, we found evidence that people who support an honor culture do not think that the state \textit{should} provide justice in certain circumstances.
 
@@
 \end{table}
+
+\newpage
 
@@
 \begin{figure}[ht]
-\includegraphics[width=17cm]{conjoint-black.pdf}
+\includegraphics[width=17cm]{conjoint-color.pdf}
 \caption{Relative preferences for lynching-episode attributes (marginal means)}
@@
 Subjects were indifferent as to whether the crime perpetrator lives in the area (0.498, SE = 0.004, $p$-value = 0.668) or in another neighborhood (0.502, SE = 0.004, $p$-value = 0.668).
-In this sense, it is possible that subjects see lynchings not as a means to protect the area in which they live, which we commonly suppose vigilante groups do, but rather as retribution in specific cases.
+In this sense, it is possible that subjects see lynchings not as a means to protect the area in which they live, which people commonly suppose vigilante groups do, but rather as retribution in specific cases.
 
@@
 Rape was by far the most significant attribute in our model (0.719, SE = 0.009, $p$-value $<$ 0.001), followed by murder (0.608, SE = 0.006, $p$-value $<$ 0.001) and molestation (0.538, SE = 0.006, $p$-value $<$ 0.001).
-It is not surprising that murder was an important offense mentioned by respondents, and the fact that rape appeared as subjects' first choice is not entirely unexpected either.
-Among incarcerated populations, sex offenders are near-universally seen as having the lowest standing in the community and typically are subject to more violence than most other incarcerated people \citep{fleisher2009myth}.
-These findings support Hypothesis 3, in that honor cultures tend to view heinous and sex crimes as warranting an extrajudicial response.
+It is not surprising that murder and rape were the most important offenses to respondents.
 Overall, we found that respondents do not believe that property crimes, such as car theft (0.351, SE = 0.009, $p$-value $<$ 0.001) and pickpocketing (0.314, SE = 0.006, $p$-value $<$ 0.001), provide justification for lynching.
 When we analyzed the data by groups, we also saw that poorer respondents, whose household income is less than R\$3,000 (US\$650) per month, are more likely to support the lynching of individuals who commit a property crime.
+
+For age, we observed that respondents were particularly concerned about children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this attribute is strongly correlated with support for lynchings.
+Respondents also thought lynchings are more justified when the victim is a teenager (0.505, SE = 0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$ 0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001).
 
@@
 
-For age, we observed that respondents were particularly concerned about children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this attribute is strongly correlated with support for lynchings.
-Respondents also thought lynchings are more justified when the victim is a teenager (0.505, SE = 0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$ 0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001).
-Together, these facts lend credence to the idea that citizens see lynchings as a valid punishment when the victims have little chance of defending themselves.
-
-Lastly, we examined who respondents believed are more legitimate perpetrators of lynchings.
-Consistent with a key aspect of an honor culture, respondents considered the family to be the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$ 0.001).
+Lastly, and related to this, we examined who respondents believed are more legitimate perpetrators of lynchings.
+Respondents considered the family to be the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$ 0.001).
 Again, the intervals here did not overlap with those of any other category.
@@
 We analyzed a random sample of nearly 17 percent of the answers.
-Three major themes emerge that are consistent with the argument that elements of an honor culture played an important role.
-First, respondents felt that crimes that were especially heinous deserved a response, and often one that would follow lex talionis.
+Three major themes emerge.
+First, respondents felt that crimes that were especially heinous deserved a response.
 For example, one respondent explained their choice of a particular case as more justified by noting, ``Eye for an eye, it's absolutely fair.'' A second  theme is the injustice of victimizing vulnerable populations.
-Two quotes representative of this theme are: ``The victim is an elderly person, it's okay to lynch the criminal,'' and ``If the victim is a child, lynchings are not enough, they deserve more.'' Finally, a third theme is that families have a special right to vengeance.
-One respondent explained their choice by saying, ``The family was appalled and did justice with their own hands!'' These open-ended answers are consistent with the quantitative results about \textit{what} people believe, but they also provide additional evidence about \textit{why} they hold their beliefs.
-Elements of an honor culture matter.
+One respondent explains, ``The victim is an elderly person, it's okay to lynch the criminal.'' Another respondent says, ``If the victim is a child, lynchings are not enough, they deserve more.'' Finally, a third theme is that families have a special right to vengeance.
+One respondent explained their choice by saying, ``The family was appalled and did justice with their own hands!'' These open-ended answers are consistent with the quantitative results about what people believe, but they also provide additional evidence about why they hold their beliefs.
 
@@
 This finding has practical implications, as many campaigns against violent crimes are conducted by human rights groups, which tend to emphasize this type of message.
-However, in an honor culture, participants do not generally believe that offenders have human rights.
+However, participants do not generally believe that offenders do, in fact, have human rights.
 Accordingly, we have little reason to believe that such messaging is effective.
@@
 
-Our last treatment, which raises the possibility of sparking vendettas, exerts a large, negative effect on support for lynchings.
+Our last treatment, which raises the possibility of sparking vendettas, has a large, negative effect on support for lynchings.
 Mentioning that lynchings trigger cycles of violence has a negative effect of about 8 percent when compared with the control group.
@@
 As with the other experiments, the results remain stable when we conduct subgroup analyses.
-
-In sum, reminding respondents of human rights guarantees does not reduce support for lynchings, but affirming that they can be punished for their acts, either by the state or by individuals, can change their opinions.
 
@@
 In Brazil, lynchings are commonplace and are only one form of vigilantism and extralegal violence plaguing the country.
-Many favelas are dominated by organized crime groups that engage in violence and wield the threat of violence extralegally \citep{arias2006dynamics,barnes2017criminal}.
+Many favelas are dominated by organized crime groups that engage in violence and wield the threat of violence extralegally \citep{arias2006dynamics,barnes2021logic}.
 In this paper, we used survey experiments to examine people's attitudes toward lynching to better understand what makes people feel some instances are more justified, which reasons for doing so gain support, and how to reduce support for lynchings.
 If people felt like they cannot rely on the state to provide effective regulation of serious violence, then they were more likely to develop beliefs and norms that legitimate the extrajudicial use of violence.
-More specifically, we found evidence that elements of an honor culture influence how and why extrajudicial violence is used and legitimated.
 People found lynchings more justifiable when they were in response to especially heinous crimes and when the crimes were perpetrated against vulnerable populations, and they viewed the family as having a distinctive duty for carrying out vengeance.
@@
 
-This paper highlights the importance of ideas, norms, and culture in shaping the prevalence of extrajudicial violence.
-Most directly, our data show that an honor culture affects when and where lynchings are believed to be justified.
-Yet, ideas, norms, and culture also affect whether the phenomenon continues.
-In the United States, for example, Southern lynchings were supported tacitly and openly well into the early twentieth century.
-Lynching did not decline until newspapers in other parts of the country began to notice, publicize, and criticize the practice \citep{weaver2019judge}.\footnote{On the history and decline of lynching in the United States, see also \citet{wood2011lynching} and \citet{rushdy2012american}.} Local elites could not control these narratives, and these outside voices helped to delegitimize lynchings.
-Our findings support the argument that norms of legitimacy are crucial to understand the patterns and practices of vigilante violence.
-
-Extrajudicial violence also has profound consequences on political development and the rule of law.
+Extrajudicial violence has several profound consequences on political development and the rule of law.
 First, extensive reliance on extrajudicial violence undermines legal and judicial reform because people feel informal, local dispute resolution is preferable to state-based institutions \citep{blair2020peacekeeping}.

### 2022-06-16 appendix/appendix-short.Rmd
add pdfs
Signed-off-by: Danilo Freire <danilofreire@gmail.com>

@@
 - "David Skarbek[^skarbek]"
-date: 14 June 2022
+date: \today
 fontfamily: libertine
@@
 
-We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
-sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
-five regions of the country (Center-West, North, Northeast, South, and
-Southeast).
+We ran our survey experiments from October 30 to December 14, 2020 via
+Qualtrics. Our sample includes `r nrow(df1)` Brazilians older than 18 years of
+age from the five regions of the country (Center-West, North, Northeast, South,
+and Southeast).
 

### 2022-06-16 appendix/appendix.Rmd
add pdfs
Signed-off-by: Danilo Freire <danilofreire@gmail.com>

@@
 
-We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
-sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
-five regions of the country (Center-West, North, Northeast, South, and
-Southeast). We used quotas for gender and region to ensure that our sample was
-similar to the Brazilian population in those characteristics. We also collected
-information about whether the subjects had been victimized in the previous 12
-months, as well as their opinion of the Brazilian judicial system and the
-police forces. They follow in the graphs and tables below.
+We ran our survey experiments from October 30 to December 14, 2020 via
+Qualtrics. Our sample includes `r nrow(df1)` Brazilians older than 18 years of
+age from the five regions of the country (Center-West, North, Northeast, South,
+and Southeast). We used quotas for gender and region to ensure that our sample
+was similar to the Brazilian population in those characteristics. We also
+collected information about whether the subjects had been victimized in the
+previous 12 months, as well as their opinion of the Brazilian judicial system
+and the police forces. They follow in the graphs and tables below.
 

### 2022-08-22 appendix/appendix.Rmd
update short article and appendix

@@
 
-In our first experiment, we analyze how respondents justify their preferences
-towards extralegal violence. We assess the impact of three factors that have
-been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
-criminal justice; 3) demand for harsher punishment for criminals. Below, we
-discuss them in further detail.
-
-Research shows that police ineffectiveness frequently appears as a strong
-predictor of vigilantism [@cruz2019determinants; @garcia2019anger]. The direct
-result of the weakness of police institutions is that citizens decide to take
-criminal matters "into their own hands", thus persecuting and punishing the
-criminals by themselves. A recent statistic indicates that the police solves
-only 10% of the homicides in Brazil, which lends support to the link between
-weak law enforcement and lynchings [@pearson2018latam].
-
-Another possible determinant of lynching support is lack of trust in the
-justice system [@godoy2004justice; @smith2019contradictions]. This is often due
-to long criminal proceedings, which cause significant anxiety for the victims.
-In Brazil, the penal code allows the accused to appeal each decision several
-times, so it can take decades before a criminal case is closed
-[@sousa2005utilizaccao]. In this respect, citizens do not believe that, even if
-the criminal is put to trial, he/she will be punished in a timely matter. Note
-that although the police is technically part of the criminal justice system, we
-analyze the two institutions separately in our experiment.
-
-Lastly, we evaluate whether respondents think that the legal punishment
-assigned to criminals is not proportional to the severity of their crimes. In
-particular, we intend to gauge the demand for iron-fisted criminal justice in
-Brazil. Although this treatment arm is related to the previous ones, it
-addresses not the efficiency of the institutions, but their legitimacy
-[@nivette2016institutional]. In fact, Brazilians are often vocal about their
-preference for repressive legal punishment. In a recent article in _The Wall
-Street Journal_, a bar owner justified the lynching of the local thug who
-killed his son by saying that "_even if he had been put behind bars for 100
-years it wouldn't have been enough to pay for all his crimes_"
-[@pearson2018latam]. We hypothesize that many Brazilians also share this view.
-
-The experiment consists of three treatment conditions and one control group.
-Respondents read an excerpt of a news article describing a real lynching case.
-We have slightly edited the original text so that respondents have no prior
-knowledge of the crime.[^jornal] The vignette for the control group includes no
-information about the reasons behind the lynching. We ask respondents to show
-their level of lynching support using a 0-100 slider, where 0 means no support
-and 100 means full support. Respondents in each of the three treatment arms
-read the same piece, but with one additional sentence explaining the
-motivations behind the lynching. The vignettes are as follows:
-
-[^jornal]: The original article is available at the following address:
-<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
-Access: August 2020.
-
-* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
-  According to the neighbours, he tried to break into a house but was
-  immobilised and beaten by members of the community.[^control-exp01]
-
-[^control-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade.
-
-* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
-  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
-  house but was immobilised and beaten by members of the community. **One of
-  the residents who took part in the lynching said they had beaten the suspect
-  because "the police never patrols the area"**.[^treat01-exp01]
-
-[^treat01-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
-nunca patrulha o local".**
-
-* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial system is too slow and the perpetrator is on
-  the street until the case is heard"**.[^treat02-exp01]
-
-[^treat02-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
-é muito lenta e os criminosos ficam soltos até o julgamento"**.
-
-* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
-  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
-  into a house but was immobilised and beaten by members of the community.
-  **One of the residents who took part in the lynching said they had beaten the
-  suspect because "the judicial punishment is not harsh
-  enough"**.[^treat03-exp01]
-
-[^treat03-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
-Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
-mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
-envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
-da justiça não é dura o suficiente"**.
-
-Before each vignette, respondents read the following text:
-
-* You will be shown a news article. Please read it carefully. After you read
-  the article, we will ask you one question about it.[^vig01-exp01]
-
-[^vig01-exp01]: In Portuguese: Uma notícia será apresentada para você. Por
-favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
-sobre ele.
-
-After the vignette, respondents were presented with this question:
-
-* Do you think that the lynching was justified? Please use the slider below
-  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
-  use 51 to 100. Please use 50 if you neither agree nor
-  disagree.[^vig02-exp01]
-
-[^vig02-exp01]: In Portuguese: Você acha que o linchamento foi correto? Por
-favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
-49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
-discordar.
-
-## Main Results
-
-Table \ref{tab:exp01main} summarizes our results. As we see, none of the
-treatment effects are statistically significant at conventional levels. This
-suggests that institutional factors do not affect lynching support in our
-sample.
-
-\footnotesize
-```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-df_exp01 <- df1 %>%
-  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
-                                   exp01_slow_justice, exp01_small_punishment),
-         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
-                                     !is.na(exp01_police) ~ "1",
-                                     !is.na(exp01_slow_justice) ~ "1",
-                                     !is.na(exp01_small_punishment) ~ "1",
-                                     TRUE ~ NA_character_),
-         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
-                                        !is.na(exp01_police) ~ "1"),
-         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
-                                              !is.na(exp01_slow_justice) ~ "1"),
-         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
-                                                  !is.na(exp01_small_punishment) ~ "1"))
-
-m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
-m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
-m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
-m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)
-
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp01main", title = "Experiment 01 -- Main Results",
-          style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Police does not patrol area", "Justice too slow",
-                               "Punishment not harsh enough", "Combined treatments"),
-          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
-
-## Determinants of Baseline Levels
-
-Here we estimate the effect of gender, race, and political ideology on lynching
-support. We find that males are more likely to tolerate lynchings, whereas left
-and center-left voters oppose lynchings more strongly than centrists. In our
-second model, we find no effect for race, and in the last column we see that
-white respondents are less supportive of lynchings.
-
-\footnotesize
-```{r exp01-baseline, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
-df_exp01_group <- df_exp01 %>%
-  filter(gender == c("Female", "Male"),
-         race %in% c("Asian", "Black", "Mixed Race", "White"),
-         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
-  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))
-
-df_exp01_gender <- df_exp01 %>% filter(gender == c("Female", "Male"))
-df_exp01_race <- df_exp01 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
-  mutate(race = fct_relevel(race, "Black"))
-df_exp01_ideology <- df_exp01 %>%
-         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
-         mutate(ideology = fct_relevel(ideology, "Center"))
-
-m1 <- lm(exp01_outcomes ~ gender, data = df_exp01_gender)
-m2 <- lm(exp01_outcomes ~ race, data = df_exp01_race)
-m3 <- lm(exp01_outcomes ~ ideology, data = df_exp01_ideology)
-m4 <- lm(exp01_outcomes ~ gender + race + ideology, data = df_exp01_group)
-
-stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
-          header = FALSE, align = TRUE, label = "tab:exp01baseline",
-          title = "Experiment 01 -- Determinants of Baseline Levels of
-          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
-          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
-                               "Left", "Center-Left", "Center-Right", "Right"),
-          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
-          keep.stat = "n", no.space = TRUE)
-```
-\normalsize
-
-\newpage
-
-## Heterogeneous Effects
-
-We estimate heterogeneous effects for our experiment using Bayesian Additive
-Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
-allow users to detect non-linear interactions and are insensitive to the choice
-of tuning parameters, so they are well-suited to analyze observational and
-experimental data [@green2012modeling]. More specifically, we employ the
-`bartCause` package, which is designed to estimate causal inference models.
-
-### Treatment 01: Police Ineffectiveness
-
-Our results indicate that the effects for this treatment arm is null in every
-model specification. We find no evidence of heterogeneous effects.
-
-\footnotesize
-```{r exp01-bart01, warning=F, error=F, message=F, cache=T}
-df_exp01_het <- df_exp01 %>%
-  filter(gender %in% c("Female", "Male")) %>%
-  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
-                            "Indigenous"),
-         education = fct_relevel(education, "Primary School", "Secondary School",
-                                  "High School", "College", "Graduate School"),
-         views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
-                                    "Bad", "Very Bad"),
-         views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good",
-                                     "Bad", "Very Bad"),
-         ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
-                                "Center-Right", "Right", "Don't Know", "Rather Not Say"),
-         household_income = fct_relevel(household_income, "Up to R$1,000", "From R$1,001 to R$2,000",
-                                         "From R$2,001 to R$3,000", "From R$3,001 to R$5,000",
-                                         "From R$5,001 to R$10,000", "From R$10,001 to R$20,000",
-                                         "Above R$20,000"),
-         previous_victim_dummy = fct_relevel(previous_victim_dummy, "Yes", "No"),
-         death_penalty = fct_relevel(death_penalty, "Yes", "No"),
-         age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
-                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
-
-df_exp01_police <- df_exp01_het %>%
-  mutate(exp01_police_treat = as.numeric(exp01_police_treat)) %>%
-  drop_na(exp01_police_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_police_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp01_outcomes, exp01_police_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_police_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_police_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_police_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_police_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_police_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_police2 <- df_exp01_police %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_police_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_police2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_police_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_police_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_police,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-### Treatment 02: Criminal Justice Ineffectiveness
-
-We do not find any evidence of heterogeneous treatment effects in this
-condition either.
-
-\footnotesize
-```{r exp01-bart02, warning=F, error=F, message=F, cache=T}
-# Remove "Indigenous" and "Other" from `race` as they only
-# have 1 observation each. The model cannot be estimated otherwise.
-df_exp01_slow_justice <- df_exp01_het %>%
-  filter(race %in% c("White", "Asian", "Black", "Mixed Race", "Rather Not Say")) %>%
-  mutate(exp01_slow_justice_treat = as.numeric(exp01_slow_justice_treat)) %>%
-  drop_na(exp01_slow_justice_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Age
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_slow_justice2 <- df_exp01_slow_justice %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_slow_justice2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_slow_justice_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_slow_justice,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-### Treatment 03: Demand for Harsher Legal Punishment
-
-As in the last two series of models, our results show no evidence of
-heterogeneous treatment effects.
-
-\footnotesize
-```{r exp01-bart03, warning=F, error=F, message=F, cache=T}
-df_exp01_small_punishment <- df_exp01_het %>%
-  mutate(exp01_small_punishment_treat = as.numeric(exp01_small_punishment_treat)) %>%
-  drop_na(exp01_small_punishment_treat)
-
-# Gender
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, gender,
-              group.by = gender, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Age
-df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(age2)
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, age2,
-              group.by = age2, group.effects = TRUE, data = df_exp01_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Race
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, race,
-              group.by = race, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Education
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, education,
-              group.by = education, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Household Income
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, household_income,
-              group.by = household_income, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Political Ideology
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, ideology,
-              group.by = ideology, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Support for Death Penalty
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, death_penalty,
-              group.by = death_penalty, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Previous Victimization
-df_exp01_small_punishment2 <- df_exp01_small_punishment %>% drop_na(previous_victim_dummy)
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, previous_victim_dummy,
-              group.by = previous_victim_dummy, group.effects = TRUE, data = df_exp01_small_punishment2,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Police
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_police,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-
-# Opinion on the Judicial System
-summary(bartc(exp01_outcomes, exp01_small_punishment_treat, views_justice,
-              group.by = views_police, group.effects = TRUE, data = df_exp01_small_punishment,
-              n.chains = 5L, seed = 144))
-```
-\normalsize
-
-\newpage
-
-# Experiment 02
-
-## Description
-
-In our second experiment, we present five pairs of criminal profiles to
+In our first experiment, we present five pairs of criminal profiles to
 respondents. Each profile consists of eight attributes: 1) gender of the crime
@@
 
-# Experiment 03
+# Experiment 02
 
@@
 
-Our last experiment measures the effect of information provision on attitudes
+Our second experiment measures the effect of information provision on attitudes
 about lynching. In particular, we test whether reminding respondents
@@
 
-As we did in the first experiment, we evaluate how individual characteristics
-impact lynching support. The results are similar to those presented in table
-\ref{tab:exp01baseline}, with the exception that the coefficient for white
+We also evaluate how individual characteristics
+impact lynching support. We find that the coefficient for white
 respondents is negative in two estimations, and the coefficient for male does
 not reach statistical significance in the last model ($p$-value = 0.11).
+Political ideology is strongly correlated with support for lynchings.
 

### 2022-08-22 short-article/short-article.tex
update short article and appendix

--- 2022-06-15 article/main.tex
@@
-% !TEX program = XeLaTeX
-\documentclass[12pt,ansiapaper]{article}
+\documentclass[12pt,a4paper]{article}
 
@@
 
-% Dots in toc
-\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
-
 % Colours
@@
 
-% Packages I've been using for different reasons
+% Packages I've been using for differen reasons
 \usepackage{hyperref}
@@
 \usepackage[english]{isodate}
-\cleanlookdateon
+% \cleanlookdateon
 
@@
 % Title
-\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
-D'Amico, Miriam Golden, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
-Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, and Georg Vanberg for their valuable comments.
+\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
+D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
+Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments.
 We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington.
@@
 \doublespacing \noindent Why do people support extrajudicial violence?
-In a series of survey experiments with respondents in Brazil, we examine how people view different motivations for lynchings, which characteristics of lynching scenarios garner greater support for lynching, and whether providing different types of information about lynching reduces support for it.
-We find that people do not believe that criminal justice institutions should be relied on to solve serious crimes and do believe that in such instances, community members have the right to take vengeance.
+In two survey experiments with respondents in Brazil, we examine which characteristics of lynching scenarios garner greater support for lynching and whether providing different types of information about lynching reduces support for it.
+We find that people often do support community members to take vengeance.
 In particular, our analysis finds that people strongly support the use of extrajudicial violence by families of victims against men who sexually assault and murder women and children.
+We also find that criminal punishment and the threat of vendettas reduce support, but appeals to the human rights of victims have zero effect on support for lynchings.
 \vspace{.25cm}
@@
 
-The regulation of violence is one of the most important functions of the state.
-When states control violence effectively, markets, politics, and civil society can flourish.
-However, in many places, violence is poorly regulated and nonstate armed actors---ranging from residents to rebel groups---use violence at their own discretion.
-The extralegal use of violence is also a clear violation of the rule of law \citep[48-49]{blair2020peacekeeping}.
-More generally, the challenge of monopolizing violence is at the heart of the Weberian definition of the state, and it is arguably one of the most fundamental questions of political economy.
-While political scientists have written extensively on civil wars, rebel governance, and criminal violence \citep{arjona2016rebelocracy, trejo2021high, barnes2017criminal}, they have written far less about vigilante violence.
-In this paper, we use survey experiments to better understand people's attitudes toward the use of extralegal violence.
+The regulation of violence is a crucial function of the state. When states
+control violence effectively, markets, politics, and civil society can flourish
+\citep{besley2011pillars, north2009violence}. However, states still struggle to
+maintain the monopoly of force in much of the Global South. Scholars have
+written extensively about how rebel organizations build support to challenge
+government institutions, yet we know little about what motivates local
+extrajudicial violence in the developing world \citep{bateson2020politics,
+smith2000new}. This omission is significant not only because local violence is
+pervasive in weak states, but also because it can be even more costly than war-
+or terrorism-related violence \citep{blair2017predicting}.
 
-Although lynchings and mob violence more generally have decreased in advanced democracies, it remains widespread in many parts of the world.
-Based on US State Department reports, \citet[33]{jung2020lynching} find that between 1976 and 2018, lynchings occurred in all regions of the world and in more than a hundred countries.
-In particular, Latin America has been severely affected by a recent increase in lynchings.
-Such a surge in citizen-led violence has reportedly been motivated by growing numbers of drug-related crimes and by police ineffectiveness \citep{mallen2014vigilantes}.
-Brazil provides a telling example.
-From 2011 to 2015, the country registered about 2,500 lynching episodes.
-In 2015, 173 people were killed by angry mobs---nearly one execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
-According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for more than thirty years, these figures are not only the highest in the country's history, but among the highest in the world.
-The people who participate in lynchings are typically  young men, but they also sometimes include teenage women and girls, elderly women, and even members of the local police \citep{moura2017linchamentos}.\footnote{Brazilian police forces in São Paulo kill hundreds of people every year in a way that looks similar to vigilantism \citep{willis2015killing}.
-Recent work also documents how organized crime groups in Brazil use extralegal violence in the process of governing favelas  \citep{magaloni2020killing}.}
+One of the most serious forms of extrajudicial violence is lynching, which can
+be defined as ``incidents of physical violence committed by large numbers of
+private citizens against one or more individuals accused of having committed a
+``criminal'' offense, whether or not this violence resulted in the death of the
+victim(s)'' \citep[645]{godoy2004justice}. Although lynchings occur in more
+than one hundred countries in all regions of the world
+\citep[33]{jung2020lynching}, Latin America has been particularly affected by a
+sharp increase in vigilante violence. In recent years, countries like Brazil
+and Venezuela have experience nearly one execution every two days, and lynching
+episodes have also been reported in Guatemala, Mexico, Peru, and other
+countries in the region \citep{cruz2019determinants, godoy2004justice,
+barbara2015vigilantes}. These alarming figures suggest that, despite being
+dismissed by policymakers as irrational and senseless, vigilantism enjoys
+considerable approval in Latin America \citep{berg2011globalizing,
+goldstein2005flexible}. This raises a number of puzzles: under which conditions
+do citizens perceive lynchings as a legitimate response to crime? Are some
+groups seen as more ``deserving'' of lynchings that others? And how can we
+reduce pro-vigilantism attitudes in young, unequal democracies?
 
-There is no strong consensus about what factors explain people's participation in vigilantism.
-Some of the most common explanations focus on the role of state-based institutions.
-People living in places with weak or failed states might engage in vigilante activity to control crime and to enforce social order \citep{bancroft1887works}.
-However, others argue that it is growth in state capacity that motivates people to take justice into their own hands out of fear that the state will not punish perpetrators or will do so too lightly \citep{smith2019contradictions}.
-In Latin America in particular, vigilantism has been found to be associated with previous exposure to violence \citep{garcia2019anger}, untrustworthy law enforcement \citep{zizumbo2017community}, perceived insecurity \citep{ceobanu2011crime, godoy2004justice}, and economic and social inequality \citep{phillips2017inequality,godoy2006popular,arias2010violent}.
+In this study, we run two survey experiments and use primary qualitative data
+to understand attitudes toward lynchings in Brazil. First, we employ a conjoint
+experiment with eight attributes to evaluate in which circumstances citizens
+perceive lynchings as a justifiable punishment for crime. We also included
+open-ended questions for respondents to elaborate on their decision process.
+Finally, we use an information provision experiment to test the efficacy of
+three strategies to reduce individual support for lynchings.
 
-Part of the reason for the proliferation of findings is that studying vigilantism empirically presents a substantial challenge.
-Many studies focus on vigilantism along the American frontier in the mid-nineteenth century, drawing on archival and historical documents  \citep{brown1975strain, courtwright2009violent, obert2018six}.
-However, much relevant evidence needed to test competing theories has been lost to history.
-Qualitative and ethnographic research provides deep insights into the motivations and emotions surrounding social disorder, violence, and vigilantism \citep{godoy2002lynchings}.
-Yet, like all research approaches, this method has shortcomings, including recall bias and social desirability bias.
-Quantitative approaches that rely on observational data are likewise often limited in important ways, including that relevant data may be absent, data may imperfectly map onto theoretical concepts, and data may be collected and aggregated at a level of analysis far removed from the studied phenomenon.
-Finally, while a credible identification strategy is not necessary for making causal claims, it can often solve issues that arise from poor-quality data.
-Unfortunately, credible identification strategies are often not available.
-As \citet[17]{bateson2020politics} notes, ``Field experiments on vigilantism would raise serious ethical concerns, and natural experiments are rare.''
+Our empirical approach offers several distinct advantages. First, the data we
+collected come from the same level of analysis as the phenomenon itself: local
+residents. Second, online surveys are less susceptible to social desirability
+bias, and survey experiments help to elicit sensitive information---an
+especially important benefit in researching this topic \citep{grimm2010social}.
+Third, the experimental nature of the approach allows us to precisely estimate
+the size of effects and compare different theoretical explanations
+simultaneously. Finally, we can also control for confounding, which is a
+potential concern in previous research on vigilantism.
 
-In this paper, we use survey experiments to better understand individual perceptions of vigilantism.
-Based on the existing literature, we designed three survey experiments to understand lynchings in Brazil in particular.
-This empirical approach offers several distinct advantages.
-First, the data we collected come from the same level of analysis as the phenomenon itself: local residents.
-Second, online surveys are less susceptible to social desirability bias, and survey experiments help to elicit sensitive information---an especially important benefit in researching this topic \citep{grimm2010social}.
-Third, the experimental nature of the approach allows us to estimate the size of effects.
-Finally, we can also control for confounding, which is a potential concern with more qualitative methods.
-
-One obvious downside to survey experiments is the difficulty in making inferences about the external validity of findings.
-\citet[17-18]{bateson2020politics} suggests that the closer that a fictional survey prompt matches the real world, the better the external validity.
-Accordingly, our first experiment is based on an actual account of a lynching in Jundia\'{i}, Brazil.
-In the second experiment, we include a wide range of lynching-scenario characteristics that allow respondents to consider detailed, realistic examples.
-Our third experiment examines whether providing different types of information can affect respondents' perceptions of lynchings.
-Our strategy here is similar to that of public marketing campaigns that governments often use to change public opinion.
-In this experiment, we provide information akin to government messaging to the general public.
-
-In the first experiment, we attempt to understand how the underlying motivation for a lynching affects support for it.
-In particular, we test whether police absence, the slowness of the legal process, and the belief that punishment will not be harsh enough affect support.
-We find no effect for any treatment.
-Instead, combined with existing data on measures of police ineffectiveness and state capacity, we argue that the evidence is consistent with the claim that respondents simply do not view the police as a genuine source of assistance for serious crimes.
-Our second experiment is a conjoint experiment designed to see which characteristics of a lynching lead people to believe it is more or less justified.
-People believe that the victims of crimes or their family members have the right to seek revenge, especially for heinous or otherwise serious crimes.
-People see crimes such as forcible rape and murder as especially suitable for extrajudicial violence.
-In the final experiment, we provide information to respondents to attempt to reduce support for lynching.
-We remind respondents that lynching is a crime, that all citizens have human rights, and that lynchings can prompt violent vendettas.
-We find large negative effects of reminding respondents that lynching is a crime and that lynchings carry the risk of vendettas.
-
-In studying lynching, this  paper contributes to several debates.
-First, we provide causal estimates of why Brazilians justify lynching, how vigilantes' motivation affects the justification, and how to reduce support for lynchings.
-Second, we provide evidence that is consistent with the common argument that vigilantism is driven by state absence or weakness.
-However, state absence or weakness alone is not enough to explain support for vigilantism.
-Like \cite{jung2020lynching}, we argue that people's beliefs and cultural norms are crucial to whether vigilantism is perceived to be justified.
-It is not simply the fact that the state is unavailable to enforce the law that leads people to support lynchings.
-Instead, it is the belief that it is not the proper role of the police to do so and that the response should instead be carried out by the family of the victim.
-Third, our findings inform the relationship between political development and informal norms.
-Even when legal institutions are present, norms  can undermine people's reliance on them.
-This is a major challenge in establishing the rule of law in developing countries, where residents often prefer informal solutions to crime over state-based solutions \citep[10]{blair2020peacekeeping}.
-As a result, the prevalence of lynchings undermines political development and state capacity, which can fall into a self-reinforcing cycle \citep{jung2020lynching}.
-As such, solving the problem of discretionary, extrajudicial use of violence is crucial for understanding political and economic development more generally.
-
-\section{Literature Review and Hypotheses}
-\label{sec:theory}
-
-In an important recent article, Regina Bateson \citeyearpar{bateson2020politics} conceptualizes vigilantism and defines it as ``the extralegal prevention, investigation, or punishment of offenses'' (3).
-She identifies five key characteristics of vigilantism, each of which varies along a continuum (11--14).
-First, vigilantism can be carried out by an individual or by a group of people.
-Second, vigilantism ranges from nonviolent interventions to extremely violent ones, including even the torture and murder of someone who is suspected of committing a crime.
-Third, it can occur in private or public, and some acts of vigilantism are intentionally carried out in elaborate, public displays.
-Fourth, vigilantism can arise spontaneously or it can be highly organized and institutionalized.
-Finally, vigilantism can operate to prevent crime in the first place or to respond to crime during or after its occurrence (what Bateson calls ``defensive'' and ``offensive'' vigilantism).
-In this paper, we focus on lynchings, a form of vigilantism that is carried out by groups, with violence, in public, spontaneously, and in response to crime being committed.\footnote{Different types of vigilantism might arise for different reasons.
-For example, highly organized and institutionalized ``vigilance committees'' might be caused by entirely different social forces than are spontaneous lynchings.
-Accordingly, we focus on a single, specific type of vigilantism---lynching---throughout the paper.}
-
-The study of vigilantism has a long and multidisciplinary history.
-Both classic works and contemporary research draw from a variety of fields and methods, including anthropology, criminology, history, sociology, and, more recently, political science \citep{moncada2017varieties}.
-These studies rely on historical, archival, observational, and statistical empirical approaches.
-This work---which strongly informs our survey design---offers several theories to explain variation in the prevalence of vigilantism.\footnote{We are obviously not testing all existing theories of vigilantism.
-This is partly because of constraints facing survey-based research.
-For example,  recent work shows that economic inequality drives Mexican \textit{autodefensa} activity \citep{phillips2017inequality}.
-Likewise, there are  long-run historical determinants that explain variation in armed resistance \citep{Osorio2019mexico}.
-Surveys are not especially conducive to testing those types of variables and theories.
-Instead, we focus on theories based on state presence, perceptions of legitimacy, and cultural norms, which are well suited to survey research.}  First, many scholars argue that vigilantism arises in response to the inability of states to effectively control crime and enforce social order \citep{bancroft1887works}.
-Historical studies of California identify state absence or weakness as a major cause of the emergence of vigilance committees and miners' courts during the gold rush (1848--55) \citep{hunt1920committees,rohrbough1997days,couttenier2017wild}.\footnote{There is substantial debate about the effectiveness of these activities \citep{clay2003order}.
-More generally, on extralegal institutions along the nineteenth-century frontier, see \cite{murtazashvili2013political}.} While gold miners often pursued justice in loose, disorganized, and fleeting ways \citep{mcdowell2002commons,mcdowell2007criminal}, some of these vigilance committees were highly organized and semipermanent \citep{bancroft1887works}.\footnote{\citet{taniguchi2016dirty} argues that the committee's actions in 1856 were not a response to a need for order, but instead a land grab from people who acquired land rights when Mexico controlled the region.} Outside of the United States, many studies likewise find that a desire for security and safety drive vigilantism.
-In Ghana, for example, the lack of criminal justice resources and the presence of corruption among security actors have been blamed for a rise of vigilantism between 1990 and 2000 \citep[416]{adinkrah2005vigilante}.
-Similarly, in  Guatemala since 1996, lack of effective state-based crime control was partly responsible for the rise of vigilantism \citep{godoy2006popular}.
-This research suggests the first hypothesis:
-
-\begin{itemize}
-  \item \textbf{Hypothesis 1:} Support for vigilantism will increase if people believe they cannot rely on the state to control crime and enforce social order.
-\end{itemize}
-
-One challenge to the hypothesis in the context of the US frontier is that vigilante activity was also widespread during roughly the same time along the East Coast and in the South, where states were far more established than along the Western frontier.
-In response, one theory argues that vigilantism in these locations instead arose along ``social frontiers'' \citep{obert2018keeping}.
-These are places where social relationships and social standing were ambiguous among different racial, ethnic, and class-based groups.
-If the state was not strong or stable enough to eliminate these ambiguities, then vigilantism emerged as a way to create and entrench social and political identities.
-Black Americans, in particular, were lynched in shocking numbers and frequency across the South well into the twentieth century \citep{dray2003hands,seguin2019national}.
-Likewise, based on studies of executions of Muslim men in Bosnia and a lynching in Jim Crow--era Maryland, Lee Ann Fujii \citeyearpar{fujii2017talk} argues that lynchings serve as ``violent displays'' that send signals to observers in the community and entrench social hierarchies and political identities.
-
-While the racial prejudice that drove violence in the United States is clear, vigilantism more generally need not be driven primarily by racial tensions.
-For example, \citet{martins2015linchamentos} writes that lynchings in Brazil are not mainly due to racial prejudice.
-Local accounts report no significant social difference between victims and perpetrators; nor are Black Brazilians particularly targeted by lynch mobs \citep{band2015rocinha, pearson2018latam, sinhoretto2009linchamentos}.
-These events might be driven by racism, but they do not reproduce the stark, racially disparate patterns that existed in the United States historically \citep[23]{martins2015linchamentos}.
-\citet[8]{jung2020lynching} likewise note that ``\textit{racist} social control'' is a unique property of American vigilantism.
-Brazil's patterns thus pose a puzzle for existing explanations for mob violence and stand in contrast to the American experience \citep{smaangs2016doing, wood2011lynching}.
-
-Recent research has shown that the relationship between states and vigilantism is more complicated than some early studies assumed.
-Based on extensive interviews and fieldwork in post-apartheid South Africa, Nicholas Rush \citet{smith2019contradictions} finds that people participate in vigilantism because the state is seen to be \textit{too} strong.
-Residents perceive a strengthening of the state, fuller support for human rights, and a stronger rule of law.
-As a result of these perceived changes, crime victims and other community members feel that the state will take too long to arrest, charge, and convict a perpetrator.
-If the perpetrator is released before trial, they might harm others or intimidate witnesses.
-Finally, people in South Africa fear that any punishment eventually received will not be severe enough.
-Accordingly, many South Africans believe it is right for people to take justice into their own hands.
-As a result, achieving legal reform and a  closer adherence to the rule of law can actually sparks greater use of extrajudicial violence.
-This suggests a second hypothesis:
-
-\begin{itemize}
-  \item \textbf{Hypothesis 2:} Support for vigilantism will increase if people believe states provide too much protection for offenders' rights. 
-  \end{itemize}
-
-Studies of vigilantism in Africa likewise find that religion, norms, and gender are powerful forces shaping the emergence and operation of vigilante groups.
-For example, in Nigeria, an increase in the influence of neoliberalism (alongside other political changes) drove vigilantism \citep[5]{pratten2008politics}.
-In Ghana, nearly 20 percent of the lynchings between 1990 and 2000 happened because people believed that someone (usually an older woman) had used ``mystical powers'' to wound someone's genitals or to cause other health problems  \citep[414]{adinkrah2005vigilante}.
-More generally, gender norms play an important role in the use of extrajudicial violence.
-The family members of people who are victims of a serious crime, such as forcible rape, often believe it tarnishes the reputation of the victim and their family.
-As a result, they believe they have the right to punish the offender.
-This suggests a third hypothesis:
-
-\begin{itemize}
-  \item \textbf{Hypothesis 3:} Support for vigilantism will increase when victims are female and their family carries out retribution.  
-  \end{itemize}
-
-In our three experiments, we argue that respondents do not believe that state-based legal institutions are the primary way to respond to serious crime.
-We find that people's attitudes toward vigilantism are shaped strongly by the characteristics of the incident that gives rise to it.
-In particular, people strongly support lynching by the family of a victim of a sexual offense or murder.
-Finally, our third experiment shows that support for lynchings can be reduced by reminding people of the penalties for lynching and of the risk of sparking vendettas.
+Our results show that people's attitudes toward lynching are shaped strongly by
+the characteristics of the incident that gives rise to it. In particular,
+respondents express support for lynchings perpetrated by the family of a victim
+of a sexual offense or murder. Subgroup analyses show that our findings are
+consistent across different segments of the population. In line with
+\citet{godoy2006popular} and \citet{martins2015linchamentos}, we find no
+experimental or qualitative evidence that lynching support is primarily driven
+by the race of the criminal. Our results also indicate that popular support for
+lynchings can be substantially reduced by reminding individuals of the
+penalties for lynching and of the risk of sparking vendettas, but not by
+emphasizing human rights protections. This suggests that campaigns focusing on
+the risks to vigilantes' personal security can be effective correctives to
+pro-lynching attitudes and may strengthen support for the rule of law.
 
 %%%%%%%%%%%%%
-
-\section{What Motivates Support for Lynching?}
-\label{sub:exp02}
-We invited respondents from all regions of Brazil to participate in our experiment.
-Qualtrics recruited 2,406 adult Brazilian citizens in 2020 between October 30 and December 22 to take part in our survey experiment.\footnote{Our ethics statement is available in Section E of the supplementary material.} We included ten questions on demographics and other information that might influence the results.
-These include the respondent's age, gender, ethnicity, level of education, monthly family income relative to the minimum wage, political orientation (left to right), support for the death penalty, whether they had been victimized in the last year, their trust in the police, and their trust in the judicial system.
-We used these measures to disentangle heterogeneous effects in the main responses.
-
-In our first experiment, we examined how the stated motivation for a lynching affects respondents' views about whether it is justified.
-In particular, we assessed the impact of three factors that have been cited as major drivers of vigilante justice: (1) police ineffectiveness; (2) slow response by the criminal legal system; and (3) demand for harsher punishment for offenders.
-Belief in the ineffectiveness of policing appears to be a strong predictor of vigilantism \citep{cruz2019determinants, garcia2019anger}.
-If police cannot or will not stop crime, then people often believe they have a right to do so themselves.
-Related to this, within the academic literature, lack of trust in the criminal legal system often motivates vigilantism \citep{godoy2004justice, smith2019contradictions}.
-This is often because of long criminal proceedings, which cause significant anxiety for the victims.
-Finally, we examined whether respondents believe that the legal punishment given to offenders is severe enough.
-In particular, we wanted to assess whether respondents are motivated by a desire for harsher penalties in Brazil's criminal legal system.
-
-The experiment consisted of three treatment conditions and one control group.
-Respondents read an excerpt of a news article describing a real lynching case in Jundia\'{i}, Brazil.
-Jundia\'{i} is a well-known metropolitan city of about four hundred thousand residents in the state of S\~{a}o Paulo, and we chose it because it is not a particularly distinctive, violent, or unusual city.
-We slightly edited the original text so that respondents had no prior knowledge of the crime.\footnote{The original article is available at \url{https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso}.
-Access: August 2020.} Consistent with Bateson's \citeyearpar[3]{bateson2020politics} emphasis on vigilantism as including ``prevention, investigation, or punishment of offenses,'' the vignette for the control group explains that the lynching took place while a crime was occurring.
-We asked respondents to show their level of support for mob violence using a 0--100 slider, where 0 means no support and 100 means full support.\footnote{We chose not to describe an especially heinous crime, such as murder or sexual assault, because we wanted people to respond to the treatment rather than the crime itself.
-By focusing on a less serious crime, the treatment is more salient.
-As shown in the second experiment, there is strong support for lynching for more serious crimes.
-The baseline of support for lynching in this vignette is about 36 percent (on a scale of 0 to 100), so the crime discussed appears sufficiently serious to justify lynching to a significant number of people.} Respondents in each of the three treatments read the same piece, but with one additional sentence explaining the motivations behind the lynching.
-Treatment 1 (which is motivated by Hypothesis 1) aimed to test the state-absence explanation.
-Hypothesis 2 claims that greater protection of offenders' rights increases vigilantism.
-Treatments 2 and 3 tested two versions of that hypothesis, in the form of slower judicial processes and insufficiently harsh punishments.
-The vignettes are as follows:
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Control group}: A man was lynched last Friday in Jundiaí, São Paulo.
-According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community.\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo.
-De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade.''}
-\end{itemize}
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Treatment 1 (Police ineffectiveness)}: A man was lynched last Friday in Jundiaí, São Paulo.
-According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community.
-\textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the police never patrol the area.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo.
-De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade.
-\textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque `a polícia nunca patrulha o local.'''}}
-\end{itemize}
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Treatment 2 (Slow criminal legal system)}: A man was lynched last Friday in Jundiaí, São Paulo.
-According to the neighbors, he tried to break into a house but was immobilized and beaten by members of the community.
-\textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the judicial system is too slow and the perpetrator is on the street until the case is heard.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo.
-De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade.
-\textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque ``a justiça é muito lenta e os criminosos ficam soltos até o julgamento.'''}}
-\end{itemize}
-
-\begin{itemize}
-\tightlist
-\item
-  \emph{Treatment 3 (Demand for harsher legal punishment)}: A man was lynched last Friday in Jundiaí, São Paulo.
-According to the neighbours, he tried to break into a house but was immobilised and beaten by members of the community.
-\textbf{One of the residents who took part in the lynching said they had beaten the suspect because ``the judicial punishment is not harsh enough.''}\footnote{In Portuguese: ``Um homem foi linchado na última sexta-feira em Jundiaí, São Paulo.
-De acordo com vizinhos, ele tentou invadir uma residência mas foi imobilizado e agredido por membros da comunidade.
-\textbf{Um dos moradores envolvidos no linchamento disse que eles agrediram o suspeito porque `a punição da justiça não é dura o suficiente.'''}}
-\end{itemize}
-
-Before each vignette, respondents read the following text:
-
-\begin{itemize}
-\tightlist
-\item
-  You will be shown a news article.
-Please read it carefully.
-After you read the article, we will ask you one question about it.\footnote{In Portuguese: ``Uma notícia será apresentada para você.
-Por favor, leia a notícia com atenção.
-Após você ler o artigo, faremos uma pergunta sobre ele.''}
-\end{itemize}
-
-After the vignette, respondents were presented with this question:
-
-\begin{itemize}
-\tightlist
-\item
-  Do you think that the lynching was justified?
-Please use the slider below to indicate your opinion.
-For disagreement, use 0 to 49; for agreement, use 51 to 100.
-Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``Você acha que o linchamento foi correto?
-Por favor, use a barra abaixo para indicar sua opinião.
-Para discordar, use de 0 a 49; para concordar, use de 51 a 100.
-Por favor, use 50 para não concordar nem discordar.''}
-\end{itemize}
-
-\begin{table}[htbp] \centering
-  \caption{Average treatment effects for experiment 1}
-  \label{tab:exp01main}
-\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
-\\[-1.8ex]\hline \\[-1.8ex]
-\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
-\hline \\[-1.8ex]
- Police do not patrol area & 1.115 &  &  &  \\
-  & (1.861) &  &  &  \\
-  Justice too slow &  & -0.289 &  &  \\
-  &  & (1.927) &  &  \\
-  Punishment not harsh enough &  &  & 0.438 &  \\
-  &  &  & (1.921) &  \\
-  Combined treatments &  &  &  & 0.443 \\
-  &  &  &  & (1.545) \\
-  Constant & 36.300^{***} & 36.300^{***} & 36.300^{***} & 36.300^{***} \\
-  & (1.332) & (1.332) & (1.332) & (1.332) \\
- N & \multicolumn{1}{c}{1,161} & \multicolumn{1}{c}{1,111} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{2,215} \\
-\hline \\[-1.8ex]
-\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
-\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
-\end{tabular}
-\end{table}
-
-We randomized the treatment and control conditions for the entire respondent pool.
-This randomization procedure was independent of that of the other experiments.
-We carried out our hypothesis tests with OLS.
-We compared the average score given by the control group with the average score given by respondents in each treatment condition.
-
-The first piece of evidence that the experiment provides concerns how baseline levels of support for lynching vary according to individual characteristics.
-Table \ref{tab:exp01-baselines} shows the impact of gender, race, and ideology on the subjects' tolerance of lynchings.
-Our dependent variable ranges from 0 to 100.
-We observed that men are more likely to support lynchings when compared with women.
-This is in contrast to research in Uganda, Tanzania, and South Africa, where women support mob vigilantism more than men do because they believe that they are less likely to be subject to false accusations \citep{wilke2021gender}.\footnote{On the relationships between gender and violence, see \citet{kadera2018gendered} and related papers.} In line with \citet{martins2015linchamentos}, we found little evidence that support for lynchings is driven primarily by outright racial prejudice.\footnote{We recognize that race is socially-constructed and that racial categories can be codified in multiple ways.
-We adopt the racial classification used by the Brazilian Census Bureau (IBGE) as it is widely employed in social research \citep[e.g.][24]{lapop2018brazil} and intuitive to our respondents.
-Nevertheless, our findings are also consistent with research that uses different, and often more nuanced, conceptions of race \citep{monk2016consequences, schwartzman2020colour}.
-} Ideology is strongly correlated with support for lynching, with a negative coefficient for citizens who identify as being on the center left or left.\footnote{The results are very similar when we estimated the models using data from our third experiment.
-Please refer to Section D.2 in the supplementary material for the more information.}
-
-\begin{table}[ht] \centering
-  \caption{Determinants of baseline levels of lynching support}
-  \label{tab:exp01-baselines}
-\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
-\\[-1.8ex]\hline \\[-1.8ex]
-\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
-\hline \\[-1.8ex]
- Male & 5.124^{***} &  &  & 4.945^{**} \\
-  (\textit{Reference: female}) & (1.828) &  &  & (2.165) \\ \\
-  Asian &  & 1.119 &  & -6.050 \\
-  &  & (4.646) &  & (7.288) \\
-  Mixed race &  & 0.724 &  & -5.256 \\
-  &  & (2.467) &  & (4.026) \\
-  White &  & -1.283 &  & -9.877^{***} \\
-  (\textit{Reference: Black}) &  & (2.288) &  & (3.672) \\ \\
-  Left &  &  & -11.895^{***} & -10.108^{***} \\
-  &  &  & (2.388) & (3.199) \\
-  Center left &  &  & -14.707^{***} & -17.484^{***} \\
-  &  &  & (2.673) & (3.575) \\
-  Center right &  &  & -3.019 & -5.047 \\
-  &  &  & (2.881) & (3.838) \\
-  Right &  &  & 0.610 & 2.722 \\
-  (\textit{Reference: center}) &  &  & (2.328) & (3.235) \\ \\
-  Constant & 33.105^{***} & 37.122^{***} & 41.804^{***} & 45.738^{***} \\
-  & (1.251) & (2.109) & (1.793) & (4.160) \\
- N & \multicolumn{1}{c}{1,142} & \multicolumn{1}{c}{2,186} & \multicolumn{1}{c}{1,632} & \multicolumn{1}{c}{838} \\
-\hline \\[-1.8ex]
-\multicolumn{5}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\
-\multicolumn{5}{l}{Robust standard errors in parentheses.} \\
-\end{tabular}
-\end{table}
-
-There were no significant effects on any of the treatments.
-One possible interpretation of the null findings is that state presence and activity have no influence on attitudes toward lynching.
-If that interpretation is correct, we should reject Hypotheses 1 and 2.
-
-Given the extensive literature discussed above and the qualitative evidence collected in the next experiment (discussed in Section \ref{sec:exp01}), an alternative explanation is that the null results reflect the fact that respondents simply have little to no faith in the criminal legal system in general.
-Several pieces of evidence support this interpretation.
-First, many crimes in Brazil are never solved.
-For example, a recent statistic indicates that the police only solve about 10 percent of the homicides in Brazil, suggesting that even for serious crimes, the police provide little help \citep{pearson2018latam}.
-Second, Brazilian police forces themselves carry out a substantial number of unjustified killings of people from disadvantaged and minority communities, which undermines their legitimacy and the sense that they can be relied on \citep{willis2015killing}.\footnote{Recent work on Mexico shows that implementing rule of law reforms can reduce police violence \citep{magaloni2020institutionalized}.} In 2019, police killed more than 1,800 people in Rio de Janeiro alone.
-Third, the Brazilian penal code allows an accused person to appeal each decision several times, so it can take several years (and sometimes more than a decade) before a criminal case is closed \citep{sousa2005utilizaccao}.
-Given this, people do not believe that a perpetrator will be punished in a timely matter even if put on trial.
-Finally, along with the rise of Jair Bolsonaro---the far-right president who has publicly called for people to take the law into their own hands \citep{brant2021armas, uol2021bolsonaro}---survey evidence suggests that people have grown considerably more punitive \citep{datafolha2018penademorte}.
 
@@
 
-In the second experiment, we used a choice-based conjoint experimental design.
-We presented respondents with five pairs of profiles.
-Each profile consisted of eight attributes: (1) gender of the crime perpetrator; (2) age of the crime perpetrator; (3) race of the crime perpetrator; (4) residency of the crime perpetrator (local or nonlocal); (5) type of offense; (6) gender of the victim of the crime; (7) age of the crime victim; (8) type of lynching perpetrator.
-The attributes and levels are displayed in table \ref{tab:categories}.\footnote{Limits to the length of the survey mean that many possible attributes and levels could not be included.
-We chose these particular ones based on a reading of the existing literature and to ensure wide variation in the nature of the lynching scenario.}
+We invited respondents from all regions of Brazil to participate in our
+experiment. Qualtrics recruited 2,406 adult Brazilian citizens between October
+30 and December 22, 2020 to take part in our survey experiment.\footnote{Our
+ethics statement is available in Section E of the Supplementary Material.} We
+included ten questions on demographics and other information that might
+influence the results. These include the respondent's age, gender, ethnicity,
+level of education, monthly family income, political orientation (left to
+right), support for the death penalty, whether they had been victimized in the
+last year, their trust in the police, and their trust in the judicial system.
+We used these measures to disentangle heterogeneous effects in the main
+responses. Descriptive statistics are available in Section B of the
+Supplementary Material.
+
+In our first experiment, we used a choice-based conjoint experimental design.
+We presented respondents with five pairs of profiles. Each profile consisted of
+eight attributes: (1) gender of the crime perpetrator; (2) age of the crime
+perpetrator; (3) race of the crime perpetrator; (4) residency of the crime
+perpetrator (local or nonlocal); (5) type of offense; (6) gender of the victim
+of the crime; (7) age of the crime victim; (8) type of lynching perpetrator.
+The attributes and levels are displayed in table \ref{tab:categories}.
 
@@
 
-\newpage
+Respondents were asked to indicate in which scenario in each pair they thought
+that extrajudicial punishment was more justified. We also included a text box
+below each experiment for subjects to explain why they selected a particular
+case and whether they believed lynching was justified in neither case.
+Respondents read the following prompt before they started the
+experiment:\footnote{The vignettes were presented in Portuguese. The original
+text is available in Section C.1 of the Supplementary Material.}
 
-Respondents were asked to indicate in which scenario in each pair they thought that extrajudicial punishment was more justified.
-We also included a text box below each experiment for subjects to explain why they selected a particular case and whether they believed lynching was justified in neither case.
-Respondents read the following prompt before they started the experiment:
-
-\begin{itemize}
-\tightlist
-\item
-  Lynchings are often used as social punishment in Brazil.
-Lynchings are cases in which three or more people physically attack or execute a suspected criminal in public.
-We are interested in knowing more about how Brazilians see these episodes.
-In the next five questions, please read the description of two possible lynching victims in Brazil and indicate in which case you believe the punishment is more justified.
-Even if you are not entirely sure, please select one of the cases.\footnote{In Portuguese: ``Linchamentos são às vezes usados como punição social no Brasil.
-Linchamentos são casos nos quais três ou mais pessoas agridem fisicamente ou executam em público um suspeito de um crime.
-Estamos interessados em saber mais sobre como os brasileiros vêem estes episódios.
-Nas próximas cinco questões, por favor, leia a descrição de duas possíveis vítimas de linchamento no Brasil e indique em quais delas você acredita que a punição é mais justificada.
-Mesmo que você não tenha certeza, por favor, escolha um dos casos.''}
+\begin{itemize} \tightlist \item Lynchings are often used as social punishment
+  in Brazil. Lynchings are cases in which three or more people physically
+  attack or execute a suspected criminal in public. We are interested in
+  knowing more about how Brazilians see these episodes. In the next five
+  questions, please read the description of two possible lynching victims in
+  Brazil and indicate in which case you believe the punishment is more
+  justified. Even if you are not entirely sure, please select one of the cases.
 \end{itemize}
 
-We estimated our conjoint experiments with the \texttt{cregg} package \citep{leeper2018cregg} for the R statistical language \citep{rstats2019}.
-We report marginal means in our main analysis instead of average marginal component effects (AMCEs).
-\citet{leeper2018subgroup} show that AMCEs can be misleading in subgroup comparisons as model results are sensitive to the choice of reference categories in interactions.
-In contrast, marginal means allow for a clear description of quantities of interest, in our case preferences about lynching, while also allowing for easy comparisons between groups of respondents.
-In a forced-choice experiment such as this one, marginal means are interpreted as probabilities.
-A marginal-means estimate of 0.5 indicates that respondents are indifferent to this attribute vis-à-vis other attributes.
-When the coefficient is lower than 0.5, respondents dislike profiles with this attribute.
-Conversely, when the point estimate is higher than 0.5, respondents prefer profiles containing a given attribute.
+We report marginal means in our main analysis instead of average marginal
+component effects (AMCEs). \citet{leeper2018subgroup} show that AMCEs can be
+misleading in subgroup comparisons as model results are sensitive to the choice
+of reference categories in interactions. In contrast, marginal means allow for
+a clear description of quantities of interest, in our case preferences about
+lynching, while also allowing for easy comparisons between groups of
+respondents. In a forced-choice experiment such as this one, a marginal-means
+estimate of 0.5 indicates that respondents are indifferent to this attribute
+vis-à-vis other attributes. When the coefficient is lower than 0.5, respondents
+dislike profiles with this attribute. Conversely, when the point estimate is
+higher than 0.5, respondents prefer profiles containing a given attribute.
 
-Figure \ref{fig:exp01} shows the main results for the conjoint experiment.
-The graph illustrates the preference associated with each attribute of the hypothetical lynching episode.
-Dots with horizontal bars represent point estimates and 95 percent confidence intervals from linear regressions with robust standard errors clustered at the respondent level.\footnote{This was a forced-choice experiment, so respondents had to choose one of the scenarios as more justified.
-To see whether this was problematic, we included an optional open-text box inviting respondents to explain their choices.
-Based on a semisupervized Dirichlet allocation model, we estimated about 20 percent of respondents were opposed to lynchings in general.
-Please refer to Section C.4 of the supplementary material for further information.}
+Figure \ref{fig:exp01} shows the main results for the conjoint experiment. The
+graph illustrates the preference associated with each attribute of the
+hypothetical lynching episode. Dots with horizontal bars represent point
+estimates and 95 percent confidence intervals from linear regressions with
+robust standard errors clustered at the respondent level.\footnote{Based on a
+semisupervized Dirichlet allocation model, we estimated about 20 percent of
+respondents were opposed to lynchings in general but forced to choose. Please
+refer to Section C.5 of the supplementary material for further information.}
 
@@
 
-Respondents selected male offenders (0.548, SE = 0.003, $p$-value $<$ 0.001) as preferred lynching victims more often than female offenders (0.438, SE = 0.004, $p$-value $<$ 0.001).
-We found identical results in our subgroup analyses, in which we disaggregated our sample according to respondents' gender, income, race, support for the death penalty, and views on the police and judiciary.
-In all cases, men and teenage boys were more likely to be selected as more justified victims of lynching.
-Compared with the attributes we discuss below, the gender of the crime perpetrator had one of the largest effects in our experiment.
-With regard to the age of the crime perpetrator, respondents tolerated the lynching of adults (0.520, SE = 0.005, $p$-value $<$ 0.001) more than attacks against teenagers (0.498, SE = 0.005, $p$-value = 0.650) or the elderly (0.483, SE = 0.005, $p$-value $<$ 0.001).
-More precisely, subjects were indifferent toward teenagers but reacted positively to lynching of adults and negatively to lynching of elderly people.
+Respondents selected male offenders (0.548, SE = 0.003, $p$-value $<$ 0.001) as
+preferred lynching victims more often than female offenders (0.438, SE = 0.004,
+$p$-value $<$ 0.001). We found identical results in our subgroup analyses, in
+which we disaggregated our sample according to respondents' gender, income,
+race, support for the death penalty, and views on the police and judiciary. In
+all cases, men and teenage boys were more likely to be selected as more
+justified victims of lynching. Compared with the attributes we discuss below,
+the gender of the crime perpetrator had one of the largest effects in our
+experiment. With regard to the age of the crime perpetrator, respondents
+tolerated the lynching of adults (0.520, SE = 0.005, $p$-value $<$ 0.001) more
+than attacks against teenagers (0.498, SE = 0.005, $p$-value = 0.650) or the
+elderly (0.483, SE = 0.005, $p$-value $<$ 0.001). More precisely, subjects were
+indifferent toward teenagers but reacted positively to lynching of adults and
+negatively to lynching of elderly people.
 
-When we analyzed the effect of the race of the crime perpetrator, in contrast with the American experience, respondents favored the lynching of white perpetrators (0.512, SE = 0.006, $p$-value = 0.050) the most.
-Of all the racial identities that we included in the experiment, Black people were the least likely to be chosen as a more justified lynching victim (0.490, SE = 0.006, $p$-value = 0.092), although the 95 percent confidence intervals overlap with the remaining categories.
-The effect is also robust for most subgroups, including white respondents.
-Asian respondents, however, rated fellow Asians as their least preferred choice.
-Taken together, the results provide experimental evidence that support for lynchings in Brazil does not resemble the typical racial patterns scholars have observed in the United States \citep{dray2003hands,seguin2019national,obert2018keeping}.
-These findings are consistent with recent research on vigilantism in Haiti \citep{jung2020lynching} and with journalistic observations.
-They further suggest that the US experience with lynchings might be distinct from vigilantism in other places and times \citep{oliveira2016mob}.
+When we analyzed the effect of the race of the crime perpetrator, in contrast
+with the American experience, respondents favored the lynching of white
+perpetrators (0.512, SE = 0.006, $p$-value = 0.050) the most. Of all the racial
+identities that we included in the experiment, Black people were the least
+likely to be chosen as a more justified lynching victim (0.490, SE = 0.006,
+$p$-value = 0.092), although the 95 percent confidence intervals overlap with
+the remaining categories. The effect is also robust for most subgroups,
+including white respondents. Asian respondents, however, rated fellow Asians as
+their least preferred choice. Taken together, the results provide experimental
+evidence that support for lynchings in Brazil does not resemble the typical
+racial patterns scholars have observed in the United States
+\citep{dray2003hands,seguin2019national,obert2018keeping}. These findings are
+consistent with recent research on vigilantism in Haiti
+\citep{jung2020lynching} and with journalistic observations. They further
+suggest that the US experience with lynchings might be distinct from
+vigilantism in other places and times \citep{oliveira2016mob}.
 
-The residency of the perpetrator is not a significant driver of support for lynching.
-Subjects were indifferent as to whether the crime perpetrator lives in the area (0.498, SE = 0.004, $p$-value = 0.668) or in another neighborhood (0.502, SE = 0.004, $p$-value = 0.668).
-In this sense, it is possible that subjects see lynchings not as a means to protect the area in which they live, which people commonly suppose vigilante groups do, but rather as retribution in specific cases.
+The residency of the perpetrator is not a significant driver of support for
+lynching. Subjects were indifferent as to whether the crime perpetrator lives
+in the area (0.498, SE = 0.004, $p$-value = 0.668) or in another neighborhood
+(0.502, SE = 0.004, $p$-value = 0.668). In this sense, it is possible that
+subjects see lynchings not as a means to protect the area in which they live,
+which people commonly suppose vigilante groups do, but rather as retribution in
+specific cases.
 
-The next attribute is type of offense.
-Rape was by far the most significant attribute in our model (0.719, SE = 0.009, $p$-value $<$ 0.001), followed by murder (0.608, SE = 0.006, $p$-value $<$ 0.001) and molestation (0.538, SE = 0.006, $p$-value $<$ 0.001).
-It is not surprising that murder and rape were the most important offenses to respondents.
-Overall, we found that respondents do not believe that property crimes, such as car theft (0.351, SE = 0.009, $p$-value $<$ 0.001) and pickpocketing (0.314, SE = 0.006, $p$-value $<$ 0.001), provide justification for lynching.
-When we analyzed the data by groups, we also saw that poorer respondents, whose household income is less than R\$3,000 (US\$650) per month, are more likely to support the lynching of individuals who commit a property crime.
+The next attribute is type of offense. Rape was by far the most significant
+attribute in our model (0.719, SE = 0.009, $p$-value $<$ 0.001), followed by
+murder (0.608, SE = 0.006, $p$-value $<$ 0.001) and molestation (0.538, SE =
+0.006, $p$-value $<$ 0.001). It is not surprising that murder and rape were the
+most important offenses to respondents. Overall, we found that respondents do
+not believe that property crimes, such as car theft (0.351, SE = 0.009,
+$p$-value $<$ 0.001) and pickpocketing (0.314, SE = 0.006, $p$-value $<$
+0.001), provide justification for lynching. When we analyzed the data by
+groups, we also saw that poorer respondents, whose household income is less
+than R\$3,000 (US\$650) per month, are more likely to support the lynching of
+individuals who commit a property crime.
 
-For age, we observed that respondents were particularly concerned about children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this attribute is strongly correlated with support for lynchings.
-Respondents also thought lynchings are more justified when the victim is a teenager (0.505, SE = 0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$ 0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001).
+For age, we observed that respondents were particularly concerned about
+children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this
+attribute is strongly correlated with support for lynchings. Respondents also
+thought lynchings are more justified when the victim is a teenager (0.505, SE =
+0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$
+0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001).
 
-Consistent with Hypothesis 3, when we analyzed the gender of the crime victim, we found that respondents support lynchings more strongly when the victim is a woman or teenage girl (0.511, SE = 0.004, $p$-value = 0.002) and less strongly when the lynching victim is a man or teenage boy (0.489, SE = 0.004, $p$-value = 0.002).
-The difference here is smaller than when we considered the gender of the crime perpetrator, but as in the previous estimation the 95 percent confidence intervals of each attribute did not overlap.
+When we analyzed the gender of the crime victim, we found that respondents
+support lynchings more strongly when the victim is a woman or teenage girl
+(0.511, SE = 0.004, $p$-value = 0.002) and less strongly when the lynching
+victim is a man or teenage boy (0.489, SE = 0.004, $p$-value = 0.002). The
+difference here is smaller than when we considered the gender of the crime
+perpetrator, but as in the previous estimation the 95 percent confidence
+intervals of each attribute did not overlap.
 
-Lastly, and related to this, we examined who respondents believed are more legitimate perpetrators of lynchings.
-Respondents considered the family to be the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$ 0.001).
-Again, the intervals here did not overlap with those of any other category.
-Bystanders (0.505, SE = 0.007, $p$-value = 0.450), gangs (0.502, SE = 0.007, $p$-value = 0.815), and neighbors (0.492, SE = 0.007, $p$-value = 0.262) do not increase or decrease respondents attitudes about lynching.
-If the police carry out a lynching, that reduced the perceived justification (0.467, SE = 0.007, $p$-value $<$ 0.001).
-In sum, respondents did not believe that lynchings should be carried out by the state but did believe they should be used as a tool for individual or family retribution.
+Lastly, and related to this, we examined who respondents believed are more
+legitimate perpetrators of lynchings. Respondents considered the family to be
+the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$
+0.001). Again, the intervals here did not overlap with those of any other
+category. Bystanders (0.505, SE = 0.007, $p$-value = 0.450), gangs (0.502, SE =
+0.007, $p$-value = 0.815), and neighbors (0.492, SE = 0.007, $p$-value = 0.262)
+do not increase or decrease respondents attitudes about lynching. If the police
+carry out a lynching, that reduced the perceived justification (0.467, SE =
+0.007, $p$-value $<$ 0.001). In sum, respondents did not believe that lynchings
+should be carried out by the state but did believe they should be used as a
+tool for individual or family retribution.
 
-Respondents were given the opportunity to explain the reason why they answered as they did.
-We analyzed a random sample of nearly 17 percent of the answers.
-Three major themes emerge.
-First, respondents felt that crimes that were especially heinous deserved a response.
-For example, one respondent explained their choice of a particular case as more justified by noting, ``Eye for an eye, it's absolutely fair.'' A second  theme is the injustice of victimizing vulnerable populations.
-One respondent explains, ``The victim is an elderly person, it's okay to lynch the criminal.'' Another respondent says, ``If the victim is a child, lynchings are not enough, they deserve more.'' Finally, a third theme is that families have a special right to vengeance.
-One respondent explained their choice by saying, ``The family was appalled and did justice with their own hands!'' These open-ended answers are consistent with the quantitative results about what people believe, but they also provide additional evidence about why they hold their beliefs.
+Respondents were given the opportunity to explain the reason why they answered
+as they did. We analyzed a random sample of nearly 17 percent of the answers.
+Three major themes emerge. First, respondents felt that crimes that were
+especially heinous deserved a response. For example, one respondent explained
+their choice of a particular case as more justified by noting, ``Eye for an
+eye, it's absolutely fair.'' A second  theme is the injustice of victimizing
+vulnerable populations. One respondent explains, ``The victim is an elderly
+person, it's okay to lynch the criminal.'' Another respondent says, ``If the
+victim is a child, lynchings are not enough, they deserve more.'' Finally, a
+third theme is that families have a special right to vengeance. One respondent
+explained their choice by saying, ``The family was appalled and did justice
+with their own hands!'' These open-ended answers are consistent with the
+quantitative results about what people believe, but they also provide
+additional evidence about why they hold their beliefs.\footnote{Please refer to
+Section C.5 of the Supplementary Materials for further information.}
 
@@
 
-Even if people view lynchings as a legitimate activity, that does not mean that this norm cannot be changed \citep{weaver2019judge}.
-In the third experiment, we measured the effect of information provision on attitudes about lynching.
+Even if people view lynchings as a legitimate activity, that does not mean that this norm cannot be changed.
+In our second experiment, we measured the effect of information provision on attitudes about lynching.
 More specifically, we tested whether reminding respondents about the legal and social consequences of vigilante justice reduces subjects' support for it.
@@
 Subjects in the control group received no information about the consequences of lynchings.
-The text shown to the control and treatment groups can be read below.
+The text shown to the control and treatment groups can be read below.\footnote{The Portuguese version is available in Section D.1 of the Supplementary Material.}
 
@@
 For disagreement, use 0 to 49; for agreement, use 51 to 100.
-Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições.
-O quanto você concorda ou discorda que linchamentos podem ser justificados?
-Por favor, use a barra abaixo para indicar sua preferência.
-Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100.
-Por favor, use 50 caso você não concorde nem discorde.''}
+Please use 50 if you neither agree nor disagree.
 \end{itemize}
@@
 For disagreement, use 0 to 49; for agreement, use 51 to 100.
-Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições.
-\textbf{Entretanto, a constituição e o código penal do Brasil proíbem estritamente os linchamentos e os envolvidos podem ser acusados de tortura ou assassinato.} O quanto você concorda ou discorda que linchamentos podem ser justificados?
-Por favor, use a barra abaixo para indicar sua preferência.
-Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100.
-Por favor, use 50 caso você não concorde nem discorde.''}
+Please use 50 if you neither agree nor disagree.
 \end{itemize}
@@
 For disagreement, use 0 to 49; for agreement, use 51 to 100.
-Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições.
-\textbf{Entretanto, a constituição do Brasil afirma que todos os indivíduos têm o direito de não serem torturados, inclusive criminosos}.
-O quanto você concorda ou discorda que linchamentos podem ser justificados?
-Por favor, use a barra abaixo para indicar sua preferência.
-Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100.
-Por favor, use 50 caso você não concorde nem discorde.''}
+Please use 50 if you neither agree nor disagree.
 \end{itemize}
@@
 For disagreement, use 0 to 49; for agreement, use 51 to 100.
-Please use 50 if you neither agree nor disagree.\footnote{In Portuguese: ``No Brasil, algumas pessoas acreditam que linchamentos são justificados sob certas condições.
-\textbf{Entretanto, linchamentos podem iniciar um ciclo de violência pois a família ou amigos da vítima podem retaliar a comunidade}.
-O quanto você concorda ou discorda que linchamentos podem ser justificados?
-Por favor, use a barra abaixo para indicar sua preferência.
-Para indicar que discorda, use de 0 a 49; para concordar, use de 51 a 100.
-Por favor, use 50 caso você não concorde nem discorde.''}
+Please use 50 if you neither agree nor disagree.
 \end{itemize}
 
-We are interested in the difference between the average score given by each of the treatment groups and the average score given by the control group.\footnote{As we did in the previous experiment, we randomized the treatment and control conditions to all subjects included in our sample.
-The treatment assignment here was independent of that of the previous two experiments.} We estimate average treatment effects using OLS with dummy indicators for the treatment groups.
+We are interested in the difference between the average score given by each of the treatment groups and the average score given by the control group.
+We estimate average treatment effects using OLS with dummy indicators for the treatment groups.
 
@@
 
-Regulating violence is one of the most fundamental responsibilities of the state, and in many places in the world today, states are failing to do so.
-In Brazil, lynchings are commonplace and are only one form of vigilantism and extralegal violence plaguing the country.
-Many favelas are dominated by organized crime groups that engage in violence and wield the threat of violence extralegally \citep{arias2006dynamics,barnes2021logic}.
-In this paper, we used survey experiments to examine people's attitudes toward lynching to better understand what makes people feel some instances are more justified, which reasons for doing so gain support, and how to reduce support for lynchings.
-If people felt like they cannot rely on the state to provide effective regulation of serious violence, then they were more likely to develop beliefs and norms that legitimate the extrajudicial use of violence.
-People found lynchings more justifiable when they were in response to especially heinous crimes and when the crimes were perpetrated against vulnerable populations, and they viewed the family as having a distinctive duty for carrying out vengeance.
-Nevertheless, we were able to reduce support for lynchings by reminding respondents that lynchings are a criminal act and that lynchings risk igniting vendettas.
+Regulating violence is one of the most fundamental responsibilities of the
+state, and in many places in the world today, states are failing to do so.
+Brazil provides a telling example of how extrajudicial violence can escalate
+and pose a serious threat to the stability of government institutions. From
+2011 to 2015, the country registered about 2,500 lynching episodes, and 173
+people were killed by angry mobs in 2015 alone---nearly one execution every two
+days \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
+Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
+Brazil for more than thirty years, these figures are not only the highest in
+the country's history, but among the highest in the world. The people who
+participate in lynchings are typically young men, but they also sometimes
+include teenage women and girls, elderly women, and even members of the local
+police \citep{moura2017linchamentos}. In this respect, interventions that
+reduce popular support for extrajudicial violence can have a substantial impact
+on citizen welfare and potentially increase state legitimacy in young
+democracies.
 
-Extrajudicial violence has several profound consequences on political development and the rule of law.
-First, extensive reliance on extrajudicial violence undermines legal and judicial reform because people feel informal, local dispute resolution is preferable to state-based institutions \citep{blair2020peacekeeping}.
-This prevents the state from becoming the focal body to resolve criminal and civil conflicts.
-Second, and related, this has the potential to create a feedback effect in which more vigilantism leads to people viewing the state as less effective and less legitimate, which then leads to more vigilantism and less state effectiveness \citep{jung2020lynching}.
-Third, a legacy of lynchings can have detrimental effects on political participation.
-In the United States, for instance, racist lynchings reduced local Black voter turnout substantially \citep{jones2017political}.
-Given the prevalence of vigilantism in places with precarious electoral systems and substantial ethnic diversity, vigilantism is likely to undermine many forms of political participation.
-Finally, improving institutions often has negative, unintended consequences that are difficult to ameliorate.
-This is well documented in the case of rule-of-law reform and vigilantism in South Africa \citep{smith2019contradictions}, but we also see it in the push for democratization in Mexico \citep{trejo2021high} and attempts to reduce gang control of Brazilian favelas \citep{magaloni2020killing}.
-Outcomes often worsen on important margins when people seek to improve judicial practice, reduce corruption, or reduce the use of extrajudicial violence.
-Developing effective political institutions is one of the state's most important responsibilities, and vigilante violence presents a substantial challenge to doing so.
+Our results show that the characteristics of a lynching significantly effect
+people's support for it, especially when the crimes are heinous or committed
+against vulnerable populations. In contrast with studies about mob violence in
+the American South, we find no evidence that lynchings are strictly racially
+motivated in Brazil. While we were able to reduce support for lynchings by
+reminding respondents that lynchings are a criminal act and that lynchings risk
+igniting vendettas, appeals to human rights had no effect in our experiment.
 
-\newpage
+Our work also suggests new avenues for further research. While previous studies
+indicate that there is a relationship between pro-lynching attitudes and actual
+engagement in vigilante violence \citep{weisburd1988vigilantism}, future
+research should try to identify which factors motivate citizens to participate
+in lynchings episodes \citep{nivette2016institutional}. Moreover, it is still
+unclear whether other forms of vigilantism, such as security patrols, property
+damages, or coercive interrogations \citep{bateson2020politics} have similar
+levels of popular support. Finally, lynchings have often been described as a
+response to low state capacity, yet in many cases state agents actively incite
+or engage in vigilante violence themselves \citep{arias2010violent}. Future
+studies may investigate in which circumstances state authorities favor informal
+local control instead of public law enforcement. Unravelling these issues is
+crucial if scholars wish to better understand how and why states and civil
+society decide to use violence.
 

### 2022-09-08 appendix/appendix.Rmd
update submission

@@
 author:
-- "Danilo Freire[^freire]"
-- "David Skarbek[^skarbek]"
-date: \today
 fontfamily: libertine
@@
 
-[^freire]: School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <http://danilofreire.github.io>.
-
-[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, <davidskarbek@brown.edu>, <http://davidskarbek.com>.
-
 \newpage
@@
 packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
-              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
+              "janitor", "quanteda", "quanteda.textmodels", "quanteda.textplots",
+              "quanteda.textstats", "seededlda", "stargazer", "tidyverse")
 installed_packages <- packages %in% rownames(installed.packages())

### 2022-09-08 article/article.tex
update submission

--- 2022-08-22 short-article/short-article.tex
@@
 % Title
-\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
+\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil}
+
+% \footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
 D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
@@
 % Author
-\author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
+% \author{Danilo Freire\footnote{School of Social and Political Sciences, University of Lincoln, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{https://danilofreire.github.io}.} \and David Skarbek\footnote{Department of Political Science, Brown University, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \url{http://davidskarbek.com}.}}
 
 % Date
-\date{\today}
+\date{}
 
@@
 
-Even if people view lynchings as a legitimate activity, that does not mean that this norm cannot be changed.
-In our second experiment, we measured the effect of information provision on attitudes about lynching.
-More specifically, we tested whether reminding respondents about the legal and social consequences of vigilante justice reduces subjects' support for it.
-The experiment included three treatment conditions and a control group.
-In all of them we presented respondents with a short statement affirming that some Brazilians support vigilantism under certain conditions.
-We asked the control group to rate their agreement with the statement.
-Respondents were asked to use 0 to 49 if they disagreed, 50 if they neither agreed nor disagreed, and 50--100 if they agreed with the statement.
+Even if people view lynchings as a legitimate activity, that does not mean that
+this norm cannot be changed. In our second experiment, we measured the effect
+of information provision on attitudes about lynching. More specifically, we
+tested whether reminding respondents about the legal and social consequences of
+vigilante justice reduces subjects' support for it. The experiment included
+three treatment conditions and a control group. In all of them we presented
+respondents with a short statement affirming that some Brazilians support
+vigilantism under certain conditions. We asked the control group to rate their
+agreement with the statement. Respondents were asked to use 0 to 49 if they
+disagreed, 50 if they neither agreed nor disagreed, and 50--100 if they agreed
+with the statement.
 
-Each of the three treatment groups received a different message about the legal or social consequences of lynching in Brazil.
-In the first treatment, we informed subjects about how the Brazilian constitution and penal code punishes civilian violence.
-The second treatment group was notified about the human rights guarantees enshrined in Brazil's legal framework.
-The last treatment noted that lynchings can spark vendettas and initiate a cycle of violence in the community.
-Subjects in the control group received no information about the consequences of lynchings.
-The text shown to the control and treatment groups can be read below.\footnote{The Portuguese version is available in Section D.1 of the Supplementary Material.}
+Each of the three treatment groups received a different message about the legal
+or social consequences of lynching in Brazil. In the first treatment, we
+informed subjects about how the Brazilian constitution and penal code punishes
+civilian violence. The second treatment group was notified about the human
+rights guarantees enshrined in Brazil's legal framework. The last treatment
+noted that lynchings can spark vendettas and initiate a cycle of violence in
+the community. Subjects in the control group received no information about the
+consequences of lynchings. The text shown to the control and treatment groups
+can be read below.\footnote{The Portuguese version is available in Section D.1
+of the Supplementary Material.}
 
@@
 
-We are interested in the difference between the average score given by each of the treatment groups and the average score given by the control group.
-We estimate average treatment effects using OLS with dummy indicators for the treatment groups.
+We are interested in the difference between the average score given by each of
+the treatment groups and the average score given by the control group. We
+estimate average treatment effects using OLS with dummy indicators for the
+treatment groups.
 
@@
 
-Table \ref{tab:exp03main} summarizes our main results for this experiment.
-We find that when respondents are reminded of legal punishments associated with lynchings, their support for lynching decreases by about 11 percent.
-This result is consistent with the idea that respondents will support an activity less if they perceive it to be more costly.
-The next treatment group was told the human rights message.
-The result is not statistically significant and indicates that appeals to individual liberties and the rule of law are likely to fall short.
-This finding has practical implications, as many campaigns against violent crimes are conducted by human rights groups, which tend to emphasize this type of message.
-However, participants do not generally believe that offenders do, in fact, have human rights.
-Accordingly, we have little reason to believe that such messaging is effective.
-By contrast, Treatment 1 reminds respondents that perpetrators of lynching potentially face a high personal cost from doing so.
+Table \ref{tab:exp03main} summarizes our main results for this experiment. We
+find that when respondents are reminded of legal punishments associated with
+lynchings, their support for lynching decreases by about 11 percent. This
+result is consistent with the idea that respondents will support an activity
+less if they perceive it to be more costly. The next treatment group was told
+the human rights message. The result is not statistically significant and
+indicates that appeals to individual liberties and the rule of law are likely
+to fall short. This finding has practical implications, as many campaigns
+against violent crimes are conducted by human rights groups, which tend to
+emphasize this type of message. However, participants do not generally believe
+that offenders do, in fact, have human rights. Accordingly, we have little
+reason to believe that such messaging is effective. By contrast, Treatment 1
+reminds respondents that perpetrators of lynching potentially face a high
+personal cost from doing so.
 
-Our last treatment, which raises the possibility of sparking vendettas, has a large, negative effect on support for lynchings.
-Mentioning that lynchings trigger cycles of violence has a negative effect of about 8 percent when compared with the control group.
-While we expected that the coefficient for this treatment condition would be larger than that for the treatment on legal punishments, the means of both groups are not statistically different from each other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]).
-As with the other experiments, the results remain stable when we conduct subgroup analyses.
+Our last treatment, which raises the possibility of sparking vendettas, has a
+large, negative effect on support for lynchings. Mentioning that lynchings
+trigger cycles of violence has a negative effect of about 8 percent when
+compared with the control group. While we expected that the coefficient for
+this treatment condition would be larger than that for the treatment on legal
+punishments, the means of both groups are not statistically different from each
+other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). As with the
+other experiments, the results remain stable when we conduct subgroup analyses.
 
@@
 
+\newpage
 \setlength{\parindent}{0cm}

### 2022-09-08 article/old-article.tex
update submission

--- 2022-06-15 article/main.tex
@@
 \title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
-D'Amico, Miriam Golden, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
-Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, and Georg Vanberg for their valuable comments.
+D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
+Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments.
 We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington.
@@
 Our third experiment examines whether providing different types of information can affect respondents' perceptions of lynchings.
-Our strategy here is similar to that of public marketing campaigns that governments often use to change public opinion.
+Our strategy here is similar to that of public marketing campaigns that governments often use to try to change public opinion.
 In this experiment, we provide information akin to government messaging to the general public.
@@
 Instead, it is the belief that it is not the proper role of the police to do so and that the response should instead be carried out by the family of the victim.
-Third, our findings inform the relationship between political development and informal norms.
+Third, our findings inform the relationship between politics and informal norms.
 Even when legal institutions are present, norms  can undermine people's reliance on them.
 This is a major challenge in establishing the rule of law in developing countries, where residents often prefer informal solutions to crime over state-based solutions \citep[10]{blair2020peacekeeping}.
-As a result, the prevalence of lynchings undermines political development and state capacity, which can fall into a self-reinforcing cycle \citep{jung2020lynching}.
+As a result, the prevalence of lynchings undermines politics and state capacity, which can fall into a self-reinforcing cycle \citep{jung2020lynching}.
 As such, solving the problem of discretionary, extrajudicial use of violence is crucial for understanding political and economic development more generally.
@@
 Studies of vigilantism in Africa likewise find that religion, norms, and gender are powerful forces shaping the emergence and operation of vigilante groups.
-For example, in Nigeria, an increase in the influence of neoliberalism (alongside other political changes) drove vigilantism \citep[5]{pratten2008politics}.
+For example, in Nigeria, an increase in the influence of neoliberal policies drove vigilantism \citep[5]{pratten2008politics}.
 In Ghana, nearly 20 percent of the lynchings between 1990 and 2000 happened because people believed that someone (usually an older woman) had used ``mystical powers'' to wound someone's genitals or to cause other health problems  \citep[414]{adinkrah2005vigilante}.
@@
 
-Extrajudicial violence has several profound consequences on political development and the rule of law.
+Extrajudicial violence has several profound consequences on politics and the rule of law.
 First, extensive reliance on extrajudicial violence undermines legal and judicial reform because people feel informal, local dispute resolution is preferable to state-based institutions \citep{blair2020peacekeeping}.

### 2022-09-08 cover-letter/cover-letter.Rmd
update submission

---
author: 
    - Danilo Freire
opening: Dear Editors of Research & Politics,
closing: Sincerely,
address:
    - \textbf{The Editors}
    - Research & Politics
return-address: 
    - Danilo Freire
    - University of Lincoln
    - Brayford Pool, Lincoln LN6 7TS
    - United Kingdom
    - dfreire@lincoln.ac.uk
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: onehalf
margin: 2cm
papersize: a4paper
fontsize: 12pt
inline-links: true
colorlinks: true
output: 
    pdf_document:
        template: letter-template.latex
---

\doublespacing

I am writing to submit our research note entitled "Vigilantism and
Institutions: Understanding Attitudes toward Lynching in Brazil" for
consideration as a _Research & Politics_ research article. We use two survey
experiments and collect primary quality evidence to examine in which
circumstances individuals perceive lynchings as a justified extrajudicial
punishment and whether providing different types of information about lynching
reduces support for it. Our results show that respondents strongly support
lynchings perpetrated by the family of a victim of sexual abuse or murder. We
also find that that popular support for lynchings can be substantially reduced
by reminding individuals of the penalties for lynching and of the risk of
sparking vendettas, but not by emphasizing human rights protections.

We believe out findings sheds new light on what drives attitudes towards
vigilantism, particularly in a country that has been affected by a sharp rise
in lynching episodes. Our paper should appeal especially to researchers in
Comparative Politics and in Development Studies, particularly those interested
in extralegal violence and in Latin America. We incentivize scholars to
investigate whether other forms of vigilante violence enjoy similar levels of
popular support, as well as to study which factors increase the likelihood that
citizens will actually engage in vigilante violence.

We also provide extensive supplementary materials with data, replication code,
and additional analyses for consultation at
<https://github.com/danilofreire/lynching-experiment-brazil>. The appendix
describes the survey procedures in detail and contains further information on
the qualitative evidence we gathered from respondents.

Each of the authors confirms that this manuscript has not been previously
published and is not currently under consideration by any other journal. All of
the authors have approved the contents of this paper and have agreed to
_Research & Politics_' submission policies.

Each named author has equally contributed to conducting the underlying research
and drafting this manuscript. To the best of our knowledge, the authors have no
conflict of interest, financial or otherwise.

Author names, affiliation and contact details:

* Danilo Freire: Senior Lecturer, School of Social and Political Sciences,
  University of Lincoln, <dfreire@lincoln.ac.uk>,
  <https://danilofreire.github.io>. Corresponding author.

* David Skarbek, Associate Professor, Department of Political Science, Brown
  University, <david_skarbek@brown.edu>, <http://davidskarbek.com>.

\vspace{1cm}

### 2022-09-08 article/article.tex
prepare manuscript submission

@@
 
+% Endnotes
+\usepackage{endnotes}
+\let\footnote\endnote
+\def\footnotetext{\endnotetext[\number\numexpr\value{endnote}+1]}
+\let\footnotemark\endnotemark
+
 % Colours
@@
 % Margins
-\usepackage[margin=2cm]{geometry}
+\usepackage[margin=3cm]{geometry}
 
-% Packages I've been using for differen reasons
+% Packages I've been using for different reasons
 \usepackage{hyperref}
@@
 % Title
-\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil}
+\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil}
 
@@
 
-We invited respondents from all regions of Brazil to participate in our
-experiment. Qualtrics recruited 2,406 adult Brazilian citizens between October
-30 and December 22, 2020 to take part in our survey experiment.\footnote{Our
-ethics statement is available in Section E of the Supplementary Material.} We
-included ten questions on demographics and other information that might
-influence the results. These include the respondent's age, gender, ethnicity,
-level of education, monthly family income, political orientation (left to
-right), support for the death penalty, whether they had been victimized in the
-last year, their trust in the police, and their trust in the judicial system.
-We used these measures to disentangle heterogeneous effects in the main
-responses. Descriptive statistics are available in Section B of the
-Supplementary Material.
+We recruited 2,406 adult Brazilian citizens between October 30 and December 22,
+2020 to participate in our survey experiment.\footnote{Our ethics statement is
+available in Section E of the Supplementary Material.} We included ten
+questions on demographics and other information that might influence the
+results. These include the respondent's age, gender, ethnicity, level of
+education, monthly family income, political orientation (left to right),
+support for the death penalty, whether they had been victimized in the last
+year, their trust in the police, and their trust in the judicial system. We
+used these measures to disentangle heterogeneous effects in the main responses.
+Descriptive statistics are available in Section B of the Supplementary
+Material.
 
@@
 \begin{figure}[ht]
-\includegraphics[width=17cm]{conjoint-color.pdf}
+\includegraphics[width=15cm]{conjoint-color.pdf}
 \caption{Relative preferences for lynching-episode attributes (marginal means)}
@@
   \label{tab:exp03main}
-\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
-\\[-1.8ex]\hline \\[-1.8ex]
-\\[-1.8ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
-\hline \\[-1.8ex]
+  \addtolength{\tabcolsep}{-0.3em}
+\begin{tabular}{@{\extracolsep{.01pt}}lD{.}{.}{-5} D{.}{.}{-5} D{.}{.}{-5} D{.}{.}{-5} }
+\\[-2.5ex]\hline \\[-2ex]
+\\[-2.5ex] & \multicolumn{4}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
+\\[-2.5ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\
+\hline \\[-2ex]
  Constitution and penal code & -4.509^{**} &  &  &  \\
@@
 punishments, the means of both groups are not statistically different from each
-other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). As with the
-other experiments, the results remain stable when we conduct subgroup analyses.
+other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]). The results
+remain stable in the subgroup analyses.
 
@@
 
-\newpage
+% Endnotes
+\renewcommand {\footnotesize} {\normalsize}
+\theendnotes
+
+% Bibliography
 \setlength{\parindent}{0cm}
 \setlength{\parskip}{5pt}
-
-% Bibliography
 \bibliography{references.bib}

### 2022-09-08 cover-letter/cover-letter.Rmd
prepare manuscript submission

@@
 * Danilo Freire: Senior Lecturer, School of Social and Political Sciences,
-  University of Lincoln, <dfreire@lincoln.ac.uk>,
-  <https://danilofreire.github.io>. Corresponding author.
+  University of Lincoln, Brayford Pool, Lincoln, Lincolnshire LN6 7TS, United Kingdom, `+44 077-630-647-58`, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+  Corresponding author.
 
 * David Skarbek, Associate Professor, Department of Political Science, Brown
-  University, <david_skarbek@brown.edu>, <http://davidskarbek.com>.
+  University, 111 Thayer Street, Third Floor, Providence, RI 02912, United States of America, `+1 401-863-2825`, <david_skarbek@brown.edu>, <http://davidskarbek.com>, <https://twitter.com/davidskarbek>.
 

### 2022-09-08 title-page/title-page.Rmd
prepare manuscript submission

---
title:  Title Page
author: 
date: 
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: onehalf
papersize: a4paper
output:
  pdf_document:
    number_sections: no
    keep_tex: no
    toc: no
    template: title-page-template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
```

### Manuscript Title:

\noindent Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil

### Authors:

\noindent Danilo Freire: Senior Lecturer, School of Social and Political Sciences,
  University of Lincoln, Brayford Pool, Lincoln, Lincolnshire LN6 7TS, United Kingdom, \texttt{+44 077-630-647-58}, <dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
  Corresponding author.

\vspace{.4cm}

\noindent David Skarbek, Associate Professor, Department of Political Science, Brown
  University, 111 Thayer Street, Third Floor, Providence, RI 02912, United States of America, `+1 401-863-2825`, <david_skarbek@brown.edu>, <http://davidskarbek.com>, <https://twitter.com/davidskarbek>.

### 2022-09-08 appendix/lynchings.R

@@ -1,1352 +1,0 @@
-##############################################################
-## "Casting the First Stone: Lynching Attitudes in Brazil"  ##
-## Danilo Freire and David Skarbek                          ##
-## January 2021                                             ##
-##############################################################
-
-# Install and load required packages
-packages <- c("cjoint", "cregg", "kableExtra",
-              "janitor", "stargazer", "tidyverse")
-installed_packages <- packages %in% rownames(installed.packages())
-if (any(installed_packages == FALSE)) {
-  install.packages(packages[!installed_packages])
-}
-invisible(lapply(packages, library, character.only = TRUE))
-
-# Load the dataset, remove unused rows and columns,
-# and convert variable names to snake case
-df <- read_csv("../data/data.csv") %>%
-  clean_names() %>%
-  mutate(response_id            = as.character(response_id),
-         consent                = as.factor(q1),
-         progress               = as.numeric(progress),
-         finished               = as.factor(finished),
-         age                    = as.numeric(q2),
-         gender                 = as.factor(q3),
-         race                   = as.factor(q4),
-         education              = as.factor(q5),
-         region                 = as.factor(q6),
-         household_income       = as.factor(q7),
-         ideology               = as.factor(q8),
-         death_penalty          = as.factor(q9),
-         previous_victim        = as.character(q10),
-         previous_victim_text   = as.character(q10_text),
-         views_police           = as.factor(q11),
-         views_justice          = as.factor(q12),
-         exp02_control          = as.numeric(q18),
-         exp02_police           = as.numeric(q19),
-         exp02_slow_justice     = as.numeric(q20),
-         exp02_small_punishment = as.numeric(q21),
-         exp03_control          = as.numeric(q22),
-         exp03_constitution     = as.numeric(q23),
-         exp03_rights           = as.numeric(q24),
-         exp03_vendetta         = as.numeric(q25)) %>%
-  slice(-1L) %>%
-  select(-c(q1:q12, q18:q25)) %>%
-  relocate(response_id, consent, progress, finished,
-           location_latitude, location_longitude) %>%
-  mutate(across(where(is.character), tolower)) %>%
-  mutate(across(where(is.factor), tolower))
-
-# write_csv(df, "../data/data-portuguese.csv")
-
-# Translate factor values from Portuguese to English
-df <- df %>%
-  mutate(consent = recode(consent,
[…]

### 2022-09-08 data/lynchings.R

@@ -1,0 +1,757 @@
+#########################################################################################
+## "Vigilantism and Institutions: Understanding Attitudes towards Lynching in Brazil"  ##
+## January 2021                                                                        ##
+#########################################################################################
+
+# Record output log
+sink("./lynchings-log.txt")
+
+# Install and load required packages
+packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
+              "janitor", "quanteda", "quanteda.textmodels", "quanteda.textplots",
+              "quanteda.textstats", "seededlda", "stargazer", "tidyverse")
+installed_packages <- packages %in% rownames(installed.packages())
+if (any(installed_packages == FALSE)) {
+  install.packages(packages[!installed_packages])
+}
+invisible(lapply(packages, library, character.only = TRUE))
+
+# Load the dataset, remove unused rows and columns,
+# and convert variable names to snake case
+df <- read_csv("../data/data.csv") %>%
+  clean_names() %>%
+  mutate(response_id            = as.character(response_id),
+         consent                = as.factor(q1),
+         progress               = as.numeric(progress),
+         finished               = as.factor(finished),
+         age                    = as.numeric(q2),
+         gender                 = as.factor(q3),
+         race                   = as.factor(q4),
+         education              = as.factor(q5),
+         region                 = as.factor(q6),
+         household_income       = as.factor(q7),
+         ideology               = as.factor(q8),
+         death_penalty          = as.factor(q9),
+         previous_victim        = as.character(q10),
+         previous_victim_text   = as.character(q10_text),
+         views_police           = as.factor(q11),
+         views_justice          = as.factor(q12),
+         exp02_control          = as.numeric(q18),
+         exp02_police           = as.numeric(q19),
+         exp02_slow_justice     = as.numeric(q20),
+         exp02_small_punishment = as.numeric(q21),
+         exp03_control          = as.numeric(q22),
+         exp03_constitution     = as.numeric(q23),
+         exp03_rights           = as.numeric(q24),
+         exp03_vendetta         = as.numeric(q25)) %>%
+  slice(-1L) %>%
+  select(-c(q1:q12, q18:q25)) %>%
+  relocate(response_id, consent, progress, finished,
+           location_latitude, location_longitude) %>%
+  mutate(across(where(is.character), tolower)) %>%
[…]

### 2022-10-28 article/article.tex
updated article

--- 2022-08-22 short-article/short-article.tex
@@
 \usepackage[english]{isodate}
-% \cleanlookdateon
+\cleanlookdateon
 
@@
 \usepackage{natbib}
-\bibliographystyle{chicago-ff}
+\bibliographystyle{apalike}
 \makeatletter
@@
 We also find that criminal punishment and the threat of vendettas reduce support, but appeals to the human rights of victims have zero effect on support for lynchings.
+Unlike the U.S.
+experience with lynchings, race was not observed to play an important role in how respondents answered the survey.
 \vspace{.25cm}
 
-\noindent \textbf{Keywords:} extralegal violence, vigilantism, lynching, Brazil, crime 
+\noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
 \vspace{.25cm}
@@
 government institutions, yet we know little about what motivates local
-extrajudicial violence in the developing world \citep{bateson2020politics,
-smith2000new}. This omission is significant not only because local violence is
-pervasive in weak states, but also because it can be even more costly than war-
-or terrorism-related violence \citep{blair2017predicting}.
+extrajudicial violence and vigilantism in the developing world
+\citep{bateson2020politics}.\footnote{On vigilantism more generally, see
+\citet{schuberth2013challenging,
+zizumbo2017community,smith2019contradictions,cohen2022collective}.} This
+omission is significant not only because violence is pervasive in weak states,
+but it also comes at a great cost \citep{blair2017predicting}.
 
@@
 than one hundred countries in all regions of the world
-\citep[33]{jung2020lynching}, Latin America has been particularly affected by a
-sharp increase in vigilante violence. In recent years, countries like Brazil
-and Venezuela have experience nearly one execution every two days, and lynching
-episodes have also been reported in Guatemala, Mexico, Peru, and other
+\citep{jung2020lynching,smith2019contradictions}, Latin America has been
+particularly affected by a sharp increase in vigilante violence. Lynching
+episodes have been reported in Guatemala, Mexico, Peru, Venezuela and other
 countries in the region \citep{cruz2019determinants, godoy2004justice,
-barbara2015vigilantes}. These alarming figures suggest that, despite being
-dismissed by policymakers as irrational and senseless, vigilantism enjoys
-considerable approval in Latin America \citep{berg2011globalizing,
-goldstein2005flexible}. This raises a number of puzzles: under which conditions
-do citizens perceive lynchings as a legitimate response to crime? Are some
-groups seen as more ``deserving'' of lynchings that others? And how can we
-reduce pro-vigilantism attitudes in young, unequal democracies?
+barbara2015vigilantes}. From 2011 to 2015, Brazil registered about 2,500
+lynching episodes, and 173 people were killed by angry mobs in 2015
+alone---nearly one execution every two days \citep{barbara2015vigilantes,
+oliveira2016mob}. According to José de Souza Martins
+\citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for
+more than thirty years, these figures are not only the highest in the country's
+history, but among the highest in the world. The people who participate in
+lynchings are typically young men, but they also sometimes include teenage
+women and girls, elderly women, and even members of the local police
+\citep{moura2017linchamentos}.
+
+These alarming figures suggest that, despite being dismissed by policymakers as
+irrational and senseless, vigilantism enjoys considerable approval in Latin
+America \citep{berg2011globalizing, goldstein2005flexible}. This raises a
+number of puzzles: under which conditions do citizens perceive lynchings as a
+legitimate response to crime? Are some groups seen as more ``deserving'' of
+lynchings that others? And how can we reduce pro-vigilantism attitudes in
+young, unequal democracies?
 
 In this study, we run two survey experiments and use primary qualitative data
-to understand attitudes toward lynchings in Brazil. First, we employ a conjoint
-experiment with eight attributes to evaluate in which circumstances citizens
-perceive lynchings as a justifiable punishment for crime. We also included
-open-ended questions for respondents to elaborate on their decision process.
-Finally, we use an information provision experiment to test the efficacy of
-three strategies to reduce individual support for lynchings.
+to understand attitudes toward lynchings in Brazil. Our paper begins with a
+conjoint experiment that evaluates in which circumstances citizens perceive
+lynchings as a justifiable punishment for crime. We also included open-ended
+questions for respondents to elaborate on their decision process. Lastly, we
+employ an information provision experiment to test the efficacy of three
+strategies to reduce individual support for lynchings.
 
@@
 bias, and survey experiments help to elicit sensitive information---an
-especially important benefit in researching this topic \citep{grimm2010social}.
-Third, the experimental nature of the approach allows us to precisely estimate
-the size of effects and compare different theoretical explanations
-simultaneously. Finally, we can also control for confounding, which is a
-potential concern in previous research on vigilantism.
+especially important benefit in researching this topic
+\citep{horiuchi2022does}. Third, the experimental nature of the approach allows
+us to precisely estimate the size of effects and compare different theoretical
+explanations simultaneously. Finally, we can also control for confounding,
+which is a potential concern in previous research on vigilantism.
 
@@
 The attributes and levels are displayed in table \ref{tab:categories}.
+
+In addition to our knowledge of the Brazilian case, we also chose our
+attributes based partly on existing work on crime, vigilantism, and
+extrajudicial violence. From the prison violence literature, we know that the
+relative age differences and the genders of perpetrators and victims affect how
+it is perceived \citep{fleisher2009myth}. We likewise know that certain
+offenses are seen as especially reprehensible \citep{skarbek2014social}, so we
+included such offenses, like molestation, alongside less serious offenses. We
+include race because, in the United States, violent lynchings have often been
+wielded for racist reasons \citep{dray2003hands}. Likewise, we include
+residency because extrajudicial violence is often used against people ``who
+don't belong'' or are ``outsiders'' in some respect. Finally, in honor cultures
+that value retaliatory violence, people believe that victims and the family of
+victims have a special right (and often an obligation) to enact retribution
+\citep{weiner2013rule}.
 
@@
 We report marginal means in our main analysis instead of average marginal
-component effects (AMCEs). \citet{leeper2018subgroup} show that AMCEs can be
+component effects (AMCEs). \citet{leeper2020measuring} show that AMCEs can be
 misleading in subgroup comparisons as model results are sensitive to the choice
@@
 
-Respondents selected male offenders (0.548, SE = 0.003, $p$-value $<$ 0.001) as
-preferred lynching victims more often than female offenders (0.438, SE = 0.004,
-$p$-value $<$ 0.001). We found identical results in our subgroup analyses, in
+Respondents selected male offenders as preferred lynching victims more often
+than female offenders. We found identical results in our subgroup analyses, in
 which we disaggregated our sample according to respondents' gender, income,
@@
 experiment. With regard to the age of the crime perpetrator, respondents
-tolerated the lynching of adults (0.520, SE = 0.005, $p$-value $<$ 0.001) more
-than attacks against teenagers (0.498, SE = 0.005, $p$-value = 0.650) or the
-elderly (0.483, SE = 0.005, $p$-value $<$ 0.001). More precisely, subjects were
-indifferent toward teenagers but reacted positively to lynching of adults and
-negatively to lynching of elderly people.
+tolerated the lynching of adults more than attacks against teenagers or the
+elderly. More precisely, subjects were indifferent toward teenagers but reacted
+positively to lynching of adults and negatively to lynching of elderly people.
 
@@
 with the American experience, respondents favored the lynching of white
-perpetrators (0.512, SE = 0.006, $p$-value = 0.050) the most. Of all the racial
-identities that we included in the experiment, Black people were the least
-likely to be chosen as a more justified lynching victim (0.490, SE = 0.006,
-$p$-value = 0.092), although the 95 percent confidence intervals overlap with
-the remaining categories. The effect is also robust for most subgroups,
-including white respondents. Asian respondents, however, rated fellow Asians as
-their least preferred choice. Taken together, the results provide experimental
+perpetrators the most. Of all the racial identities that we included in the
+experiment, Black people were the least likely to be chosen as a more justified
+lynching victim, although the 95 percent confidence intervals overlap with the
+remaining categories. The effect is also robust for most subgroups, including
+white respondents. Asian respondents, however, rated fellow Asians as their
+least preferred choice. Taken together, the results provide experimental
 evidence that support for lynchings in Brazil does not resemble the typical
@@
 lynching. Subjects were indifferent as to whether the crime perpetrator lives
-in the area (0.498, SE = 0.004, $p$-value = 0.668) or in another neighborhood
-(0.502, SE = 0.004, $p$-value = 0.668). In this sense, it is possible that
+in the area or in another neighborhood. In this sense, it is possible that
 subjects see lynchings not as a means to protect the area in which they live,
@@
 The next attribute is type of offense. Rape was by far the most significant
-attribute in our model (0.719, SE = 0.009, $p$-value $<$ 0.001), followed by
-murder (0.608, SE = 0.006, $p$-value $<$ 0.001) and molestation (0.538, SE =
-0.006, $p$-value $<$ 0.001). It is not surprising that murder and rape were the
-most important offenses to respondents. Overall, we found that respondents do
-not believe that property crimes, such as car theft (0.351, SE = 0.009,
-$p$-value $<$ 0.001) and pickpocketing (0.314, SE = 0.006, $p$-value $<$
-0.001), provide justification for lynching. When we analyzed the data by
-groups, we also saw that poorer respondents, whose household income is less
-than R\$3,000 (US\$650) per month, are more likely to support the lynching of
-individuals who commit a property crime.
+attribute in our model, followed by murder and molestation. It is not
+surprising that murder and rape were the most important offenses to
+respondents. Overall, we found that respondents do not believe that property
+crimes, such as car theft and pickpocketing, provide justification for
+lynching. When we analyzed the data by groups, we also saw that poorer
+respondents, whose household income is less than R\$3,000 (US\$650) per month,
+are more likely to support the lynching of individuals who commit a property
+crime.
 
 For age, we observed that respondents were particularly concerned about
-children as crime victims (0.571, SE = 0.007, $p$-value $<$ 0.001), as this
-attribute is strongly correlated with support for lynchings. Respondents also
-thought lynchings are more justified when the victim is a teenager (0.505, SE =
-0.007, $p$-value = 0.474), an elderly person (0.479, SE = 0.006, $p$-value $<$
-0.001), or an adult (0.464, SE = 0.006, $p$-value $<$ 0.001).
+children as crime victims, as this attribute is strongly correlated with
+support for lynchings. Respondents also thought lynchings are more justified
+when the victim is a teenager, an elderly person, or an adult.
 
 When we analyzed the gender of the crime victim, we found that respondents
-support lynchings more strongly when the victim is a woman or teenage girl
-(0.511, SE = 0.004, $p$-value = 0.002) and less strongly when the lynching
-victim is a man or teenage boy (0.489, SE = 0.004, $p$-value = 0.002). The
-difference here is smaller than when we considered the gender of the crime
-perpetrator, but as in the previous estimation the 95 percent confidence
-intervals of each attribute did not overlap.
+support lynchings more strongly when the victim is a woman or teenage girl and
+less strongly when the lynching victim is a man or teenage boy. The difference
+here is smaller than when we considered the gender of the crime perpetrator,
+but as in the previous estimation the 95 percent confidence intervals of each
+attribute did not overlap.
 
@@
 legitimate perpetrators of lynchings. Respondents considered the family to be
-the most justified in carrying out a lynching (0.534, SE = 0.007, $p$-value $<$
-0.001). Again, the intervals here did not overlap with those of any other
-category. Bystanders (0.505, SE = 0.007, $p$-value = 0.450), gangs (0.502, SE =
-0.007, $p$-value = 0.815), and neighbors (0.492, SE = 0.007, $p$-value = 0.262)
+the most justified in carrying out a lynching. Again, the intervals here did
+not overlap with those of any other category. Bystanders, gangs, and neighbors
 do not increase or decrease respondents attitudes about lynching. If the police
-carry out a lynching, that reduced the perceived justification (0.467, SE =
-0.007, $p$-value $<$ 0.001). In sum, respondents did not believe that lynchings
-should be carried out by the state but did believe they should be used as a
-tool for individual or family retribution.
+carry out a lynching, that reduced the perceived justification. In sum,
+respondents did not believe that lynchings should be carried out by the state
+but did believe they should be used as a tool for individual or family
+retribution. These results are consistent with norms of an honor culture in
+which offenses are seen to tarnish the victim's status and the only way to
+remove the stigma is through self-help efforts in the form of retaliatory
+violence \citep{nisbett2018culture}.
 
@@
 \begin{table}[ht] \centering
-  \caption{Average treatment effects for experiment 3}
-  \label{tab:exp03main}
+  \caption{Average treatment effects for experiment 2}
+  \label{tab:exp02}
 \begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
@@
 
-Table \ref{tab:exp03main} summarizes our main results for this experiment.
-We find that when respondents are reminded of legal punishments associated with lynchings, their support for lynching decreases by about 11 percent.
-This result is consistent with the idea that respondents will support an activity less if they perceive it to be more costly.
-The next treatment group was told the human rights message.
-The result is not statistically significant and indicates that appeals to individual liberties and the rule of law are likely to fall short.
-This finding has practical implications, as many campaigns against violent crimes are conducted by human rights groups, which tend to emphasize this type of message.
-However, participants do not generally believe that offenders do, in fact, have human rights.
-Accordingly, we have little reason to believe that such messaging is effective.
-By contrast, Treatment 1 reminds respondents that perpetrators of lynching potentially face a high personal cost from doing so.
+Table \ref{tab:exp02} summarizes our main results for this experiment. We find
+that when respondents are reminded of legal punishments associated with
+lynchings, their support for lynching decreases by about 11 percent. This
+result is consistent with the idea that respondents will support an activity
+less if they perceive it to be more costly. The next treatment group was told
+the human rights message. The result is not statistically significant and
+indicates that appeals to individual liberties and the rule of law are likely
+to fall short. This finding has practical implications, as many campaigns
+against violent crimes are conducted by human rights groups, which tend to
+emphasize this type of message. However, participants do not generally believe
+that offenders do, in fact, have human rights. Accordingly, we have little
+reason to believe that such messaging is effective. By contrast, Treatment 1
+reminds respondents that perpetrators of lynching potentially face a high
+personal cost from doing so.
 
-Our last treatment, which raises the possibility of sparking vendettas, has a large, negative effect on support for lynchings.
-Mentioning that lynchings trigger cycles of violence has a negative effect of about 8 percent when compared with the control group.
-While we expected that the coefficient for this treatment condition would be larger than that for the treatment on legal punishments, the means of both groups are not statistically different from each other ($t$ = -0.729, $p$-value = 0.466, 95\% CI: [-4.994; 2.288]).
-As with the other experiments, the results remain stable when we conduct subgroup analyses.
+Our last treatment, which raises the possibility of sparking vendettas, has a
+large, negative effect on support for lynchings. Mentioning that lynchings
+trigger cycles of violence has a negative effect of about 8 percent when
+compared with the control group. While we expected that the coefficient for
+this treatment condition would be larger than that for the treatment on legal
+punishments, the means of both groups are not statistically different from each
+other. As with the other experiments, the results remain stable when we conduct
+subgroup analyses.
 
@@
 Brazil provides a telling example of how extrajudicial violence can escalate
-and pose a serious threat to the stability of government institutions. From
-2011 to 2015, the country registered about 2,500 lynching episodes, and 173
-people were killed by angry mobs in 2015 alone---nearly one execution every two
-days \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
-Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
-Brazil for more than thirty years, these figures are not only the highest in
-the country's history, but among the highest in the world. The people who
-participate in lynchings are typically young men, but they also sometimes
-include teenage women and girls, elderly women, and even members of the local
-police \citep{moura2017linchamentos}. In this respect, interventions that
-reduce popular support for extrajudicial violence can have a substantial impact
-on citizen welfare and potentially increase state legitimacy in young
-democracies.
+and pose a serious threat to the stability of government institutions.
 
-Our results show that the characteristics of a lynching significantly effect
+%%%%DELETE OR REVISE In this respect, interventions that reduce popular support for extrajudicial violence can have a substantial impact on citizen welfare and potentially increase state legitimacy in young democracies.
+
+Our results show that the characteristics of a lynching significantly affect
 people's support for it, especially when the crimes are heinous or committed

### 2022-11-29 response-reviewers/response-reviewers.tex
add paragraph to conclusion

\documentclass[a4paper,12pt]{article}
\usepackage{anysize}
\usepackage[T1]{fontenc}
\usepackage[stable]{footmisc}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=0.825]{FiraMono}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{mathtools}
\usepackage[authoryear]{natbib}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{babelbib}
\usepackage{graphicx}
\usepackage{booktabs, makecell, longtable}
\usepackage{dcolumn}
\usepackage{float}
\usepackage[caption = false]{subfig}
\floatplacement{figure}{H}
\usepackage{caption}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcomman{\elandscape}{\end{landscape}}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{markdown}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\setcitestyle{aysep={}}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
   {\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\usepackage{hyperref}

\hypersetup{
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true}

\newcommand*\justify{%
  \fontdimen2\font=0.4em% interword space
  \fontdimen3\font=0.2em% interword stretch
  \fontdimen4\font=0.1em% interword shrink
  \fontdimen7\font=0.1em% extra space
  \hyphenchar\font=`\-% allowing hyphenation
}

\begin{document}

\doublespacing

\noindent \textbf{Research \& Politics}

\noindent \today

\vspace{.5cm}

\noindent Dear Editor and Reviewers,

\vspace{.5cm}

We would like to thank you for the opportunity to revise our manuscript,
``Vigilantism and Institutions: Understanding Attitudes toward Lynching in
Brazil'' (Ms. No. RAP-22-0164). Following the comments and suggestions of the
editors and reviewers, we have thoroughly revised our research letter and we
believe it has improved significantly as a result.

We were especially committed to increasing the appeal of our research note to BJPolS's readership, emphasising the dialogue between our findings and those in the literature. We did this by extensively editing the Introduction and Discussion sections. We expand the literature review and add more references to the original theory as recommended by the editor and Reviewers 1 \& 2. We detail how the latest papers on the relationship between legislative size and public expenditure frame that debate and attempt to resolve it. We have also moved the references to our methodology from the Introduction to the Data and Methods section, as per the suggestion of Reviewer 2, to dedicate more space to theoretical issues. In the Discussion, having presented our results, we further specify the reasons why we believe past results have been highly heterogeneous. Lastly, we recommend possible avenues for further research that follow from our analyses, such as testing combinations of variables that we did not find in our search or measuring how domestic factors like gerrymandering or party effects influence the dynamics of the "law of $1/n$".

Following Reviewer 3's proposition, we conducted two new paper searches to broaden the scope of our previous query. In the first search, we ran a keyword-based query on Google Search to look for articles that discuss the "law of $1/n$" but do not cite \citet{weingast1981political}. We also checked the personal websites of the authors we had previously included in the paper in order to find unpublished research on our topic of interest. We thank Reviewer 3 for their insightful comment, as we included 2 new articles in our analysis as a result.

Throughout the paper, we clarify all of Reviewer 1 \& 2's questions about our independent variables, coding procedures, and modelling techniques. We have also changed our model specifications to more properly account for effect size independence, following Reviewer 2's critique. We identified the sources of dependence in our sample and adopted multilevel random effects models in all of our estimations. We are extremely appreciative of this recommendation, as it is now an important methodological strength in our paper.

When it comes to our results, we follow Reviewer 2's insight on how to interpret the evolution of research designs, toning down the idea that most of the variation in our estimates derives from methodological choices. We also present new results by adding a moderator for unicameralism, following Reviewer 1's reference.

Below we discuss these changes in further detail, as well as the other
improvements we have done to the paper in response to the editors' and
reviewers' comments. We are pleased with the outcome and hope to have satisfied
all of your concerns. Again, we thank the editor for the opportunity to revise
our manuscript, and the reviewers for their immensely valuable comments.

\vspace{.5cm}

\noindent Yours Truly,

\vspace{.5cm}

\noindent The Authors

\section*{Editor Comments and Responses}

\textbf{1)} The editor writes: ``The Reviewers provide helpful comments. Specifically, Reviewer 1 suggests that you re-frame the paper to acknowledge that the inconsistency of the results has long been understood in the literature, and that the search for explanations of that inconsistency is an important driver of that literature. Please give further thought to the key contribution of your meta-analysis against that background, as Reviewers 1 and 2 suggest, and discuss the theoretical contribution and its meaning more fully in the introduction and conclusion.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have completely restructured the Introduction and Discussion sections to establish a better dialogue with the literature. We better contextualise our motivation to write this piece and more concretely demonstrate the implications of our results regarding previous findings. To illustrate the theory, we have provided the reader with a brief summary of the "law of $1/n$" model in Section A of the Supplementary Materials. We have also expanded the literature review in the Introduction. In the Discussion section, our hypotheses on the sources of heterogeneity are more clearly connected with the themes previously explored in the literature.

    We refer to these changes more specifically in our responses to Reviewer 1 in page 3, and to Reviewer 2 in page 7 of this document.
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} The editor writes: ``All Reviewers also provide detailed comments on your empirical analysis. Reviewer 3 has useful suggestions regarding your sampling strategy; Reviewers 1 and 2 focus on your dependent and explanatory variable. Please address these comments.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have followed Reviewer 3's suggestion and nearly tripled the amount of records we assessed for eligibility, seeking articles within the distributive politics literature through broader criteria. Thanks to this review, we added two new articles to our meta-analysis.

    The main methodological adaptation we made was in response to Reviewer 2's extremely valuable comment on the need for using multilevel models. We are extremely grateful for this comment, and we thank Reviewer 2 for pointing out this crucial aspect in our empirical strategy.

    We also added a series of clarifications regarding our coding procedures, specially regarding the independent variables. We specify where these explanations can be found in the main article along this letter, according to each of the specific suggestions the Reviewers made.
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} The editor writes: ``Reviewers 1 and 2 also ask you to make better use of the Supplementary Materials (SI). In your main text, please refer to specific sections in the SI, please explain your results in the SI, and leave out the R code, which should be made publicly available separately from the SI with the replication materials.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have made the changes requested by Reviewers 1 and 2 accordingly. The ``Supplementary Materials'' we refer to hereinafter contain only a discussion of the \citet{weingast1981political} and \citet{primo2008distributive} models in Section A, a detailed description of the search and eligibility procedures for study inclusion (Sections B and C), a guide to how we built the meta-analysis dataset from our pool of diverse coefficients (Section D), a presentation of the descriptive statistics of the included articles (Sections E and F), and the results for the binomials tests, meta-analyses, and meta-regressions (Sections G through K). The R scripts we previously presented along with this information are now in a different document referred to as ``Replication Materials''. For the purpose of reproducibility, the full datasets listing all the records we assessed and the stage and reason for each exclusion are also available online for consultation in the article's GitHub repository. 
\end{quote}

\vspace{.3cm}

We would like to thank the editors for their helpful comments and suggestions.

\section*{Reviewer 1 Comments and Responses}

\noindent \textbf{1)} Reviewer 1 writes: ``It has long been known that the empirical results are inconsistent in this literature. To wit, a major theme in the empirical literature -- at least for the last decade or so -- has been to try to explain the previously inconsistent findings, especially between upper and lower chambers; papers like Chen and Malhotra, Crowley, Lee, etc. take it as a main motivation to explain these inconsistencies. There have also been theoretical contributions in this vein, such as Pecorino's 2018 piece in Public Choice. In other words, these various approaches the authors note have been evolving not just as new techniques have been made available, but precisely *because* of the inconsistency in the findings the authors are discussing here. While I understand this paper is endeavoring to be concise, some service should be paid to a fuller discussion of the trends in the literature--noting that the previous authors in this literature were well aware of its inconsistent results--beyond just changes in methodology.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Reviewer 1 makes an excellent point. We agree that we had not properly expressed how more recent works identified and searched for strategies that solved the discrepancies in the literature. We have changed the framing of the paper so it is clear that scholars were well aware of the heterogeneity, and that our contribution in this sense is to quantitatively find the sources of such variation. While this idea permeates the Introduction section, here is one sentence we added that specifically addresses this point (p.2):

    ``\textit{In this respect, scholars have long been aware of the theoretical and empirical limitations of the ``law of $1/n$'', and the proliferation of new studies reflect a conscious attempt to assess the robustness of the theory.}''

    As mentioned above, we have also expanded the literature review from paragraphs 1 through 3 in the Introduction section (p.2) as follows:

    ``\textit{Early studies that empirically tested the "law of $1/n$", as the theory is currently known, indeed found a positive correlation between the number of legislature seats and different measures of government spending, although these first results were mainly based on US state legislatures and the effect was often limited to one house (e.g., \citet{baqir2002districting, gilligan1995deviations, gilligan2001fiscal}).}

    \textit{Later research, however, has questioned the validity of the "law of $1/n$". \citet{primo2008distributive} affirm that, due to spatial spillovers, a collection of small districts can supply public goods more efficiently than the central government. The authors conclude that a "reverse law of $1/n$" may hold, wherein a higher number of legislators in small constituencies decrease the overall public spending. Similarly, \citet{primo2006stop} and \citet{chen2007law} find that lower and upper chambers may have mixed effects on government spending, while \citet{petterssonlidbom2012size} argues that the impact of larger chamber sizes is negative when using data from Finland and Sweden.}

    \textit{Since many empirical tests of the "law of $1/n$" have produced conflicting results, scholars have expanded this research agenda and closely investigated how institutional factors condition the original formulation of the theory. For instance, authors such as \citet{crowley2019law} and \citet{pecorino2018supermajority} accurately point out that collective action problems have been overlooked in the literature, and recent findings indicate that bicameralism \citep{maldonado2013legislatures}, intergovernmental competition \citep{crowley2015local}, redistricting \citep{lee2018court}, and party ideology \citep{bjedov2014impact} strongly influence the relationship between seats and spending. Moreover, the literature has increasingly applied causal inference methods to estimate the effect of the "law of $1/n$", and in contrast to previous studies using panel data, regression discontinuity designs generally indicate that more legislators decrease public expenditures \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 1 writes: ``In the empirical exercise, the authors routinely reference separating the empirical studies they use as their sample based on the "main explanatory variable." For instance, in section 3.3. This strikes me as problematic (or at least poorly explained) because it is typically standard in this literature (at least for those studies on bicameral legislatures such as cross-state studies on the US) to include both the upper and lower chamber size variables. So it is unclear to me how such a study would have a "main explanatory variable." This needs to be more clearly explained.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that our explanations regarding the choice and use of the variables of interest were insufficient. When studies use evidence from bicameral legislatures, we included the coefficients for both upper and lower chamber size in all our samples. This is the case for thirteen articles in our analysis. Using data from both chambers is one of the reasons why our restricted sample contains 45 coefficients for a total of 30 papers. We added clarifications regarding our choice of independent variable in the first paragraph of the Data and Methods section, on page four.

    A specific comment on variable choice in bicameral systems is in footnote \#2. It reads: ``\textit{Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as main explanatory variables.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 1 writes: ``In Table 3, the authors also only present N and log(N) results; K is not indicated—was it an excluded group? If so, this needs to be made clear.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We acknowledge that Table 3 did not display the reference categories clearly enough. We have highlighted the notes below the table so the reader can have a more straightforward interpretation of the estimates. They present the reference category for each variable and moderator in the meta-regressions. For the independent variable, the reference category was upper chamber size, which is why this category was omitted in the table.
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 1 writes: ``Further, it is not clear to the reader why the authors use lower chamber size, upper chamber size, and then a log of only lower chamber size. Are there no studies which employ a log of upper chamber size?''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Following the reviewer's remark, we double checked our study sample and confirm that the natural logarithm of upper chamber size is not present in any papers. As mentioned above, we included clarifications about our choice of independent variable in the first paragraph of the Data and Methods section (p.4). Footnote \#2 reads: ``\textit{We did not find any article that used the natural logarithm of upper chamber size in their models.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 1 writes: ``How did the authors handle those studies in this literature which focused on unicameral legislatures? Were these grouped in with the "lower chamber" studies? Were they excluded? This is not clearly explained in the paper. In general, the results on unicameral legislatures tend to support the law of $1/n$.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As noted above, we agree that important details about data collection and coding were missing. Unicameral legislature sizes were coded under lower chamber size or natural logarithm of lower chamber size. Many studies consider lower chambers and unicameral legislatures as analogous institutions for quantitative purposes. An example is one of the papers in our meta-analysis \citep{stein1998institutional}. We expand the explanations surrounding the treatment of independent variables in the first paragraph of the Data and Methods section. A specific clarification on unicameral legislatures is in Footnote \#2. It reads: ``\textit{There are a few important nuances concerning coding of these variables. Unicameralism, for example, is captured both by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).}''

    Upon reading this comment, we also acknowledged that although the differences between upper and lower chambers were so relevant to the discussion, we had not given enough attention to unicameral legislatures. Inspired by this remark, we coded a new moderator for institutional design. The categories were `Unicameral', for coefficients from purely unicameral systems; `Bicameral', for coefficients from purely bicameral systems; and `Mixed', for coefficients from studies that used samples which contained a mix of unicameral and bicameral systems. Examples of the latter were all the papers that used country-level data. Our findings confirm the Reviewer's insight: in the meta-regressions that aggregate all coefficients, unicameralism is a significant positive predictor of the $1/n$ effect.

    Since this is an important finding, we discuss the Institutional Design moderator in all sections. The Data and Methods section presents under which category each article fits in Table 1, and its descriptive statistics in Table 2. In the first paragraph of the Meta-Regressions subsection, we explain how the variable is coded (p.12), and briefly interpret its results in the last paragraph (p.14).

    Because we found such interesting results in the meta-regressions, we decided to perform subgroup analyses with heterogeneous effects for unicameralism as well. The results can be found in section H.13 in the Supplementary Materials. We undertook tests similar to those we present in the article for Estimation Methods (p.12). Using the lower chamber size $\times$ per capita expenditure combination, we aggregated the data in two groups: one just for unicameral systems, and the other for all institutional designs excluding unicameralism. For unicameral systems, the estimates were mostly positive in the restricted sample, but none was statistically significant. Results were overwhelmingly positive for the extended sample, where they almost reached statistical significance. These results are in line with what we found in the rest of the paper, however they do not help us reach more robust conclusions on the effect of institutional design on the ``law of $1/n$''.
\end{quote}

\vspace{.3cm}

\noindent \textbf{6)} Reviewer 1 writes: ``The Supplementary Materials is full of content that is of very little use to the reader; even as an online appendix, there is no need to include roughly 100 pages of code from a statistical software. I believe the most relevant Supplementary Materials is the detailed discussion on selection.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that the R script is useful to a limited amount of scholars, and not to the vast majority of readers. As mentioned above, we have separated the Supplementary Materials in two parts. The first follows Reviewer 1's recommendation, including a discussion of the theory, the study selection procedures, a description of how we coded the data in detail, and analysis results. The second gathers all scripts we use in each step of the study, and is aimed at those wishing to replicate our work or to produce new meta-analyses in the social sciences.
\end{quote}

\vspace{.3cm}

We would like to thank Reviewer 1 for her/his helpful comments and suggestions.

\section*{Reviewer 2 Comments and Responses}

\textbf{Major issues:}

\noindent \textbf{1)} Reviewer 2 writes: ``I believe the main framing of this manuscript should focus on explaining the interesting variation between studies (i.e., when do the law of 1/n or the reverse law are expected). From this perspective, the introduction part of the paper currently quickly jumps to the technicalities of the meta-analysis (e.g., a description of the two models used, measurement of DV etc.; see p. 2). These technical descriptions should appear in the method section. Instead, it would be more helpful to see some theoretical discussion on the reasons the literature proposes for the heterogeneity found in this study - even in a concise manner.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that the technical discussion in the introductory section was misplaced. We have restructured the Introduction to fit Reviewer 1 and Reviewer 2's recommendations. As displayed above (p.4 of this letter), we expanded the literature review to capture the main points in the debate that dialogue with our findings. We have also made our critiques of the scholarship more clear, explicitly pointing to which we thought were the sources of heterogeneity in previous work in the Discussion section. Moreover, in Section A of the Supplementary Materials, we added a brief discussion of the theory developed by \citet{weingast1981political}, and also the "reverse law of $1/n$" by \citet{primo2008distributive}. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2.1)} Reviewer 2 writes: ``It is currently difficult to understand why many studies included in the meta-analysis have several effect sizes. Is it because of using different dependent? Some examples would help the readers.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    In our restricted sample, a study can supply more than one coefficient if it employs more than one dependent or independent variable. Studies that analyse bicameral systems use upper chamber size and lower chamber size as independent variables, and thus supply two coefficients each. These studies are \citet{chen2007law, crowley2019law, gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court, maldonado2013legislatures, ricciuti2003trading, ricciuti2004legislatures, primo2006stop}. The paper by \citet{bradbury2001legislative} alone supplies four coefficients, as they use two independent variables (upper chamber size and lower chamber size) and two dependent variables (expenditure as share of the GDP and per capita expenditure). Two other papers \citep{bjedov2014impact, erler2007termlimits} also use both of these dependent variables and only one independent (lower chamber size), supplying two coefficients each.

    To the extended sample, each paper can supply several coefficients because studies usually submit their data to a series of models where they include or exclude different controls or interaction terms, or perform slightly different tests. For instance, we drew twelve coefficients from \citet{fiorino2007legislature}. From a single table (Table 4) in their paper, we extracted four coefficients for the same variable combination (lower chamber size and per capita expenditure).
\end{quote}

\vspace{.3cm}

\noindent \textbf{2.2)} Reviewer 2 writes: ``Moreover, and more substantially, I am not sure how including studies with several effect sizes in a separate model (p. 7) can solve the violation of non-independent effect sizes, required in meta-analyses. The authors do not report the statistical models they used for solving these violations (I did not find it in the appendix either). There are various ways to address such issues, such as robust variance estimation (see Hedges et al., 2010) or using multi-level meta-analyses (see e.g. application in Matthes et al., 2019).

Furthermore, since there were several studies focusing on the same country (e.g., 14 studies investigating the US), did they use the same samples in their analysis? If so, doesn't it violate the non-independence assumption on its own (as they use the same district ``sample'')? If that is the case, the authors should treat this effect size dependency also for the first model (with the 42 main coefficients). These issues are very important since some of the authors' findings are based only on the ``extended models'' in Table 3 (i.e., those including 142 effect sizes, even from studies reporting several effect sizes related to the same sample). If these findings are based on biased estimates, we should be a lot more cautious interpreting them.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As Reviewer 2 correctly notes, the coefficient extraction procedure we just presented in the previous response is the main source of effect size dependence in our extended sample analyses. An additional source of dependence is the fact that many studies analyse the same cases, sometimes even using the same data sources. The Reviewer is also correct to point out that separating the effect sizes into a restricted and an extended sample does not properly address the dependence of the coefficients within the extended sample. We followed the Reviewer's suggestion rigorously by employing multilevel random effect models \citep{cheung2014modeling, matthes2019meta} in all of our estimations. A thorough explanation of how we identified, grouped the studies that constitute the new levels, and coded them can be found in section H.1 of the Supplementary Materials. We describe the procedure more succinctly in the Data and Methods section in the main paper (last paragraph on page 7):

    ``\textit{We add two extra levels to the regular meta-analysis, one including a unique publication ID for each paper, and another indicating the data source used in the original study. By adding these two levels, we account for within- and between-study variation, thus removing these sources of effect size dependency and improving the accuracy of the results.}''

    We believe the inclusion of additional levels reduces the bias previously present in our analyses, producing far more reliable estimates. We are highly appreciative of this comment, as it has ignited major changes in our manuscript, severely improving the robustness of our results. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 2 writes: ``How did the authors convert the original studies' coefficients into standardized effect sizes? It is important to mention how the authors render these coefficients comparable due to the various research designs included in the meta-analysis.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have included a paragraph in the Data and Methods section (p.7) to clarify the coefficient standardisation procedure. It reads:

    ``\textit{We use Hedges' $g$ to calculate effect sizes in our meta-analysis \citep{hedges1981distribution}. While there are other methods to standardise coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in small sample sizes and is considered more robust than measures such as Cohen's $d$ \citep{lakens2013calculating}. We estimate the Standardised Mean Difference (SMD), which represents the effect size in each study relative to the variability observed in that study, by extracting the coefficients and the standard errors from all articles included in our sample and converting them to Hedges' $g$. In cases where authors did not report the standard errors for their estimates, we computed them using the t-statistic presented in the original tables.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 2 writes: ``our results suggest that study coefficients are highly sensitive to research design choices'' (p. 13) - this is a rather bold statement (``highly sensitive'') since most differences between study designs are nonsignificant (on Table 3). I would tone down this argument much more and address its limitations in the discussion.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have adapted the language when referring to the effects of estimation methods according to the Reviewer's suggestions throughout the paper. For instance, paragraph 6 of the Introduction (p.3) reads:

    ``\textit{However, when we look only at articles that employ regression discontinuity designs, we see that all four papers included in our sample suggest that a higher number of legislators leads to lower public spending \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}. In this regard, it is possible that methodological choices partially explain the divergent results observed in the literature, as studies that use causal inference methods consistently point to the same direction. One limitation of this finding is that these studies only test the impact of lower house size on the natural logarithm of expenditure per capita, thus it remains unclear whether the results hold with other variables.}''

    The Results and Discussion sections present these findings more objectively. On page 14, we report the following conclusion regarding estimation methods: ``\textit{The meta-regressions confirm that modern estimation methods such as RDDs and panel/fixed-effects models decrease effects more frequently than OLS regressions.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 2 writes: ``I encourage the authors to elaborate more on the implications of their results rather than to simply describe them, especially in the context of their moderators (electoral systems and possibly, the research design - but see my above concerns regarding the results related to study designs). Although the format should be concise, such a discussion will improve the readers' understanding of the main findings much more (especially non-expert readers). For example, the seemingly "methodological" explanation of research design as a moderator has substantial implications. If that is the case, to what extent can we lean on earlier studies that did not use causal inference?''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Following Reviewer 2's recommendations, we have more appropriately framed the paper so that we discuss the institutional moderators and their relationship to the theory across the entire piece. Since we changed our model specifications and added a new moderator, our Results section was also significantly altered. We reduced the Meta-Analysis subsection (3.2) and expanded the Meta-Regressions subsection (3.3) to account for the most relevant and auspicious findings. In this sense, in paragraph 2 of subsection 3.3, we explain to the reader how she should interpret the meta-regression results. We believe this makes our arguments about the meta-regression results more compelling. We also added more substantive insights to accompany the description of meta-regression results in each paragraph of section 3.3.

    We present and partly interpret our results in the Introduction section, reporting back to elements from the literature and to the theory. The last paragraph in the Introduction (p.3) reads:

    ``\textit{The meta-regressions provide additional evidence that our study sample is highly heterogeneous and that effect sizes differ substantially according to study specifications. When using an extended sample of 162 coefficients, we find that unicameralism is associated with higher public spending, as predicted by the ``law of $1/n$''. Since most unicameral legislatures in our sample are local governments (municipalities or districts), this result supports the predictions of \citet{weingast1981political}. Moreover, our meta-regressions indicate that larger upper chambers spend more in terms of per capita expenditure than lower chambers, a result that also appears in the binomial tests. Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original definition of the law. Finally, meta-regression results confirm that regression discontinuity designs reduce public spending estimates.}''

    The Discussion section has also increased both in size and scope. Now, we more aptly establish the dialogue between our electoral system findings and the original theory and literature. For instance, in page 15, the following reads:

    ``\textit{While we believe that moving beyond the majoritarian districts framework could produce valuable insights, institutional features that are central to the theory cannot be overrun. For example, proportional representation (PR) electoral systems allow candidates whose constituents are spread across large territories to provide diffused public goods and win elections. However, geographically-targeted service provision is at the very core of the legislative behaviour that produces the "law of $1/n$". Thus, scholars should consider the possible implications of these micro-level dynamics when applying the "law of $1/n$" logic to different settings.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{More minor comments:}

\vspace{.3cm}

\noindent \textbf{1)} Reviewer 2 writes: ``Table 1 - it will be clearer to separate the notes at the bottom of the table into separate columns. For instance, note \#1 will explain the abbreviations of the Journal column note \#2 will refer to the Country column. Otherwise, the reader has to manually look for a given abbreviation out of the rather long list.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree this can be an unnecessary inconvenience to the reader. We have changed the notes in Table 1 according to the Reviewer's specifications. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 2 writes: ``Also regarding Table 1, I believe it will be more convenient to simply write the authors and the year of publication in the first column (e.g., "Stein et al., 1998") while keeping the table order as it is (according to the year of publication) - rather than splitting them into two columns. I am also not sure whether the title of the paper really helps the readers or simply confuses them (it makes the table less elegant in my opinion). I would delete the title (if a reader wishes to see the full reference, she can look it in the bibliography). In contrast, it will be more beneficial to mention inside the table the DVs used in each study (as currently explained in the body text; p. 6).''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have made these alterations to Table 1 accordingly. We also added a column for the new Institutional Design moderator.
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 2 writes: ``The use of $n$ and $k$ as signifiers of the independent variables is a bit confusing throughout the paper since in the meta-analyses domain, they usually signify the number of effect sizes ($k$) and the number of respondents per study ($n$). More broadly, it is even more confusing when discussing Table 3 (the reader has to remember what $n$ and $k$ represent, instead of simply writing the meanings) or when interpreting its results in the discussion part.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that adding labels to variables is an unnecessary inconvenience to the reader. All references to the independent variables now translate their full meaning.
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 2 writes: ``I appreciate the authors' elaborated appendix, but the readers might get a bit lost without specific references to the sub-sections in it throughout the main paper: for example, not just referring to the Supplementary Materials in general, but to the specific section in it. Moreover, the authors should consider leaving out the R code from the online appendix, and simply anonymously upload it to an external open science source. For people who are not experts in R (and perhaps also for those who are), the combination of code and text can be a bit confusing.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As noted above, we agree that only a handful of scholars would be interested in R scripts, which get in the way of most readers. We have split the Supplementary Materials into two documents. The one we refer to as the ``Supplementary Materials'' includes a discussion of the theory, the study selection procedures, a description of how we treated the data in detail, and analysis results. The other collects all the R code we wrote for each stage of data collection and analysis. We recommend the latter is used by those wishing to replicate our work and strongly encourage peers to use it and produce new meta-analyses in the social sciences.
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 2 writes: ``To facilitate interpretation of Figure 1, it would be more convenient to number each plot, and refer to it in the body text (pp. 10-11).''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    All plots in Figures 1 and 2 are now individually numbered, and referred to in the body text.
\end{quote}

We would like to thank Reviewer 2 for her/his helpful comments and suggestions.

\section*{Reviewer 3 Comments and Responses}

\noindent \textbf{1)} Reviewer 3 writes: ``First, I am concerned about the first criterion for inclusion in the meta-analysis. Studies could only be included if they cited the Weingast et al. (1981) study. While I don't doubt that this work is foundational to the distributive politics literature, it is an unnecessary restriction. Are there any studies that fit the other two inclusion criteria but do NOT cite Weingast? Maybe there aren't any, but if there are, they should be included since they are still just as relevant to the question at hand. The second inclusion criterion is the most important: a study that quantitatively analyzes the variables of interest. This of course makes the literature search more difficult, but also more comprehensive, which is a main benefit of good meta-analyses.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    The concern Reviewer 3 expresses is one we share. We address this comment by conducing a second round of record collection. We increased our breadth by using a search string with key terms on Google Scholar. We meant to capture all articles that approached the relationship between legislature size and public spending. The search string we used is the following:

    \texttt{\justify ("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")}

    We fuzzy matched the resulting database with the one we had originally analysed to remove all entries we had already covered. As part of this eligibility analysis, we assessed an additional 3,042 records. The exclusion criteria and procedures were the exact same as those performed in the first round (for the original manuscript the Reviewers and Editors read). They are fully detailed in Sections B and C of the Supplementary Materials. The full dataset of excluded records is available for online consultation in the article's GitHub repository.

    Resulting from this second round of surveying the literature, we found two articles that satisfied all the criteria. They were thus included in our analysis. The new papers are \citet{coate2011government} and \citet{debenedetto2018effect}. We thank Reviewer 3 for this comment, as it has effectively made our survey more comprehensive. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 3 writes: ``Second, another main benefit of meta-analyses is to assess the possibility of publication bias. Studies are often more likely to be published if they find statistically significant effects in the direction that is expected, but a comprehensive search of ongoing studies allows meta-analysts to check this. In the current sample, only 4 papers are unpublished, but I also wonder if this is due to the restricted inclusion criteria. For example, if one uses the Google Scholar feature to find articles citing Weingast et al, that would only pick up papers that are already published in a journal or otherwise online, but it may miss any working papers that are not shared publicly. A more comprehensive search may result in more unpublished studies. Either way, can the authors include some sort of formal tests or visualizations for publication bias, such as funnel plots? I think if these two revisions could be made this paper would make a strong contribution.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We understand the Reviewer's concern with publication bias, and we accept both of her/his suggestions in this comment. First, so as not to miss any papers that have not been circulated as Working Papers, we seek after those that have been shared as ongoing projects. We looked into the personal webpages of the scholars who wrote all of the papers in our original sample of studies. In their personal platforms, we scouted for pieces of research about distributive politics. We targeted specifically those that had not been uploaded to large repositories and open archives such as SocArXiv, as those tend to appear in Google Scholar searches. We gathered 15 pieces of work with titles potentially related to our research topic and submitted them to the eligibility criteria. None of these papers were included in the final sample. This procedure is also explained in Section B of the Supplementary Materials, and a dataset displaying all records assessed and their reason for exclusion is available for online consultation as well.

    Attending to the Reviewer's second request, we add \citet{egger1997bias} funnel plots to assess publication bias in all of our meta-analyses. Funnel plots display the possibility of having a file-drawer effect, meaning they can indicate whether null results are under-represented in our sample or not. The funnel plots are available in the Supplementary Materials below the forest plot for each variable combination in the restricted and in the extended samples (Sections H and I). All but one of our \citet{egger1997bias} tests reject the hypothesis of publication bias.
\end{quote}

We would like to thank Reviewer 3 for her/his helpful comments and suggestions.

\newpage
\bibliography{references.bib}
\bibliographystyle{apalike}

\end{document}d

### 2022-11-29 appendix/appendix.Rmd
add paragraph to conclusion

@@
 author: 
+  - Danilo Freire[^danilo]
+  - David Skarbek[^david]
+date: \today
 fontfamily: libertine
@@
 bibliography: ../article/references.bib
-biblio-style: ../article/chicago-ff.bst
+biblio-style: apalike
 output:
@@
 
+[^danilo]: School of Social and Political Sciences, University of Lincoln,
+<dfreire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
+[^david]: Department of Political Science, Brown University,
+<david_skarbek@brown.edu>, <http://davidskarbek.com>.
+
 \appendix
@@
 
-This appendix contains the `R` code required to replicate the results we
-present in "_Vigilantism and Institutions: Understanding Attitudes towards
-Lynching in Brazil_". This file also includes the descriptive statistics of our
-sample, the average marginal component effects (AMCEs) for our conjoint
-experiment, and additional subgroup analyses for all three experiments.
+This appendix contains the `R` code required to replicate the results we present
+in "_Vigilantism and Institutions: Understanding Attitudes towards Lynching in
+Brazil_". This file also includes the descriptive statistics of our sample, the
+average marginal component effects (AMCEs) for our conjoint experiment, and
+additional subgroup analyses for the two experiments included in the main
+article.
 
@@
                                    "de r$ 5.001 a r$ 10.000"  = "From R$5,001 to R$10,000"),
-         household_income = fct_relevel(household_income, "Up to R$1,000",
+         household_income = fct_relevel(household_income,
+                                        "Up to R$1,000",
                                         "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
@@
 The age distribution of our sample is shown below. The median age of the survey
-respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which
-indicates that our sample is older than the Brazilian population (median age $=
-33.4$ years old) [@ciafactbook2020].
+respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which indicates
+that our sample is older than the Brazilian population (median age $= 33.4$
+years old).
 
@@
 The next demographic variable we show here is race. According to the [Brazilian
-Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
+Census
+Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
 42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4%
-as Blacks, and 1,1% as Asians or Indigenous. As we see below, our sample
-includes more Whites and fewer individuals who identify as Mixed Race. The
-number of Blacks roughly coincide with the population statistics.
+as Blacks, and 1.1% as Asians or Indigenous. As we see below, our sample
+includes more Whites and fewer Mixed-Race individuals. The number of Blacks
+roughly coincide with their actual population share.
 
@@
 In our first experiment, we present five pairs of criminal profiles to
-respondents. Each profile consists of eight attributes: 1) gender of the crime
+respondents. Each profile contains eight attributes: 1) gender of the crime
 perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
@@
 Age of crime victim & Child; teenager; adult; elderly\\ [4pt]
-Lynching perpetrators & Bystanders; neighbours; family of the victim; gangs; police \\
+Lynching perpetrators & Bystanders; neighbors; family of the victim; gangs; police \\
 \Xhline{2\arrayrulewidth}
@@
 
-Respondents indicated which profile they preferred for extrajudicial
-punishment. Prior to the experiments, they had read the following prompt:
+Respondents indicated which profile they preferred for extrajudicial punishment.
+Prior to selecting the profiles, respondents were asked to read the following prompt:
 
@@
 Next, we divide our data according to respondents' level of education. As the
-number of interviewees with primary or secondary education is low, we merge
-them into a single category, while the other levels (high school, college, and
-graduate school) remain the same as in our questionnaire.
+number of interviewees with primary or secondary education is low, we merge them
+into a single category, while the other levels (high school, college, and
+graduate school) remain the same as in our questionnaire. While most results are
+similar across all model specifications, we find that respondents with a high
+school degree tend to punish Blacks more severely, but participants with a
+college degree believe that White criminals should be punished more harshly
+instead. The finding deserves attention because it indicates that individuals
+with lower levels of education, who are more likely to be Black and Mixed Race
+in Brazil, perhaps prefer to punish criminals of own race. The same is true for
+Whites, who are usually overrepresented in college education. The differences
+are not statistically significant, however, for respondents with university
+degrees.
 
@@
 above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
-high-income households. We find no considerable differences among them.
+high-income households. We find no considerable differences among them, except
+the fact that respondents with lower incomes are more likely to select profiles
+that include White criminals.
 
@@
 different preferences towards lynchings victim profiles. The results are
-virtually identical for both groups, as one can see below.
+virtually identical for both groups, as one can see below. The only exception is
+that respondents who had not been victimized one year prior to the research are
+slightly more likely to support the lynching of White criminals.
 
@@
 factors. Criminal characteristics, such as age or race, do not seem to be
-particularly relevant, as respondents do not mention them as much. The
-following terms are _nenhum_ (none), _contra_ (against), _acho_ (I think),
-_casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe these
-words correspond to cases where respondents wanted to affirm that they do not
-have any preference regarding the lynching profiles, or that they would rather
-not have chosen any of the alternatives.
+particularly relevant, as respondents do not mention them as much. Then
+respondents mention terms like _nenhum_ (none), _contra_ (against), _acho_ (I
+think), _casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe
+these words correspond to cases where respondents wanted to affirm that they do
+not have any preference regarding the lynching profiles, or that they would
+rather not have chosen any of the alternatives.
 
@@
 about the legal and social consequences of vigilante justice reduces the
-subjects' level of support for such practice.
+subjects' level of support for such practice.[^carryover-effects]
+
+[^carryover-effects]: To prevent eventual carryover effects caused by the
+conjoint, we randomized the order of the conjoint and the information provision
+experiments.
 
@@
 at Brown University and APSA's Principles and Guidance. To facilitate
-transparency, we comment here on a few aspects of our research design. First,
-we worked with the Brown University IRB to reduce the risk of harm for
-participants taking the survey. This included consultation with a cultural
-expert to inform the phrasing of the survey. Second, respondents received
-compensation via Qualtrics, which paid respondents directly after they completed
-the questionnaire. Each subject in Qualtrics' online panel received the
-equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
-not finish the survey will not receive compensation. The compensation is
-appropriate for the participant population. As of August 17, 2020, Brazil's
-monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
-working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
-survey takes about 20 minutes to complete and respondents received 2.5 USD,
-therefore subjects will receive a monetary compensation that is 6 times higher
-than the local minimum wage. Third, we do not see any potential or perceived
-conflicts of interest in carrying out this research. We received a grant of
-$10,000 to conduct this research from the Centre for the Study of Governance &
-Society at King’s College London, which receives support from the Templeton
-Foundation. We are aware of no conflicts of interest from either source. All of
-the code and data will be made publicly available.
+transparency, we comment here on a few aspects of our research design. First, we
+worked with Brown University's IRB to reduce the risk of harm for participants
+taking the survey. This included consultation with a cultural expert to inform
+the phrasing of the survey. Second, respondents received compensation via
+Qualtrics, which paid respondents directly after they completed the
+questionnaire. Each subject in Qualtrics' online panel received the equivalent
+of 2.5 USD in Brazilian Reals (local currency). Respondents who did not finish
+the survey did not receive compensation. The compensation was appropriate for
+the participant population. As of August 17, 2020, Brazil's monthly minimum wage
+was BRL 1039, which amounted to 191 US dollars. Assuming 40 working hours per
+week, the hourly minimum wage equals 1.19 US dollars. Our survey took about 20
+minutes to complete and respondents received 2.5 USD, therefore subjects
+received a monetary compensation that was 6 times higher than the local minimum
+wage. Third, we do not see any potential or perceived conflicts of interest in
+carrying out this research. We received a grant of USD 10,000 to conduct this
+research from the Centre for the Study of Governance & Society at King’s College
+London, which in turn receives support from the Templeton Foundation. We are not
+aware of any conflicts of interest from either source. All of the code and data
+used in this article have already been made publicly available.
 

### 2022-11-29 article/article.tex
add paragraph to conclusion

@@
 
-% Packages I've been using for differen reasons
+% Packages I've been using for different reasons
 \usepackage{hyperref}
@@
 
-\section{Introduction}
+\section*{Introduction}
 \label{sec:introduction}
@@
 zizumbo2017community,smith2019contradictions,cohen2022collective}.} This
-omission is significant not only because violence is pervasive in weak states,
-but it also comes at a great cost \citep{blair2017predicting}.
+omission is significant not only because local violence is pervasive in weak
+states, but also because it often comes at a greater social cost than terrorism
+or civil wars \citep{blair2017predicting}.
 
-One of the most serious forms of extrajudicial violence is lynching, which can
-be defined as ``incidents of physical violence committed by large numbers of
-private citizens against one or more individuals accused of having committed a
-``criminal'' offense, whether or not this violence resulted in the death of the
-victim(s)'' \citep[645]{godoy2004justice}. Although lynchings occur in more
+One of the most serious forms of extrajudicial violence is lynching. Lynching
+can be defined as ``incidents of physical violence committed by large numbers
+of private citizens against one or more individuals accused of having committed
+a ``criminal'' offense, whether or not this violence resulted in the death of
+the victim(s)'' \citep[645]{godoy2004justice}. Although lynchings occur in more
 than one hundred countries in all regions of the world
@@
 episodes have been reported in Guatemala, Mexico, Peru, Venezuela and other
-countries in the region \citep{cruz2019determinants, godoy2004justice,
-barbara2015vigilantes}. From 2011 to 2015, Brazil registered about 2,500
-lynching episodes, and 173 people were killed by angry mobs in 2015
-alone---nearly one execution every two days \citep{barbara2015vigilantes,
-oliveira2016mob}. According to José de Souza Martins
-\citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for
-more than thirty years, these figures are not only the highest in the country's
-history, but among the highest in the world. The people who participate in
-lynchings are typically young men, but they also sometimes include teenage
-women and girls, elderly women, and even members of the local police
-\citep{moura2017linchamentos}.
+countries in the region \citep{barbara2015vigilantes, cruz2019determinants,
+godoy2004justice}. From 2011 to 2015, Brazil registered about 2,500 lynching
+episodes, and 173 people were killed by angry mobs in 2015 alone---nearly one
+execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
+According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who
+has studied lynchings in Brazil for more than thirty years, these figures are
+not only the highest in the country's history, but among the highest in the
+world. The people who participate in lynchings are typically young men, but
+they also sometimes include teenage women and girls, elderly women, and even
+members of the local police \citep{moura2017linchamentos}.
 
@@
 \citep{horiuchi2022does}. Third, the experimental nature of the approach allows
-us to precisely estimate the size of effects and compare different theoretical
+us to precisely estimate effect sizes and compare different theoretical
 explanations simultaneously. Finally, we can also control for confounding,
@@
 
-\section{When Is Lynching Perceived as More Justified?}
+\section*{When Is Lynching Perceived as More Justified?}
 \label{sec:exp01}
@@
 respondents were opposed to lynchings in general but forced to choose. Please
-refer to Section C.5 of the supplementary material for further information.}
+refer to Section C.5 of the Supplementary Material for further information.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%
-\section{How to Reduce Support for Lynchings}
+\section*{How to Reduce Support for Lynchings}
 \label{sec:exp03}
@@
 tested whether reminding respondents about the legal and social consequences of
-vigilante justice reduces subjects' support for it. The experiment included
-three treatment conditions and a control group. In all of them we presented
+vigilante justice reduces subjects' support for it.\footnote{To prevent
+carryover effects caused by previous exposure to the conjoint, we randomized
+the order of experiments in our survey.} The experiment included three
+treatment conditions and a control group. In all of them we presented
 respondents with a short statement affirming that some Brazilians support
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 \label{conclusion}
@@
 and pose a serious threat to the stability of government institutions.
-
-%%%%DELETE OR REVISE In this respect, interventions that reduce popular support for extrajudicial violence can have a substantial impact on citizen welfare and potentially increase state legitimacy in young democracies.
 
@@
 
+These findings have implications that extend well beyond Brazil. In particular,
+our experiments indicate that lynchings have a crucial gendered aspect, which
+has also been documented in other contexts. Using data from 18 Latin American
+countries, \citet{nivette2016institutional} also finds that respondents are
+most likely to support lynchings when the criminal raped a child, and studies
+about lynchings in the American South point out that several episodes resulted
+from accusations of sexual assault \citep{jacquet2013giles, smaangs2020race}.
+We believe that a culture of honor may explain these results. Individuals in
+honor societies view crime as an attack on their personal reputation and, in
+turn, are more likely to take revenge to defend their status and that of people
+perceived as deserving protection, such as women and children
+\citep{nisbett2018culture}. A culture of honor may also explain why Brazilians
+see lynchings carried out by the family of the victim as more justified, as
+well as refraining from using extralegal violence if it can trigger vendettas.
+We expect similar results in societies which share those cultural norms.
+Lastly, the fact that race does not appear to be a major motivation behind
+lynchings also reflects the experience of places like Haiti or Southern Africa,
+where popular violence was mainly driven by other social factors
+\citep{berg2011globalizing, jung2020lynching}. Even in the American South, it
+Whites and Blacks also lynched people of their own race \citep{beck1997race}.
+In this respect, our paper also highlights that lynchings in the Global South
+may be more strongly connected with ideas of ``popular justice'' than racial
+animus \citep{martins2015linchamentos}.
+
 Our work also suggests new avenues for further research. While previous studies
@@
 unclear whether other forms of vigilantism, such as security patrols, property
-damages, or coercive interrogations \citep{bateson2020politics} have similar
-levels of popular support. Finally, lynchings have often been described as a
-response to low state capacity, yet in many cases state agents actively incite
-or engage in vigilante violence themselves \citep{arias2010violent}. Future
-studies may investigate in which circumstances state authorities favor informal
-local control instead of public law enforcement. Unravelling these issues is
-crucial if scholars wish to better understand how and why states and civil
-society decide to use violence.
+damages, or coercive interrogations have similar levels of popular support
+\citep{bateson2020politics}. Finally, lynchings have often been described as a
+response to low state capacity \citep{trevizo2022mexico}, yet in some cases
+state agents actively incite or engage in vigilante violence themselves
+\citep{arias2010violent}. Future studies may investigate in which circumstances
+state authorities favor informal local control instead of public law
+enforcement. Unravelling these issues is crucial if scholars wish to better
+understand how and why states and civil society decide to use violence.
 

### 2022-12-01 response-reviewers/response-reviewers.tex
add response, edit manuscript

@@
 \usepackage{pdflscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcomman{\elandscape}{\end{landscape}}
 \usepackage{ifthen}
 \usepackage{graphicx}
-\usepackage{markdown}
 \usepackage[usenames,dvipsnames]{xcolor}
@@
 Brazil'' (Ms. No. RAP-22-0164). Following the comments and suggestions of the
-editors and reviewers, we have thoroughly revised our research letter and we
-believe it has improved significantly as a result.
+editors and reviewers, we have thoroughly revised our article and we believe it
+has improved significantly as a result.
 
-We were especially committed to increasing the appeal of our research note to BJPolS's readership, emphasising the dialogue between our findings and those in the literature.
-We did this by extensively editing the Introduction and Discussion sections.
-We expand the literature review and add more references to the original theory as recommended by the editor and Reviewers 1 \& 2.
-We detail how the latest papers on the relationship between legislative size and public expenditure frame that debate and attempt to resolve it.
-We have also moved the references to our methodology from the Introduction to the Data and Methods section, as per the suggestion of Reviewer 2, to dedicate more space to theoretical issues.
-In the Discussion, having presented our results, we further specify the reasons why we believe past results have been highly heterogeneous.
-Lastly, we recommend possible avenues for further research that follow from our analyses, such as testing combinations of variables that we did not find in our search or measuring how domestic factors like gerrymandering or party effects influence the dynamics of the "law of $1/n$".
-
-Following Reviewer 3's proposition, we conducted two new paper searches to broaden the scope of our previous query.
-In the first search, we ran a keyword-based query on Google Search to look for articles that discuss the "law of $1/n$" but do not cite \citet{weingast1981political}.
-We also checked the personal websites of the authors we had previously included in the paper in order to find unpublished research on our topic of interest.
-We thank Reviewer 3 for their insightful comment, as we included 2 new articles in our analysis as a result.
-
-Throughout the paper, we clarify all of Reviewer 1 \& 2's questions about our independent variables, coding procedures, and modelling techniques.
-We have also changed our model specifications to more properly account for effect size independence, following Reviewer 2's critique.
-We identified the sources of dependence in our sample and adopted multilevel random effects models in all of our estimations.
-We are extremely appreciative of this recommendation, as it is now an important methodological strength in our paper.
-
-When it comes to our results, we follow Reviewer 2's insight on how to interpret the evolution of research designs, toning down the idea that most of the variation in our estimates derives from methodological choices.
-We also present new results by adding a moderator for unicameralism, following Reviewer 1's reference.
+We were especially committed to discussing the scope conditions of our article
+and to clarifying some technical questions about our experiments as highlighted
+by Reviewers 1 and 2. We did this by editing the Introduction, adding a new
+paragraph to the Conclusion, and including more details about our methodology
+in section two and in the Supplementary Materials. We also removed the
+significance tests from the manuscript, as per the suggestion of Reviewer 2,
+and added a footnote in the Supplementary Materials indicating that we
+randomized the order of the experiments to reduce the risk of order effects.
+Moreover, we now show how the findings we report in the article compare with
+those found in other contexts, as suggested by Reviewer 1. We also discuss the
+results of our subgroup analyses in the Supplementary Materials, again
+following the recommendation of Reviewer 1. Lastly, we include all references
+suggested by Reviewer 1 and 2 in the main body of the manuscript. We are
+extremely appreciative of these recommendations and agree that the manuscript
+is now stronger and appeals to a broader readership.
 
@@
 
-\noindent Yours Truly,
+\noindent Sincerely yours,
 
@@
 
+\newpage
+
 \section*{Editor Comments and Responses}
 
-\textbf{1)} The editor writes: ``The Reviewers provide helpful comments.
-Specifically, Reviewer 1 suggests that you re-frame the paper to acknowledge that the inconsistency of the results has long been understood in the literature, and that the search for explanations of that inconsistency is an important driver of that literature.
-Please give further thought to the key contribution of your meta-analysis against that background, as Reviewers 1 and 2 suggest, and discuss the theoretical contribution and its meaning more fully in the introduction and conclusion.''
+\textbf{1)} The editor writes: ``I agree with R2 that the framing of the study
+could be improved. You currently cite a number of interesting figures and basic
+facts about lynching in Brazil in the start of the conclusion. I think this
+would fit better in the introduction. R2 also argues that the reference to the
+Blair et al study on greater costs of local violence is imprecise. I am
+guessing you mean something along the lines of likely to affect a greater
+number directly than terrorism or civil war, which I think is reasonable but
+could be said more directly.''
 
@@
 \begin{quote}
-    We have completely restructured the Introduction and Discussion sections to establish a better dialogue with the literature.
-We better contextualise our motivation to write this piece and more concretely demonstrate the implications of our results regarding previous findings.
-To illustrate the theory, we have provided the reader with a brief summary of the "law of $1/n$" model in Section A of the Supplementary Materials.
-We have also expanded the literature review in the Introduction.
-In the Discussion section, our hypotheses on the sources of heterogeneity are more clearly connected with the themes previously explored in the literature.
 
-    We refer to these changes more specifically in our responses to Reviewer 1 in page 3, and to Reviewer 2 in page 7 of this document.
+We have moved the facts about lynchings in Brazil to the Introduction and we
+agree that the section now provides more context for our experiments. The
+second paragraph of the Introduction is as follows: ``\textit{One of the most
+serious forms of extrajudicial violence is lynching. Lynching can be defined
+as ``incidents of physical violence committed by large numbers of private
+citizens against one or more individuals accused of having committed a
+``criminal'' offense, whether or not this violence resulted in the death of
+the victim(s)'' \citep[645]{godoy2004justice}. Although lynchings occur in
+more than one hundred countries in all regions of the world
+\citep{jung2020lynching,smith2019contradictions}, Latin America has been
+particularly affected by a sharp increase in vigilante violence. Lynching
+episodes have been reported in Guatemala, Mexico, Peru, Venezuela and other
+countries in the region \citep{barbara2015vigilantes, cruz2019determinants,
+godoy2004justice}. From 2011 to 2015, Brazil registered about 2,500 lynching
+episodes, and 173 people were killed by angry mobs in 2015 alone---nearly one
+execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
+According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who
+has studied lynchings in Brazil for more than thirty years, these figures are
+not only the highest in the country's history, but among the highest in the
+world. The people who participate in lynchings are typically young men, but
+they also sometimes include teenage women and girls, elderly women, and even
+members of the local police \citep{moura2017linchamentos}.}
+
+We have also changed the sentence in which we cite \citet{blair2017predicting}
+to make our claims more explicit. The last sentence in the first paragraph now
+reads: ``\textit{This omission is significant not only because local violence
+is pervasive in weak states, but also because it often comes at a greater
+social cost than terrorism or civil wars \citep{blair2017predicting}}.''
+
 \end{quote}
@@
 
-\noindent \textbf{2)} The editor writes: ``All Reviewers also provide detailed comments on your empirical analysis.
-Reviewer 3 has useful suggestions regarding your sampling strategy; Reviewers 1 and 2 focus on your dependent and explanatory variable.
-Please address these comments.''
+\noindent \textbf{2)} The editor writes: ``The manuscript is focused primarily
+on the empirical approach, but I agree with R1 that you could say a bit more
+about the rationale for the covariates considered, perhaps drawing out why more
+``novel'' features such as family or type of crime is likely to be important.''
 
@@
 \begin{quote}
-    We have followed Reviewer 3's suggestion and nearly tripled the amount of records we assessed for eligibility, seeking articles within the distributive politics literature through broader criteria.
-Thanks to this review, we added two new articles to our meta-analysis.
 
-    The main methodological adaptation we made was in response to Reviewer 2's extremely valuable comment on the need for using multilevel models.
-We are extremely grateful for this comment, and we thank Reviewer 2 for pointing out this crucial aspect in our empirical strategy.
+We have followed Reviewer 1's suggestion and have extended section two (``When
+Is Lynching Perceived as More Justified?'')  to provide further information
+about our choice of covariates. The third paragraph of that section now reads:
+``\textit{In addition to our knowledge of the Brazilian case, we also chose our
+attributes based partly on existing work on crime, vigilantism, and
+extrajudicial violence. From the prison violence literature, we know that the
+relative age differences and the genders of perpetrators and victims affect
+how it is perceived \citep{fleisher2009myth}. We likewise know that certain
+offenses are seen as especially reprehensible \citep{skarbek2014social}, so
+we included such offenses, like molestation, alongside less serious offenses.
+We include race because, in the United States, violent lynchings have often
+been wielded for racist reasons \citep{dray2003hands}. Likewise, we include
+residency because extrajudicial violence is often used against people ``who
+don't belong'' or are ``outsiders'' in some respect. Finally, in honor
+cultures that value retaliatory violence, people believe that victims and the
+family of victims have a special right (and often an obligation) to enact
+retribution \citep{weiner2013rule}.}
 
-    We also added a series of clarifications regarding our coding procedures, specially regarding the independent variables.
-We specify where these explanations can be found in the main article along this letter, according to each of the specific suggestions the Reviewers made.
+As we show below, we have also included an additional paragraph in the
+Conclusion to discuss how our findings relate to the literature on extralegal
+violence.
+
 \end{quote}
@@
 
-\noindent \textbf{3)} The editor writes: ``Reviewers 1 and 2 also ask you to make better use of the Supplementary Materials (SI).
-In your main text, please refer to specific sections in the SI, please explain your results in the SI, and leave out the R code, which should be made publicly available separately from the SI with the replication materials.''
+\noindent \textbf{3)} The editor writes: ``On the presentation of the results,
+I agree with R2 that the discussion of the results does not need to re-report
+all the significance tests, and the full tables could be included in the text
+or appendix.''
 
@@
 \begin{quote}
-    We have made the changes requested by Reviewers 1 and 2 accordingly.
-The ``Supplementary Materials'' we refer to hereinafter contain only a discussion of the \citet{weingast1981political} and \citet{primo2008distributive} models in Section A, a detailed description of the search and eligibility procedures for study inclusion (Sections B and C), a guide to how we built the meta-analysis dataset from our pool of diverse coefficients (Section D), a presentation of the descriptive statistics of the included articles (Sections E and F), and the results for the binomials tests, meta-analyses, and meta-regressions (Sections G through K).
-The R scripts we previously presented along with this information are now in a different document referred to as ``Replication Materials''.
-For the purpose of reproducibility, the full datasets listing all the records we assessed and the stage and reason for each exclusion are also available online for consultation in the article's GitHub repository.
+
+We have deleted the statistical details from the main text to improve the
+readability of the manuscript. All significance tests are now reported only in
+the Supplementary Materials.
+
 \end{quote}
@@
 
-We would like to thank the editors for their helpful comments and suggestions.
-
-\section*{Reviewer 1 Comments and Responses}
-
-\noindent \textbf{1)} Reviewer 1 writes: ``It has long been known that the empirical results are inconsistent in this literature.
-To wit, a major theme in the empirical literature -- at least for the last decade or so -- has been to try to explain the previously inconsistent findings, especially between upper and lower chambers; papers like Chen and Malhotra, Crowley, Lee, etc.
-take it as a main motivation to explain these inconsistencies.
-There have also been theoretical contributions in this vein, such as Pecorino's 2018 piece in Public Choice.
-In other words, these various approaches the authors note have been evolving not just as new techniques have been made available, but precisely *because* of the inconsistency in the findings the authors are discussing here.
-While I understand this paper is endeavoring to be concise, some service should be paid to a fuller discussion of the trends in the literature--noting that the previous authors in this literature were well aware of its inconsistent results--beyond just changes in methodology.''
+\noindent \textbf{4)} The editor writes: ``It would be useful to add a bit more
+discussion of Brazil in comparative perspective. I wonder if the results for
+Brazil are likely to be more general and that the US could be an outlier, for
+example.''
 
@@
 \begin{quote}
-    Reviewer 1 makes an excellent point.
-We agree that we had not properly expressed how more recent works identified and searched for strategies that solved the discrepancies in the literature.
-We have changed the framing of the paper so it is clear that scholars were well aware of the heterogeneity, and that our contribution in this sense is to quantitatively find the sources of such variation.
-While this idea permeates the Introduction section, here is one sentence we added that specifically addresses this point (p.2):
 
-    ``\textit{In this respect, scholars have long been aware of the theoretical and empirical limitations of the ``law of $1/n$'', and the proliferation of new studies reflect a conscious attempt to assess the robustness of the theory.}''
+We have made the changes requested by the editor and Reviewer 1 and our
+Conclusion section has been significantly expanded. We are especially grateful
+for this suggestion, as it has allowed us to better situate our article in the
+broader literate on vigilantism. Paragraph three of the Conclusion, the longest
+in the section, is now exclusively dedicated to the scope conditions of our
+research. We have linked our findings to important works in the literature and
+have also discussed how a culture of honor may explain some of our main
+findings.
 
-    As mentioned above, we have also expanded the literature review from paragraphs 1 through 3 in the Introduction section (p.2) as follows:
+The paragraph reads: ``\textit{These findings have implications that extend
+well beyond Brazil. In particular, our experiments indicate that lynchings
+have a crucial gendered aspect, which has also been documented in other
+contexts. Using data from 18 Latin American countries,
+\citet{nivette2016institutional} also finds that respondents are most likely
+to support lynchings when the criminal raped a child, and studies about
+lynchings in the American South point out that several episodes resulted from
+accusations of sexual assault \citep{jacquet2013giles, smaangs2020race}. We
+believe that a culture of honor may explain these results. Individuals in
+honor societies view crime as an attack on their personal reputation and, in
+turn, are more likely to take revenge to defend their status and that of
+people perceived as deserving protection, such as women and children
+\citep{nisbett2018culture}. A culture of honor may also explain why
+Brazilians see lynchings carried out by the family of the victim as more
+justified, as well as refraining from using extralegal violence if it can
+trigger vendettas. We expect similar results in societies which share those
+cultural norms. Lastly, the fact that race does not appear to be a major
+motivation behind lynchings also reflects the experience of places like Haiti
+or Southern Africa, where popular violence was mainly driven by other social
+factors \citep{berg2011globalizing, jung2020lynching}. Even in the American
+South, Whites and Blacks also lynched people of their own race
+\citep{beck1997race}. In this respect, our paper also highlights that
+lynchings in the Global South may be more strongly connected with the idea of
+``popular justice'' than with racial animus \citep{martins2015linchamentos}.}''
 
-    ``\textit{Early studies that empirically tested the "law of $1/n$", as the theory is currently known, indeed found a positive correlation between the number of legislature seats and different measures of government spending, although these first results were mainly based on US state legislatures and the effect was often limited to one house (e.g., \citet{baqir2002districting, gilligan1995deviations, gilligan2001fiscal}).}
+\end{quote}
 
-    \textit{Later research, however, has questioned the validity of the "law of $1/n$".
-\citet{primo2008distributive} affirm that, due to spatial spillovers, a collection of small districts can supply public goods more efficiently than the central government.
-The authors conclude that a "reverse law of $1/n$" may hold, wherein a higher number of legislators in small constituencies decrease the overall public spending.
-Similarly, \citet{primo2006stop} and \citet{chen2007law} find that lower and upper chambers may have mixed effects on government spending, while \citet{petterssonlidbom2012size} argues that the impact of larger chamber sizes is negative when using data from Finland and Sweden.}
+\vspace{.3cm}
 
-    \textit{Since many empirical tests of the "law of $1/n$" have produced conflicting results, scholars have expanded this research agenda and closely investigated how institutional factors condition the original formulation of the theory.
-For instance, authors such as \citet{crowley2019law} and \citet{pecorino2018supermajority} accurately point out that collective action problems have been overlooked in the literature, and recent findings indicate that bicameralism \citep{maldonado2013legislatures}, intergovernmental competition \citep{crowley2015local}, redistricting \citep{lee2018court}, and party ideology \citep{bjedov2014impact} strongly influence the relationship between seats and spending.
-Moreover, the literature has increasingly applied causal inference methods to estimate the effect of the "law of $1/n$", and in contrast to previous studies using panel data, regression discontinuity designs generally indicate that more legislators decrease public expenditures \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}.}''
+\noindent \textbf{5)} The editor writes: ``Finally, in order to ensure any
+delays on a decision on the resubmission I would encourage you to make sure
+that the final manuscript follows the journal guidelines,
+\url{https://journals.sagepub.com/author-instructions/rap}. For example, the
+sections should not be numbered, and the references should have first initial
+only rather than full names and books should have location before publisher
+(please ensure that all references are complete – Grimm looks incomplete to me,
+for example).''
+
+\noindent \textbf{Response:} 
+\begin{quote}
+
+We have completed the references according to Research \& Politics' guidelines
+and the sections are unnumbered as requested.
+
+\end{quote}
+
+\vspace{.3cm}
+
+We would like to thank the editor Kristian Skrede Gleditsch for his very
+helpful comments and suggestions.
+
+\section*{Reviewer 1 Comments and Responses}
+
+\noindent \textbf{1)} Reviewer 1 writes: ``The empirical approach is presented
+as offering many benefits---I would also acknowledge the drawbacks. And many of
+these results do not seem to square with other parts of the world (which is a
+feature and I would ask the authors for a little bit of speculation as to why!)
+but I would suggest the authors think about the scope conditions imposed by the
+setting and how well they seem to extend (the gendered aspect, yes, the race
+aspect, perhaps there are some conditions).''
+
+\vspace{.3cm}
+
+\noindent \textbf{Response:} \begin{quote}
+
+Reviewer 1 makes an excellent point. We agree that we had not properly
+explained the scope conditions of our research and, as mentioned above, we have
+included a long paragraph in the Conclusion to detail
+
 \end{quote}
@@
 Many studies consider lower chambers and unicameral legislatures as analogous institutions for quantitative purposes.
-An example is one of the papers in our meta-analysis \citep{stein1998institutional}.
+An example is one of the papers in our meta-analysis.
 We expand the explanations surrounding the treatment of independent variables in the first paragraph of the Data and Methods section.
@@
 We have also made our critiques of the scholarship more clear, explicitly pointing to which we thought were the sources of heterogeneity in previous work in the Discussion section.
-Moreover, in Section A of the Supplementary Materials, we added a brief discussion of the theory developed by \citet{weingast1981political}, and also the "reverse law of $1/n$" by \citet{primo2008distributive}.
 \end{quote}
@@
 Studies that analyse bicameral systems use upper chamber size and lower chamber size as independent variables, and thus supply two coefficients each.
-These studies are \citet{chen2007law, crowley2019law, gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court, maldonado2013legislatures, ricciuti2003trading, ricciuti2004legislatures, primo2006stop}.
-The paper by \citet{bradbury2001legislative} alone supplies four coefficients, as they use two independent variables (upper chamber size and lower chamber size) and two dependent variables (expenditure as share of the GDP and per capita expenditure).
-Two other papers \citep{bjedov2014impact, erler2007termlimits} also use both of these dependent variables and only one independent (lower chamber size), supplying two coefficients each.
-
-    To the extended sample, each paper can supply several coefficients because studies usually submit their data to a series of models where they include or exclude different controls or interaction terms, or perform slightly different tests.
-For instance, we drew twelve coefficients from \citet{fiorino2007legislature}.
-From a single table (Table 4) in their paper, we extracted four coefficients for the same variable combination (lower chamber size and per capita expenditure).
 \end{quote}
@@
 The Reviewer is also correct to point out that separating the effect sizes into a restricted and an extended sample does not properly address the dependence of the coefficients within the extended sample.
-We followed the Reviewer's suggestion rigorously by employing multilevel random effect models \citep{cheung2014modeling, matthes2019meta} in all of our estimations.
+We followed the Reviewer's suggestion rigorously by employing multilevel random effect models in all of our estimations.
 A thorough explanation of how we identified, grouped the studies that constitute the new levels, and coded them can be found in section H.1 of the Supplementary Materials.
@@
 
-    ``\textit{We use Hedges' $g$ to calculate effect sizes in our meta-analysis \citep{hedges1981distribution}.
-While there are other methods to standardise coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in small sample sizes and is considered more robust than measures such as Cohen's $d$ \citep{lakens2013calculating}.
-We estimate the Standardised Mean Difference (SMD), which represents the effect size in each study relative to the variability observed in that study, by extracting the coefficients and the standard errors from all articles included in our sample and converting them to Hedges' $g$.
-In cases where authors did not report the standard errors for their estimates, we computed them using the t-statistic presented in the original tables.}''
+    ``\textit{We use Hedges' $g$ to calculate effect }''
 \end{quote}
@@
 
-    ``\textit{However, when we look only at articles that employ regression discontinuity designs, we see that all four papers included in our sample suggest that a higher number of legislators leads to lower public spending \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}.
-In this regard, it is possible that methodological choices partially explain the divergent results observed in the literature, as studies that use causal inference methods consistently point to the same direction.
-One limitation of this finding is that these studies only test the impact of lower house size on the natural logarithm of expenditure per capita, thus it remains unclear whether the results hold with other variables.}''
+    ``\textit{However, when we look only at articles that employ regression discontinuity designs, we see that all four papers included in our sample suggest that a hi}''
 
@@
 When using an extended sample of 162 coefficients, we find that unicameralism is associated with higher public spending, as predicted by the ``law of $1/n$''.
-Since most unicameral legislatures in our sample are local governments (municipalities or districts), this result supports the predictions of \citet{weingast1981political}.
-Moreover, our meta-regressions indicate that larger upper chambers spend more in terms of per capita expenditure than lower chambers, a result that also appears in the binomial tests.
+Since most unicameral legislatures in our sample are local governments (municipalities or districts), this result supports the predictions of Moreover, our meta-regressions indicate that larger upper chambers spend more in terms of per capita expenditure than lower chambers, a result that also appears in the binomial tests.
 Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original definition of the law.
@@
 
-\section*{Reviewer 3 Comments and Responses}
-
-\noindent \textbf{1)} Reviewer 3 writes: ``First, I am concerned about the first criterion for inclusion in the meta-analysis.
-Studies could only be included if they cited the Weingast et al.
-(1981) study.
-While I don't doubt that this work is foundational to the distributive politics literature, it is an unnecessary restriction.
-Are there any studies that fit the other two inclusion criteria but do NOT cite Weingast?
-Maybe there aren't any, but if there are, they should be included since they are still just as relevant to the question at hand.
-The second inclusion criterion is the most important: a study that quantitatively analyzes the variables of interest.
-This of course makes the literature search more difficult, but also more comprehensive, which is a main benefit of good meta-analyses.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    The concern Reviewer 3 expresses is one we share.
-We address this comment by conducing a second round of record collection.
-We increased our breadth by using a search string with key terms on Google Scholar.
-We meant to capture all articles that approached the relationship between legislature size and public spending.
-The search string we used is the following:
-
-    \texttt{\justify ("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")}
-
-    We fuzzy matched the resulting database with the one we had originally analysed to remove all entries we had already covered.
-As part of this eligibility analysis, we assessed an additional 3,042 records.
-The exclusion criteria and procedures were the exact same as those performed in the first round (for the original manuscript the Reviewers and Editors read).
-They are fully detailed in Sections B and C of the Supplementary Materials.
-The full dataset of excluded records is available for online consultation in the article's GitHub repository.
-
-    Resulting from this second round of surveying the literature, we found two articles that satisfied all the criteria.
-They were thus included in our analysis.
-The new papers are \citet{coate2011government} and \citet{debenedetto2018effect}.
-We thank Reviewer 3 for this comment, as it has effectively made our survey more comprehensive.
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{2)} Reviewer 3 writes: ``Second, another main benefit of meta-analyses is to assess the possibility of publication bias.
-Studies are often more likely to be published if they find statistically significant effects in the direction that is expected, but a comprehensive search of ongoing studies allows meta-analysts to check this.
-In the current sample, only 4 papers are unpublished, but I also wonder if this is due to the restricted inclusion criteria.
-For example, if one uses the Google Scholar feature to find articles citing Weingast et al, that would only pick up papers that are already published in a journal or otherwise online, but it may miss any working papers that are not shared publicly.
-A more comprehensive search may result in more unpublished studies.
-Either way, can the authors include some sort of formal tests or visualizations for publication bias, such as funnel plots?
-I think if these two revisions could be made this paper would make a strong contribution.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    We understand the Reviewer's concern with publication bias, and we accept both of her/his suggestions in this comment.
-First, so as not to miss any papers that have not been circulated as Working Papers, we seek after those that have been shared as ongoing projects.
-We looked into the personal webpages of the scholars who wrote all of the papers in our original sample of studies.
-In their personal platforms, we scouted for pieces of research about distributive politics.
-We targeted specifically those that had not been uploaded to large repositories and open archives such as SocArXiv, as those tend to appear in Google Scholar searches.
-We gathered 15 pieces of work with titles potentially related to our research topic and submitted them to the eligibility criteria.
-None of these papers were included in the final sample.
-This procedure is also explained in Section B of the Supplementary Materials, and a dataset displaying all records assessed and their reason for exclusion is available for online consultation as well.
-
-    Attending to the Reviewer's second request, we add \citet{egger1997bias} funnel plots to assess publication bias in all of our meta-analyses.
-Funnel plots display the possibility of having a file-drawer effect, meaning they can indicate whether null results are under-represented in our sample or not.
-The funnel plots are available in the Supplementary Materials below the forest plot for each variable combination in the restricted and in the extended samples (Sections H and I).
-All but one of our \citet{egger1997bias} tests reject the hypothesis of publication bias.
-\end{quote}
-
-We would like to thank Reviewer 3 for her/his helpful comments and suggestions.
-
 \newpage
-\bibliography{references.bib}
+\bibliography{../article/references.bib}
 \bibliographystyle{apalike}

### 2022-12-01 article/article.tex
add response, edit manuscript

@@
 where popular violence was mainly driven by other social factors
-\citep{berg2011globalizing, jung2020lynching}. Even in the American South, it
+\citep{berg2011globalizing, jung2020lynching}. Even in the American South,
 Whites and Blacks also lynched people of their own race \citep{beck1997race}.
 In this respect, our paper also highlights that lynchings in the Global South
-may be more strongly connected with ideas of ``popular justice'' than racial
-animus \citep{martins2015linchamentos}.
+may be more strongly connected with the idea of ``popular justice'' than with
+racial animus \citep{martins2015linchamentos}.
 

### 2022-12-03 response-reviewers/response-reviewers.tex
add r1 reviews, review art and app

@@
 significance tests from the manuscript, as per the suggestion of Reviewer 2,
-and added a footnote in the Supplementary Materials indicating that we
-randomized the order of the experiments to reduce the risk of order effects.
-Moreover, we now show how the findings we report in the article compare with
-those found in other contexts, as suggested by Reviewer 1. We also discuss the
-results of our subgroup analyses in the Supplementary Materials, again
-following the recommendation of Reviewer 1. Lastly, we include all references
-suggested by Reviewer 1 and 2 in the main body of the manuscript. We are
-extremely appreciative of these recommendations and agree that the manuscript
-is now stronger and appeals to a broader readership.
+and added a footnote to the Supplementary Materials indicating that we
+randomized the order of the experiments to reduce the risk of carryover
+effects. Moreover, we now show how our findings compare with those found in
+other studies, as suggested by Reviewer 1. We also discuss the results of our
+subgroup analyses in the Supplementary Materials, again following the
+recommendation of Reviewer 1. Lastly, we include all references suggested by
+Reviewer 1 and 2 in the main body of the manuscript. We are extremely
+appreciative of these recommendations and agree that the manuscript is now
+stronger and appeals to a broader readership.
 
@@
 
-\noindent Sincerely yours,
+\noindent Sincerely Yours,
 
@@
 agree that the section now provides more context for our experiments. The
-second paragraph of the Introduction is as follows: ``\textit{One of the most
-serious forms of extrajudicial violence is lynching. Lynching can be defined
-as ``incidents of physical violence committed by large numbers of private
-citizens against one or more individuals accused of having committed a
-``criminal'' offense, whether or not this violence resulted in the death of
-the victim(s)'' \citep[645]{godoy2004justice}. Although lynchings occur in
-more than one hundred countries in all regions of the world
-\citep{jung2020lynching,smith2019contradictions}, Latin America has been
-particularly affected by a sharp increase in vigilante violence. Lynching
-episodes have been reported in Guatemala, Mexico, Peru, Venezuela and other
-countries in the region \citep{barbara2015vigilantes, cruz2019determinants,
-godoy2004justice}. From 2011 to 2015, Brazil registered about 2,500 lynching
-episodes, and 173 people were killed by angry mobs in 2015 alone---nearly one
-execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
-According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who
-has studied lynchings in Brazil for more than thirty years, these figures are
-not only the highest in the country's history, but among the highest in the
-world. The people who participate in lynchings are typically young men, but
-they also sometimes include teenage women and girls, elderly women, and even
-members of the local police \citep{moura2017linchamentos}.}
+second paragraph of the Introduction now reads as follows (page 02):
+``\textit{One of the most serious forms of extrajudicial violence is lynching.
+  Lynching can be defined as ``incidents of physical violence committed by
+  large numbers of private citizens against one or more individuals accused of
+  having committed a ``criminal'' offense, whether or not this violence
+  resulted in the death of the victim(s)'' \citep[645]{godoy2004justice}.
+  Although lynchings occur in more than one hundred countries in all regions of
+  the world \citep{jung2020lynching,smith2019contradictions}, Latin America has
+  been particularly affected by a sharp increase in vigilante violence.
+  Lynching episodes have been reported in Guatemala, Mexico, Peru, Venezuela
+  and other countries in the region \citep{barbara2015vigilantes,
+  cruz2019determinants, godoy2004justice}. From 2011 to 2015, Brazil registered
+  about 2,500 lynching episodes, and 173 people were killed by angry mobs in
+  2015 alone---nearly one execution every two days
+  \citep{barbara2015vigilantes, oliveira2016mob}. According to José de Souza
+  Martins \citeyearpar{martins2015linchamentos}, who has studied lynchings in
+  Brazil for more than thirty years, these figures are not only the highest in
+  the country's history, but among the highest in the world. The people who
+participate in lynchings are typically young men, but they also sometimes
+include teenage women and girls, elderly women, and even members of the local
+police \citep{moura2017linchamentos}.}
 
 We have also changed the sentence in which we cite \citet{blair2017predicting}
-to make our claims more explicit. The last sentence in the first paragraph now
-reads: ``\textit{This omission is significant not only because local violence
-is pervasive in weak states, but also because it often comes at a greater
-social cost than terrorism or civil wars \citep{blair2017predicting}}.''
+to make our claims more precise. The last sentence in the first paragraph reads
+(page 02): ``\textit{This omission is significant not only because local
+  violence is pervasive in weak states, but also because it possibly comes at a
+greater social cost than terrorism or wars \citep{blair2017predicting}}.''
 
@@
 Is Lynching Perceived as More Justified?'') to provide further information
-about our choice of covariates. The third paragraph of that section now reads:
-``\textit{In addition to our knowledge of the Brazilian case, we also chose our
-attributes based partly on existing work on crime, vigilantism, and
-extrajudicial violence. From the prison violence literature, we know that the
-relative age differences and the genders of perpetrators and victims affect
-how it is perceived \citep{fleisher2009myth}. We likewise know that certain
-offenses are seen as especially reprehensible \citep{skarbek2014social}, so
-we included such offenses, like molestation, alongside less serious offenses.
-We include race because, in the United States, violent lynchings have often
-been wielded for racist reasons \citep{dray2003hands}. Likewise, we include
-residency because extrajudicial violence is often used against people ``who
-don't belong'' or are ``outsiders'' in some respect. Finally, in honor
-cultures that value retaliatory violence, people believe that victims and the
-family of victims have a special right (and often an obligation) to enact
-retribution \citep{weiner2013rule}.}
+about our choice of covariates. The third paragraph of that section now reads
+(page 04): ``\textit{In addition to our knowledge of the Brazilian case, we
+  also chose our attributes based partly on existing work on crime,
+  vigilantism, and extrajudicial violence. From the prison violence literature,
+  we know that the relative age differences and the genders of perpetrators and
+  victims affect how it is perceived \citep{fleisher2009myth}. We likewise know
+  that certain offenses are seen as especially reprehensible
+  \citep{skarbek2014social}, so we included such offenses, like molestation,
+  alongside less serious offenses. We include race because, in the United
+  States, violent lynchings have often been wielded for racist reasons
+  \citep{dray2003hands}. Likewise, we include residency because extrajudicial
+  violence is often used against people ``who don't belong'' or are
+  ``outsiders'' in some respect. Finally, in honor cultures that value
+  retaliatory violence, people believe that victims and the family of victims
+  have a special right (and often an obligation) to enact retribution
+\citep{weiner2013rule}.}
 
@@
 
-The paragraph reads: ``\textit{These findings have implications that extend
-well beyond Brazil. In particular, our experiments indicate that lynchings
-have a crucial gendered aspect, which has also been documented in other
-contexts. Using data from 18 Latin American countries,
+The paragraph reads (page 11): ``\textit{These findings have implications that
+  extend well beyond Brazil. In particular, our experiments indicate that
+  lynchings have a crucial gendered aspect, which has also been documented in
+  other contexts. Using data from 18 Latin American countries,
   \citet{nivette2016institutional} also finds that respondents are most likely
@@
 
-We have completed the references according to Research \& Politics' guidelines
-and the sections are unnumbered as requested.
+The sections are now unnumbered and we have completed the references according
+to Research \& Politics' guidelines.
 
@@
 setting and how well they seem to extend (the gendered aspect, yes, the race
-aspect, perhaps there are some conditions).''
+aspect, perhaps there are some conditions). The finding I think is most
+interesting to draw out is the family of rape/murder victims, this is—I think—a
+facet not typically focused on and strikes me as the ``newest'' finding and one
+I would encourage the authors to pull forward and (in the context of a strict
+word limit) emphasize and do a bit of theoretical speculation for others to
+build upon!''
 
@@
 
-\noindent \textbf{Response:} \begin{quote}
+\noindent \textbf{Response:}
+
+\begin{quote}
 
@@
 explained the scope conditions of our research and, as mentioned above, we have
-included a long paragraph in the Conclusion to detail
+written a new paragraph in the Conclusion to provide further context for our
+findings. We compare our results with studies on vigilantism in other Latin
+American countries and in the United States, and we also discuss how social
+norms, especially those related to a culture of honor, may explain why
+Brazilians are more likely to support lynchings when the victim is a woman or a
+child. Finally, we also briefly speculate why race does not seem to influence
+individual preferences for lynchings in Brazil.
+
+The paragraph reads (page 11): ``\textit{These findings have implications that
+  extend well beyond Brazil. In particular, our experiments indicate that
+  lynchings have a crucial gendered aspect, which has also been documented in
+  other contexts. Using data from 18 Latin American countries,
+  \citet{nivette2016institutional} also finds that respondents are most likely
+  to support lynchings when the criminal raped a child, and studies about
+  lynchings in the American South point out that several episodes resulted from
+  accusations of sexual assault \citep{jacquet2013giles, smaangs2020race}. We
+  believe that a culture of honor may explain these results. Individuals in
+  honor societies view crime as an attack on their personal reputation and, in
+  turn, are more likely to take revenge to defend their status and that of
+  people perceived as deserving protection, such as women and children
+  \citep{nisbett2018culture}. A culture of honor may also explain why
+  Brazilians see lynchings carried out by the family of the victim as more
+  justified, as well as refraining from using extralegal violence if it can
+  trigger vendettas. We expect similar results in societies which share those
+  cultural norms. Lastly, the fact that race does not appear to be a major
+  motivation behind lynchings also reflects the experience of places like Haiti
+  or Southern Africa, where popular violence was mainly driven by other social
+  factors \citep{berg2011globalizing, jung2020lynching}. Even in the American
+  South, Whites and Blacks also lynched people of their own race
+  \citep{beck1997race}. In this respect, our paper also highlights that
+lynchings in the Global South may be more strongly connected with the idea of
+``popular justice'' than with racial animus \citep{martins2015linchamentos}.}''
+
+We have added three sentences on pages 6 and 7 to offer readers more context
+about our covariates. They read (pages 6--7): ``\textit{Taken together, the
+  results provide experimental evidence that support for lynchings in Brazil
+  does not resemble the typical racial patterns scholars have observed in the
+  United States \citep{dray2003hands,obert2018keeping,seguin2019national}.
+  These findings are consistent with recent research on vigilantism in Haiti
+  \citep{jung2020lynching} and with journalistic observations. They further
+  suggest that the US experience with lynchings might be distinct from
+vigilantism in other places and times \citep{oliveira2016mob}.}''
+
+Finally, we have added two sentences on page 8 to discuss how cultural norms
+are relevant to our results. They read (page 8): ``\textit{In sum,
+respondents did not believe that lynchings should be carried out by the state
+but did believe they should be used as a tool for individual or family
+retribution. These results are consistent with norms of an honor culture in
+which offenses are seen to tarnish the victim's status and the only way to
+remove the stigma is through self-help efforts in the form of retaliatory
+violence \citep{nisbett2018culture}.}''
 
@@
 
-\noindent \textbf{2)} Reviewer 1 writes: ``In the empirical exercise, the authors routinely reference separating the empirical studies they use as their sample based on the "main explanatory variable." For instance, in section 3.3.
-This strikes me as problematic (or at least poorly explained) because it is typically standard in this literature (at least for those studies on bicameral legislatures such as cross-state studies on the US) to include both the upper and lower chamber size variables.
-So it is unclear to me how such a study would have a "main explanatory variable." This needs to be more clearly explained.''
+\noindent \textbf{2)} Reviewer 1 writes: ``With respect to experiment two---I
+would be very clear about the control group (in my reading) having been
+``treated'' by the conjoint. In terms of estimation this is fine, but in terms
+of baseline attitudes that we might use to benchmark in future studies, I do
+worry a bit.  I would also encourage a bit more description of the subgroup
+analyses on experiment 2 since I think they are likely interesting/important
+for future work.''
 
@@
 \begin{quote}
-    We agree that our explanations regarding the choice and use of the variables of interest were insufficient.
-When studies use evidence from bicameral legislatures, we included the coefficients for both upper and lower chamber size in all our samples.
-This is the case for thirteen articles in our analysis.
-Using data from both chambers is one of the reasons why our restricted sample contains 45 coefficients for a total of 30 papers.
-We added clarifications regarding our choice of independent variable in the first paragraph of the Data and Methods section, on page four.
 
-    A specific comment on variable choice in bicameral systems is in footnote \#2.
-It reads: ``\textit{Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as main explanatory variables.}''
+We agree that our explanations regarding our experimental design were
+incomplete. We randomized the order of the experiments precisely to avoid
+carryover effects, thus we hope our estimates are unbiased because of this
+procedure. We have added a footnote to the Supplementary Material to explain
+this point. It reads (page 83 of the SM, footnote number 02): ``\textit{To
+  prevent eventual carryover effects caused by the conjoint, we randomized the
+  order of the conjoint and the information provision experiments
+\citep{perreault1975controlling}.}''.
+
+We also agree that the subgroup analyses may be interesting to scholars. Our
+Supplementary Materials now include a short comment about each of our subgroup
+tests. We note when the results are statistically significant and when they are
+vary according to the covariates we control for. For instance, Section C.4.1 of
+the Supplementary Materials, in which we assess whether our results for the
+conjoint experiment differs between genders, we write the following (page 24):
+``\textit{Results do not seem to vary according to the gender of the
+  respondent. We focus here on the differences between males and females and
+  exclude the 11 observations in which respondents preferred not to say their
+  gender or marked ``other'' in our questionnaire. Across all conjoint
+experiment attributes, we see an overlap between the 95\% confidence intervals
+for males and females.}'' Similarly, in Section C.4.3, in which we test whether
+our results vary by race, we write: ``\textit{Below are our results when we
+disaggregate the data by race. We find that they are almost identical is all
+dimensions except for offense. Asian respondents are much less likely to select
+profiles that contain pickpocketing as a crime.}''  All analyses are also
+accompanied by their corresponding \texttt{R} code to facilitate the
+replication of our results.
+
 \end{quote}
@@
 
-\noindent \textbf{3)} Reviewer 1 writes: ``In Table 3, the authors also only present N and log(N) results; K is not indicated—was it an excluded group? If so, this needs to be made clear.''
+\noindent \textbf{3)} Reviewer 1 writes: ``Minor: 1) I recommend citing Nick
+Rush Smith and there is a new special issue out at Comparative Politics that
+looks to have several pieces that are relevant! 2) I would like to see the
+supplementary materials included!''
 
@@
 \begin{quote}
-    We acknowledge that Table 3 did not display the reference categories clearly enough.
-We have highlighted the notes below the table so the reader can have a more straightforward interpretation of the estimates.
-They present the reference category for each variable and moderator in the meta-regressions.
-For the independent variable, the reference category was upper chamber size, which is why this category was omitted in the table.
-\end{quote}
 
-\vspace{.3cm}
+We have added a citation to Nick Rush Smith's work on page 02 and a citation to
+the special issue in footnote 01 (page 02). The Supplementary
+Materials are now included in the submission as well.
 
-\noindent \textbf{4)} Reviewer 1 writes: ``Further, it is not clear to the reader why the authors use lower chamber size, upper chamber size, and then a log of only lower chamber size.
-Are there no studies which employ a log of upper chamber size?''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    Following the reviewer's remark, we double checked our study sample and confirm that the natural logarithm of upper chamber size is not present in any papers.
-As mentioned above, we included clarifications about our choice of independent variable in the first paragraph of the Data and Methods section (p.4).
-Footnote \#2 reads: ``\textit{We did not find any article that used the natural logarithm of upper chamber size in their models.}''
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{5)} Reviewer 1 writes: ``How did the authors handle those studies in this literature which focused on unicameral legislatures?
-Were these grouped in with the "lower chamber" studies?
-Were they excluded?
-This is not clearly explained in the paper.
-In general, the results on unicameral legislatures tend to support the law of $1/n$.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    As noted above, we agree that important details about data collection and coding were missing.
-Unicameral legislature sizes were coded under lower chamber size or natural logarithm of lower chamber size.
-Many studies consider lower chambers and unicameral legislatures as analogous institutions for quantitative purposes.
-An example is one of the papers in our meta-analysis.
-We expand the explanations surrounding the treatment of independent variables in the first paragraph of the Data and Methods section.
-A specific clarification on unicameral legislatures is in Footnote \#2.
-It reads: ``\textit{There are a few important nuances concerning coding of these variables.
-Unicameralism, for example, is captured both by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).}''
-
-    Upon reading this comment, we also acknowledged that although the differences between upper and lower chambers were so relevant to the discussion, we had not given enough attention to unicameral legislatures.
-Inspired by this remark, we coded a new moderator for institutional design.
-The categories were `Unicameral', for coefficients from purely unicameral systems; `Bicameral', for coefficients from purely bicameral systems; and `Mixed', for coefficients from studies that used samples which contained a mix of unicameral and bicameral systems.
-Examples of the latter were all the papers that used country-level data.
-Our findings confirm the Reviewer's insight: in the meta-regressions that aggregate all coefficients, unicameralism is a significant positive predictor of the $1/n$ effect.
-
-    Since this is an important finding, we discuss the Institutional Design moderator in all sections.
-The Data and Methods section presents under which category each article fits in Table 1, and its descriptive statistics in Table 2.
-In the first paragraph of the Meta-Regressions subsection, we explain how the variable is coded (p.12), and briefly interpret its results in the last paragraph (p.14).
-
-    Because we found such interesting results in the meta-regressions, we decided to perform subgroup analyses with heterogeneous effects for unicameralism as well.
-The results can be found in section H.13 in the Supplementary Materials.
-We undertook tests similar to those we present in the article for Estimation Methods (p.12).
-Using the lower chamber size $\times$ per capita expenditure combination, we aggregated the data in two groups: one just for unicameral systems, and the other for all institutional designs excluding unicameralism.
-For unicameral systems, the estimates were mostly positive in the restricted sample, but none was statistically significant.
-Results were overwhelmingly positive for the extended sample, where they almost reached statistical significance.
-These results are in line with what we found in the rest of the paper, however they do not help us reach more robust conclusions on the effect of institutional design on the ``law of $1/n$''.
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{6)} Reviewer 1 writes: ``The Supplementary Materials is full of content that is of very little use to the reader; even as an online appendix, there is no need to include roughly 100 pages of code from a statistical software.
-I believe the most relevant Supplementary Materials is the detailed discussion on selection.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    We agree that the R script is useful to a limited amount of scholars, and not to the vast majority of readers.
-As mentioned above, we have separated the Supplementary Materials in two parts.
-The first follows Reviewer 1's recommendation, including a discussion of the theory, the study selection procedures, a description of how we coded the data in detail, and analysis results.
-The second gathers all scripts we use in each step of the study, and is aimed at those wishing to replicate our work or to produce new meta-analyses in the social sciences.
 \end{quote}
@@
 
-\noindent \textbf{1)} Reviewer 2 writes: ``I believe the main framing of this manuscript should focus on explaining the interesting variation between studies (i.e., when do the law of 1/n or the reverse law are expected).
-From this perspective, the introduction part of the paper currently quickly jumps to the technicalities of the meta-analysis (e.g., a description of the two models used, measurement of DV etc.; see p.
-2).
-These technical descriptions should appear in the method section.
-Instead, it would be more helpful to see some theoretical discussion on the reasons the literature proposes for the heterogeneity found in this study - even in a concise manner.''
+\noindent \textbf{1)} Reviewer 2 writes: ``Framing. The abstract is rather
+short, and I believe R&P abstracts can be up to 200 words. It would be good to
+make use of the space to highlight additional results that are especially
+counterintuitive or interesting.''
 
@@
 \begin{quote}
-    We agree that the technical discussion in the introductory section was misplaced.
-We have restructured the Introduction to fit Reviewer 1 and Reviewer 2's recommendations.
-As displayed above (p.4 of this letter), we expanded the literature review to capture the main points in the debate that dialogue with our findings.
-We have also made our critiques of the scholarship more clear, explicitly pointing to which we thought were the sources of heterogeneity in previous work in the Discussion section.
+
+We agree that the abstract could be improved. We have added two sentences to
+the revised abstract and it now reads as follows: ``\textit{Why do people
+support extrajudicial violence? In two survey experiments with respondents in
+Brazil, we examine which characteristics of lynching scenarios garner greater
+support for lynching and whether providing different types of information about
+lynching reduces support for it. We find that people often do support community
+members to take vengeance. In particular, our analysis finds that people
+strongly support the use of extrajudicial violence by families of victims
+against men who sexually assault and murder women and children. We also find
+that criminal punishment and the threat of vendettas reduce support, but
+appeals to the human rights of victims have zero effect on support for
+lynchings. Unlike the U.S. experience with lynchings, race was not observed to
+play an important role in how respondents answered the survey.}''
+
 \end{quote}
@@
 
-\noindent \textbf{2.1)} Reviewer 2 writes: ``It is currently difficult to understand why many studies included in the meta-analysis have several effect sizes.
-Is it because of using different dependent?
-Some examples would help the readers.''
+\noindent \textbf{2)} Reviewer 2 writes: ``The introduction motivates the study
+by noting that ``local violence'' can be more costly than war or terrorism
+violence. This raises questions about what is ``local violence'', and I'm not
+sure the cited source after this statement clarifies the situation. The cited
+Blair at al piece indicates that local violence is ``possibly'' more costly
+than war or terrorism, but this seems imprecise to me. If there is more space
+to defend this statement more, that might be ok, but it is probably better just
+to cut it and motivate the study in other ways.''
 
@@
 \begin{quote}
-    In our restricted sample, a study can supply more than one coefficient if it employs more than one dependent or independent variable.
-Studies that analyse bicameral systems use upper chamber size and lower chamber size as independent variables, and thus supply two coefficients each.
+
 \end{quote}
@@
 
-\noindent \textbf{2.2)} Reviewer 2 writes: ``Moreover, and more substantially, I am not sure how including studies with several effect sizes in a separate model (p.
-7) can solve the violation of non-independent effect sizes, required in meta-analyses.
-The authors do not report the statistical models they used for solving these violations (I did not find it in the appendix either).
-There are various ways to address such issues, such as robust variance estimation (see Hedges et al., 2010) or using multi-level meta-analyses (see e.g.
-application in Matthes et al., 2019).
-
-Furthermore, since there were several studies focusing on the same country (e.g., 14 studies investigating the US), did they use the same samples in their analysis?
-If so, doesn't it violate the non-independence assumption on its own (as they use the same district ``sample'')?
-If that is the case, the authors should treat this effect size dependency also for the first model (with the 42 main coefficients).
-These issues are very important since some of the authors' findings are based only on the ``extended models'' in Table 3 (i.e., those including 142 effect sizes, even from studies reporting several effect sizes related to the same sample).
-If these findings are based on biased estimates, we should be a lot more cautious interpreting them.''
+\noindent \textbf{3)} Reviewer 2 writes: ``Why is the scale of disagree to
+agree 0-100? Could the authors cite a source or sources on why this precise
+range was used, and briefly discuss some tradeoffs with such a scale? Why not
+a, for example, seven-point Likert scale?''
 
@@
 \begin{quote}
-    As Reviewer 2 correctly notes, the coefficient extraction procedure we just presented in the previous response is the main source of effect size dependence in our extended sample analyses.
-An additional source of dependence is the fact that many studies analyse the same cases, sometimes even using the same data sources.
-The Reviewer is also correct to point out that separating the effect sizes into a restricted and an extended sample does not properly address the dependence of the coefficients within the extended sample.
-We followed the Reviewer's suggestion rigorously by employing multilevel random effect models in all of our estimations.
-A thorough explanation of how we identified, grouped the studies that constitute the new levels, and coded them can be found in section H.1 of the Supplementary Materials.
-We describe the procedure more succinctly in the Data and Methods section in the main paper (last paragraph on page 7):
 
-    ``\textit{We add two extra levels to the regular meta-analysis, one including a unique publication ID for each paper, and another indicating the data source used in the original study.
-By adding these two levels, we account for within- and between-study variation, thus removing these sources of effect size dependency and improving the accuracy of the results.}''
-
-    We believe the inclusion of additional levels reduces the bias previously present in our analyses, producing far more reliable estimates.
-We are highly appreciative of this comment, as it has ignited major changes in our manuscript, severely improving the robustness of our results.
 \end{quote}
@@
 
-\noindent \textbf{3)} Reviewer 2 writes: ``How did the authors convert the original studies' coefficients into standardized effect sizes?
-It is important to mention how the authors render these coefficients comparable due to the various research designs included in the meta-analysis.''
+\noindent \textbf{4)} Reviewer 2 writes: ``Related to the above, the wording of
+the instructions seem to suggest that respondents could select anywhere between
+0 and 49 if they disagree; unless I am mistaken, the instructions do not
+indicate, for example, that 0 indicates fully disagree and 100 indicates fully
+agree. Were any more detailed instructions provided? Is there any evidence that
+people fully understood the instructions in this regard?''
 
@@
 \begin{quote}
-    We have included a paragraph in the Data and Methods section (p.7) to clarify the coefficient standardisation procedure. It reads:
 
-    ``\textit{We use Hedges' $g$ to calculate effect }''
 \end{quote}
@@
 
-\noindent \textbf{4)} Reviewer 2 writes: ``our results suggest that study coefficients are highly sensitive to research design choices'' (p.
-13) - this is a rather bold statement (``highly sensitive'') since most differences between study designs are nonsignificant (on Table 3).
-I would tone down this argument much more and address its limitations in the discussion.''
+\noindent \textbf{5)} Reviewer 2 writes: ``In the results section, it is
+probably not necessary to list the coefficient, SE, and p-value in the text for
+so many variables when the figures show the most important information,
+assuming the full tables are in the supplementary information.''
 
@@
 \begin{quote}
-    We have adapted the language when referring to the effects of estimation methods according to the Reviewer's suggestions throughout the paper.
-For instance, paragraph 6 of the Introduction (p.3) reads:
 
-    ``\textit{However, when we look only at articles that employ regression discontinuity designs, we see that all four papers included in our sample suggest that a hi}''
-
-    The Results and Discussion sections present these findings more objectively.
-On page 14, we report the following conclusion regarding estimation methods: ``\textit{The meta-regressions confirm that modern estimation methods such as RDDs and panel/fixed-effects models decrease effects more frequently than OLS regressions.}''
 \end{quote}
@@
 
-\noindent \textbf{5)} Reviewer 2 writes: ``I encourage the authors to elaborate more on the implications of their results rather than to simply describe them, especially in the context of their moderators (electoral systems and possibly, the research design - but see my above concerns regarding the results related to study designs).
-Although the format should be concise, such a discussion will improve the readers' understanding of the main findings much more (especially non-expert readers).
-For example, the seemingly "methodological" explanation of research design as a moderator has substantial implications.
-If that is the case, to what extent can we lean on earlier studies that did not use causal inference?''
+\noindent \textbf{6)} Reviewer 2 writes: ``There is other recent survey work on
+support for vigilantism that could be acknowledged, like Zizumbo-Colunga 2017.
+On Brazil, there is Schuberth and others. Beyond survey work, there is a
+growing line of work on vigilantes or autodefensas in other Latin American
+countries, such as Peru or Mexico, that could be briefly discussed. For example
+Kloppe-Santamaria on Puebla in JLAS or Trevizo on Mexico generally in LAPS.
+This work seems relevant in many ways.''
 
@@
 \begin{quote}
-    Following Reviewer 2's recommendations, we have more appropriately framed the paper so that we discuss the institutional moderators and their relationship to the theory across the entire piece.
-Since we changed our model specifications and added a new moderator, our Results section was also significantly altered.
-We reduced the Meta-Analysis subsection (3.2) and expanded the Meta-Regressions subsection (3.3) to account for the most relevant and auspicious findings.
-In this sense, in paragraph 2 of subsection 3.3, we explain to the reader how she should interpret the meta-regression results.
-We believe this makes our arguments about the meta-regression results more compelling.
-We also added more substantive insights to accompany the description of meta-regression results in each paragraph of section 3.3.
+    Following Reviewer 2's recommendations,
 
-    We present and partly interpret our results in the Introduction section, reporting back to elements from the literature and to the theory. The last paragraph in the Introduction (p.3) reads:
-
-    ``\textit{The meta-regressions provide additional evidence that our study sample is highly heterogeneous and that effect sizes differ substantially according to study specifications.
-When using an extended sample of 162 coefficients, we find that unicameralism is associated with higher public spending, as predicted by the ``law of $1/n$''.
-Since most unicameral legislatures in our sample are local governments (municipalities or districts), this result supports the predictions of Moreover, our meta-regressions indicate that larger upper chambers spend more in terms of per capita expenditure than lower chambers, a result that also appears in the binomial tests.
-Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original definition of the law.
-Finally, meta-regression results confirm that regression discontinuity designs reduce public spending estimates.}''
-
-    The Discussion section has also increased both in size and scope.
-Now, we more aptly establish the dialogue between our electoral system findings and the original theory and literature.
-For instance, in page 15, the following reads:
-
-    ``\textit{While we believe that moving beyond the majoritarian districts framework could produce valuable insights, institutional features that are central to the theory cannot be overrun.
-For example, proportional representation (PR) electoral systems allow candidates whose constituents are spread across large territories to provide diffused public goods and win elections.
-However, geographically-targeted service provision is at the very core of the legislative behaviour that produces the "law of $1/n$".
-Thus, scholars should consider the possible implications of these micro-level dynamics when applying the "law of $1/n$" logic to different settings.}''
 \end{quote}
@@
 
-\noindent \textbf{More minor comments:}
-
-\vspace{.3cm}
-
-\noindent \textbf{1)} Reviewer 2 writes: ``Table 1 - it will be clearer to separate the notes at the bottom of the table into separate columns.
-For instance, note \#1 will explain the abbreviations of the Journal column note \#2 will refer to the Country column.
-Otherwise, the reader has to manually look for a given abbreviation out of the rather long list.''
+\noindent \textbf{7)} Reviewer 2 writes: ``Very minor note: on page 12,
+significantly effect should be significantly affect.''
 
@@
 \begin{quote}
-    We agree this can be an unnecessary inconvenience to the reader. We have changed the notes in Table 1 according to the Reviewer's specifications. 
+    We have corrected this typo in the revised version of the paper.
 \end{quote}
@@
 \vspace{.3cm}
-
-\noindent \textbf{2)} Reviewer 2 writes: ``Also regarding Table 1, I believe it will be more convenient to simply write the authors and the year of publication in the first column (e.g., "Stein et al., 1998") while keeping the table order as it is (according to the year of publication) - rather than splitting them into two columns.
-I am also not sure whether the title of the paper really helps the readers or simply confuses them (it makes the table less elegant in my opinion).
-I would delete the title (if a reader wishes to see the full reference, she can look it in the bibliography).
-In contrast, it will be more beneficial to mention inside the table the DVs used in each study (as currently explained in the body text; p.
-6).''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    We have made these alterations to Table 1 accordingly. We also added a column for the new Institutional Design moderator.
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{3)} Reviewer 2 writes: ``The use of $n$ and $k$ as signifiers of the independent variables is a bit confusing throughout the paper since in the meta-analyses domain, they usually signify the number of effect sizes ($k$) and the number of respondents per study ($n$).
-More broadly, it is even more confusing when discussing Table 3 (the reader has to remember what $n$ and $k$ represent, instead of simply writing the meanings) or when interpreting its results in the discussion part.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    We agree that adding labels to variables is an unnecessary inconvenience to the reader. All references to the independent variables now translate their full meaning.
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{4)} Reviewer 2 writes: ``I appreciate the authors' elaborated appendix, but the readers might get a bit lost without specific references to the sub-sections in it throughout the main paper: for example, not just referring to the Supplementary Materials in general, but to the specific section in it.
-Moreover, the authors should consider leaving out the R code from the online appendix, and simply anonymously upload it to an external open science source.
-For people who are not experts in R (and perhaps also for those who are), the combination of code and text can be a bit confusing.''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    As noted above, we agree that only a handful of scholars would be interested in R scripts, which get in the way of most readers.
-We have split the Supplementary Materials into two documents.
-The one we refer to as the ``Supplementary Materials'' includes a discussion of the theory, the study selection procedures, a description of how we treated the data in detail, and analysis results.
-The other collects all the R code we wrote for each stage of data collection and analysis.
-We recommend the latter is used by those wishing to replicate our work and strongly encourage peers to use it and produce new meta-analyses in the social sciences.
-\end{quote}
-
-\vspace{.3cm}
-
-\noindent \textbf{5)} Reviewer 2 writes: ``To facilitate interpretation of Figure 1, it would be more convenient to number each plot, and refer to it in the body text (pp. 10-11).''
-
-\vspace{.3cm}
-
-\noindent \textbf{Response:} 
-\begin{quote}
-    All plots in Figures 1 and 2 are now individually numbered, and referred to in the body text.
-\end{quote}
 

### 2022-12-03 appendix/appendix.Rmd
add r1 reviews, review art and app

@@
 conjoint, we randomized the order of the conjoint and the information provision
-experiments.
+experiments [@perreault1975controlling].
 

### 2022-12-03 article/article.tex
add r1 reviews, review art and app

@@
 \citep{bateson2020politics}.\footnote{On vigilantism more generally, see
-\citet{schuberth2013challenging,
-zizumbo2017community,smith2019contradictions,cohen2022collective}.} This
+\citet{cohen2022collective}, \citet{schuberth2013challenging},
+\citet{smith2019contradictions}, and \citet{zizumbo2017community}.} This
 omission is significant not only because local violence is pervasive in weak
-states, but also because it often comes at a greater social cost than terrorism
-or civil wars \citep{blair2017predicting}.
+states, but also because it possibly comes at a greater social cost than
+terrorism or wars \citep{blair2017predicting}.
 
@@
 racial patterns scholars have observed in the United States
-\citep{dray2003hands,seguin2019national,obert2018keeping}. These findings are
+\citep{dray2003hands, obert2018keeping, seguin2019national}. These findings are
 consistent with recent research on vigilantism in Haiti

### 2022-12-11 response-reviewers/response-reviewers.tex
add revised version

@@
 Below we discuss these changes in further detail, as well as the other
-improvements we have done to the paper in response to the editors' and
+improvements we have done to the paper in response to the editor's and
 reviewers' comments. We are pleased with the outcome and hope to have satisfied
@@
 We have also changed the sentence in which we cite \citet{blair2017predicting}
-to make our claims more precise. The last sentence in the first paragraph reads
-(page 02): ``\textit{This omission is significant not only because local
-  violence is pervasive in weak states, but also because it possibly comes at a
-greater social cost than terrorism or wars \citep{blair2017predicting}}.''
+to make our claims more precise. The last sentence in the first paragraph now
+reads (page 02): ``\textit{This omission is significant not only because
+  vigilantism can entrench group animosities and create vicious cycles of
+violence, but also because it severely undermines state legitimacy and the rule
+of law, two key pillars of democratic stability and economic development
+\citep{jung2020lynching, tankebe2009self}}.''
 
@@
 We agree that our explanations regarding our experimental design were
-incomplete. We randomized the order of the experiments precisely to avoid
-carryover effects, thus we hope our estimates are unbiased because of this
-procedure. We have added a footnote to the Supplementary Material to explain
-this point. It reads (page 83 of the SM, footnote number 02): ``\textit{To
-  prevent eventual carryover effects caused by the conjoint, we randomized the
-  order of the conjoint and the information provision experiments
-\citep{perreault1975controlling}.}''.
+incomplete. We actually randomized the order of the experiments to avoid
+carryover effects, although we did not mention that explicitly in the text. We
+have added a footnote to the Supplementary Material to explain this point. It
+reads (page 83 of the SM, footnote number 02): ``\textit{To prevent eventual
+  carryover effects caused by the conjoint, we randomized the order of the
+  conjoint and the information provision experiments
+\citep{perreault1975controlling}.}''. We hope our estimates are unbiased
+because of this procedure.
 
@@
 We have added a citation to Nick Rush Smith's work on page 02 and a citation to
-the special issue in footnote 01 (page 02). The Supplementary
-Materials are now included in the submission as well.
+the special issue in footnote 01 (page 02). The Supplementary Materials are now
+included in the submission as well.
 
@@
 \noindent \textbf{1)} Reviewer 2 writes: ``Framing. The abstract is rather
-short, and I believe R&P abstracts can be up to 200 words. It would be good to
+short, and I believe R\&P abstracts can be up to 200 words. It would be good to
 make use of the space to highlight additional results that are especially
@@
 We agree that the abstract could be improved. We have added two sentences to
-the revised abstract and it now reads as follows: ``\textit{Why do people
-support extrajudicial violence? In two survey experiments with respondents in
-Brazil, we examine which characteristics of lynching scenarios garner greater
-support for lynching and whether providing different types of information about
-lynching reduces support for it. We find that people often do support community
-members to take vengeance. In particular, our analysis finds that people
-strongly support the use of extrajudicial violence by families of victims
-against men who sexually assault and murder women and children. We also find
-that criminal punishment and the threat of vendettas reduce support, but
-appeals to the human rights of victims have zero effect on support for
-lynchings. Unlike the U.S. experience with lynchings, race was not observed to
-play an important role in how respondents answered the survey.}''
+the abstract and it now reads as follows: ``\textit{Why do people support
+  extrajudicial violence? In two survey experiments with respondents in Brazil,
+  we examine which characteristics of lynching scenarios garner greater support
+  for lynching and whether providing different types of information about
+  lynching reduces support for it. We find that people often do support
+  community members to take vengeance. In particular, our analysis finds that
+  people strongly support the use of extrajudicial violence by families of
+  victims against men who sexually assault and murder women and children. We
+  also find that criminal punishment and the threat of vendettas reduce
+  support, but appeals to the human rights of victims have zero effect on
+  support for lynchings. Unlike the U.S. experience with lynchings, race was
+not observed to play an important role in how respondents answered the
+survey.}''
 
@@
 
+Reviewer 2 has a valid concern about the imprecision of our statement. We have
+deleted the former sentence and replaced it with the following one (page 02):
+``\textit{This omission is significant not only because vigilantism can
+  entrench group animosities and create vicious cycles of violence, but also
+  because it severely undermines state legitimacy and the rule of law, two key
+pillars of democratic stability and economic development
+\citep{jung2020lynching, tankebe2009self}}.''
+
 \end{quote}
@@
 \begin{quote}
+
+Reviewer 2 is correct that we did not explain why we used a 0-100 scale. We
+believe that a fine-grained scale gives us the ability to measure a wider range
+of responses and better capture the nuances of our treatments, with the
+advantage of being easy to interpret and convert into discrete categories. This
+is also the default scale range of several survey platforms, such as
+\href{https://www.surveymonkey.co.uk/curiosity/new-introducing-slider-star-rating-question-types/}{SurveyMonkey},
+\href{https://www.questionpro.com/blog/use-slider-scales-for-a-more-accurate-rating/}{QuestionPro},
+and
+\href{https://www.qualtrics.com/support/survey-platform/survey-module/editing-questions/question-types-guide/standard-content/slider/}{Qualtrics},
+the firm we used to conduct our survey experiments. Thus, our respondents are
+likely familiar with this scale as they were contacted directly by Qualtrics.
+We implemented this scale following the recommendation of
+\citet{carter2020}, who use the same range in their research design. In
+this regard, while we agree that a seven-point Likert scale would also be a
+good option, we believe that the 0-100 scale is appropriate for our purposes.
 
@@
 
+Reviewer 2 raises a valid concern about our second experiment. We believe that
+respondents were able to understand the instructions as they were written.
+First, as we noted above, Qualtrics uses the 0-100 scale by default in its
+survey platform. Since our respondents were recruited from Qualtrics' online
+panel, they have likely seen a similar scale a few times before. Second, we
+plotted the distribution of responses for the second experiment and found that
+the majority of respondents selected zero, which indicates that they do not
+agree that lynchings are justified. The histogram is available below. This is
+similar to what we we found in our quantitative text analysis. On page 81 of
+the Supplementary Materials, we estimate a latent Dirichlet allocation (LDA)
+model and find that one of the most common topics in the text responses is
+``lynchings are not justified.''
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{hist.pdf}
+  \caption{Support for Lynchings - Experiment 2}
+  \label{fig:hist}
+\end{figure}
+
+We then cross-checked the distribution of responses with the qualitative
+evidence we collected for the conjoint experiment, in which participants had to
+justify their choices. If we filter the responses to include only individuals
+who selected zero in the scale, we find the following sentences (Portuguese
+version in parentheses):
+
+\begin{itemize}
+
+  \item ``\textit{It is not justified, but I'm forced to give my opinion.
+We have a death here.
+But it's not justified}.'' (``não se justifica, mas sou obrigado a opinar.
+temos uma morte.
+mas não se jutifica'')
+  \item ``\textit{I've chosen one just because I had to, as described.
+But I don't agree with either of the two lynchings and believe that the Judiciary should fill the gap that people use as an excuse to keep such practices}.'' (``escolhi somente pois deveria obrigatoriamente selecionar um caso, como enunciado.
+mas não concordo com nenhum dos dois linchamentos e acredito que a justiça deveria cobrir a lacuna que as pessoas utilizam como desculpa para tal prática'')
+  \item ``\textit{I don't know...
+I selected one because I had to do so, but I'm strongly against lynchings, eye for an eye, tooth for a tooth}.'' (``não sei bem...
+escolhi porque tinha que escolher, mas sou fortemente contra linchamento.
+olho por olho, dente por dente'')
+  \item ``\textit{First of all, I want to make clear than I do not agree with any of the two cases.
+I think there should not be any lynching, regardless of the crime.
+This said, I believe that case 2 is far more concerning, as the victim is a child and the perpetrator is an adult, it is different in case 1}.'' (``à princípio quero deixar claro que não compactuo com nenhum dos dois casos.
+acho que não deve haver linchamento, independente do crime.
+nessa abordagem, acho que o caso 2 é bem mais grave, pois a vítima se trata de uma criança e autor de adulto, diferentemente do caso 1'')
+  \item ``\textit{Any of the responses is immoral.
+Never, in no circumstances, justice by one's own hands is justified}.'' (``qualquer das respostas é imoral.
+nunca, em hipótese alguma a justiça pelas próprias mãos é justificada'')
+
+\end{itemize}
+
+There are several more such examples in the text. In contrast, when we filter
+the responses to include only individuals who selected 100 in the scale, these
+are some of the justifications mentioned in the first experiment:
+
+\begin{itemize}
+  \item ``\textit{A killer deserves the death penalty}.'' (``um assassino merece pena de morte.'')
+  \item ``\textit{Because it is a murder: eye for an eye!}'' (``por tratar-se de um assassinato: olho por olho !'')
+  \item ``\textit{There must be some punishment}.'' (``tem que haver punição.'')
+  \item ``\textit{In both cases lynchings is appropriate}.'' (``nos dois casos cabe o linchamento.'')
+  \item ``\textit{Because Brazil's Judiciary is s**t}.'' (``porque a justiça do brasil é uma merda'')
+  \item ``\textit{Even if the criminal is indigenous, they must pay, do not mess with children}.'' (``mesmo que o criminoso seja indigena, tem que pagar, com criança não se mexe'')
+\end{itemize}
+
+All sentences above are included in the \texttt{q13\_text} variable in our
+data. Although we cannot provide a statistical test to assess whether all
+participants understood the instructions correctly, the evidence above suggests
+that respondents did not find the scale confusing and that the quantitative
+responses largely mirror our qualitative evidence.
+
 \end{quote}
@@
 \begin{quote}
+
+We agree that it is not necessary to list the significance tests in the text.
+We have removed them from the manuscript as suggested.
 
@@
 \begin{quote}
-    Following Reviewer 2's recommendations,
+
+The reviewer is correct that there is a growing literature on vigilantism in
+Latin American countries and we have cited all articles mentioned by the
+reviewer. Footnote number 01 (page 02), now reads: ``\textit{On vigilantism
+  more generally, see \citet{cohen2022collective},
+\citet{schuberth2013challenging}, \citet{smith2019contradictions}, and
+\citet{zizumbo2017community}.}.'' Paragraphs three and four of the Conclusion
+(pages 11--12), in turn, now read: ``\textit{Even in the American South, Whites
+  and Blacks also lynched people of their own race \citep{beck1997race}. In
+  this respect, our paper also highlights that lynchings in the Global South
+  may be more strongly connected with the idea of ``popular justice'' than with
+  racial animus \citep{kloppe2019lynching, martins2015linchamentos}.} [...]
+  \textit{Finally, lynchings have often been described as a response to low
+    state capacity \citep{trevizo2022mexico}, yet in some cases state agents
+    actively incite or engage in vigilante violence themselves
+  \citep{arias2010violent}.}''
 
@@
 
-\end{document}d
+\end{document}

### 2022-12-11 article/article.tex
add revised version

@@
 \citet{smith2019contradictions}, and \citet{zizumbo2017community}.} This
-omission is significant not only because local violence is pervasive in weak
-states, but also because it possibly comes at a greater social cost than
-terrorism or wars \citep{blair2017predicting}.
+omission is significant not only because vigilantism can entrench group
+animosities and create vicious cycles of violence, but also because it severely
+undermines state legitimacy and the rule of law, two key pillars of democratic
+stability and economic development \citep{jung2020lynching, tankebe2009self}.
 
@@
 may be more strongly connected with the idea of ``popular justice'' than with
-racial animus \citep{martins2015linchamentos}.
+racial animus \citep{kloppe2019lynching, martins2015linchamentos}.
 

### 2022-12-12 response-reviewers/response-reviewers.tex
small changes to memo, article and appendix

--- 2022-12-03 response-reviewers/response-reviewers.tex
@@
 
-We would like to thank you for the opportunity to revise our manuscript,
-``Vigilantism and Institutions: Understanding Attitudes toward Lynching in
-Brazil'' (Ms. No. RAP-22-0164). Following the comments and suggestions of the
-editors and reviewers, we have thoroughly revised our article and we believe it
-has improved significantly as a result.
+Thank you for giving us the opportunity to revise our manuscript, ``Vigilantism
+and Institutions: Understanding Attitudes toward Lynching in Brazil'' (Ms. No.
+RAP-22-0164). We have made several changes to the article based on the feedback
+from the editor and reviewers, and we believe the manuscript has improved
+significantly as a result.
 
-We were especially committed to discussing the scope conditions of our article
-and to clarifying some technical questions about our experiments as highlighted
-by Reviewers 1 and 2. We did this by editing the Introduction, adding a new
-paragraph to the Conclusion, and including more details about our methodology
-in section two and in the Supplementary Materials. We also removed the
-significance tests from the manuscript, as per the suggestion of Reviewer 2,
-and added a footnote to the Supplementary Materials indicating that we
-randomized the order of the experiments to reduce the risk of carryover
-effects. Moreover, we now show how our findings compare with those found in
-other studies, as suggested by Reviewer 1. We also discuss the results of our
-subgroup analyses in the Supplementary Materials, again following the
-recommendation of Reviewer 1. Lastly, we include all references suggested by
-Reviewer 1 and 2 in the main body of the manuscript. We are extremely
-appreciative of these recommendations and agree that the manuscript is now
-stronger and appeals to a broader readership.
+In particular, we have focused on addressing the scope and methodology of our
+study, as highlighted by Reviewers 1 and 2. We have edited the Introduction and
+added a new paragraph to the Conclusion to better explain the scope of our
+work. We have also included more details about our methodology in section two
+and in the Supplementary Materials. In response to Reviewer 2's suggestion, we
+have removed the significance tests from the manuscript. We have also added a
+footnote to the Supplementary Materials indicating that we randomized the order
+of the experiments to reduce the risk of carryover effects.
 
-Below we discuss these changes in further detail, as well as the other
-improvements we have done to the paper in response to the editors' and
-reviewers' comments. We are pleased with the outcome and hope to have satisfied
-all of your concerns. Again, we thank the editor for the opportunity to revise
-our manuscript, and the reviewers for their immensely valuable comments.
+Furthermore, we have added a discussion of how our findings compare with those
+of other studies, as suggested by Reviewer 1. We have also included the results
+of our subgroup analyses in the Supplementary Materials, again following
+Reviewer 1's recommendation. Additionally, we have included all references
+suggested by Reviewers 1 and 2 in the main body of the manuscript.
+
+Overall, we believe that the manuscript is now stronger and more appealing to a
+broader audience. We discuss the changes in more detail below. We are grateful
+for the feedback and suggestions provided by the editor and reviewers, and we
+hope that we have addressed all of their concerns. Thank you again for the
+opportunity to revise our manuscript.
 
@@
 
-We have moved the facts about lynchings in Brazil to the Introduction and we
-agree that the section now provides more context for our experiments. The
+We have moved the facts about lynchings in Brazil to the Introduction and 
+the section now provides more context for our experiments. The
 second paragraph of the Introduction now reads as follows (page 02):
@@
 
-We have also changed the sentence in which we cite \citet{blair2017predicting}
-to make our claims more precise. The last sentence in the first paragraph reads
-(page 02): ``\textit{This omission is significant not only because local
-  violence is pervasive in weak states, but also because it possibly comes at a
-greater social cost than terrorism or wars \citep{blair2017predicting}}.''
+We have also changed the last sentence in the first paragraph to make our
+claims more precise. It now reads (page 02): ``\textit{This
+omission is significant not only because vigilantism can deepen group enmities
+and lead to cycles of violence, but also because it undermines the legitimacy
+of the state and the rule of law, which are essential for economic development
+and democratic stability \citep{jung2020lynching, tankebe2009self}}.''
 
@@
 
-As we show below, we have also included an additional paragraph in the
-Conclusion to discuss how our findings relate to the literature on extralegal
-violence.
+As we show in the next section, we have also included a new paragraph in the
+Conclusion to discuss the relationship between our findings and the existing
+literature on extralegal violence. By doing this, we aim to provide a more
+comprehensive overview of our work and its significance within the broader
+field.
 
@@
 
-We have made the changes requested by the editor and Reviewer 1 and our
-Conclusion section has been significantly expanded. We are especially grateful
-for this suggestion, as it has allowed us to better situate our article in the
-broader literate on vigilantism. Paragraph three of the Conclusion, the longest
-in the section, is now exclusively dedicated to the scope conditions of our
-research. We have linked our findings to important works in the literature and
-have also discussed how a culture of honor may explain some of our main
-findings.
+We have made the requested changes and significantly expanded the Conclusion
+section based on the feedback from the editor and Reviewer 1. We are grateful
+for this suggestion, as it has allowed us to better connect our article to the
+broader literature on vigilantism.
+
+The third paragraph of the Conclusion, now the longest in the section, is
+exclusively dedicated to discussing the scope conditions of our research. We
+have linked our findings to important works in the literature and have also
+discussed how a culture of honor may help to explain some of our main findings.
+This new paragraph provides valuable insight and enhances the broader
+significance of our study. Overall, we believe that the revised Conclusion
+section is stronger and more useful to readers interested in this topic.
 
@@
 
-Reviewer 1 makes an excellent point. We agree that we had not properly
-explained the scope conditions of our research and, as mentioned above, we have
-written a new paragraph in the Conclusion to provide further context for our
-findings. We compare our results with studies on vigilantism in other Latin
-American countries and in the United States, and we also discuss how social
-norms, especially those related to a culture of honor, may explain why
-Brazilians are more likely to support lynchings when the victim is a woman or a
-child. Finally, we also briefly speculate why race does not seem to influence
-individual preferences for lynchings in Brazil.
+Reviewer 1 raises an important issue. We agree that we had not adequately
+explained the scope conditions of our research and have therefore added a new
+paragraph to the Conclusion to provide additional context. In this paragraph,
+we compare our results with studies on vigilantism in other Latin American
+countries and the United States, and we also discuss the role of social norms,
+particularly those related to a culture of honor, in shaping attitudes towards
+lynching in Brazil. Additionally, we speculate on why race does not seem to
+influence individual preferences for lynchings in Brazil.
 
@@
 
-We agree that our explanations regarding our experimental design were
-incomplete. We randomized the order of the experiments precisely to avoid
-carryover effects, thus we hope our estimates are unbiased because of this
-procedure. We have added a footnote to the Supplementary Material to explain
-this point. It reads (page 83 of the SM, footnote number 02): ``\textit{To
-  prevent eventual carryover effects caused by the conjoint, we randomized the
+We agree that our explanations regarding the experimental design were
+inadequate. We actually randomized the order of the experiments to avoid
+carryover effects, but we did not mention this explicitly in the text. We have
+therefore added a footnote to the Supplementary Material to clarify this point.
+The footnote, which can be found on page 83 of the SM, reads: ``\textit{To
+prevent potential carryover effects caused by the conjoint, we randomized the
 order of the conjoint and the information provision experiments
-\citep{perreault1975controlling}.}''.
+\citep{perreault1975controlling}.''} We believe that this procedure ensures
+that our estimates are unbiased.
 
-We also agree that the subgroup analyses may be interesting to scholars. Our
-Supplementary Materials now include a short comment about each of our subgroup
-tests. We note when the results are statistically significant and when they are
-vary according to the covariates we control for. For instance, Section C.4.1 of
-the Supplementary Materials, in which we assess whether our results for the
-conjoint experiment differs between genders, we write the following (page 24):
-``\textit{Results do not seem to vary according to the gender of the
-  respondent. We focus here on the differences between males and females and
-  exclude the 11 observations in which respondents preferred not to say their
-  gender or marked ``other'' in our questionnaire. Across all conjoint
+We agree that the subgroup analyses may be of interest to scholars. In response
+to this feedback, we have added a short comment about each of our subgroup
+tests to the Supplementary Materials. These comments provide information about
+the statistical significance of the results and highlight any variations that
+we observed according to the covariates that we controlled for. For example, in
+Section C.4.1 of the Supplementary Materials, where we assess whether our
+results for the conjoint experiment differ between genders, we write the
+following (page 24): ``\textit{Results do not seem to vary according to the
+  gender of the respondent. We focus here on the differences between males and
+  females and exclude the 11 observations in which respondents preferred not to
+say their gender or marked ``other'' in our questionnaire. Across all conjoint
 experiment attributes, we see an overlap between the 95\% confidence intervals
 for males and females.}'' Similarly, in Section C.4.3, in which we test whether
-our results vary by race, we write: ``\textit{Below are our results when we
-disaggregate the data by race. We find that they are almost identical is all
-dimensions except for offense. Asian respondents are much less likely to select
-profiles that contain pickpocketing as a crime.}''  All analyses are also
-accompanied by their corresponding \texttt{R} code to facilitate the
-replication of our results.
+our results vary by race, we write (page 32): ``\textit{Below are our results
+  when we disaggregate the data by race. We find that they are almost identical
+  is all dimensions except for offense. Asian respondents are much less likely
+to select profiles that contain pickpocketing as a crime.}''
+
+All analyses are also accompanied by their corresponding \texttt{R} code to
+facilitate the replication of our results.
 
@@
 
+Reviewer 2's concern about the imprecision of our statement is valid. We have
+deleted the original sentence and replaced it with the following (page 02):
+``\textit{This omission is significant not only because vigilantism can
+  entrench group animosities and create vicious cycles of violence, but also
+because it severely undermines state legitimacy and the rule of law, two key
+pillars of democratic stability and economic development
+\citep{jung2020lynching, tankebe2009self}}.''
+
 \end{quote}
@@
 \begin{quote}
+
+Reviewer 2 is correct that we did not explain why we used a 0-100 scale in our
+study. We chose this scale because it allows us to measure a wider range of
+responses and capture the nuances of our treatments more accurately. This scale
+is also easy to interpret and convert into discrete categories, which makes it
+useful for our analysis. Additionally, the 0-100 scale is the default range
+used by many survey platforms, such as
+\href{https://www.surveymonkey.co.uk/curiosity/new-introducing-slider-star-rating-question-types/}{SurveyMonkey},
+\href{https://www.questionpro.com/blog/use-slider-scales-for-a-more-accurate-rating/}{QuestionPro},
+and
+\href{https://www.qualtrics.com/support/survey-platform/survey-module/editing-questions/question-types-guide/standard-content/slider/}{Qualtrics},
+which was the firm we used to conduct our survey experiments. As such, our
+respondents are likely familiar with this scale.
+
+We implemented the 0-100 scale following the recommendation of
+\citet{carter2020}, who used the same range in their research design. While we
+agree that a seven-point Likert scale would also be a good option, we believe
+that the 0-100 scale is appropriate for our purposes.
 
@@
 
+Reviewer 2 raises a valid concern about the instruction for our second
+experiment. While we acknowledge that we could have worded the instructions
+better, we believe that respondents were able to understand them as intended.
+As we mentioned earlier, Qualtrics uses the 0-100 scale by default in its
+survey platform, so our respondents, who were recruited from Qualtrics' online
+panel, are likely familiar with this scale. Additionally, we have plotted the
+distribution of responses for the second experiment and have found that the
+majority of respondents selected zero, which indicates that they do not agree
+that lynchings are justified. This is consistent with the findings of our
+quantitative text analysis, which estimates a latent Dirichlet allocation (LDA)
+model and finds that one of the most common topics in the text responses is
+``lynchings are not justified'' (page 81 of the Supplementary Materials).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{hist.pdf}
+  \caption{Support for Lynchings - Experiment 2}
+  \label{fig:hist}
+\end{figure}
+
+We then cross-checked the distribution of responses with the qualitative
+evidence we collected for the conjoint experiment, in which participants had to
+justify their choices. When we filter our data to only include respondents who
+selected zero on the 0-100 scale, we find the following justifications for
+their choices (Portuguese version in parentheses):
+
+\begin{itemize}
+
+  \item ``\textit{It is not justified, but I am forced to express my opinion.
+We have a death here, but it is not justified}.'' (``não se justifica, mas sou obrigado a opinar.
+temos uma morte.
+mas não se jutifica'')
+  \item ``\textit{I only chose because I had to select a case, as stated.
+But I do not agree with either of the lynchings and I believe that justice should cover the gap that people use as an excuse for such practice}.'' (``escolhi somente pois deveria obrigatoriamente selecionar um caso, como enunciado.
+mas não concordo com nenhum dos dois linchamentos e acredito que a justiça deveria cobrir a lacuna que as pessoas utilizam como desculpa para tal prática'')
+  \item ``\textit{I don't know...
+I selected one because I had to do so, but I am strongly against lynching.
+Eye for an eye, tooth for a tooth}.'' (``não sei bem...
+escolhi porque tinha que escolher, mas sou fortemente contra linchamento.
+olho por olho, dente por dente'')
+  \item ``\textit{First of all, I want to make it clear that I do not condone either of the two cases.
+I think there should be no lynching, regardless of the crime.
+In this approach, I think case 2 is much more serious, because the victim is a child and the perpetrator is an adult, unlike in case 1}.'' (``à princípio quero deixar claro que não compactuo com nenhum dos dois casos.
+acho que não deve haver linchamento, independente do crime.
+nessa abordagem, acho que o caso 2 é bem mais grave, pois a vítima se trata de uma criança e autor de adulto, diferentemente do caso 1'')
+  \item ``\textit{Either of the answers is immoral.
+Never, under any circumstances, is vigilante justice justified}.'' (``qualquer das respostas é imoral.
+nunca, em hipótese alguma a justiça pelas próprias mãos é justificada'')
+
+\end{itemize}
+
+There are several more such examples in the text. In contrast, when we include
+only individuals who selected 100 on the scale, these are some of the
+justifications mentioned in the first experiment:
+
+\begin{itemize}
+  \item ``\textit{A killer deserves the death penalty}.'' (``um assassino merece pena de morte.'')
+  \item ``\textit{Because it is a murder: eye for an eye!}'' (``por tratar-se de um assassinato: olho por olho !'')
+  \item ``\textit{There must be some punishment}.'' (``tem que haver punição.'')
+  \item ``\textit{In both cases lynchings is appropriate}.'' (``nos dois casos cabe o linchamento.'')
+  \item ``\textit{Because Brazil's Judiciary is s**t}.'' (``porque a justiça do brasil é uma merda'')
+  \item ``\textit{Even if the criminal is indigenous, they must pay, you do not mess with a child}.'' (``mesmo que o criminoso seja indigena, tem que pagar, com criança não se mexe'')
+\end{itemize}
+
+All sentences above are included in the \texttt{q13\_text} variable in our
+data. Although we cannot provide a statistical test to assess whether all
+participants understood the instructions correctly, the evidence above suggests
+that respondents did not find the scale confusing and that the quantitative
+responses largely mirror our qualitative evidence. We appreciate Reviewer 2's
+feedback and are grateful for the opportunity to address this concern.
+
 \end{quote}
@@
 \begin{quote}
-    Following Reviewer 2's recommendations,
+
+The reviewer is correct that there is a growing literature on vigilantism in
+Latin American countries and the articles cited by the reviewer are indeed
+relevant. We have added some of them to footnote number 01 (page 02), which now
+reads: ``\textit{On vigilantism more generally, see
+\citet{cohen2022collective}, \citet{schuberth2013challenging},
+\citet{smith2019contradictions}, and \citet{zizumbo2017community}}.''
+
+Paragraphs three and four of the Conclusion (pages 11--12), in turn, now read:
+``\textit{Even in the American South, Whites and Blacks also lynched people of
+  their own race \citep{beck1997race}. In this respect, our paper also
+  highlights that lynchings in the Global South may be more strongly connected
+with the idea of ``popular justice'' than with racial animus
+\citep{kloppe2019lynching, martins2015linchamentos}.} [...] \textit{Finally,
+lynchings have often been described as a response to low state capacity
+\citep{trevizo2022mexico}, yet in some cases state agents actively incite or
+engage in vigilante violence themselves \citep{arias2010violent}.}''
 
@@
 
-\newpage
 \bibliography{../article/references.bib}

### 2022-12-12 appendix/appendix.Rmd
small changes to memo, article and appendix

@@
 carrying out this research. We received a grant of USD 10,000 to conduct this
-research from the Centre for the Study of Governance & Society at King’s College
+research from the Centre for the Study of Governance & Society at King's College
 London, which in turn receives support from the Templeton Foundation. We are not

### 2022-12-12 article/article.tex
small changes to memo, article and appendix

@@
 
-The regulation of violence is a crucial function of the state. When states
-control violence effectively, markets, politics, and civil society can flourish
-\citep{besley2011pillars, north2009violence}. However, states still struggle to
-maintain the monopoly of force in much of the Global South. Scholars have
-written extensively about how rebel organizations build support to challenge
-government institutions, yet we know little about what motivates local
-extrajudicial violence and vigilantism in the developing world
+The regulation of violence is a crucial role of the state. When states control
+violence effectively, markets, politics, and civil society can flourish
+\citep{besley2011pillars, north2009violence}. However, many states in the
+Global South still struggle to maintain a monopoly on the use of force.
+Scholars have written extensively about how rebel organizations build support
+to challenge government institutions, yet we know little about what motivates
+local extrajudicial violence and vigilantism in the developing world
 \citep{bateson2020politics}.\footnote{On vigilantism more generally, see
@@
 \citet{smith2019contradictions}, and \citet{zizumbo2017community}.} This
-omission is significant not only because vigilantism can entrench group
-animosities and create vicious cycles of violence, but also because it severely
-undermines state legitimacy and the rule of law, two key pillars of democratic
-stability and economic development \citep{jung2020lynching, tankebe2009self}.
+omission is significant not only because vigilantism can deepen group enmities
+and lead to cycles of violence, but also because it undermines the legitimacy
+of the state and the rule of law, which are essential for economic development
+and democratic stability \citep{jung2020lynching, tankebe2009self}.
 

### 2022-12-16 response-reviewers/response-reviewers.tex
final edits to revised version
update response reviewers, readme

@@
 
-\noindent \today
+\noindent December 12, 2022
 
@@
 include teenage women and girls, elderly women, and even members of the local
-police \citep{moura2017linchamentos}.}
+police \citep{moura2017linchamentos}.}''
 
@@
 explained the scope conditions of our research and have therefore added a new
-paragraph to the Conclusion to provide additional context. In this paragraph,
+paragraph to the Conclusion to provide additional context. In that paragraph,
 we compare our results with studies on vigilantism in other Latin American
@@
 mas não se jutifica'')
-  \item ``\textit{I only chose because I had to select a case, as stated.
+  \item ``\textit{I only chose it because I had to select a case, as stated.
 But I do not agree with either of the lynchings and I believe that justice should cover the gap that people use as an excuse for such practice}.'' (``escolhi somente pois deveria obrigatoriamente selecionar um caso, como enunciado.

### 2022-12-17 appendix/appendix.Rmd
final edits to revised version
final edits

@@
 This appendix contains the `R` code required to replicate the results we present
-in "_Vigilantism and Institutions: Understanding Attitudes towards Lynching in
+in "_Vigilantism and Institutions: Understanding Attitudes toward Lynching in
 Brazil_". This file also includes the descriptive statistics of our sample, the
@@
 Below are our results when we disaggregate the data by race. We find that they are
-almost identical is all dimensions except for offense. Asian respondents are
+almost identical in all dimensions except for offense. Asian respondents are
 much less likely to select profiles that contain pickpocketing as a crime.

### 2022-12-17 article/article.tex
final edits to revised version
final edits

@@
 % Title
-\title{Vigilantism and Institutions:\\ Understanding Attitudes Toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Louise Araújo, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nicholas Cowen, Daniel J.
+\title{Vigilantism and Institutions:\\ Understanding Attitudes toward Lynching in Brazil\footnote{We thank Rosario Aguilar, Nicholas Barnes, Hannah Baron, Dara Kay Cohen, Nick Cowen, Daniel J.
 D'Amico, Miriam Golden, Richard Locke, Umberto Mignozzetti, Eduardo Moncada, Irfan Nooruddin, Jonathan Obert, Brian J.
-Phillips, Catarina Roman, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments.
+Phillips, Alexandra Scacco, Livia Schubiger, Natán Skigin, Nicholas Rush Smith, Richard Snyder, and Georg Vanberg for their valuable comments.
 We received helpful feedback in seminars at EGAP, the Extra-legal Governance Institute at the University of Oxford, the Comparative Workshop at Brown University, the Kroc-Kellogg Peace, Conflict, Crime and Violence Workshop at Notre Dame, and the Severyns Ravenholt Seminar in Comparative Politics at the University of Washington.
@@
 % Date
-\date{\today}
+\date{December 16, 2022}
 
@@
 included ten questions on demographics and other information that might
-influence the results. These include the respondent's age, gender, ethnicity,
-level of education, monthly family income, political orientation (left to
-right), support for the death penalty, whether they had been victimized in the
-last year, their trust in the police, and their trust in the judicial system.
-We used these measures to disentangle heterogeneous effects in the main
+influence the results. The covariates are the respondent's age, gender,
+ethnicity, level of education, monthly family income, political orientation
+(left to right), support for the death penalty, whether they had been victimized
+in the last year, their trust in the police, and their trust in the judicial
+system. We used these measures to disentangle heterogeneous effects in the main
 responses. Descriptive statistics are available in Section B of the

### 2022-12-17 data/lynchings.R

@@ -1,7 +1,9 @@
-#########################################################################################
-## "Vigilantism and Institutions: Understanding Attitudes towards Lynching in Brazil"  ##
-## January 2021                                                                        ##
-#########################################################################################
+########################################################################################
+## "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"  ##
+##                                                                                    ##
+## Danilo Freire and David Skarbek                                                    ##
+## January 2021                                                                       ##
+########################################################################################
 
 # Record output log
 sink("./lynchings-log.txt")

### 2022-12-22 appendix/appendix.Rmd
production version

@@
   - David Skarbek[^david]
-date: \today
+date: December 16, 2022
 fontfamily: libertine
@@
     toc_depth: 3
-    keep_tex: no
+    keep_tex: yes
     template: template.latex

### 2022-12-22 article/article.tex
production version

@@
 Replication materials are available at \url{https://github.com/danilofreire/lynching-experiment-brazil}.
-We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.}}
+We thank the Centre for the Study of Governance \& Society at King's College London and the Templeton Foundation for financial support.
+The authors declare that they have no conflict of interest.}}
 
@@
 
-\noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
+% \noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
 \vspace{.25cm}
@@
 of the crime; (7) age of the crime victim; (8) type of lynching perpetrator.
-The attributes and levels are displayed in table \ref{tab:categories}.
+The attributes and levels are displayed in Table \ref{tab:categories}.
 

### 2023-01-03 article/article.tex
production version
small changes to intro

@@
 
-% \noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
+\noindent \textbf{Keywords:} Brazil, crime, extralegal violence, lynching, vigilantism
 \vspace{.25cm}
@@
 Global South still struggle to maintain a monopoly on the use of force.
-Scholars have written extensively about how rebel organizations build support
-to challenge government institutions, yet we know little about what motivates
-local extrajudicial violence and vigilantism in the developing world
+Scholars have written extensively about how rebel organizations challenge
+government institutions, yet we know little about what motivates local
+extrajudicial violence and vigilantism in the developing world
 \citep{bateson2020politics}.\footnote{On vigilantism more generally, see
@@
 omission is significant not only because vigilantism can deepen group enmities
-and lead to cycles of violence, but also because it undermines the legitimacy
-of the state and the rule of law, which are essential for economic development
-and democratic stability \citep{jung2020lynching, tankebe2009self}.
+and lead to vicious cycles of violence, but also because it undermines the rule
+of law and the legitimacy of the state, which are essential for long-term
+economic development and democratic stability \citep{jung2020lynching,
+tankebe2009self}.
 
@@
 particularly affected by a sharp increase in vigilante violence. Lynching
-episodes have been reported in Guatemala, Mexico, Peru, Venezuela and other
-countries in the region \citep{barbara2015vigilantes, cruz2019determinants,
-godoy2004justice}. From 2011 to 2015, Brazil registered about 2,500 lynching
-episodes, and 173 people were killed by angry mobs in 2015 alone---nearly one
-execution every two days \citep{barbara2015vigilantes, oliveira2016mob}.
-According to José de Souza Martins \citeyearpar{martins2015linchamentos}, who
-has studied lynchings in Brazil for more than thirty years, these figures are
-not only the highest in the country's history, but among the highest in the
-world. The people who participate in lynchings are typically young men, but
-they also sometimes include teenage women and girls, elderly women, and even
-members of the local police \citep{moura2017linchamentos}.
+episodes have been reported in Guatemala, Mexico, Peru, Venezuela, and many
+other countries in the region \citep{barbara2015vigilantes,
+cruz2019determinants, godoy2004justice}. From 2011 to 2015, Brazil registered
+about 2,500 lynching episodes, and 173 people were killed by angry mobs in 2015
+alone---nearly one execution every two days \citep{barbara2015vigilantes,
+oliveira2016mob}. According to José de Souza Martins
+\citeyearpar{martins2015linchamentos}, who has studied lynchings in Brazil for
+more than thirty years, these numbers are not only the highest in the country's
+history, but among the highest in the world. The people who participate in
+lynchings are typically young men, but they also sometimes include teenage
+girls, elderly women, and even members of the local police
+\citep{moura2017linchamentos}.
 
